### 2019-03-01 doc/Paper/main.tex
First commit on the paper

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jcappub} % for details on the use of the package, please
                     % see the JCAP-author-manual

\usepackage[T1]{fontenc} % if needed
\usepackage{natbib}
\bibliographystyle{JHEP}
\title{Clustering analysis of the HSC-SSP DR1 data as precursor for the LSST Dark Energy Survey Collaboration Analysis (or some fancier title)}

%% %simple case: 2 authors, same institution
%% \author{A. Uthor}
%% \author{and A. Nother Author}
%% \affiliation{Institution,\\Address, Country}

% more complex case: 4 authors, 3 institutions, 2 footnotes
\author[a,b,1]{F. Irst,\note{Corresponding author.}}
\author[c]{S. Econd,}
\author[a,2]{T. Hird\note{Also at Some University.}}
\author[a,2]{and Fourth}

% The "\note" macro will give a warning: "Ignoring empty anchor..."
% you can safely ignore it.

\affiliation[a]{One University,\\some-street, Country}
\affiliation[b]{Another University,\\different-address, Country}
\affiliation[c]{A School for Advanced Studies,\\some-location, Country}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{first@one.univ}
\emailAdd{second@asas.edu}
\emailAdd{third@one.univ}
\emailAdd{fourth@one.univ}

\abstract{With the increasing statistical power in Stage IV Dark Energy experiments, new analysis strategies must be developed and tested in order to fully exploit their data. In this work we present the current state-of-the-art clustering pipeline developed for the upcoming data from the LSST and use the public data from the Hiper-Suprime Camera Subaru Strategic Program first data release (DR1) as a proof concept. In addition, we obtain the first HOD resuts for these data (and compare with something else maybe??).}

\begin{document}
\maketitle
\flushbottom

\section{Introduction}
\label{sec:intro}

$\cdots$ TBC, \citep{2006astro.ph..9591A}

Here follow some examples of common features that you may wanto to use
or build upon.

For internal references use label-refs: see section~\ref{sec:intro}.
Bibliographic citations can be done with cite: refs.~\cite{a,b,c}.
When possible, align equations on the equal sign. The package
\texttt{amsmath} is already loaded. See \eqref{eq:x}.
\begin{equation}
\label{eq:x}
\begin{split}
x &= 1 \,,
\qquad
y = 2 \,,
\\
z &= 3 \,.
\end{split}
\end{equation}
Also, watch out for the punctuation at the end of the equations.

If you want some equations without the tag (number), please use the available
starred-environments. For example:
\begin{equation*}
x = 1
\end{equation*}

The amsmath package has many features. For example, you can use use
\texttt{subequations} environment:
\begin{subequations}\label{eq:y}
\begin{align}
\label{eq:y:1}
a & = 1
\\
\label{eq:y:2}
b & = 2
\end{align}
and it will continue to operate across the text also.
\begin{equation}
\label{eq:y:3}
c = 3
\end{equation}
\end{subequations}
The references will work as you'd expect: \eqref{eq:y:1},
\eqref{eq:y:2} and \eqref{eq:y:3} are all part of \eqref{eq:y}.

A similar solution is available for figures via the \texttt{subfigure}
package (not loaded by default and not shown here).
All figures and tables should be referenced in the text and should be
placed at the top of the page where they are first cited or in
subsequent pages. Positioning them in the source file
after the paragraph where you first reference them usually yield good
results. See figure~\ref{fig:i} and table~\ref{tab:i}.

\begin{table}[tbp]
\centering
\begin{tabular}{|lr|c|}
\hline
x&y&x and y\\
\hline
a & b & a and b\\
1 & 2 & 1 and 2\\
$\alpha$ & $\beta$ & $\alpha$ and $\beta$\\
\hline
\end{tabular}
\caption{\label{tab:i} We prefer to have borders around the tables.}
\end{table}

We discourage the use of inline figures (wrapfigure), as they may be
difficult to position if the page layout changes.

We suggest not to abbreviate: ``section'', ``appendix'', ``figure''
and ``table'', but ``eq.'' and ``ref.'' are welcome. Also, please do
not use \texttt{\textbackslash emph} or \texttt{\textbackslash it} for
latin abbreviaitons: i.e., et al., e.g., vs., etc.

\section{Sections}
\subsection{And subsequent}
\subsubsection{Sub-sections}
\paragraph{Up to paragraphs.} We find that having more levels usually
reduces the clarity of the article. Also, we strongly discourage the
use of non-numbered sections (e.g.~\texttt{\textbackslash
  subsubsection*}).  Please also see the use of
``\texttt{\textbackslash texorpdfstring\{\}\{\}}'' to avoid warnings
from the hyperref package when you have math in the section titles

\appendix
\section{Some title}
Please always give a title also for appendices.

\acknowledgments

This is the most common positions for acknowledgments. A macro is
available to maintain the same layout and spelling of the heading.

\paragraph{Note added.} This is also a good position for notes added
after the paper has been written.

\bibliography{bibliography}

\end{document}

### 2019-03-01 doc/Paper/main.tex
Added some structure

@@
 \abstract{With the increasing statistical power in Stage IV Dark Energy experiments, new analysis strategies must be developed and tested in order to fully exploit their data.
-In this work we present the current state-of-the-art clustering pipeline developed for the upcoming data from the LSST and use the public data from the Hiper-Suprime Camera Subaru Strategic Program first data release (DR1) as a proof concept.
+In this work we present the current state-of-the-art clustering pipeline developed for the upcoming data from the LSST and use the public data from the Hyper-Suprime Camera Subaru Strategic Program (HSC-SSP) first data release (DR1) as a proof concept.
 In addition, we obtain the first HOD resuts for these data (and compare with something else maybe??).}
@@
 $\cdots$ TBC, \citep{2006astro.ph..9591A}
-
-Here follow some examples of common features that you may wanto to use
-or build upon.
-
-For internal references use label-refs: see section~\ref{sec:intro}.
-Bibliographic citations can be done with cite: refs.~\cite{a,b,c}.
-When possible, align equations on the equal sign. The package
-\texttt{amsmath} is already loaded. See \eqref{eq:x}.
-\begin{equation}
-\label{eq:x}
-\begin{split}
-x &= 1 \,,
-\qquad
-y = 2 \,,
-\\
-z &= 3 \,.
-\end{split}
-\end{equation}
-Also, watch out for the punctuation at the end of the equations.
-
-If you want some equations without the tag (number), please use the available
-starred-environments. For example:
-\begin{equation*}
-x = 1
-\end{equation*}
-
-The amsmath package has many features. For example, you can use use
-\texttt{subequations} environment:
-\begin{subequations}\label{eq:y}
-\begin{align}
-\label{eq:y:1}
-a & = 1
-\\
-\label{eq:y:2}
-b & = 2
-\end{align}
-and it will continue to operate across the text also.
-\begin{equation}
-\label{eq:y:3}
-c = 3
-\end{equation}
-\end{subequations}
-The references will work as you'd expect: \eqref{eq:y:1},
-\eqref{eq:y:2} and \eqref{eq:y:3} are all part of \eqref{eq:y}.
-
-A similar solution is available for figures via the \texttt{subfigure}
-package (not loaded by default and not shown here).
-All figures and tables should be referenced in the text and should be
-placed at the top of the page where they are first cited or in
-subsequent pages. Positioning them in the source file
-after the paragraph where you first reference them usually yield good
-results. See figure~\ref{fig:i} and table~\ref{tab:i}.
-
-\begin{table}[tbp]
-\centering
-\begin{tabular}{|lr|c|}
-\hline
-x&y&x and y\\
-\hline
-a & b & a and b\\
-1 & 2 & 1 and 2\\
-$\alpha$ & $\beta$ & $\alpha$ and $\beta$\\
-\hline
-\end{tabular}
-\caption{\label{tab:i} We prefer to have borders around the tables.}
-\end{table}
-
-We discourage the use of inline figures (wrapfigure), as they may be
-difficult to position if the page layout changes.
-
-We suggest not to abbreviate: ``section'', ``appendix'', ``figure''
-and ``table'', but ``eq.'' and ``ref.'' are welcome. Also, please do
-not use \texttt{\textbackslash emph} or \texttt{\textbackslash it} for
-latin abbreviaitons: i.e., et al., e.g., vs., etc.
-
-\section{Sections}
-\subsection{And subsequent}
-\subsubsection{Sub-sections}
-\paragraph{Up to paragraphs.} We find that having more levels usually
-reduces the clarity of the article. Also, we strongly discourage the
-use of non-numbered sections (e.g.~\texttt{\textbackslash
-  subsubsection*}).  Please also see the use of
-``\texttt{\textbackslash texorpdfstring\{\}\{\}}'' to avoid warnings
-from the hyperref package when you have math in the section titles
-
-\appendix
-\section{Some title}
-Please always give a title also for appendices.
+\section{Data}
+\label{sec:data}
+In this work we use the public data products from HSC-SSP DR1~\citep{2018PASJ...70S...8A}.
+In particular, we generated a Python script \texttt{hscQuery.py}\footnote{\url{https://github.com/LSSTDESC/HyperSupremeStructure-HSC-LSS/blob/master/data_query/hscReleaseQuery.py}} to retrieve the data products available at \url{https://hsc-release.mtk.nao.ac.jp/datasearch/api/catalog_jobs/}.
+The data products obtained encompass the forced photometry object catalogs for the wide fields, the metadata and observing logs including the observing conditions, and the tables that include the photometric redshift information.
+We join the object catalog and the photometric redshift table by matching IDs in both tables.
+We restricted our queries to only include objects that pass the selection cuts included in~\citep{2018PASJ...70S..25M}
+\subsection{Data selection}
+\label{ssec:data_selection}
+\subsection{Mapping observing conditions}
+\label{ssec:observing_conditions}
+\section{Analysis}
+\label{sec:analysis}
+\subsection{Estimation of power-spectra}
+\label{ssec:cls}
+\subsection{HOD model}
+\label{ssec:HOD}
+\section{Discussion}
+\label{sec:discussion}
 

### 2019-07-05 notebooks/LSS_nmaps.py
Switched to using scripts instead of python notebook.  Script is *untested* so far, and will need revision.

@@ -1,0 +1,250 @@
+# Make sure we can find ceci and NaMaster
+
+import sys
+sys.path.append('/global/homes/a/abrouss/ceci')
+sys.path.append('/global/homes/a/abrouss/HSCLink')
+sys.path.append('/global/u1/a/abrouss/NaMaster')
+# sys.path.append('/global/homes/a/abrouss/HyperSuprimeStructure-HSC-LSS/hsc_lss/flatmaps.py')
+# sys.path.append('/global/u1/a/abrouss/.local/cori/3.6-anaconda-4.4/lib/python3.6/site-packages')
+
+from glob import glob
+import numpy as np
+from astropy.io import fits
+from astropy.wcs import WCS
+from numpy.random import poisson
+from hsc_lss.flatmaps import read_flat_map, FlatMapInfo
+from hsc_lss.map_utils import createCountsMap
+from hsc_lss.tracer import Tracer
+import pymaster as nmt
+
+catalogs = glob('/global/cscratch1/sd/damonge/HSC_ceci/WIDE_*_sirius_out/')
+
+ell_bins = [100.0,200.0,300.0,400.0,600.0,800.0,1000.0,1400.0,1800.0,2200.0,3000.0,3800.0,4600.0,6200.0,7800.0,9400.0,12600.0,15800.0]
+z_bins = [0.15,0.50,0.75,1.00,1.50]
+
+
+# modified from cat_mapper
+def get_nmaps(catfolder, pz_code = 'ephor_ab', pz_mark = 'best') :
+    """
+    Get number counts map from catalog
+    """
+    maps=[]
+    
+    if pz_code == 'ephor_ab':
+        pz_code_col = 'eab'
+    
+    cat=fits.open(catfolder + '/clean_catalog.fits')[1].data
+    column_mark='pz_'+pz_mark+'_'+pz_code_col
+
+    for zi,zf in zip(pz_i, pz_f) :
+        msk_bin=(cat[column_mark]<=zf) & (cat[column_mark]>zi)
+        subcat=cat[msk_bin]
+        masked_fraction = catfolder + '/masked_fraction.fits'
+        fsk,_=read_flat_map(masked_fraction)
+        nmap=createCountsMap(subcat['ra'],subcat['dec'],fsk)
+        maps.append(nmap)
+    return np.array(maps)
+
+
+
+def get_nmaps_split(catfolder, pz_bins = [0.15,0.50,0.75,1.00,1.50]):
+
[…]

### 2019-08-07 hsc_lss/power_specter.py
updated covariance to latest in namaster

@@ -252,19 +252,20 @@ class PowerSpecter(PipelineStage) :
                 cls_coupled.append(cl_coupled[0])
         return np.array(cls_all),np.array(cls_coupled)
 
-    def get_covar(self,lth,clth,bpws,wsp,temps,cl_dpj_all) :
+    def get_covar(self,lth,clth,bpws,tracers,wsp,temps,cl_dpj_all) :
         """
         Estimate the power spectrum covariance
         :param lth: list of multipoles.
         :param clth: list of guess power spectra sampled at the multipoles stored in `lth`.
         :param bpws: NaMaster bandpowers.
+        :params tracers: tracers.
         :param wsp: NaMaster workspace.
-        :param temps: list of contaminatn templates.
+        :param temps: list of contaminant templates.
         :params cl_dpj_all: list of deprojection biases for each bin pair combination.
         """
         if self.config['gaus_covar_type']=='analytic' :
             print("Computing analytical Gaussian covariance")
-            cov=self.get_covar_analytic(lth,clth,bpws,wsp)
+            cov=self.get_covar_analytic(lth,clth,bpws,tracers,wsp)
         elif self.config['gaus_covar_type']=='gaus_sim' :
             print("Computing simulated Gaussian covariance")
             cov=self.get_covar_gaussim(lth,clth,bpws,wsp,temps,cl_dpj_all)
@@ -286,14 +287,15 @@ class PowerSpecter(PipelineStage) :
         
         return wsp
 
-    def get_covar_mcm(self,wsp) :
+    def get_covar_mcm(self,tracers,bpws):
         """
         Get NmtCovarianceWorkspaceFlat for our mask
         """
         cwsp=nmt.NmtCovarianceWorkspaceFlat()
         if not os.path.isfile(self.get_output_fname('cov_mcm',ext='dat')) :
             print("Computing covariance MCM")
-            cwsp.compute_coupling_coefficients(wsp,wsp)
+            cwsp.compute_coupling_coefficients(tracers[0].field,
+                                               tracers[0].field,bpws)
             cwsp.write_to(self.get_output_fname('cov_mcm',ext='dat'))
         else :
             print("Reading covariance MCM")
@@ -356,12 +358,13 @@ class PowerSpecter(PipelineStage) :
         covar=np.cov(cells_sims.T)
         return covar
 
[…]

### 2019-08-07 run_gama09h_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA09H_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA
[…]

### 2019-08-07 run_gama15h_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA15H_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_GAMA
[…]

### 2019-08-07 run_hectomap_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_HECTOMAP_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damon
[…]

### 2019-08-07 run_vvds_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/skylevel_maps.fits   --
[…]

### 2019-08-07 run_wide12h_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE12H_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_WIDE
[…]

### 2019-08-07 run_xmmlss_i24p5.sh

@@ -10,7 +10,7 @@
 
 #python3 -m hsc_lss CatMapper   --clean_catalog=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/clean_catalog.fits   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/masked_fraction.fits   --cosmos_weights=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/cosmos_weights.fits   --pdf_matched=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/pdf_matched.txt   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits   --config=./hsc_lss_params/params_i24p5/config.yml 
 
-python3 -m hsc_lss MapDiagnoser   --masked_fraction=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/masked_fraction.fits   --ngal_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits   --dust_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/dust_map.fits   --star_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/star_map.fits   --depth_map=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/depth_map.fits   --ccdtemp_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ccdtemp_maps.fits   --airmass_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/airmass_maps.fits   --exptime_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/exptime_maps.fits   --skylevel_maps=/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XM
[…]

### 2019-08-07 plot_scripts/flatmaps.py
mask plots

@@ -1,0 +1,435 @@
+from __future__ import print_function
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import cm
+import pymaster as nmt
+from astropy.io import fits
+from astropy.wcs import WCS
+
+class FlatMapInfo(object) :
+    def __init__(self,wcs,nx=None,ny=None,lx=None,ly=None) :
+        """
+        Creates a flat map
+        :param wcs: WCS object containing information about reference point and resolution
+        :param nx,ny: Number of pixels in the x/y axes. If None, dx/dy must be provided
+        :param lx,ly: Extent of the map in the x/y axes. If None, nx/ny must be provided
+        """
+        self.wcs=wcs.copy()
+
+        if nx is None and lx is None :
+            raise ValueError("Must provide either nx or lx")
+
+        if ny is None and ly is None :
+            raise ValueError("Must provide either ny or ly")
+
+        if nx is None :
+            self.lx=lx
+            self.nx=int(self.lx/np.abs(self.wcs.wcs.cdelt[0]))+1
+        else :
+            self.nx=nx
+            self.lx=np.fabs(nx*self.wcs.wcs.cdelt[0])
+        self.dx=self.lx/self.nx
+
+        if ny is None :
+            self.ly=ly
+            self.ny=int(self.ly/np.abs(self.wcs.wcs.cdelt[1]))+1
+        else :
+            self.ny=ny
+            self.ly=np.fabs(ny*self.wcs.wcs.cdelt[1])
+        self.dy=self.ly/self.ny
+
+        self.npix=self.nx*self.ny
+
+    def is_map_compatible(self,mp) :
+        return self.npix==len(mp)
+
+    def get_dims(self) :
+        """
+        Returns map size
+        """
+        return [self.ny,self.nx]
+        
+    def get_size(self) :
+        """
+        Returns map size
+        """
+        return self.npix
+
+    def pos2pix(self,ra,dec) :
+        """
+        Returns pixel indices for arrays of x and y coordinates.
+        Will return -1 if (x,y) lies outside the map
+        """
+        ra=np.asarray(ra)
+        scalar_input=False
+        if ra.ndim==0 :
+            ra=x[None]
+            scalar_input=True
+
+        dec=np.asarray(dec)
+        if dec.ndim==0 :
+            dec=dec[None]
+
+        if len(ra)!=len(dec) :
[…]

### 2019-08-07 plot_scripts/plots_masks.py

@@ -1,0 +1,15 @@
+import flatmaps as fm
+import numpy as np
+import matplotlib.pyplot as plt
+
+for field in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
+    fsk,msk=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+field+"_sirius_i24p5_out/masked_fraction.fits")
+    fig=plt.figure()
+    ax=fig.add_subplot(111,projection=fsk.wcs)
+    ax.set_title(field,fontsize=14)
+    im=ax.imshow(msk.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
+                 origin='lower', interpolation='nearest')
+    ax.set_xlabel('R.A.', fontsize=14)
+    ax.set_ylabel('Dec.', fontsize=14)
+    plt.savefig("../doc/Paper/figures/mask_"+field+".pdf",bbox_inches='tight')
+plt.show()

### 2019-08-07 plot_scripts/plots_tables_summary.py

@@ -1,0 +1,49 @@
+import numpy as np
+from astropy.io import fits
+
+# Field summary
+def get_field_stats(fieldname):
+    cat=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+fieldname+"_sirius_i24p5_out/clean_catalog.fits")[1].data
+    mskd=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+fieldname+"_sirius_i24p5_out/masked_fraction.fits")[0]
+
+    area_pix_deg2=np.fabs(mskd.header['CDELT1']*mskd.header['CDELT2'])
+    area_pix_sr=area_pix_deg2*(np.pi/180)**2
+    area_deg2=np.sum(mskd.data)*area_pix_deg2
+
+    ng=len(cat)
+    print(fieldname+" %d gals, %.1lf deg^2, fsky=%.1lE"%(ng,area_deg2,area_deg2/(4*np.pi*(180/np.pi)**2)))
+    return ng,area_deg2
+ngt=0
+area_deg2t=0
+for field in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
+    n,a=get_field_stats(field)
+    ngt+=n
+    area_deg2t+=a
+print("Total: %d gals, %.1lf deg^2, fsky=%.1lE"%(ngt,area_deg2t,area_deg2t/(4*np.pi*(180/np.pi)**2)))
+
+# Bin summary
+pz_bins=[0.15,0.50,0.75,1.00,1.50]
+ng_arr=[]
+nz_arr=[]
+for fieldname in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
+    mskd=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+fieldname+"_sirius_i24p5_out/masked_fraction.fits")[0].data
+    mskbin=np.zeros_like(mskd); mskbin[mskd>0.5]=1
+    fng=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+fieldname+"_sirius_i24p5_out/ngal_maps.fits")
+    zs=0.5*(fng[1].data['z_f']+fng[1].data['z_i'])
+    ngs=[]
+    nzs=[]
+    for i in range(4):
+        #print(fng[0].data.shape)
[…]

### 2019-08-08 plot_scripts/plots_sysmaps.py
systematic plots

@@ -1,0 +1,50 @@
+import flatmaps as fm
+import numpy as np
+import matplotlib.pyplot as plt
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/"
+fsk,msk=fm.read_flat_map(prefix+"masked_fraction.fits")
+msk_bin=np.zeros_like(msk); msk_bin[msk>0.]=1
+
+def plot_syst(name,fname,band,units=None,savename=None):
+    label=name
+    if band is None:
+        imap=0
+    else:
+        imap=['g','r','i','z','y'].index(band)
+        label+=" "+band
+    if units is not None:
+        label+=" ["+units+"]"
+
+    _,mp=fm.read_flat_map(prefix+fname,i_map=imap)
+    mp_mean=np.sum(msk_bin*msk*mp)/np.sum(msk_bin*msk)
+    mp_plot=msk_bin*(mp-mp_mean)+mp_mean
+    mp_min=np.amin(mp_plot)
+    mp_max=np.amax(mp_plot)
+    mp_plot[msk_bin<1]=mp_min-1
+    fig=plt.figure()
+    ax=fig.add_subplot(111,projection=fsk.wcs)
+    im=ax.imshow(mp_plot.reshape([fsk.ny,fsk.nx]),
+                 vmin=mp_min,vmax=mp_max,
+                 origin='lower', interpolation='nearest')
+    im.cmap.set_under('#FFFFFF')
+    cbar=plt.colorbar(im,orientation='horizontal')
+    cbar.ax.set_xlabel(label,fontsize=14)
+    ax.set_xlabel('R.A.', fontsize=14)
+    ax.set_ylabel('Dec.', fontsize=14)
+    if savename is not None:
+        plt.savefig(savename,bbox_inches='tight')
+plot_syst('Airmass','airmass_maps.fits','g',savename='../doc/Paper/figures/syst_airmass_g.pdf')
+plot_syst('Airmass','airmass_maps.fits','i',savename='../doc/Paper/figures/syst_airmass_i.pdf')
+plot_syst('Airmass','airmass_maps.fits','y',savename='../doc/Paper/figures/syst_airmass_y.pdf')
+plot_syst('Seeing','seeing_maps.fits','g',units='pix.',savename='../doc/Paper/figures/syst_seeing_g.pdf')
[…]

### 2019-08-08 plot_scripts/plots_sysmaps.py
star map

@@ -45,6 +45,6 @@ plot_syst('Sky level','skylevel_maps.fits','i',savename='../doc/Paper/figures/sy
 plot_syst('Sky level','skylevel_maps.fits','y',savename='../doc/Paper/figures/syst_skylevel_y.pdf')
 plot_syst('Depth','depth_map.fits',None,units='mag.',savename='../doc/Paper/figures/syst_depth.pdf')
 plot_syst('Dust','dust_map.fits',None,units='mag.',savename='../doc/Paper/figures/syst_dust.pdf')
-plot_syst('Star count','star_map.fits',None,savename='../doc/Paper/figures/syst_dust.pdf')
+plot_syst('Star count','star_map.fits',None,savename='../doc/Paper/figures/syst_star.pdf')
 
 plt.show()

### 2019-08-08 plot_scripts/plots_nzs.py
nz plots

@@ -1,0 +1,80 @@
+import numpy as np
+from astropy.io import fits
+import matplotlib.pyplot as plt
+
+# Bin summary
+pz_bins=[0.15,0.50,0.75,1.00,1.50]
+ng_arr=[]
+nz_arr=[]
+nz_arr={'cosmos':[],
+        'demp':[],
+        'ephor':[],
+        'ephor_ab':[],
+        'frankenz':[]}
+labels={'cosmos':'COSMOS 30-band',
+        'demp':'DEmP',
+        'ephor':'Ephor',
+        'ephor_ab':'Ephor_AB',
+        'frankenz':'FRANKEN-Z'}
+pz_codes=sorted(list(nz_arr.keys()))
+
+for fieldname in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
+    mskd=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+
+                   fieldname+
+                   "_sirius_i24p5_out/masked_fraction.fits")[0].data
+    mskbin=np.zeros_like(mskd); mskbin[mskd>0.5]=1
+    fng=fits.open("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+
+                  fieldname+
+                  "_sirius_i24p5_out/ngal_maps.fits")
+    zis=fng[1].data['z_i']
+    zfs=fng[1].data['z_f']
+    zs=0.5*(fng[1].data['z_f']+fng[1].data['z_i'])
+    ngs=[]
+    for i in range(4):
+        ngs.append(np.sum(fng[2*i].data*mskbin))
+    ng_arr.append(ngs)
+    for c in pz_codes:
+        nzs=[]
+        for i in range(4):
+            nzs.append(fng[2*i+1].data['nz_'+c])
+        nz_arr[c].append(nzs)
+
+ng_arr=np.array(ng_arr)
+for c in pz_codes:
+    nz_arr[c]=np.array(nz_arr[c])
+
+nzs_total={}
+for c in pz_codes:
+    nzs_total[c]=np.sum(nz_arr[c]*ng_arr[:,:,None],axis=0)
+
+colz=['#CC0000','#0000CC','#FFAB00','#009900']
+fig,axes=plt.subplots(2,2,figsize=(10,7),sharex=True,sharey=True)
+plt.subplots_adjust(hspace=0,wspace=0)
[…]

### 2019-08-20 plot_scripts/plots_ndens_consistency.py
number density consistency check

@@ -1,0 +1,96 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import flatmaps as fm
+from scipy.interpolate import interp1d
+
+# Read best-fit Cls and interpolate them
+d=np.loadtxt("../hsc_lss_params/cls_guess_i24p5.txt",unpack=True)
+# Read assuming constant Cls for l<2
+ls=np.arange(int(d[0][-1])+1,dtype=float)
+cls=np.zeros([4,len(ls)])
+for i,i_d in enumerate([1,5,8,10]):
+    cls[i,2:]=d[i_d]
+cls[:,:100]=cls[:,100][:,None]
+lclf=[interp1d(ls,np.log10(c),bounds_error=False,fill_value=np.log10(c[-1])) for c in cls]
+
+def get_ndens_and_error(field_name):
+    # This computes the number density and associated uncertainty
+    # for all redshift bins for a given field.
+
+    # Read mask
+    prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
+    fsk,mskfrac=fm.read_flat_map(prefix+"WIDE_"+field_name+"_sirius_i24p5_out/masked_fraction.fits")
+    msk_bin=np.zeros_like(mskfrac)
+    msk_bin[mskfrac>0.5]=1
+    mskfrac*=msk_bin;
+
+    # Footprint area (in arcmin)
+    area=np.sum(mskfrac)*fsk.dx*fsk.dy*60**2
+    
+    # Count number of galaxies in each redshift bin
+    ngals=np.array([np.sum(msk_bin*
+                           fm.read_flat_map(prefix+"WIDE_"+field_name+
+                                            "_sirius_i24p5_out/ngal_maps.fits",
+                                            i_map=2*i)[1])
+                    for i in range(4)])
+
+    # Ell sampling for DFTs
+    dlx=2*np.pi/np.radians(fsk.lx)
+    dly=2*np.pi/np.radians(fsk.ly)
+    ell_y=np.fft.fftfreq(fsk.ny,d=1./(dly*fsk.ny))
+    ell_x=np.fft.fftfreq(fsk.nx,d=1./(dlx*fsk.nx))
+    # |l|
+    ell_mod=np.sqrt(ell_y[:,None]**2+ell_x[None,:]**2)
+    # Mask Fourier transform
[…]

### 2019-08-20 plot_scripts/plots_cls_consistency.py
cls consistency

@@ -1,0 +1,91 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sacc
+from scipy.stats import chi2 as chi2f
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
+
+def read_cls(field,
+             msk_name='sirius',
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1'):
+    file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
+    
+    s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")
+    sn=sacc.SACC.loadFromHDF(file_prefix+"noi_bias.sacc")
+    sn.precision=s.precision
+    sb=sacc.SACC.loadFromHDF(file_prefix+"dpj_bias.sacc")
+    sb.precision=s.precision
+
+    return {'data':s,'noise':sn,'dpj_bias':sb}
+
+field_names=['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']
+colors={'GAMA09H':'#CC0000',
+        'GAMA15H':'#CC6600',
+        'HECTOMAP':'#CCCC00',
+        'VVDS':'#009900',
+        'WIDE12H':'#004C99',
+        'XMMLSS':'#990099'}
+
+s_fields={}
+for f in field_names:
+    print(f)
+    s_fields[f]=read_cls(f)
+s_all={typ:sacc.coadd([s_fields[f][typ] for f in field_names],mode='area')
+       for typ in ['data','noise','dpj_bias']}
+
+lmaxs=np.array([2170,2515,3185,4017])
+
+fig,axes=plt.subplots(4,4,figsize=(15,10),sharex=True,sharey=True)
+plt.subplots_adjust(hspace=0,wspace=0)
+
+nbins=4
+for b1 in range(nbins) :
+    for b2 in range(nbins) :
+        if b2<b1 :
+            axes[b1,b2].axis('off')
+
+
+for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
+    lmax=min(lmaxs[t1],lmaxs[t2])
+    mask=ells<lmax
+    ax=axes[t1,t2]
+    dmean=s_all['data'].mean.vector[ndx]-s_all['noise'].mean.vector[ndx]
+    print("%d-%d"%(t1+1,t2+1))
+    ax.plot([2,20000],[0,0],'k--')
[…]

### 2019-08-20 plot_scripts/plots_cls_consistency.py
corrected for mean

@@ -32,6 +32,9 @@ for f in field_names:
     s_fields[f]=read_cls(f)
 s_all={typ:sacc.coadd([s_fields[f][typ] for f in field_names],mode='area')
        for typ in ['data','noise','dpj_bias']}
+areas={f:s_fields[f]['data'].meta['Area_rad'] for f in field_names}
+area_total=np.sum(np.array([areas[f]  for f in field_names]))
+weights={f:areas[f]/area_total for f in field_names}
 
 lmaxs=np.array([2170,2515,3185,4017])
 
@@ -44,12 +47,14 @@ for b1 in range(nbins) :
         if b2<b1 :
             axes[b1,b2].axis('off')
 
-
+ndx_all=[]
 for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
     lmax=min(lmaxs[t1],lmaxs[t2])
     mask=ells<lmax
+    ndx_all+=list(ndx[mask])
     ax=axes[t1,t2]
     dmean=s_all['data'].mean.vector[ndx]-s_all['noise'].mean.vector[ndx]
+    covmean=s_all['data'].precision.getCovarianceMatrix()[ndx,:][:,ndx]
     print("%d-%d"%(t1+1,t2+1))
     ax.plot([2,20000],[0,0],'k--')
     for i_f,f in enumerate(field_names):
@@ -60,7 +65,8 @@ for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
         e=np.sqrt(np.fabs(np.diag(cov)))
 
         res=(d-dmean)[mask]
-        icov_red=np.linalg.inv(cov[mask,:][:,mask])
+        cov_red=cov-2*weights[f]*cov+covmean
+        icov_red=np.linalg.inv(cov_red[mask,:][:,mask])
         chi2=np.einsum('i,ij,j',res,icov_red,res)
         ndof=len(res)
         print("  %s : %.3lf %d %.3lf"%(f,chi2,ndof,1-chi2f.cdf(chi2,ndof)))
@@ -85,6 +91,21 @@ for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
     else :
         ax.tick_params(axis='both', which='both',length=0)
         
+print("All:")
+ndx_all=np.array(ndx_all)
+dmean=s_all['data'].mean.vector[ndx_all]-s_all['noise'].mean.vector[ndx_all]
[…]

### 2019-08-21 plot_scripts/plot_cls_summary.py
cls summary

@@ -1,0 +1,85 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sacc
+from scipy.stats import chi2 as chi2f
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
+
+def read_cls(field,
+             msk_name='sirius',
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1'):
+    """Reads all power spectra for a given field"""
+    file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
+    
+    s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")
+    sn=sacc.SACC.loadFromHDF(file_prefix+"noi_bias.sacc")
+    sn.precision=s.precision
+    sb=sacc.SACC.loadFromHDF(file_prefix+"dpj_bias.sacc")
+    sb.precision=s.precision
+
+    return {'data':s,'noise':sn,'dpj_bias':sb}
+
+# Read power spectra for each field and coadd
+field_names=['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']
+s_fields={}
+for f in field_names:
+    print(f)
+    s_fields[f]=read_cls(f)
+s_all={typ:sacc.coadd([s_fields[f][typ] for f in field_names],mode='area')
+       for typ in ['data','noise','dpj_bias']}
+
+lmaxs=np.array([2170,2515,3185,4017])
+
+fig,axes=plt.subplots(4,4,figsize=(15,10),sharex=True,sharey=True)
+plt.subplots_adjust(hspace=0,wspace=0)
+
+nbins=4
+for b1 in range(nbins) :
+    for b2 in range(nbins) :
+        if b2<b1 :
+            axes[b1,b2].axis('off')
+
+ndx_all=[]
+for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
+    lmax=min(lmaxs[t1],lmaxs[t2])
+    mask=ells<lmax
+    ndx_all+=list(ndx[mask])
+    ax=axes[t1,t2]
+    cl=s_all['data'].mean.vector[ndx]
+    nl=s_all['noise'].mean.vector[ndx]
+    dl=s_all['dpj_bias'].mean.vector[ndx]
[…]

### 2019-08-21 plot_scripts/plots_cls_consistency.py
cls systematics

@@ -7,9 +7,9 @@ prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
 
 def read_cls(field,
              msk_name='sirius',
-             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1'):
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1'):
     file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
-    
+
     s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")
     sn=sacc.SACC.loadFromHDF(file_prefix+"noi_bias.sacc")
     sn.precision=s.precision

### 2019-08-21 plot_scripts/plots_cls_summary.py

@@ -39,11 +39,8 @@ for b1 in range(nbins) :
         if b2<b1 :
             axes[b1,b2].axis('off')
 
-ndx_all=[]
 for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
     lmax=min(lmaxs[t1],lmaxs[t2])
-    mask=ells<lmax
-    ndx_all+=list(ndx[mask])
     ax=axes[t1,t2]
     cl=s_all['data'].mean.vector[ndx]
     nl=s_all['noise'].mean.vector[ndx]

### 2019-08-21 plot_scripts/plots_cls_systematics.py

@@ -1,0 +1,95 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sacc
+from scipy.stats import chi2 as chi2f
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
+
+def read_cls(field,
+             wdpj=True,
+             msk_name='sirius',
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1'):
+    file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
+
+    if wdpj:
+        s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")
+    else:
+        s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wodpj.sacc")
+    sn=sacc.SACC.loadFromHDF(file_prefix+"noi_bias.sacc")
+    sn.precision=s.precision
+    sb=sacc.SACC.loadFromHDF(file_prefix+"dpj_bias.sacc")
+    sb.precision=s.precision
+
+    return {'data':s,'noise':sn,'dpj_bias':sb}
+
+def read_cls_coadd(msk_name,directory,wdpj=True):
+    field_names=['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']
+    s_fields={}
+    print(msk_name,directory)
+    for f in field_names:
+        print("   %s "%f)
+        s_fields[f]=read_cls(f,msk_name=msk_name,directory=directory,wdpj=wdpj)
+    s_all={typ:sacc.coadd([s_fields[f][typ] for f in field_names],mode='area')
+           for typ in ['data','noise','dpj_bias']}
+    return s_all
+
+s_fid=read_cls_coadd('sirius','CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1',wdpj=True)
+s_ndp=read_cls_coadd('sirius','CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1',wdpj=False)
+s_sys=read_cls_coadd('sirius','CovAna_NoiAna_MskSiriusSyst_ClFit_Dpj0_DpjBands1',wdpj=True)
+
+lmaxs=np.array([2170,2515,3185,4017])
+
+fig,axes=plt.subplots(4,4,figsize=(15,10),sharex=True,sharey=True)
[…]

### 2019-08-21 plot_scripts/plots_cls_summary.py
cls_summary

@@ -55,8 +55,15 @@ for t1,t2,typ,ells,ndx in s_all['data'].sortTracers():
         label_n=None
         label_d=None
     l_factor=1.0
-    ax.errorbar(ells,l_factor*(cl-nl),yerr=l_factor*el,fmt='r.',label=label_c)
-    eb=ax.errorbar(ells,-l_factor*(cl-nl),yerr=l_factor*el,fmt='r.')
+    msk_neg=cl-nl<0
+    ax.errorbar(ells[~msk_neg],
+                (l_factor*(cl-nl))[~msk_neg],
+                yerr=(l_factor*el)[~msk_neg],
+                fmt='ro',label=label_c,ms=3)
+    eb=ax.errorbar(ells[msk_neg],
+                   (-l_factor*(cl-nl))[msk_neg],
+                   yerr=(l_factor*el)[msk_neg],
+                   fmt='ro',mfc='white',ms=3)
     eb[-1][0].set_linestyle('--')
     ax.plot(ells,l_factor*nl,'-',c='#AAAAAA',label=label_n)
     ax.plot(ells,l_factor*dl,'-',lw=1,c='#0000CC',label=label_d)

### 2019-08-21 plot_scripts/plots_ndens_syst.py
ndens_syst

@@ -1,0 +1,47 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_VVDS_sirius_i24p5_out/systmap_plots/"
+
+# Read representative data
+d_airmass=np.load(prefix+"bin3_airmass.npz")
+d_dust=np.load(prefix+"bin3_dust.npz")
+
+# Plot
+def plot_ndata(x,y,ey,ax,xcut=None):
+    # Linear slope
+    m = np.sum((x-1)*(y-1)/ey**2)/np.sum((x-1)**2/ey**2)
+
+    # Plot data
+    ax.errorbar(x,y,yerr=ey,fmt='r.')
+    # Plot linear fit
+    x0=x[0]-(x[-1]-x[0])*0.05
+    xf=x[-1]+(x[-1]-x[0])*0.05
+    ax.plot([x0,xf],[m*(x0-1)+1,m*(xf-1)+1],'k-')
+    # Plot cutoff
+    if xcut:
+        y0=np.amin(y-ey)
+        yf=np.amax(y+ey)
+        
+        ax.plot([xcut,xcut],[y0-0.05*(yf-y0),yf+0.05*(yf-y0)],'--',c='#AAAAAA')
+        ax.set_ylim([y0-0.05*(yf-y0),yf+0.05*(yf-y0)])
+
+    ax.tick_params(labelsize="large")
+    ax.set_ylabel('$R(N_g)$',fontsize=15)
+    
+fig,axes=plt.subplots(2,1,figsize=(10,10))
+# Plot airmass
+plot_ndata(d_airmass['x_rescaled'][1],
+           d_airmass['mean'][1],
+           d_airmass['error'][1],
+           axes[0],xcut=1.15)
+axes[0].set_xlabel('$R({\\rm Airmass},r)$',fontsize=15)
+# Plot dust
+plot_ndata(d_dust['x_rescaled'][0],
+           d_dust['mean'][0],
+           d_dust['error'][0],
+           axes[1])
+axes[1].set_xlabel('$R({\\rm Dust})$',fontsize=15)
+plt.savefig('../doc/Paper/figures/ndens_syst.pdf',
+            bbox_inches='tight')
+plt.show()

### 2019-08-22 plot_scripts/plots_ndens_syst.py
systmask

@@ -13,7 +13,7 @@ def plot_ndata(x,y,ey,ax,xcut=None):
     m = np.sum((x-1)*(y-1)/ey**2)/np.sum((x-1)**2/ey**2)
 
     # Plot data
-    ax.errorbar(x,y,yerr=ey,fmt='r.')
+    ax.errorbar(x,y,yerr=ey,fmt='ro',ms=4)
     # Plot linear fit
     x0=x[0]-(x[-1]-x[0])*0.05
     xf=x[-1]+(x[-1]-x[0])*0.05

### 2019-08-22 plot_scripts/plots_systmask.py

@@ -1,0 +1,23 @@
+import flatmaps as fm
+import numpy as np
+import matplotlib.pyplot as plt
+
+prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"
+field="VVDS"
+fsk,msk1=fm.read_flat_map(prefix+field+
+                          "_sirius_i24p5_out/masked_fraction.fits")
+msk1[msk1<0.5]=0; msk1[msk1>=0.5]=1.;
+_,msk2=fm.read_flat_map(prefix+field+
+                        "_sirius_i24p5_out/"+
+                        "CovAna_NoiAna_MskSiriusSyst_ClFit_Dpj0_DpjBands1/mask_syst.fits")
+
+fig=plt.figure()
+ax=fig.add_subplot(111,projection=fsk.wcs)
+ax.set_title(field,fontsize=14)
+im=ax.imshow((msk1+msk2).reshape([fsk.ny,fsk.nx]),vmin=0,vmax=2,
+             origin='lower', interpolation='nearest')
+ax.set_xlabel('R.A.', fontsize=14)
+ax.set_ylabel('Dec.', fontsize=14)
+plt.savefig("../doc/Paper/figures/systmask.pdf",
+            bbox_inches='tight')
+plt.show()

### 2019-08-22 plot_scripts/plots_systmask.py
systmask

@@ -10,11 +10,18 @@ msk1[msk1<0.5]=0; msk1[msk1>=0.5]=1.;
 _,msk2=fm.read_flat_map(prefix+field+
                         "_sirius_i24p5_out/"+
                         "CovAna_NoiAna_MskSiriusSyst_ClFit_Dpj0_DpjBands1/mask_syst.fits")
+_,msk3=fm.read_flat_map(prefix+field+
+                        "_arcturus_i24p5_out/masked_fraction.fits")
+msk3[msk3<0.5]=0; msk3[msk3>=0.5]=1.;
 
 fig=plt.figure()
-ax=fig.add_subplot(111,projection=fsk.wcs)
-ax.set_title(field,fontsize=14)
+ax=fig.add_subplot(211,projection=fsk.wcs)
 im=ax.imshow((msk1+msk2).reshape([fsk.ny,fsk.nx]),vmin=0,vmax=2,
+             origin='lower', interpolation='nearest')
+ax.set_xlabel('R.A.', fontsize=14)
+ax.set_ylabel('Dec.', fontsize=14)
+ax=fig.add_subplot(212,projection=fsk.wcs)
+im=ax.imshow(msk3.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
              origin='lower', interpolation='nearest')
 ax.set_xlabel('R.A.', fontsize=14)
 ax.set_ylabel('Dec.', fontsize=14)

### 2019-08-22 plot_scripts/plots_ndens_syst.py
ndens_syst

@@ -26,7 +26,11 @@ def plot_ndata(x,y,ey,ax,xcut=None):
         ax.plot([xcut,xcut],[y0-0.05*(yf-y0),yf+0.05*(yf-y0)],'--',c='#AAAAAA')
         ax.set_ylim([y0-0.05*(yf-y0),yf+0.05*(yf-y0)])
 
-    ax.tick_params(labelsize="large")
+    #for tick in ax.xaxis.get_major_ticks():
+    #    tick.label.set_fontsize(14)
+    #for tick in ax.yaxis.get_major_ticks():
+    #    tick.label.set_fontsize(14)
+    ax.tick_params(labelsize="x-large")
     ax.set_ylabel('$R(N_g)$',fontsize=15)
     
 fig,axes=plt.subplots(2,1,figsize=(10,10))

### 2019-08-22 plot_scripts/plots_ndens_syst.py
ndens_syst

@@ -33,7 +33,7 @@ def plot_ndata(x,y,ey,ax,xcut=None):
     ax.tick_params(labelsize="x-large")
     ax.set_ylabel('$R(N_g)$',fontsize=15)
     
-fig,axes=plt.subplots(2,1,figsize=(10,10))
+fig,axes=plt.subplots(2,1,figsize=(8,8))
 # Plot airmass
 plot_ndata(d_airmass['x_rescaled'][1],
            d_airmass['mean'][1],

### 2019-08-22 plot_scripts/plots_systmask.py
systmask

@@ -14,13 +14,15 @@ _,msk3=fm.read_flat_map(prefix+field+
                         "_arcturus_i24p5_out/masked_fraction.fits")
 msk3[msk3<0.5]=0; msk3[msk3>=0.5]=1.;
 
-fig=plt.figure()
+fig=plt.figure(figsize=(8,8))
 ax=fig.add_subplot(211,projection=fsk.wcs)
+ax.set_title("Sirius mask",fontsize=14)
 im=ax.imshow((msk1+msk2).reshape([fsk.ny,fsk.nx]),vmin=0,vmax=2,
              origin='lower', interpolation='nearest')
 ax.set_xlabel('R.A.', fontsize=14)
 ax.set_ylabel('Dec.', fontsize=14)
 ax=fig.add_subplot(212,projection=fsk.wcs)
+ax.set_title("Arcturus mask",fontsize=14)
 im=ax.imshow(msk3.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
              origin='lower', interpolation='nearest')
 ax.set_xlabel('R.A.', fontsize=14)

### 2019-09-02 plot_scripts/plots_cls_systematics.py
arcturus mask

@@ -36,6 +36,7 @@ def read_cls_coadd(msk_name,directory,wdpj=True):
 s_fid=read_cls_coadd('sirius','CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1',wdpj=True)
 s_ndp=read_cls_coadd('sirius','CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1',wdpj=False)
 s_sys=read_cls_coadd('sirius','CovAna_NoiAna_MskSiriusSyst_ClFit_Dpj0_DpjBands1',wdpj=True)
+s_msk=read_cls_coadd('arcturus','CovAna_NoiAna_MskArcturus_ClFit_Dpj0_DpjBands1',wdpj=True)
 
 lmaxs=np.array([2170,2515,3185,4017])
 
@@ -57,23 +58,30 @@ for t1,t2,typ,ells,ndx in s_fid['data'].sortTracers():
     c_fid=s_fid['data'].mean.vector[ndxs]
     c_ndp=s_ndp['data'].mean.vector[ndxs]
     c_sys=s_sys['data'].mean.vector[ndxs]
+    c_msk=s_msk['data'].mean.vector[ndxs]
     e_fid=np.sqrt(np.fabs(np.diag(s_fid['data'].precision.getCovarianceMatrix()[ndxs,:][:,ndxs])))
     e_ndp=np.sqrt(np.fabs(np.diag(s_ndp['data'].precision.getCovarianceMatrix()[ndxs,:][:,ndxs])))
     e_sys=np.sqrt(np.fabs(np.diag(s_sys['data'].precision.getCovarianceMatrix()[ndxs,:][:,ndxs])))
+    e_msk=np.sqrt(np.fabs(np.diag(s_msk['data'].precision.getCovarianceMatrix()[ndxs,:][:,ndxs])))
     print("%d-%d"%(t1+1,t2+1))
     ax.plot([2,20000],[0,0],'k--')
     if t1==0 and t2==0:
         label_ndp='No deprojection'
         label_sys='Contaminant mask'
+        label_msk='Arcturus mask'
     else:
         label_ndp=None
         label_sys=None
-    ax.errorbar(ls*(0.95+0.1*(0+0.5)/2.),(c_ndp-c_fid)/e_ndp,
-                    yerr=e_ndp/e_ndp,
-                    fmt='.',c='r',label=label_ndp)
[…]

### 2019-10-02 doc/Paper/main.tex
changes

@@
 
-\usepackage{jcappub} % for details on the use of the package, please
-                     % see the JCAP-author-manual
+\usepackage{jcappub}
+\usepackage{graphicx}
+\usepackage{dcolumn}
+\usepackage{amssymb,amsmath,bm}
+\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
+%\usepackage[colorlinks,linkcolor=red,citecolor=blue,urlcolor=blue ]{hyperref}
+%\usepackage[utf8]{inputenc}
+\usepackage{lipsum}
+\usepackage{xfrac}
+\usepackage{aas_macros}
+\usepackage{mathrsfs}
+\usepackage{subfigure}
+\usepackage{rotating}
+\newcommand{\nv}{\vec{\theta}}
+%\newcommand{\pasj}{Publications of the ASJ}
+%\newcommand{\aap}{Astronomy and Astrophysics}
+%\newcommand{\apj}{Astrophysical Journal}
+%\newcommand{\apjs}{Astrophysical Journal, Supplement}
+%\newcommand{\mnras}{Monthly Notices of the RAS}
+\newcommand{\todo}[1]{{\bf TODO: #1}}
+
+\newcommand{\as}[1]{{\textcolor{blue}{[AS: #1]}}}
+\newcommand{\an}[1]{{\textcolor{magenta}{[AN: #1]}}}
+\newcommand{\da}[1]{{\textcolor{red}{[DA: #1]}}}
+
+\newcommand\Tstrut{\rule{0pt}{3ex}}
+
+\definecolor{internationalkleinblue}{rgb}{0.0, 0.18, 0.65}
+\hypersetup{urlcolor=internationalkleinblue, linkcolor=internationalkleinblue, citecolor=internationalkleinblue}
 
@@
 \bibliographystyle{JHEP}
-\title{Clustering analysis of the HSC-SSP DR1 data as precursor for the LSST Dark Energy Survey Collaboration Analysis (or some fancier title)}
+\title{Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release}
 
-%% %simple case: 2 authors, same institution
-%% \author{A. Uthor}
-%% \author{and A. Nother Author}
-%% \affiliation{Institution,\\Address, Country}
+\author[a,1]{Andrina Nicola,}
+\author[b]{David Alonso,}
+\author[c]{An\v{z}e Slosar,}
+\author[d]{Humna Awan,}
+\author[d]{Adam Broussard,}
+\author[b]{Zahra Gomes,}
+\author[d]{Eric Gawiser,}
+\author[x]{Rachel Mandelbaum,}
+\author[x]{Hironao Miyatake,}
+\author[e]{Jeffrey A. Newman,}
+\author[f,g]{Javier S\'anchez,}
+\author[x]{Ignacio Sevilla,}
+\author[c,h]{Sarah Skinner,}
+\author[x]{Erica Wagoner}
 
-% more complex case: 4 authors, 3 institutions, 2 footnotes
-\author[a,b,1]{F. Irst,\note{Corresponding author.}}
-\author[c]{S. Econd,}
-\author[a,2]{T. Hird\note{Also at Some University.}}
-\author[a,2]{and Fourth}
+\affiliation[a]{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton NJ 08544-0010, USA}
+\affiliation[b]{Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, United Kingdom}
+\affiliation[c]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
+\affiliation[d]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
+\affiliation[e]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
+\affiliation[f]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
+\affiliation[g]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation[h]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
 
-% The "\note" macro will give a warning: "Ignoring empty anchor..."
-% you can safely ignore it.
+\emailAdd{anicola@astro.princeton.edu}
 
-\affiliation[a]{One University,\\some-street, Country}
-\affiliation[b]{Another University,\\different-address, Country}
-\affiliation[c]{A School for Advanced Studies,\\some-location, Country}
-
-% e-mail addresses: one for each author, in the same order as the authors
-\emailAdd{first@one.univ}
-\emailAdd{second@asas.edu}
-\emailAdd{third@one.univ}
-\emailAdd{fourth@one.univ}
-
-\abstract{With the increasing statistical power in Stage IV Dark Energy experiments, new analysis strategies must be developed and tested in order to fully exploit their data.
-In this work we present the current state-of-the-art clustering pipeline developed for the upcoming data from the LSST and use the public data from the Hyper-Suprime Camera Subaru Strategic Program (HSC-SSP) first data release (DR1) as a proof concept.
-In addition, we obtain the first HOD resuts for these data (and compare with something else maybe??).}
+\abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program.
+Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets such that the Large Synoptic Survey Telescope will acquire, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
+We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$.
+We carry out a Fourier-space analysis of the two-point clustering of this sample, including all auto- and cross-correlations between bins.
+We demonstrate the use of map-level deprojection methods to account for non-physical fluctuations in the galaxy number density caused by observational systematics.
+Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses characterizing this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$ including both auto- and cross-correlations.
+Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, reproducing previous results.
+In terms of photometric redshift systematics, we show that additional care is needed in order to marginalize over uncertainties in the redshift distribution in galaxy clustering, even for samples of this small size, and that these uncertainties can be significantly constrained by including cross-bin correlations.
+We are able to make a $\sim3\sigma$ detection of the effects of lensing magnification in the HSC data.
+When freeing up cosmological parameters, we find constraints on the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ that agree well with measurements from Planck and low-redshift probes.
+Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple model for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}
 
@@
 
-\section{Introduction}
-\label{sec:intro}
+\section{Introduction}\label{sec:intro}
 
-$\cdots$ TBC, \citep{2006astro.ph..9591A}
-\section{Data}
-\label{sec:data}
-In this work we use the public data products from HSC-SSP DR1~\citep{2018PASJ...70S...8A}.
-In particular, we generated a Python script \texttt{hscQuery.py}\footnote{\url{https://github.com/LSSTDESC/HyperSupremeStructure-HSC-LSS/blob/master/data_query/hscReleaseQuery.py}} to retrieve the data products available at \url{https://hsc-release.mtk.nao.ac.jp/datasearch/api/catalog_jobs/}.
-The data products obtained encompass the forced photometry object catalogs for the wide fields, the metadata and observing logs including the observing conditions, and the tables that include the photometric redshift information.
-We join the object catalog and the photometric redshift table by matching IDs in both tables.
-We restricted our queries to only include objects that pass the selection cuts included in~\citep{2018PASJ...70S..25M}
-\subsection{Data selection}
-\label{ssec:data_selection}
-\subsection{Mapping observing conditions}
-\label{ssec:observing_conditions}
-\section{Analysis}
-\label{sec:analysis}
-\subsection{Estimation of power-spectra}
-\label{ssec:cls}
-\subsection{HOD model}
-\label{ssec:HOD}
-\section{Discussion}
-\label{sec:discussion}
+The past two decades have seen a revolution in our understanding of Universe and its constituents.
+While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular expansion history and growth that are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
+
+In studies of the low redshift universe, surveys of the large scale structure play an increasingly important role.
+Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
+The current Stage III experiments including spectroscopic ones such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric ones such as DES \cite{1708.01531,1708.01530,1708.01536}, Hyper-SupremeCam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} and major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+
+Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}.
+For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources in the field.
+The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
+These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}.
+But even with perfect measurements of fluxes, our ability to infer redshift distribution of sources is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as the scattered light from bright objects, errors in the galaxy-star separation, reddedning by the milky way dust and others will impriment their own fluctuations into the galaxy density of objects.
+These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
+Therefore, it is likely that the Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
+
+Community is well aware of these challenges lying ahead.
+There are two main approaches that are being used in preparation for the arrival of data.
+On one hand, we are building very sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
+On the other hand, we are re-analyzing the existing precursor data to test-drive our methods and codes in realistic environment.
+In this paper we focus on the latter approach using Hyper Supreme-Cam Subaru Strategic Program (HSC-SSP) first data release  \cite{2018PASJ...70S...8A}.
+The main advantage of this dataset is that it is in many respects very similar to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
+It covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
+We will work with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, similar to expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
+The primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
+With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is a perfect example of how the LSST data will look like.
+
+In this paper we focus exclusively on the galaxy clustering part of the data analysis.
+While the statistically most powerful data combination includes the full 3$\times$2 point analysis (i.e.
+shear and number density auto and cross-correlations), galaxy clustering along comes with unique challenges, which are the focus of this paper.
+In particular, galaxy clustering is more sensitive to details of redshift distribution of sources and systematic effects that can generate false fluctuations in number densities.
+These are the main effects that we study in this paper.
+We will employ basic tools of the trade, such as measuring power spectrum using mode deprojection and then fit the resulting data taking into account possible deviations from redshift distribution estimates.
+The question is whether there are sufficient given the statistical precision of the data.
+We will find that the answer is yes, at least over the total area of HSC-SSP DR1 data.
+
+Due to rather small area, we will be employing simple semi-analytical halo model to make theory predictions.
+While this model is most certainly not sophisticated enough for the full sky LSST analysis, it suffices for the statistical precision of data at hand.
+While we will derive some useful constraints on the halo model parameters, the use of halo model here should be viewed as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
+
+The paper is structured as follows.
+In Section \ref{sec:data} we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
+In Section \ref{sec:methods} we go through the methodology employed in our analysis of the data and in Section \ref{sec:results} we present results together with numerous tests.
+We discuss and conclude in Section \ref{sec:discussion}.
+
+\section{Data}\label{sec:data}
+  \begin{table}
+  \centering
+  \begin{tabular}{|l|l|}
+  \hline
+   {\bf Cut} & {\bf Comment} \\
+   \hline
+   \texttt{detect\_is\_primary}=True & Basic quality cuts, \\
+   \texttt{icmodel\_flags\_badcentroid}=False & see \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}\\
+   \texttt{icentroid\_sdss\_flags}=False & \\
+   \texttt{iflags\_pixel\_edge}=False & \\
+   \texttt{iflags\_pixel\_interpolated\_center}=False & \\
+   \texttt{iflags\_pixel\_saturated\_center}=False & \\
+   \texttt{iflags\_pixel\_cr\_center}=False & \\
+   \texttt{iflags\_pixel\_bad}=False & \\
+   \texttt{iflags\_pixel\_suspect\_center}=False & \\
+   \texttt{iflags\_pixel\_clipped\_any}=False & \\
+   \texttt{meas.ideblend\_skipped}=False & \\
+   \texttt{iblendedness\_abs\_flux}$<10^{-0.375}$ & \\
+   \hline % Strict from here on
+   \texttt{[g,r,z,y]centroid\_sdss\_flags}=False & Strict photometry cuts\\
+   \texttt{[g,r,i,z,y]cmodel\_flux\_flags}=False & \\
+   \texttt{[g,r,i,z,y]flux\_psf\_flags}=False & \\
+   \texttt{[g,r,z,y]flags\_pixel\_edge}=False & \\
+   \texttt{[g,r,z,y]flags\_pixel\_interpolated\_center}=False & \\
+   \texttt{[g,r,z,y]flags\_pixel\_saturated\_center}=False & \\
+   \texttt{[g,r,z,y]flags\_pixel\_cr\_center}=False & \\
+   \texttt{[g,r,z,y]flags\_pixel\_bad}=False & \\
+   \hline
+   \texttt{icmodel\_mag}$-$\texttt{a\_i} $<$ 24.5 & Magnitude limit\\ % Magnitude cut
+   \hline
+   \texttt{icmodel\_flux}$>10\,$\texttt{icmodel\_flux\_err} & 10$\sigma$ detections\\
+   \hline
+   \texttt{[g,r,y,z]cmodel\_flux}$>5\,$\texttt{[g,r,y,z]cmodel\_flux\_err} & 5$\sigma$ detection  (required \\
+   & only in 2 other bands)\\
+   \hline
+   \texttt{iclassification\_extendedness}=1 & Star-galaxy separator\\
+   \hline
+  \end{tabular}
+  \caption{Summary of the selection cuts performed to the original dataset to retrieve the sample considered in our analysis.} \label{tab:cuts_summary}
+  \end{table}
+
+  \begin{table}
+  \centering
+  \begin{tabular}{|l|r|c|l|}
+   \hline
+   {\bf Field name} & $N_{\rm gal}$ & {\bf Area} (deg$^2$) & $f_{\rm sky}$ \\
+   \hline
+   GAMA09H  & 1,697,713 & 14.5 & $3.5\times10^{-4}$ \\
+   GAMA15H  & 1,695,364 & 15.1 & $3.7\times10^{-4}$ \\
+   HECTOMAP &   639,970 &  5.1 & $1.2\times10^{-4}$ \\
+   VVDS     & 2,340,965 & 20.6 & $5.0\times10^{-4}$ \\
+   WIDE12H  & 1,220,816 & 11.6 & $2.8\times10^{-4}$ \\
+   XMMLSS   & 2,139,629 & 20.8 & $5.0\times10^{-4}$ \\
+   \hline
+   Total    & 9734457 & 87.7 & $2.1\times10^{-3}$ \\
+   \hline
+  \end{tabular}
+  \caption{Summary of the 6 different fields used in our analysis.
+The second column lists the number of galaxies in the DR1 catalog passing the cuts in Table \ref{tab:cuts_summary}.
+The third and fourth columns show the area and corresponding sky fraction covered by each field.
+The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}.
+\an{We don't use HECTOMAP in the fitting.
+Shall we even show it here?}} \label{tab:field_summary}
+  \end{table}
+
+  \begin{table}
+  \centering
+  \begin{tabular}{|l|l|l|l|}
+    \hline
+    $z_{\rm phot}^{\rm ini}$ & $z_{\rm phot}^{\rm end}$ & $\bar{z}$ & $N_{\rm gal}$ \\
+    \hline
+    0.15 & 0.5  & 0.57 & 1,750,274 \\
+    0.5  & 0.75 & 0.68 & 1,766,939 \\
+    0.75 & 1.0  & 0.91 & 1,702,685 \\
+    1.0  & 1.5  & 1.26 & 1,752,359 \\
+    \hline
+  \end{tabular}
+  \caption{Summary of the 4 redshift bins used in our analysis.
+The first two columns show the photo-$z$ bin edges.
+We used the {\tt photoz\_best} redshift estimator for the photo-$z$ code {\tt ephor\_ab} to assign galaxies to different bins.
+The second column shows the mean redshift of each bin calculated from the fiducial redshift distributions described in Section \ref{ssec:methods.nz}.
+The last column shows the number of galaxies in each bin.
+The bin edges were chosen to roughly contain an equal number of galaxies in each of them.} \label{tab:bins_summary}
+  \end{table}
+
+  We use data from the Hyper Suprime-Cam Subaru Strategic Program first data release (HSC DR1 hereon)\footnote{https://hsc-release.mtk.nao.ac.jp}.
+The release is extensively documented in \cite{2018PASJ...70S...8A}, and we only provide the details of the galaxy sample and associated data used for our clustering analysis.
+
+  HSC-SSP is a photometric galaxy survey that has been awared 300 nights on the Subaru Telescope starting in 2014.
+The DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degreesto $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
+In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields between 5 and 20 square degrees each.
+The image quality is impressive at median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
+DES with around 0.9 arc sec) and also likely better than median seeing that will be achieved by  LSST.
+The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and  available to the community as a publicly available database.
+
+  We use a magnitude-limited sample constructed from the WIDE DR1 sample by imposing data cuts that are similar to those used to create the HSC shear catalog \cite{2018PASJ...70S..25M}.
+The exact cuts are shown in Table~\ref{tab:cuts_summary}, and can be summarized as follows: besides a minimal set of quality cuts (selecting only primary detections with well-measured fluxes in all bands, removing objects near bad pixels, deblender artifacts, etc.), we impose an overall apparent magnitude cut in the extinction-corrected band $i_{\rm corr}<24.5$.
+This choice was based on a study of the survey depth-completeness relation in order to select a homogeneous and complete sample of high-confidence ($>10\sigma$) detections (see Section \ref{ssec:methods.syst}).
+We also select only objects with significant detections ($>5\sigma$) in at least two of the 4 remaining bands ($g,\,r,\,z,\,y$), and remove all objects classified as stars by the data reduction pipeline, using the "extendedness`` classifier as described in \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}.
+The resulting sample consists of 9,734,457 objects and covers $\sim88$ square degrees distributed across the 6 HSC DR1 fields, as described in Table \ref{tab:field_summary}.
+
+  All objects have photometric redshift measurements from 6 different codes as presented in \cite{2018PASJ...70S...9T}.
+We use the {\tt photoz\_best} redshift estimator assigned by the {\tt ephor\_ab} method as a marker to divide the sample into four tomographic samples containing roughly equal numbers of galaxies.
+The {\tt photoz\_best} estimator is defined to minimize the risk that the true galaxy redshift lies outside the range $z_{\rm true}\pm 0.15(1+z_{\rm true})$, where $z_{\rm true}$ is the galaxy's true redshift.
+A preliminary Fisher matrix study showed that the information content saturates quickly when slicing the data into more than four samples.
+The redshift bins are described in Table \ref{tab:bins_summary}, and the associated redshift distributions are discussed in Section \ref{ssec:methods.nz}.
+
+\section{Methods}\label{sec:methods}
+
+Our basic method is to measure the two point function of all possible combinations of galaxy density fluctuation fields.
+We work in the Fourier domain, so our basic quantity is the angular power spectrum $C_\ell$.
+Given four tomographic samples, our measurement consists of four auto power spectra and six cross-power spectra.
+In this section we discuss how we construct maps of galaxy density fluctuations and associate maps of potential systematics , how we use these to measure the power spectra and its covariance matrix and finally how these are modeled within the context of halo model.
+
+  \subsection{Pixels and maps}\label{ssec:methods.pix}
+    Our $C_\ell$-based analysis requires us to make maps of different quantities.
+The HSC DR1 is distributed across the 6 small fields ($\lesssim20\,{\rm deg.}^2$) summarized in Table \ref{tab:field_summary}.
+In this case, storing maps covering the full sky down to arcminute resolution, and performing operations on them such as spherical harmonic transforms, would be computationally inefficient and unnecessary.
+Instead, we perform separate power spectrum measurements on each individual field, with maps defined on rectangular sky patches covering them.
+Furthermore, the small size of each field allows us to make use of the flat-sky approximation safely.
+This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs).
+
+    To generate maps of all the quantities described in this section we make use of a rectangular pixelization scheme using the Plate Carr\'ee projection (labelled {\tt CAR} in the World Coordinate System standard \cite{2002A&A...395.1077C}).
+In this case, pixels are simply defined by equal intervals of colatitude $\theta$ and azimuth $\phi$.
+To minimize the distortions caused by the flat-sky approximation, we place the projection reference point (i.e.
+a point in the equator $\theta=\pi/2$) at the center of each field.
+We use square pixels of size $\alpha_{\rm pix}=0.6$ arcmin on a side, corresponding to a Nyquist frequency $\ell_{\rm Nyquist}=18,000$.
+The maps are defined on a rectangular patch large enough to cover all objects in each field, leaving a buffer of 10 masked pixels on all edges to avoid boundary effects when computing the FFTs.
+
+  \subsection{Survey mask}\label{ssec:methods.mask}
+    \begin{figure}
+      \centering
+      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA09H.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA15H.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/mask_HECTOMAP.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/mask_VVDS.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/mask_WIDE12H.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/mask_XMMLSS.pdf}
+      \caption{Sky masks for the 6 fields used in this analysis.
+The map pixels contain values between 0 and 1, corresponding to the fraction of the pixel's area not covered by the fiducial bright-object mask.}
+      \label{fig:masks}
+    \end{figure}
+    The reconstruction of the survey geometry is a central step in order to obtain unbiased estimates of the angular power spectrum.
+This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis.
+The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details).
+It is worth noting that the information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags.
+We transform this information into a pixelized sky map through a multi-step process:
+    \begin{enumerate}
+      \item We start by creating a low-resolution binary mask based on the presence of objects from the raw catalog in a given pixel.
+This mask has a pixel size of 0.6 arcmin.
+The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
+      \item We upgrade the low-resolution binary mask to a higher resolution (0.2 arcmin), and remove all pixels containing objects flagged by the bright object mask.
+We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
+      \item We downgrade the resulting mask back to the original resolution through an averaging procedure, producing a map quantifying the observed fraction of each pixel.
+    \end{enumerate}
+    It is worth noting that the resolution of the resulting mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis.
+After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.
+
+    This defines our fiducial masks, which are shown in Figure \ref{fig:masks} for each field.
+As part of our systematics analysis (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
+It is worth noting that the NOMAD star catalog \cite{2004AAS...205.4815Z}, one of the datasets used to construct the brigh-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
+To study the impact of this contamination on our clustering measurements, we have also estimated the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).
+
+  \subsection{Systematics maps}\label{ssec:methods.syst}
+    \begin{figure}
+      \centering
+      \includegraphics[width=0.49\textwidth]{figures/syst_seeing_g.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_seeing_i.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_seeing_y.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_airmass_y.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_skylevel_i.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_depth.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_dust.pdf}
+      \includegraphics[width=0.49\textwidth]{figures/syst_star.pdf}
+      \caption{Maps of different observational systematics that could cause an artificial modulation in the inferred galaxy overdensity.
+The maps correspond to the XMMLSS field, and were obtained as described in Section \ref{ssec:methods.syst}.
+From top to bottom and left to right, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density.
+We can visually appreciate the existing correlations between differnt systematics (e.g.
+seeing and airmass), which are automatically taken into account by the deprojection method described in Section \ref{ssec:methods.cell} and in \cite{2019MNRAS.484.4127A}.}
+      \label{fig:sysmap}
+    \end{figure}
+    A number of astrophysical and observational systematic effects can affect the observed distribution of galaxies, and therefore may bias our inference of their clustering properties.
+To mitigate this effect we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}.
+We generate maps of the most plausible sources of systematic variations in the galaxy number density:
+    \begin{enumerate}
+      \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth in different directions using a method similar to that outlined in \cite{2018PASJ...70S..25M}.
+In a given sky pixel, we collect all galaxies with $i$-band {\tt cmodel} fluxes measured with a signal-to-noise ratio between 9 and 11 (i.e.
+$9\le{\tt icmodel\_flux}/{\tt icmodel\_flux\_err}\le11$), and compute the mean of their $i$-band  {\tt cmodel} magnitude.
+We verified that we obtain similar depth estimates using other methods (e.g.
+magnitude corresponding to $10$ times the mean flux error), and that the magnitude limit of our sample ($i<24.5$) is bright enough that little or no area is lost in any of the fields by imposing this cut.
+      \item {\bf Dust extinction}: we make maps of dust absorption in each band using the data from \cite{1998ApJ...500..525S} projected onto the 6 HSC DR1 fields.
+      \item {\bf Star contamination}: we produce a map of the number density of stars using all objects passing our sample cuts but classified as stars by the star-galaxy separator.
+As described in Section \ref{ssec:methods.cell}, the method used to remove the impact of this systematic is slightly different from the rest.
+      \item {\bf Observing conditions}: the HSC DR1 provides metadata for each filter exposure, containing information about a number of observing conditions.
+We make coadded maps of these following a procedure similar to that described in \cite{2016ApJS..226...24L}.
+For each pixel in our map we gather all exposures that fully or partially overlap with it.
+For each quantity $Q$ in filter $f$, this allows us to build a list of values of $Q$ for each exposure\footnote{It is worth noting that we omit any exposure from CCD 9, since it was found to yield unreliable measurements and was never used in the HSC coadd images.}.
+We then compute the weighted mean of these values and assign the result to the pixel.
+The weights used to coadd different exposures consist of the product of the area overlap between pixel and exposure and an approximation of the weights used by the HSC pipeline to produce coadded images \cite{2018PASJ...70S...5B}.
+Since we do not have direct access to the latter, we used, as coadd weights, the inverse of the sky level of each exposure, which should be close to inverse-variance weighting.
+Following this procedure we produce maps of the following quantities: airmass, CCD temperature, seeing, point-spread function (PSF) ellipticity, exposure time, sky count level, root-mean square deviation of the sky count and number of visits.
+    \end{enumerate}
+    Figure \ref{fig:sysmap} shows examples of some of these maps.
+
+    Note that an underlying assumption of this step is that the coadded mean of different exposures fully captures the connection between fluctuations in observing conditions and the artificial fluctuations they cause on the number counts.
+In general we could also consider other cumulants of the per-exposure distribution of observing condition values.
+As shown below, we do not observe an important contamination from these systematics in our results, and we therefore leave this more thorough study for future work.
+
+  \subsection{Redshift distributions}\label{ssec:methods.nz}
+    \begin{figure}
+      \centering
+      \includegraphics[width=0.9\textwidth]{figures/nzs.pdf}
+      \caption{Redshift distributions used in this analysis.
+The histograms in each panel are the same, and correspond to the redshift distributions estimated from the COSMOS 30-band catalog.
+These are the fiducial redshift distributions used in our analysis.
+The solid curves in each panel show the stacked redshift distribution inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt Franken-Z} from left to right and top to bottom).
+The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in red, blue orange and green respectively.
+Note that all four redshift estimation codes use the same COSMOS 30-band catalog so the level of visual agreement should not be taken as realistic measure of uncertainty on the redshift distributions.}
+      \label{fig:nzs}
+    \end{figure}
+    The underlying redshift distributions of our tomographic samples ($p^i(z)$ in Eq.
+\ref{eq:cell_gg_limber}) are a central component of the theory model used to infer astrophysical and cosmological parameters.
+Estimating redshift distributions for photometric samples is a non-trivial problem that has been studied extensively in the literature \citep{2008MNRAS.390..118L,2008ApJ...684...88N,2018MNRAS.478..592H}.
+We use two different methods to estimate $p^i(z)$.
+
+    To estimate the fiducial redshift distributions used in our main analysis we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
+The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histogramming these redshifts with appropriate weights.
+These weights are calculated following the procedure described in \cite{2017MNRAS.465.1454H,2019PASJ...71...43H}, which we summarize here for completeness:
+    \begin{enumerate}
+      \item We first cross-match all objects in the COSMOS 30-band catalog with sources in the HSC COSMOS field that satisfy our sample cuts (see Section \ref{sec:data}).
+Matches are found as pairs of objects with an angular separation smaller than 1 arcsecond.
+All unmached objects in either catalog are discarded.
+      \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbours in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
+We record the distance in this space to the furthest neighbour.
+      \item We then compute the number of HSC sources $N_{\rm neigh}^{\rm HSC}$ found within the same radius in magnitude space.
+The weight applied to the COSMOS 30-band object is then given by the ratio $N^{\rm HSC}_{\rm neigh}/N^{\rm COSMOS}_{\rm neigh}$ normalized by the total number of objects in each sample.
+    \end{enumerate}
+    There are a number of caveats associated with this method to estimate redshift distributions.
+First, the COSMOS 30-band photometric redshifts are not as good as a purely spectroscopic sample in terms of redshift accuracy and precision.
+Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the colour-redshift relation has an environmental dependence.
+Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
+
+    In order to study the dependence of our results on the method used to estimate the redshift distributions, we have also produced alternative estimates through a stacking approach.
+In this case, for a given photo-$z$ code, we produce an estimate of the redshift distribution of each tomographic bin by adding the photo-$z$ probability distributions of all objects in that bin.
+Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt demp}, {\tt ephor}, {\tt ephor\_ab} and {\tt frankenz} (see \cite{2018PASJ...70S...9T}) \an{HSC gives the pzs from 6 different codes.
+Should we maybe explain here why we only use 4?.} \da{The only reason is that I had a look at the HSC photo-z paper and it seemed like these ones performed best.
+We could say that we use a ``representative sample'' of the best-performing photo-z codes?}.
+The different redshift distributions for all tomographic bins and photo-$z$ methods are shown in Figure \ref{fig:nzs}.
+The different distributions are visually compatible with each other, although it must be noted that this is, to some extent, by construction, given that the different photo-$z$ codes were trained with the same data from the COSMOS 30-band catalog.
+
+  \subsection{Angular power spectra}\label{ssec:methods.cell}
+    We compute angular power spectra using a flat-sky pseudo-$C_\ell$ (PCL) algorithm \citep{2002ApJ...567....2H} as implemented in {\tt NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}.
+The reader is referred to the code's paper \cite{2019MNRAS.484.4127A} for a detailed description of the estimator, but we provide a brief summary here for completeness.
+
+    In the absence of a sky mask, the flat-sky auto-power spectrum could be simply estimated Fourier transforming a given map $a_{\bf l}={\rm FT}[a(\nv),{\bf l}]$ (where ${\rm FT}$ denotes a Fourier transform operation, and ${\bf l}$ is a 2D wavenumber), and averaging its modulus squared over bins of $\ell\equiv|{\bf l}|$.
+In any practical situation, however, it will be desirable to apply weights on the map to e.g.
+downweight noisy areas or altogether remove pixels that haven't been observed.
+In this case the observed (``masked'') map is $\tilde{a}(\nv)=w(\nv)a(\nv)$, where $w(\nv)$ is a weight map.
+The Fourier coefficients of the observed map are therefore given by a convolution of the true Fourier coefficients with the Fourier transform of the mask, coupling different ${\bf l}$ modes in the original map.
+The result of using the na\"ive estimator of the power spectrum described above on the masked map is therefore a version of the true underlying power spectrum where different $\ell$s are coupled through the so-called {\sl mode-coupling matrix} $M_{\ell\ell'}$:
+    \begin{equation}
+      \left\langle \tilde{C}^{ab}_\ell \right\rangle = \sum_{\ell'} M_{\ell\ell'}(w_a,w_b)\,C^{ab}_{\ell'}.
+    \end{equation}
+    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$, and $C^{ab}_\ell$ is the true power spectrum.
+As explicitly written above, the mode-coupling matrix depends exclusively on the properties of the survey masks \citep{2002ApJ...567....2H}, and not on the underlying signal maps.
+The PCL algorithm calculates the mode-coupling matrix analytically using the properties of the weight maps, and uses it to obtain an unbiased estimate of $C^{ab}_\ell$.
+
+    The overdensity maps used are constructed as $\delta_{g,p}=N_p/(\bar{N}\,w_p)-1$, where $N_p$ is the number of sources in pixel $p$, $w_p$ is the survey mask described in Section \ref{ssec:methods.mask}, quantifying the unmasked area fraction in each pixel, and $\bar{N}$ is the mean number of sources per pixel, estimated as $\bar{N}=\sum_p N_p/\sum_p w_p$.
+
+    An important aspect of power spectrum estimation that is particularly relevant for galaxy clustering studies is accounting for the effect of sky contaminants on the final summary statistic.
+In this analysis we have done so using a technique called ``template deprojection''.
+We start by compiling a list of maps of quantities that can potentially cause artificial perturbations in the observed number density of sources.
+These include all the quantities described in Section \ref{ssec:methods.syst}.
+
+    For small levels of contamination, we can start by assuming that these contaminants affect the observed galaxy overdensity at a linear level:
+    \begin{equation}\label{eq:deproj1}
+      \delta_g^{\rm obs}(\nv) = \delta_g^{\rm true}(\nv) + A_{\rm syst}\,\Delta_{\rm syst}(\nv),
+    \end{equation}
+    where $\Delta_{\rm syst}$ is a template map of the fluctuation of a given contaminant around its mean across the survey footprint, and $A_{\rm syst}$ is an unknown linear factor.
+Template deprojection methods avoid systematic biases by removing all modes from the observed maps that are common to any of the systematic template maps, effectively projecting the input map onto the subspace that is orthogonal to all the contaminant templates.
+This is equivalent to building a Gaussian model for the observed map using Equation \ref{eq:deproj1} and marginalizing over the free amplitude $A_{\rm sys}$.
+In the context of pseudo-$C_\ell$ estimators this is achieved in practice by obtaining the best-fit value of $A_{\rm syst}$, subtracting the corresponding best-fit contaminant contribution from the maps and analytically accounting for the associated loss of modes when computing the angular power spectrum.
+Further details of this method can be found in \cite{2017MNRAS.465.1847E,2019MNRAS.484.4127A}.
+
+    We must note that star contamination is a special type of contaminant, since it is an additive contribution to the observed galaxy number density $n_g$, not its overdensity.
+In the simplest scenario, a fraction $f$ of stars contribute to the observed galaxy density: $n_g^{\rm obs}=n^{\rm true}_g+f\,n_s$, where $n_s$ is the local number density of stars.
+A fluctuation in the star density around the mean $\Delta_s(\nv)=n_s(\nv)/\bar{n}_s-1$, therefore produces both a multiplicative and an additive effect on $\delta_g$:
+    \begin{equation}
+      \delta_g^{\rm obs}(\nv) = (1-F_s)\,\delta_g^{\rm true}(\nv)+F_s\,\Delta_s(\nv),
+    \end{equation}
+    where $F_s$ is the fraction of the sample made out of stars (i.e.
+$F_s\equiv f\bar{n}_s/(\bar{n}_g+f\bar{n}_s)$ with the notation above).
+The linear term is taken care of by the deprojection procedure, and we correct the final map of $\delta_g$ by a factor $1/(1-F_s)$, where we estimate $F_s\simeq0.02$ independent of redshift from the HSC deep COSMOS field.
+This estimate is consistent with the star contamination found in the HSC DR1 shape catalog \citep{2018PASJ...70S..25M}.
+
+    As noted above, the power spectra are computed in rings of $\ell=|{\bf l}|$, which we will call bandpowers here.
+We use 17 contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 158800).
+Due to this bandpower averaging, the estimated power spectra cannot, strictly speaking, be compared with theoretical predictions estimated at token multipoles (e.g.
+the midpoint of each band).
+The effect of this averaging can however be taken into account exactly as a linear operation of the form $\bar{C}_b=\sum_\ell F^b_{\ell} C_\ell$, where $C_\ell$ is the theoretical prediction evaluated at all integer multipoles $\ell$, $\bar{C}_b$ is the prediction for the $b$-th bandpower and the bandpower windows $F^b_{\ell}$ incorporate the effects of mode-coupling, averaging into bandpowers and the inversion of the binned mode-coupling matrix.
+
+    Finally, a noise bias term must be subtracted from all auto-power spectra.
+In the case of galaxy clustering, and assuming this noise is entirely due to Poisson shot noise, this can be done analytically as described in \cite{2019MNRAS.484.4127A}.
+In short, the noise power spectrum before mode-decoupling (i.e.
+before multiplying by the inverse mode-coupling matrix), can be calculated as:
+    \begin{equation}\label{eq:nell}
+      \tilde{N}_\ell = \Omega_{\rm pix}\,\frac{\bar{w}}{\bar{N}},
+    \end{equation}
+    where $\bar{w}$ is the mean value of the survey mask across the map, $\bar{N}$ is the mean number density of sources per pixel, and $\Omega_{\rm pix}$ is the pixel area in units of steradians.
+
+  \subsection{Modelling the signal}\label{ssec:methods.theory}
+  \subsubsection{Projected quantities and power spectra}\label{sssec:methods.theory.cellpk}
+    Our main observable is the projected overdensity of galaxies $\delta^i_g(\nv)$ as a function of sky position $\nv$ in a given redshift bin labelled by $i$.
+This is related to the 3D galaxy overdensity $\Delta_g$ through
+    \begin{equation}
+      \delta^i_g(\nv)=\int \mathrm{d}z\,p^i(z)\,\Delta_g\left(t(z),\chi(z)\nv\right).
+    \end{equation}
+    Here $t(z)$ and $\chi(z)$ are the cosmic time and radial comoving distance as a function of redshift, and $p^i(z)$ is the redshift bin window function, given by the true redshift distribution of objects in the bin normalized to unit area.
+
+    Given the small size of the sky patches covered by the HSC DR1, we will adopt the flat sky approximation for simplicity, in which case $\nv$ is a 2D vector.
+It is common to decompose $\delta^i_g(\nv)$ into its Fourier coefficients
+    \begin{equation}
+      a^i_{\bf l}\equiv \int\frac{\mathrm{d}\theta^2}{2\pi}e^{-i{\bf l}\cdot\nv}\delta^i_g(\nv).
+    \end{equation}
+    The variance of the Fourier coefficients is the so-called angular power spectrum $\langle a^i_{\bf l}a^{j*}_{{\bf l}'}\rangle = C^{ij}_\ell\,\delta^{\cal D}({\bf l}-{\bf l}')$, where $\delta^{\cal D}$ is the 2D Dirac delta function.
+The 3D power spectrum $P_{gg}(z,{\bf k})$ is defined analogously for the 3D Fourier coefficients of $\Delta_g$.
+Both quantities are related to each other through:
+    \begin{equation}\label{eq:cell_gg_limber}
+      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)} p^i(z)p^j(z)\,P_{gg}\left(z,k=\frac{\ell+1/2}{\chi(z)}\right),
+    \end{equation}
+    where $H(z)$ is the expansion rate at redshift $z$, and we have used the so-called Limber approximation\footnote{We note that we have compared the power spectra for the redshift distributions employed in this work obtained with the Limber approximation and those obtained making no approximations.
+We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}.
+
+  \subsubsection{Halo Occupation Distribution}\label{sssec:methods.theory.hod}
+    In order to model $P_{gg}(z,k)$ we use a halo occupation distribution (HOD) model \citep{2000MNRAS.318.1144P,2002PhR...372....1C,2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}.
+In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass.
+Details about HOD parametrizations can be found in \cite{2011ApJ...736...59Z}.
+In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
+    \begin{equation}
+      P_{gg}(z,k) = P_{gg,{\rm 1h}}(z,k) + P_{gg,{\rm 2h}}(z,k),
+    \end{equation}
+    where
+    \begin{align}
+      & P_{gg,{\rm 1h}}(k)=\frac{1}{\bar{n}_g^2} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} \bar{N}_c\,\left[\bar{N}_s^2u_s^2(k)+2\bar{N}_su_s^2(k)\right],\\
+      & P_{gg,{\rm 2h}}(k)=\left(\frac{1}{\bar{n}_g} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\,b_h(M)\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right]\right)^2\,P_{\rm lin}(k).
+    \end{align}
+    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ and $\bar{N}_s(M)$ are the mean number of central and satellite galaxies respectively, $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
+    \begin{equation}
+      \bar{n}_g=\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\bar{N}_c(M)\left[1+\bar{N}_s(M)\right].
+    \end{equation}
+    A central assumption in standard HOD parametrizations is that centrals/satellites follow a binomial/Poisson distribution.
+
+    Following \cite{2011ApJ...736...59Z}, we parametrise the number of centrals and satellites as a function of mass as:
+    \begin{align}
+      &\bar{N}_c(M)=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{{\rm ln}M}}\right)\right],\\
+      &\bar{N}_s(M)=\Theta(M-M_0)\left(\frac{M-M_0}{M_1'}\right)^\alpha,
+    \end{align}
+    where $\Theta(x)$ is the Heavyside step function.
+Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$.
+Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by:
+    \begin{equation}
+      u_s(k|M)=\frac{\sin x\left[{\rm Si}\left((1+c)\,x\right)-{\rm Si}(x)\right]+\cos x\left[{\rm Ci}\left((1+c)x\right)-{\rm Ci}(x)\right]-\frac{\sin(cx)}{(1+c)x}}{{\rm ln}(1+c)-\frac{c}{1+c}},
+    \end{equation}
+    where $x=\sfrac{k R_\Delta}{c}$, $R_\Delta$ is the halo radius, $c=c(M)$ is the concentration parameter, and ${\rm Si}/{\rm Ci}$ are the sine and cosine integral functions.
+We define $R_\Delta$ as the radius that encloses $\Delta=200$ times the background matter density.
+The concentration-mass relation $c(M)$ also depends on the choice of $\Delta$, and we follow the parametrization of \cite{Duffy:2008}.
+In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}.
+Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
+
+    In order to include lensing magnification in the theory prediction (see Section \ref{ssec:results.magnification}), we also need to model the galaxy-matter and matter-matter power spectra (see Eq.
+\ref{eq:cell_gg_wmag}).
+Following the HOD parametrization, the 1-halo and 2-halo contributions to $P_{gm}(k)$ are given by:
+    \begin{align}
+      & P_{gm,{\rm 1h}}(k)=\frac{1}{\bar{n}_g\bar{\rho}_M} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} M\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right],\\
+      & P_{gm,{\rm 2h}}(k)=\left(\frac{1}{\bar{n}_g} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\,b_h(M)\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right]\right)\,P_{\rm lin}(k),
+    \end{align}
+    where $\bar{\rho}_M$ is the comoving matter density. $P_{mm}(k)$ is given by the {\tt Halofit} fitting function \cite{Smith:2003} with the revisions of \cite{Takahashi:2012}.
+
+    It is a well-known fact that the simple halo model implementation described here is not able to accurately describe the ``quasi-linear'' scales in the transition between the 1-halo and 2-halo-dominated regimes, corresponding to $k\sim0.1\,{\rm Mpc}^{-1}$ at $z\sim0$ \citep{2015MNRAS.454.1958M}.
+To correct for this inaccuracy, we multiply $P_{gg}$ and $P_{gm}$ by a universal scale-dependent factor, given by the ratio between the {\tt Halofit} and the pure halo model predictions for $P_{mm}$:
+    \begin{equation}
+      R(z,k)=\frac{P^{\rm Halofit}_{mm}(z,k)}{P^{\rm halo\,model}_{mm}(z,k)},
+    \end{equation}
+ which we compute for our fiducial cosmological model given in Sec.~\ref{ssec:methods.constr}.
+
+    We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis.
+Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$ and choose a functional form given by:
+    \begin{equation}
+      M_{i}(z) = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
+    \end{equation}
+    where $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
+This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$.
+We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.
+
+\subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
+
+Uncertainties in photometric redshifts (photo-$z$) represent one of the major systematics in photometric galaxy clustering analyses.
+To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
+In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
+\begin{equation}
+p_{i}(z) = \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
+\label{eq:photo-z-model}
+\end{equation} 
+where the index $i$ runs over the number of redshift bins considered in our analysis.
+In the above equation, $\hat{p}(z)$ denotes the estimated redshift distribution while $p(z)$ is the underlying true distribution.
+The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$.
+The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}(z)$ attains its maximal value.
+
+  \subsubsection{Covariance matrices}\label{sssec:methods.theory.covar}
+    We use an analytical procedure to estimate the uncertainties of our measured power spectra, inspired in the methods used by \cite{Krause:2017}.
+As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labelled SSC here).
+The SSC contribution accounts for the coherent shift in the amplitude of density fluctuations within the surveyed volume caused by long wavelength modes larger than the survey.
+
+    We estimate the Gaussian covariance of the pseudo-$C_\ell$ estimator as described in \cite{2004MNRAS.349..603E,2019arXiv190611765G}.
+In the absence of any approximations, the covariance of the observed power spectra is given by
+    \begin{equation}
+      {\rm Cov}\left(\tilde{C}^{ab}_\ell,\tilde{C}^{cd}_{\ell'}\right)=\sum_{{\bf l}_1,{\bf l}_2} C^{ac}_{\ell_1}C^{bd}_{\ell_2}W^a_{{\bf l}{\bf l}_1}W^b_{{\bf l}{\bf l}_2}W^c_{{\bf l}'{\bf l}_1}W^d_{{\bf l}'{\bf l}_2} + C^{ad}_{\ell_1}C^{bc}_{\ell_2}W^a_{{\bf l}{\bf l}_1}W^b_{{\bf l}{\bf l}_2}W^c_{{\bf l}'{\bf l}_2}W^d_{{\bf l}'{\bf l}_1},
+    \end{equation}
+    where $W^x_{{\bf l}{\bf l}'}$ are coupling coefficients depending only on the mask of $x$ (see \cite{2019arXiv190611765G} for further details).
+In the absence of further approximations, computing the covariance matrix would therefore imply solving a 4-dimensional integral for each pair $(\ell,\ell')$.
+This is an $O(\ell_{\rm max}^6)$ operation which easily becomes computationally unfeasible.
+Since the coupling coefficients $W^x_{{\bf l}{\bf l}'}$ are usually highly peaked around ${\bf l}={\bf l}'$, we can proceed further by approximating the power spectra to be constant within the support of $W^x_{{\bf l},{\bf l}'}$.
+Effectively this implies approximating
+    \begin{equation}
+      C^{ac}_{\ell_1}C^{bd}_{\ell_2}\simeq C^{ac}_{(\ell}C^{bd}_{\ell')}\equiv\frac{1}{2}\left(C^{ac}_\ell C^{bd}_{\ell'}+C^{ac}_{\ell'} C^{bd}_\ell\right).
+    \end{equation}
+    This allows us to simplify the expression above significantly, leading to
+    \begin{equation}
+      {\rm Cov}\left(\tilde{C}^{ab}_\ell,\tilde{C}^{cd}_{\ell'}\right)=(2\ell'+1)^{-1}\left[C^{ac}_{(\ell}C^{bd}_{\ell')}M_{\ell\ell'}(w_aw_c,w_bw_d)+C^{ad}_{(\ell}C^{bc}_{\ell')}M_{\ell\ell'}(w_aw_d,w_bw_c)\right].
+    \end{equation}
+
+    Where $M_{\ell\ell'}$ are the mode-coupling matrices described in the previous section, except now they are computed from the products of two masks.
+It has been shown by \cite{2019arXiv190611765G} that this approach yields a very good approximation for the power spectrum covariance, fully accounting for the effects of mode coupling due to survey geometry.
+
+    The second contribution to the total covariance matrix for galaxy clustering is caused by the connected part of the trispectrum, which accounts for mode-coupling due to the non-Gaussian nature of the density field.
+In our work we estimate this contribution using the halo model coupled with a halo occupation distribution.
+In general, this contribution is given by the angular projection of the three-dimensional trispectrum as (see e.g.
+\cite{Krause:2017}) \todo{Also, you need to define the $q$s.}
+    \begin{equation}
+    \begin{aligned}
+      \mathrm{Cov}_{\mathrm{NG}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) = \frac{1}{4 \pi f_{\mathrm{sky}}} \int_{\vert \boldsymbol{\ell} \vert \in \ell_{1}} \int_{\vert \boldsymbol{\ell}' \vert \in \ell_{2}} \int \frac{\mathrm{d}^{2}\boldsymbol{\ell}}{A(\ell_{1})} \; \frac{\mathrm{d}^{2}\boldsymbol{\ell}'}{A(\ell_{2})} \; \mathrm{d}\chi \; \frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{6}} \times \\ T^{abcd}(\sfrac{\boldsymbol{\ell}}{\chi}, \sfrac{-\boldsymbol{\ell}}{\chi}, \sfrac{\boldsymbol{\ell}'}{\chi}, \sfrac{-\boldsymbol{\ell}'}{\chi}).
+    \end{aligned}
+    \end{equation}
+    The quantity $A(\ell_{i})$ denotes the area of an annulus of width $\Delta \ell_{i}$ around $\ell_{i}$, i.e.
+$A(\ell_{i}) = \int_{\vert \boldsymbol{\ell} \vert \in \ell_{i}} \mathrm{d}^{2}\boldsymbol{\ell}$, which is approximately given by $A(\ell_{i}) \approx 2 \pi \Delta \ell_{i} \ell_{i}$ for $\ell_{i} \gg \Delta \ell_{i}$.
+
+    Using the halo model, the connected part of the trispectrum $T^{abcd}$ is given by (e.g. \cite{Takada:2013}):
+    \begin{equation}
+      T^{abcd} = T^{abcd, 1h} + (T^{abcd, 2h}_{22} + T^{abcd, 2h}_{13}) + T^{abcd, 3h} + T^{abcd, 4h},
+    \end{equation}
+    where
+    \begin{align}
+      &T^{abcd, 1h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = I^{0}_{abcd}(k_{a}, k_{b}, k_{c}, k_{d}), \\
+      &T^{abcd, 2h}_{22}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = P_{\mathrm{lin}}(k_{ab})I^{1}_{ab}(k_{a}, k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 2 \; \mathrm{perm.}, \\
+      &T^{abcd, 2h}_{13}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = P_{\mathrm{lin}}(k_{a})I^{1}_{a}(k_{a})I^{1}_{bcd}(k_{b}, k_{b}, k_{c}) + 3 \; \mathrm{perm.}, \\
+      &T^{abcd, 3h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = B^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{cd})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 5 \; \mathrm{perm.}, \\
+      &T^{abcd, 4h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = T^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{c}(k_{c})I^{1}_{d}(k_{d}).
+    \label{eq:halo-mod-trisp}
+    \end{align}
+    Here, ${\bf k}_{ab}\equiv {\bf k}_a+{\bf k}_b$, and the quantities $B^{\mathrm{PT}}$ and $T^{\mathrm{PT}}$ denote the matter bi- and trispectrum respectively, as estimated using tree-level perturbation theory.
+The full expressions for these terms can be found in \cite{Takada:2013}.
+Finally, $I^{n}_{a_1...b_m}$ denotes the generic halo model integral, defined as (e.g.
+\cite{Krause:2017}):
+    \begin{align}
+      I^{n}_{a_1...a_m}(k_1,...,k_m) &= \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
+    \end{align}
+    where $b_{h,1}(M)\equiv b_h(M)$ is the halo bias, $b_{h,0}\equiv1$, and $\tilde{u}_{a_i}$ is the halo profile for the $i$-th field being correlated (e.g.
+the HOD profile described in Section \ref{sssec:methods.theory.hod} in the case of galaxy clustering).
+For simplicity, we follow \cite{Krause:2017} and approximate the 2- to 4-halo trispectrum as the linearily biased matter trispectrum and only include a probe-specific 1-halo trispectrum contribution.
+Specifically, we set
+    \begin{equation}
+      T^{abcd} = T^{abcd, 1h} + b_{a}b_{b}b_{c}b_{d}T^{m, 2h+3h+4h},
+    \end{equation}
+where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Eq.~\ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling.
+\todo{Also, do you want to say anything about shot noise terms?}
+
+    Finally, we compute the super-sample covariance contribution following the treatment of \todo{cite}:
+    \begin{align}
+       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) = \int & \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
+    \end{align}
+    The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the matter power spectrum to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as\footnote{We note that we also consider an alternative SSC model, in which we estimate the response of the matter power spectrum as the linearly biased response for the matter field.
+We find our parameter constraints to be unaffected by this change.} (e.g.
+\cite{Krause:2017}):
+    \begin{align}
+      \frac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} &= \left( \frac{68}{21} - \frac{1}{3}\frac{\mathrm{d}\log{k^{3} P_{\mathrm{lin}}}(k, z)}{\mathrm{d}\log k} \right) I_{a}^{1}(k)I_{b}^{1}(k)P_{\mathrm{lin}}(k, z) + I_{ab}^{1}(k, k) \\ &- (b_{a} + b_{b})P_{ab}(k, z).
+    \label{eq:ps-resp}  
+    \end{align}
+    The last term in the above equation accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
+In addition, the quantity $b_{a}$ denotes the large-scale HOD bias for the $a$-th sample, computed as
+    \begin{equation}
+      b_{a}=\frac{1}{\bar{n}_{g, a}}\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}b_{h}(M) \bar{N}_{c, a}(1+\bar{N}_{s, a}),
+    \end{equation}
+    and $\sigma_b^2(z)$ is the variance of the long wavelength mode over the survey footprint, given by
+    \begin{equation}
+      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
+    \end{equation}
+    Finally $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
+    \begin{equation}
+      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
+    \end{equation}
+    where $J_1(x)$ is the cylindrical Bessel function of order 1.
+
+  \subsection{Parameter constraints}\label{ssec:methods.constr}
+    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross power spectra to be Gaussian 
+    \begin{align}
+      \mathscr{L}(D \vert \theta) = \frac{1}{[(2\pi)^{d}\det{\mathsf{C}}]^{\sfrac{1}{2}}} e^{-\frac{1}{2}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})^{\mathrm{T}}\mathsf{C}^{-1}(\mathbf{C}^{\mathrm{obs}}_{\ell}-\mathbf{C}^{\mathrm{theor}}_{\ell})}.
+      \label{eq:likelihood}
+    \end{align}
+    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and is kept constant during parameter estimation \citep{2019OJAp....2E...3K}.
+    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}.
+In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{0}, \allowbreak \, M_{0, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}.
+The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}.
+We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s.
+of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc.
+For all sampled parameters, we assume flat, uniform priors.
+The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}.
+Unless stated otherwise, we fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e.
+$\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).
+
+We fit all power spectra up to a maximal angular multipole $\ell_{\mathrm{max}}$ approximately corresponding to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$, as determined through the Limber relation $k_{\mathrm{max}} = \sfrac{\ell_{\mathrm{max}}}{\chi(z)}$.
+For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
+For the cross correlations, we set $\ell_{\mathrm{max}}$ to the minimal value derived for the respective two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
+
+The analytical covariance matrix $\mathsf{C}$ depends on cosmological and HOD parameters.
+In order to determine a covariance matrix that closely resembles the data, we resort to a two-step process: in a first step, we fit the data using a Gaussian covariance matrix derived from the observed data power spectra.
+We then use the best-fit parameters determined in this analysis to compute the full covariance matrix as described in Sec.~\ref{sssec:methods.theory.covar} and use this updated covariance matrix in all our subsequent analyses.
+
+It is worth noting that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$.
+This prior was estimated as the scatter between the best-fit shift parameters that recover the same shear power spectrum for different estimates of the redshift distribution and different photo-$z$ codes.
+We carried out an additional analysis where we quantified the shift and width parameters allowed by the sample variance uncertainties in our fiducial estimate of the redshift distribution from COSMOS.
+To do so, we estimated the covariance matrix of the redshift distribution amplitudes in each narrow histogram bin shown in Fig.
+\ref{fig:nzs} using a simplified linear bias model.
+From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean), and compute the mean redshift of each realization.
+Estimating the standard deviation in the mean redshift of all realizations, we find that sample variance uncertainty in COSMOS leads to 1-sigma  shifts around $\Delta z\sim0.006$ and fractional widths around $z_w\sim 0.04$.
+We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties.
+It is interesting to note that, having access to the covariance matrix of the redshift distribution would allow us to perform a more general characterization of the $N(z)$ uncertainties, beyond shift-width parametrizations (e.g.
+through principal component analysis).
+We leave this type of study for future work.
+
+    \begin{table*}
+      \caption{Summary of parameters varied in the MCMC with their respective priors.
+The posterior means and best-fits denote the values derived for our fiducial analysis.
+The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
+      \begin{center}
+        \begin{tabular}{cccc}
+          \hline\hline 
+          Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
+          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
+          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
+          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
+          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
+          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
+          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
+          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
+          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
+          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
+          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
+          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
+          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
+          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
+          $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
+          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
+          \hline\hline 
+        \end{tabular}
+      \end{center}
+    \end{table*}
+
+\section{Results}\label{sec:results}
+  \subsection{Power spectra}\label{ssec:results.spectra}
+    \subsubsection{Fiducial measurements}\label{sssec:results.spectra.fid}
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.99\textwidth]{figures/cls_summary.pdf}
+        \caption{Summary plot showing all measured auto- and cross-power spectra.
+The red data points with error bars show the coadded power spectra (see Section \ref{sssec:results.spectra.fid}), with the hollow circles showing the absolute value of negative data.
+The noise and deprojection biases subtracted from the raw power spectra are shown as grey and blue lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
+The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.}
+        \label{fig:cls_summary}
+      \end{figure}
+      We compute all auto- and cross-power spectra between the four different redshift bins (listed in Table \ref{tab:bins_summary}) in each of the 6 HSC DR1 fields (listed in Table \ref{tab:field_summary}) as described in Section \ref{ssec:methods.cell}, including the deprojection of 48 different contaminant templates (9 observing condition maps in each of the 5 HSC filters, a dust map, a star density map and a depth map).
+In order to use these measurements to constrain model parameters, we first coadd them into a single set of spectra.
+We perform this coaddition simply as a weighted average, weighting the spectra in each field by their area:
+      \begin{equation}
+        {\bf C}_{\rm coadd}=\frac{\sum_f A_f\,{\bf C}_f}{\sum_f A_f}, \hspace{12pt}{\sf Cov}_{\rm coadd}=\frac{\sum_f A_f^2\,{\sf Cov}_f}{\left(\sum_f A_f\right)^2}
+      \end{equation}
+      where ${\bf C}$ is a vector containing all power spectra, ${\sf Cov}$ is its covariance matrix, and $f$ runs through the 6 DR1 fields with area $A_f$.
+This procedure should be close to inverse-variance weighting assuming that the power spectrum covariance has a similar structure in all fields.
+The coadded spectra should therefore be close to optimally weighted, with the added advantage that the coaddition does not introduce additional scale dependence due to mode-coupling in the covariance matrix.
+
+      The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as red circles with error bars.
+In all cases we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a grey solid line in the auto-correlations.
+As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection.
+This bias is also shown as a blue solid line in Figure \ref{fig:cls_summary}, where the dashed parts show the absolute value of the bias when it is negative.
+This bias is always at least a factor $\sim5$ smaller than the measured power spectra, and is most relevant on large scales.
+The semi-transparent grey bands in the figure cover the range of scales excluded from our analysis (described in Section \ref{ssec:methods.constr}).
+Unless otherwise stated, in what follows all our results will not include any of these data.
+
+      The rest of this sub-section describes the different tests we have carried out to quantify the robustness of these measurements.
+
+    \subsubsection{Consistency across fields}\label{sssec:results.spectra.consistent}
+      The fact that the HSC DR1 sample is distributed across 6 different disconnected fields allows us to carry out consistency tests of the measurements in individual fields.
+For example, it is reasonable to expect that, if a given undetected systematic is biasing our measurements significantly, its impact would vary across different fields, and would therefore lead to inconsitent power spectrum measurements between them.
+We carry out two basic consistency tests, involving the number density of objects in each field (i.e.
+the one-point function) and the measured power spectra.
+
+      \paragraph{Number densities.} The number density of galaxies estimated in a given field is simply given by the ratio of the number of galaxies and the area of the field:
+      \begin{equation}
+        \hat{\bar{n}}=\frac{\sum_p N_p}{\sum_p \Omega_p}= \bar{n} \frac{\int \mathrm{d}\nv^2\,W(\nv)\left[1+\delta_g(\nv)\right]}{\int \mathrm{d}\nv^2\,W(\nv)},
+      \end{equation}
+      where $p$ runs over all pixels in the map, and $N_p$ and $\Omega_p$ are the number of objects and area of pixel $p$.
+In the second equality we have taken the continuum limit, $\bar{n}$ is the true number density, $\delta_g$ is the galaxy overdensity and $W$ is the field's mask.
+Using the statistics of $\delta_g$ it is straightforward to calculate the variance of the estimated $\hat{\bar n}$:
+      \begin{equation}
+       {\rm Var}(\hat{\bar n})=\int \frac{\mathrm{d}{\bf l}^2}{(2\pi)^2}\left|\frac{W_{\bf l}}{\int d\nv^2\,W(\nv)}\right|^2\,C_\ell.
+      \end{equation}
+      Here ${\bf l}$ is a 2D Fourier-space wave vector, $W_{\bf l}$ is the Fourier transform of the mask and $C_\ell$ is the power spectrum of $\delta_g$\footnote{We verified the validity of this calculation by replacing $C_\ell$ by its shot-noise contribution and recovering the Poisson limit (${\rm Var}_{\rm Poisson}(\hat{\bar n})=\bar{n}/A$, where $A$ is the footprint area).
+We find that the error on $\hat{\bar n}$ is dominated by cosmic variance (as opposed to shot noise) by more than a factor of $\sim5$ in all cases.}.
+Following this procedure we estimate the number density in each field and redshift bin as well as its uncertainty (where we use the mask described in Section \ref{ssec:methods.mask} and the best-fit theory power spectra to compute the latter).
+The results are shown in Figure \ref{fig:ndens_consistency}.
+In all cases we find no significant deviations in the number density found in each field with respect to the mean, with only one estimate out of the 24 (GAMA15H in bin 2) deviating by more than 2 $\sigma$.
+We therefore conclude that there is no evidence of inconsistency between fields on the basis of their number densities.
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.7\textwidth]{figures/ndens_consistency.pdf}
+        \caption{Source number densities estimated in the 6 different fields ($x$-axis) and in the 4 different redshift bins (in each panel, from top to bottom).
+We find no evidence of inconsistency between the number of sources found in each field.}
+        \label{fig:ndens_consistency}
+      \end{figure}
+
+      \paragraph{Power spectra.} Figure \ref{fig:cls_consistency} shows the difference between the power spectra estimated in each field and the coadded power spectra normalized by the power spectrum errors for all auto- and cross-correlations.
+We observe a reasonable scatter with respect to the coadded spectra of up to $\sim3\sigma$, which does not immediately indicate any evidence for inconsistency between fields.
+As a more quantitative check for inconsistencies we carry out a $\chi^2$ analysis of this scatter.
+Let  $\Delta {\bf C}_f={\bf C}_f-{\bf C}_{\rm coadd}$ be the difference between the power spectra measured in field $f$ and the coadded ones.
+Using the notation of Section \ref{sssec:results.spectra.fid}, the covariance of $\Delta {\bf C}_f$ is given by:
+      \begin{equation}
+        {\sf Cov}_{\Delta_f}=\left(1-2\frac{A_f}{\sum_{f'}A_{f'}}\right){\sf Cov}_f+{\sf Cov}_{\rm coadd}.
+      \end{equation}
+      We can therefore quantify the significance of the power spectrum differences by computing the $\chi^2$:
+      \begin{equation}
+        \chi^2\equiv\Delta{\bf C}_f^T\cdot{\sf Cov}_{\Delta_f}^{-1}\cdot\Delta{\bf C}_f,
+      \end{equation}
+      and its probability to exceed (PTE) under the assumption that $\chi^2$ follows a ``chi-squared'' distribution with a number of degrees of freedom given by the size of $\Delta{\bf C}_f$.
+Doing so for all the individual auto- and cross-correlations, as well as for the combined data vector containing all of them simultaneously, we find no quantitative evidence of inconsistency between fields.
+All PTEs are larger than 8\%, with the vast majority of them lying above 30\%.
+We conclude that there is no evidence for systematics from the power spectrum measurements in different fields, and therefore it is safe to coadd them and use the coadded spectra to obtain model constraints.
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.99\textwidth]{figures/cls_consistency.pdf}
+        \caption{Difference between the power spectra measured in each field and the mean coadded spectra normalized by the 1$\sigma$ errors.
+The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.
+We find no inconsistency between the different measurements.}
+        \label{fig:cls_consistency}
+      \end{figure}
+
+    \subsubsection{Robustness to contaminants} \label{sssec:results.spectra.syst}
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.99\textwidth]{figures/cls_systematics.pdf}
+        \caption{Difference with respect to our fiducial power spectra of alternative estimates of the power spectra normalized by their $1\sigma$ errors.
+The red points show the spectra estimated without contaminant deprojection.
+The blue points show spectra estimated using a conservative sky mask that removes highly contaminated regions (see Section \ref{sssec:results.spectra.syst} for details).
+The yellow points show the spectra calculated using the Arcturus bright star mask.}
+        \label{fig:cls_systematics}
+      \end{figure}
+      As described in Section \ref{ssec:methods.cell}, our main strategy to address possible contamination of the measured power by systematics causing artificial density fluctuations is to project out the systematics templates discussed above from the data at the map level.
+This procedure can also be understood as building a linear model for the contamination (see Eq.
+\ref{eq:deproj1}), finding the best-fit linear coefficients for each contaminant and substracting the corresponding contribution from the observed map.
+Finally, the estimated power spectra must be corrected for the loss of modes incurred (blue line in Figure \ref{fig:cls_summary}).
+This method is therefore able to account for any systematic contamination that is well described as a linear contribution.
+Since the impact of any contaminant can always be Taylor-expanded, this treatment is appropriate as long as the level of contamination is sufficiently small.
+In order to verify this, we have carried out two different tests.
+
+      First, we have compared our fiducial power spectra, computed using contaminant deprojection, with power spectra computed without accounting for any type of contamination (i.e.
+estimated directly from the observed galaxy overdensity maps).
+This test allows us to test the worst-case scenario where any source of contamination is completely ignored.
+The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in red in Figure \ref{fig:cls_systematics}.
+In most cases we observe very small differences (smaller than $1\sigma$) between both spectra.
+However, we see that some of the spectra involving the first redshift bin are slightly more sensitive to deprojection, exhibiting differences of up to 3$\sigma$ in the range of scales used in our analysis.
+This suggests that, although the level of contamination in the raw galaxy overdensity maps is small, it is necessary to address it.
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.49\textwidth]{figures/ndens_syst.pdf}
+        \includegraphics[width=0.49\textwidth]{figures/systmask.pdf}
+        \caption{{\sl Left panels:} relation between the galaxy density fluctuation ($y$ axis) and the fluctuation in different systematics ($x$-axis).
+In all cases $R(x)\equiv \sfrac{x}{\bar{x}}$.
+Results are shown for $r$-band airmass (top) and dust absorption (bottom) for the third redshift bin in the VVDS field.
+The data are shown in red, while the solid black line shows the best-fit linear relation between both quantities.
+In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here).
+{\sl Right panels:} the top panel shows our fiducial ``Sirius'' mask, with the additionally masked regions associated with high levels of contamination shown in turquoise.
+The bottom panel shows the alternative ``Arcturus'' bright-star mask.}
+        \label{fig:ndens_syst}
+      \end{figure}
+
+      Second, in order to explore the breakdown of the linear model used in deprojection, we have made a direct study of the relation between galaxy overdensity and the different systematics as follows: for each field and redshift bin we produce a map of the relative galaxy density $R(N_g)\equiv N_g(\nv)/\bar{N}_g$, where $N_g(\nv)$ is the number of galaxies in the pixel with coordinates $\nv$, and $\bar{N}_g$ is the mean number of galaxies per pixel across the map.
+Then, for each of the 48 systematic templates $S$, we create a similar map $R(S)\equiv S(\nv)/\bar{S}$.
+We then use both maps to calculate the mean value of $R(N_g)$ in bins of $R(S)$, estimating the error on this mean via bootstrap.
+Finally, we produce plots of this relation for all fields, bins and systematic maps, finding results such as those displayed in the left panels of Figure \ref{fig:ndens_syst}, which show this relation for bin 3 of the VVDS field for the dust absorption and $r$-band airmass templates (bottom and top panels respectively).
+In most cases we find that the relation between galaxy density and systematic fluctuation is either flat or well approximated by a linear relation, as is the case for dust absorption in the figure.
+In a few cases, however, we find that a linear relation is only appropriate in parts of the range of contaminant values, and that the observed galaxy overdensity grows or decreases much faster for large or small values of $R(S)$.
+In these cases, fitting a linear relation over the whole range of $S$ will lead to some level of contaminant residuals that could induce a significant bias on the estimated power spectra.
+To verify whether this is the case, we list all cases where we find that a linear relation is not appropriate, determine the value of $R(S)$ beyond which we observe a significant increase/decrease in $R(N_g)$ (shown as a vertical dashed line in the top left panel of Figure \ref{fig:ndens_syst} for $r$-band airmass), and mask out the corresponding regions of the map.
+The masked regions correspond to $\sim20\%$ of the available footprint on average, and are shown in the top right panel of Figure \ref{fig:ndens_syst} in turquoise for the VVDS field.
+The blue datapoints in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the power spectra estimated using these more restrictive masks, normalized by their $1\sigma$ errors.
+In the vast majority of cases we see only $<1\sigma$ differences between both spectra.
+Since small differences are to be expected when masking a significant fraction of the observed footprint, we conclude that there is no evidence of contamination in our fiducial power spectra beyond that accounted for by the template deprojection procedure.
+
+      One final possible source of systematic bias is the effect of bright sources, which cause a depletion in the number of observed galaxies around them as described in e.g.
+\cite{2018PASJ...70S...7C}.
+To mitigate this effect we make use of the bright object mask provided with the HSC DR1 (the so-called ``Sirius'' mask) as described in Section \ref{ssec:methods.mask}.
+One possible problem associated with this mask is the fact that it removes regions around both bright stars as well as a small fraction of bright extra-Galactic objects.
+Since the latter will be correlated at some level with some of the sources used in our clustering analysis, it is important to check for a possible bias associated with masking them.
+To do so, and to test our fiducial power spectra against the exact procedure used to produce the bright object mask, we have repeated our measurements making use of the bright star mask published by \cite{2018PASJ...70S...7C} (the so-called ``Arcturus mask).
+The top-right and bottom-right panels of Figure \ref{fig:ndens_syst} show both masks for the VVDS field.
+We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different \todo{we could give some details of what the differences are here}.
+The yellow datapoints in Figure \ref{fig:cls_summary} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
+As before, we do not observe any statistically significant deviation between these spectra.
+We therefore conclude that bright sources do not impact our fiducial power spectra significantly.
+
+    \subsubsection{Shot noise subtraction} \label{sssec:results.spectra.shotnoise}
+      \begin{figure}
+        \centering
+        \includegraphics[width=0.6\textwidth]{figures/shotnoise_avg.pdf}
+        \caption{Comparison between the shot noise power spectra estimated analytically using Eq.
+\ref{eq:nell} (transparent lines) and estimated from the difference-map power spectra (solid lines).
+Results are shown for the four different redshift bins.
+Our analytic estimate agrees well with this alternative method.}
+        \label{fig:shotnoise_avg}
+      \end{figure}
+      As described in Section \ref{ssec:methods.cell}, we subtract the shot-noise contribution to the auto-correlation power spectra using an analytical estimate, given by Eq.
+\ref{eq:nell}.
+Since it has been argued \citep{2013PhRvD..88h3507B} that non-linearities may produce deviations from this simple relation, we verify the validity of our calculation as follows.
+
+      We start by splitting the galaxy sample in each field into two random subsamples with the same number of objects.
+We then construct overdensity maps for each of the galaxy subsamples, which we call $\delta_1$ and $\delta_2$.
+Each of these subsamples can be thought of as an independent Poisson processes that samples the same underlying smooth overdensity field $\delta$.
+I.e.
+$\delta_i = \delta + n_i$, where $n_i$ is the shot-noise contribution in $\delta_i$.
+Therefore, we can estimate the shot-noise power spectrum from the power spectrum of the difference between the two split maps:
+      \begin{align}
+      \left\langle |\delta_1 - \delta_2|^2 \right\rangle & = \langle|n_1|^2\rangle + \langle|n_2|^2\rangle,
+      \end{align}
+      where we have assumed that $n_1$ and $n_2$ are uncorrelated (since our two sub-catalogs are disjoint).
+Since the number density in each of the subsamples is half of the full sample, we can recover an estimate of the latter's shot-noise spectrum by simply dividing the power spectrum of the difference map by $4$.
+Figure \ref{fig:shotnoise_avg} shows the comparison between the analytic estimate in Eq.
+\ref{eq:nell} (transparent lines) and the estimate from the difference map power spectra (solid lines) for the four different redshift bins \todo{what order?}.
+Within the statistical noise of the split-map estimate, both methods agree well, particularly at high $\ell$, validating our procedure to subtract the shot-noise contribution.
+
+\subsection{Covariance matrix}\label{ssec:results.covariance}
+
+We estimate the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}.
+In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions.
+As can be seen, the Gaussian contribution is dominant on large scales while the non-Gaussian part becomes important at small scales and low redshift.
+The high redshift bins are mostly insensitive to non-Gaussian contributions to the covariance.
+Finally, the SSC is subdominant in all cases.
+This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
+\caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
+\label{fig:covmat}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
+\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
+\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
+\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
+\caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
+\label{fig:covariance-contributions}
+\end{center}
+\end{figure}
+
+\subsection{Constraints on HOD parameters}\label{ssec:results.hod-constraints}
+
+\subsubsection{Fiducial constraints}\label{sssec:results.hod-constraints.fiducial}
+
+Both the auto- and cross power spectra shown in Fig.~\ref{fig:cls_summary} carry information on astrophysical, systematics and cosmological parameters.
+We especially expect the cross correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and shifts in the means of the bins.
+In this work, we therefore compute fiducial constraints from a joint fit to both auto- and cross power spectra.
+
+Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
+The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.
+As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}.
+Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
+The corresponding minimum $\chi^{2}$ is $\chi^{2} = 95.8$.
+Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.20$ ($p$-value $= 0.11$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
+\cite{Andrae:2010}).
+However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.
+
+In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}$ and the mass scale for satellites $M_{1}$ obtained in our analysis.
+To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
+As can be seen, we find that the data prefer both a decreasing $M_{\mathrm{min}}$ and $M_{1}$.
+This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times.
+We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+\caption{Fiducial constraints on HOD parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+\label{fig:constraints-fid-hod}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}
+\caption{Measured auto- and cross power spectra considered in our analysis.
+The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra.}
+\label{fig:cls-best-fit}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
+\caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
+\label{fig:hod-params-z-dep}
+\end{center}
+\end{figure}
+
+\subsubsection{Robustness to modeling and data choices}
+
+In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants, as described in the following.
+A summary of all robustness tests performed and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.
+
+\begin{sidewaystable}
+\caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
+The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
+In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$.
+The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
+\begin{center}
+\begin{tabular}{ccccccccc}
+\hline\hline 
+Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
+fiducial & $\sfrac{95.8}{80}$ $(0.11)$ & $2.93\substack{+1.56 \\ -1.47}$ & $12.29 \pm 0.15$ & $6.00\substack{+2.14 \\ -2.05}$ & $13.69 \pm 0.21$ & - & - & - \\
+auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.32\substack{+2.03 \\ -1.79}$ & $12.32 \pm 0.14$ & $6.49\substack{+2.80 \\ -2.47}$ & $13.72\substack{+0.20 \\ -0.19}$  & - & - & - \\
+G cov & $\sfrac{98.4}{80}$ $(0.080)$ & $3.59\substack{+1.52 \\ -1.44}$ & $12.34 \pm 0.14$ & $6.89\substack{+1.96 \\ -1.89}$ & $13.74\substack{+0.19 \\ -0.20}$ & - & - & - \\
+G+SSC cov & $\sfrac{97.8}{80}$ $(0.086)$ & $3.28\substack{+1.57 \\ -1.51}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.46\substack{+2.15 \\ -2.10}$ & $13.71 \pm 0.20$ & - & - & - \\
+no $z_{w, i}$ & $\sfrac{97.8}{84}$ $(0.14)$ & $2.69\substack{+1.17 \\ -1.08}$ & $12.24 \pm 0.09$ & $5.74\substack{+1.95 \\ -1.66}$ & $13.62\substack{+0.14 \\ -0.13}$ & - & - & - \\
+no $z_{w, i}, \Delta z_{i}$ & $\sfrac{102.2}{88}$ $(0.18)$ & $3.23 \pm 0.76$ & $12.27 \pm 0.06$ & $6.43\substack{+1.17 \\ -1.18}$ & $13.65 \pm 0.10$ & - & - & - \\
+bins = 0, 1, 2 & $\sfrac{56.2}{43}$ $(0.085)$ & $2.83\substack{+2.25 \\ -2.11}$ & $12.26\substack{+0.18 \\ -0.19}$ & $5.44\substack{+3.07 \\ -2.93}$ & $13.64\substack{+0.25 \\ -0.26}$ & - & - & - \\
+bins = 1, 2, 3 & $\sfrac{45.8}{46}$ $(0.48)$ & $2.38\substack{+2.32 \\ -2.26}$ & $12.16\substack{+0.25 \\ -0.13}$ & $5.31\substack{+3.17 \\ -3.09}$ & $13.53\substack{+0.32 \\ -0.19}$ & - & - & - \\
+pz = \texttt{Ephor\_AB} & $\sfrac{99.8}{80}$ $(0.066)$ & $2.96\substack{+1.22 \\ -1.12}$ & $12.45 \pm 0.11$ & $6.07\substack{+1.66 \\ -1.54}$ & $13.90 \pm 0.16$ & - & - & - \\
+pz = \texttt{Ephor} & $\sfrac{107.6}{80}$ $(0.022)$ & $3.18\substack{+1.24 \\ -1.27}$ & $12.43 \pm 0.12$ & $6.34\substack{+1.75 \\ -1.77}$ & $13.87 \pm 0.17$ & - & - & - \\
+pz = \texttt{DEmP} & $\sfrac{106.4}{80}$ $(0.026)$ & $2.90\substack{+1.35 \\ -1.33}$ & $12.37 \pm 0.12$ & $5.95\substack{+1.87 \\ -1.83}$ & $13.78 \pm 0.17$ & - & - & - \\
+pz = \texttt{FRANKEN-Z} & $\sfrac{98.6}{80}$ $(0.078)$ & $2.66\substack{+1.17 \\ -1.08}$ & $12.45 \pm 0.11$ & $5.63\substack{+1.61 \\ -1.51}$ & $13.88 \pm 0.16$ & - & - & - \\
+fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
+fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
+fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
+fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
+ \hline \hline
+\end{tabular}
+\end{center}
+\end{sidewaystable}
+
+As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra.
+However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
+In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra.
+Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone.
+As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis.
+Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra.
+As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra.
+To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only.
+As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
+We find $\chi^{2} = 102.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra (see Tab.~\ref{tab:constraints_robustness}).
+This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.
+
+An important part of our data model is the analytical covariance matrix described in Sec.~\ref{sssec:methods.theory.covar}.
+In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian contributions.
+As can be seen from Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}, these constraints agree very well with each other.
+The constraints from the G and the G+SSC case yield almost identical constraints, which is expected due to the suppression of the SSC contribution by the number density correction (c.f.
+Sec.~\ref{ssec:results.covariance}).
+Accounting for all non-Gaussian contributions to the covariance results in slightly broadened but consistent constraints.
+Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra.
+Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data increase as we account for less contributions to the total covariance, as expected.
+However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
+\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+\label{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}
+\end{center}
+\end{figure}
+
+\subsubsection{Robustness to photometric redshift uncertainties}
+
+One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.
+
+In Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we show the constraints on photometric redshift systematics parameters derived in our fiducial analysis.
+We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those.
+We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
+While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.021$ ($68 \%$ c.l.).
+This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.
+
+It is instructive to investigate which part of the data drives the constraints on photometric redshift systematics.
+To this end we compare the constraints obtained using auto power spectra only to those obtained from auto- and cross power spectra (our fiducial case).
+As can be seen from Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we find that the auto power spectra do not constrain the photo-$z$ systematics parameters $\Delta z_{i} - \Delta z_{j}$, as opposed to the combination of auto- and cross power spectra.
+This shows that the cross correlations drive the constraints on photometric redshift systematics and are thus essential for jointly constraining redshift systematics and astrophysical/cosmological parameters from galaxy clustering data.
+
+In order to test the impact of photometric redshift uncertainties on our fiducial HOD constraints, we compare them to those obtained when separately fixing $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$.
+The results are shown in Fig.~\ref{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}.
+As expected, we find that the constraints on HOD parameters successively weaken as we include more freedom in the photo-$z$ error model.
+However, as can be seen both from Fig.~\ref{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts} and Tab.~\ref{tab:constraints_robustness}, the constraints obtained in the three cases agree very well.
+In addition, we find acceptable $\chi^{2}$ values both for the model with $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$.
+This suggests that our fiducial HOD constraints are robust to photo-$z$ uncertainties in the COSMOS 30-band catalog, as parametrized through Eq.~\ref{eq:photo-z-model}.
+
+As described in Sec.~\ref{ssec:methods.nz}, our fiducial constraints use the redshift distributions derived using COSMOS 30-band data \cite{2016ApJS..224...24L}.
+There are several potential caveats associated with this approach.
+First, the   photometric redshift accuracy decreases significantly for objects in the COSMOS 30-band catalog with $z > 1.4$ and second, the fraction of catastrophic outliers at faint magnitudes ($23 \leq$ \texttt{i+} $\leq 25$) is estimated to be around $6-10 \%$ \cite{2016ApJS..224...24L}.
+We expect the highest redshift bin to be mostly affected by decreasing photometric redshift accuracy.
+However, as noted in \cite{Joudaki:2019}, catastrophic outliers that are erroneously assigned to too low redshifts are more likely to fall into our sample than outliers assigned to too high redshifts.
+Therefore, the lowest redshift bin in particular might also be affected by photometric redshift errors \an{not sure this is the reason for which Jeff asked us to remove the low-z bin...}.
+In order to test the robustness of our results to photometric redshift uncertainties at low and high redshifts, we compute parameter constraints separately neglecting the high and low redshift bin and all its cross-correlations.
+The results of these two analyses are shown alongside our fiducial constraints in Fig.~\ref{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}.
+As can be seen, we find all constraints to agree well with each other.
+This suggests that our analysis is robust against photometric redshift uncertainties in the COSMOS 30-band catalog affecting the lowest or highest of our redshift bins.
+
+We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin.
+This secondary peak contains 5\% of galaxies and peaks around $z\sim 2.5$ (hence cannot be seen in Figure \ref{fig:nzs}).
+To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.1$.
+This indicates that the effect of this bump is to small to be statistically significant.
+We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
+\as{Fix numbers once Sarah gets back}
+
+ \begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=auto+cross-vs-fit=auto.pdf}
+\caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained from auto power spectra alone. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+\label{fig:constraints-pz-syst-auto+cross-vs-auto}
+\end{center}
+\end{figure}
+
+ \begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
+\caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+\label{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
+\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+\label{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}
+\end{center}
+\end{figure}
+
+As a last test of robustness against photometric redshift errors, we compare our fiducial constraints to those obtained with the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}, as provided by the HSC Collaboration \cite{2018PASJ...70S...9T}.
+In analogy to our fiducial analysis, we use the photometric redshift error model given in Eq.~\ref{eq:photo-z-model} for each photo-$z$ code.
+The comparison of the constraints on HOD and photo-$z$ systematics parameters obtained for the five different methods are shown in Figures \ref{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}.
+As can be seen, the constraints on HOD parameters from all codes are in very good agreement, while we see some discrepancies between the constraints on photometric redshift systematics parameters, especially between $z_{w, 3}$ and $\Delta z_{3} - \Delta z_{2}$.
+However, these differences are not unexpected as these redshift distributions differ in means and shapes and are therefore not required to give consistent constraints on photo-$z$ systematics parameters.
+
+Even though the photo-$z$ error model given in Eq.~\ref{eq:photo-z-model} leads to consistent constraints on HOD parameters from all photo-$z$ methods considered, there is no guarantee that it is flexible enough to capture all redshift distribution differences important for galaxy clustering statistics.
+We investigate this by comparing the auto power spectra for a fixed HOD model obtained when forcing the five redshift distributions to have approximately the same means and widths.
+We find that the resulting power spectra exhibit significant differences, which suggests that features in the redshift distribution beyond mean and width can significantly impact observed galaxy clustering power spectra.
+In our case, accounting for uncertainties in means and widths gives consistent constraints on HOD parameters and we therefore conclude that this error model is flexible enough to characterize photo-$z$ uncertainties in the present case.
+However, this will probably cease to be true for future photometric clustering analyses (e.g.
+using LSST data) and suggests that these data sets will have to be analyzed accounting for the full uncertainty on the shape of the photometric redshift distributions.
+
+In order to further illustrate the effects of an incomplete photo-$z$ error model, we perform two additional analyses in which we compare the constraints obtained from the five photo-$z$ methods setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$ respectively.
+In the former case we find that the values for the photo-$z$ systematics parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{i} - \Delta z_{j}$ required by the different codes differ significantly, which leads to differences in both constraining power and constraints on HOD parameters.
+We especially find significant shifts in $M_{\mathrm{min}}$ and $M_{1}$ along their degeneracy direction.
+Investigating this further, we find that the observed differences in $\Delta z_{i}$ cannot be explained with the differences in mean redshift between the distributions derived using the five separate methods.
+In addition, we find that for the redshift distributions considered in this analysis, mean shifts mainly affect low redshift auto power spectra but have a significantly smaller impact on high redshift bins.
+Variations in the widths of the photo-$z$ distributions on the other hand, have a similar impact at low and high redshifts.
+This suggests that a photo-$z$ error model accounting only for mean shifts is too simplistic to account for the redshift distribution differences observed in this analysis.
+As borne out by the observed discrepancies in HOD constraints, our analysis is sensitive to these differences and we therefore need to extend the photo-$z$ error model.
+From the discussion above it follows that additionally accounting for variations in the widths of the distributions is sufficient, as this error model yields HOD constraints that are robust to changes in the photo-$z$ estimation method.
+
+The discrepancies between HOD parameters derived from the five different methods become even stronger when we do not account for photo-$z$ uncertainties, as can be seen from Fig.~\ref{fig:constraints-HOD-no-pz-shifts-pz-methods}.
+In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties.
+The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 2.08$ and $\chi^{2}_{\mathrm{red}} = 5.04$.
+This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+\label{fig:constraints-HOD-fit-pz-shifts+pz-widths-pz-methods}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+\label{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}
+\end{center}
+\end{figure}
+
+\subsubsection{Interpretation of HOD results}\label{sssec:results.hod-constraints.constraints-interpretation}
+As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to decrease with redshift.
+In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies considered in our analysis and how these change with redshift.
+However, computing k-corrections and absolute magnitudes for broad-band photometric data can be challenging and we therefore choose an alternative approach.
+We cross-match galaxies passing our selection criteria within the HSC COSMOS field to galaxies also included in the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
+The COSMOS 30-band catalog contains, among others, absolute magnitudes in Subaru \texttt{B}-band, $M_{B}$, and Subaru \texttt{r+}-band, $M_{R}$.
+Using these quantities, we construct color-magnitude diagrams for all cross-matched galaxies.
+Fig.~\ref{fig:color-mag} shows the $M_{B}-M_{R}$ color as a function of $M_{R}$ magnitude for 10 equally spaced redshift bins in $z \in [0.15, 1.5]$\footnote{The galaxies are split into redshift bins according to COSMOS 30-band photometric redshifts.
+We note that we have repeated the analysis splitting the sample according to HSC \texttt{Ephor\_AB} photometric redshifts, finding consistent results.}.
+In this diagram, red galaxies populate the high $M_{B}-M_{R}$ color, high $M_{R}$ magnitude plane, while blue galaxies tend to have lower $M_{B}-M_{R}$ and $M_{R}$.
+As can be seen from the figure, red galaxies increasingly drop-out of the high redshift samples.
+We can quantify this effect by computing the fraction of red galaxies in our sample as a function of redshift: we empirically determine the separation between the blue and red clouds (denoted by the solid lines in the figure) and compute the fraction of galaxies in the red cloud as $f_{R} = \sfrac{N_{R}}{(N_{R}+N_{B})}$, where $N_{R}$ denotes the number of galaxies above the separation line, while $N_{B}$ is the number of galaxies below the line.
+Consistent with the figure, we find decreasing $f_{R}$ as a function of redshift.
+
+These results suggest that red galaxies are increasingly underrepresented with respect to blue galaxies in our sample at higher redshifts.
+This is probably due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$, which translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
+As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed decreasing trend in $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
+This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift})
+
+In Fig.~\ref{fig:HOD-redshift}, we additionally show the large-scale galaxy bias as a function of redshift derived from our best-fit HOD model.
+As can be seen, the large-scale bias scales approximately as $b(z) \sim \sfrac{1}{D(z)}$, where $D(z)$ denotes the linear growth factor.
+This behavior is consistent with e.g.
+studies of galaxies in the DEEP2 survey, which found constant clustering strengths as a function of redshift (and thus $b(z) \sim \sfrac{1}{D(z)}$) for magnitude-limited samples \cite{Coil:2004}.
+\todo{How about saying that a more thorough analysis of the color-dependence of clustering properties would be needed to fully characterize this effect and that we leave this for future work?}
+
+\begin{figure}
+\begin{center}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
+The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
+\label{fig:HOD-redshift}
+\end{center}
+\end{figure}
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[scale=0.55]{figures/color-magnitude_cut=pz_best_eab_nbin=4_weights=True.pdf}
+%\caption{Synopsis of the framework for integrated probe combination employed in this work.}
+%\label{fig:color-mag}
+%\end{center}
+%\end{figure}
+
+      \begin{sidewaysfigure}
+        \begin{center}
+          \includegraphics[width=0.95\textwidth]{figures/color-magnitude_cut=COSMOS30_nbin=10_weights=True.pdf}
+          \caption{Color-magnitude diagrams of COSMOS 30-band galaxies cross-matched to HSC galaxies passing our selection cuts for 10 tomographic redshift bins with $z \in [0.15, 1.5]$.}
+          \label{fig:color-mag}
+        \end{center}
+      \end{sidewaysfigure}
+
+ \subsection{Magnification}\label{ssec:results.magnification}
+
+    In addition to intrinsic correlations between galaxy positions, there exist several additional effects affecting the observed clustering of galaxies.
+One of these is the magnification of distant sources due to gravitational lensing by the intervening LSS, an effect usually called magnification bias (e.g.
+\cite{Schneider:1989, Narayan:1989}).
+The main effect of magnification on the statistical distribution of galaxies is to increase observed galaxy fluxes, thus allowing dim galaxies to pass survey selection thresholds, and to alter their observed angular positions.
+The combined effect, is a position-dependent modulation of the number density that distorts the clustering pattern.
+It has been shown that the clustering signal due to magnification can be comparable to the intrinsic clustering signal for cross-correlations between widely separated redshift bins (see e.g.
+\cite{Challinor:2011}).
+
+    In the presence of magnification, the equations in Section \ref{ssec:methods.theory} get slightly modified. The projected galaxy overdensity becomes:
+    \begin{equation}
+      \delta^i_g(\nv)=\int dz\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
+    \end{equation}
+    where $\Delta_m$ is the 3D matter overdensity (we have omitted the dependence on $t$ and $\chi\nv$ for brevity) and $W_\mu$ is the magnification kernel
+    \begin{equation}
+      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty dz'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
+    \end{equation}
+    Here, $H_0\equiv H(z=0)$, $\Omega_M$ is the cosmological matter fraction, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
+    \begin{equation}
+      s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m},
+      \label{eq:s-func}
+    \end{equation}
+    where $m$ denotes the observed magnitude.
+    The angular power spectrum is then given by:
+    \begin{equation}\label{eq:cell_gg_wmag}
+      C^{ij}_\ell = \int dz\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
+    \end{equation}
+    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=(\ell+1/2)/\chi$ for brevity.
+
+    The magnitude of the magnification signal crucially depends on the derivative of the galaxy number counts with respect to observed magnitude, $s(z)$.
+In order to obtain a data-driven model for magnification in our particular sample, we therefore estimate $s(z)$ from the observed number counts.
+Using linear least squares, we fit a fourth-order polynomial to the logarithm of the observed cumulative apparent $\tt{i}$-band magnitude distribution $N(<m, z)$ in each of the four tomographic redshift bins considered in our analysis.
+We then determine $s(z)$ at the effective redshift of each bin\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.} by taking the derivative of the best-fit function at the magnitude limit of our sample, i.e.
+$m_{i, \mathrm{lim}} = 24.5$.
+In addition to the WIDE HSC galaxy data used in this work, PDR1 also contains data from two deep patches, called DEEP and UDEEP.
+We repeat the above analysis with these galaxy samples to ensure the stability of our results.
+As an example, Fig.~\ref{fig:s-func-estimation} shows the observed number counts as a function of $i$-band magnitude for the lowest redshift bin in the WIDE sample alongside the derived best-fit function.
+In Fig.~\ref{fig:s-func-estimation}, we show the $s(z)$ functions derived as outlined above for HSC WIDE, DEEP and UDEEP.
+As can be seen, the three estimates agree well with each other and we use the $s(z)$ function derived from our fiducial WIDE sample in the following.
+    \begin{figure}
+      \begin{center}
+        \subfigure[Cumulative galaxy number counts as a function of $i$-band magnitude for lowest tomographic redshift bin.]{\includegraphics[width=0.49\textwidth]{figures/mag-dist-cumulative=True+fit-mmin=23-sample=WIDE-bin=0.pdf}}
+        \subfigure[Comparison of $s(z)$ (see Eq.~\ref{eq:s-func}) derived using WIDE, DEEP and UDEEP HSC galaxy samples.]{\includegraphics[width=0.49\textwidth]{figures/s-z-func-samples=WIDE-DEEP-UDEEP.pdf}}
+        \caption{Illustration of data-driven estimation of $s(z)$ for galaxy sample used in our analysis.} 
+        \label{fig:s-func-estimation}
+      \end{center}
+    \end{figure}
+
+    Using the estimated $s(z)$, we can derive theoretical predictions for the angular galaxy power spectra in presence of magnification.
+In order to investigate the sensitivity of the data to magnification we run two different MCMC analyses: in the first case, we fix the magnification amplitude to the predictions from the empirically determined $s(z)$ function.
+In the second case we include an additional magnification parameter $A_{\mu}$ that scales the amplitude of the magnification kernel $W_{\mu}$ and we fit it alongside our fiducial parameter set.
+
+    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 0.99\substack{+0.37 \\ -0.36}$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+This is consistent with our fiducial model for $s(z)$, which corresponds to $A_{\mu} = 1$ and constitutes a $\sim 2.8 \sigma$ detection of magnification from our HSC sample.
+The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 83.8$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 83.4$.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.06$ ($p$-value $= 0.33$).
+This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 95.8 - 83.8 = 12.0$, consistent with the $\sim 3 \sigma$ detection.
+The constraints on HOD parameters obtained when including magnification agree very well with our fiducial constraints, as can be seen from Fig.~\ref{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}.
+In addition, we find the significance of the magnification detection to be largely insensitive to photo-$z$ systematics modeling choices, as it is not significantly affected by relaxing our photo-$z$ systematics model by fixing $z_{w, i} = 0$.
+
+    In order to identify the part of the data vector driving the constraints on $A_{\mu}$, we repeat this analysis only including the auto power spectra.
+The comparison between the constraints on $A_{\mu}$ from auto- and cross power spectra to those obtained from auto power spectra alone in shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+As can be seen, the auto power spectra alone do not constrain $A_{\mu}$, which implies that the constraints on the magnification amplitude are solely driven by the cross power spectra.
+This sensitivity of the cross power spectra to magnification mainly stems from the fact that the intrinsic cross correlations between widely separated bins are small, which leads to an increased sensitivity to any non-intrinsic source of cross correlation, such as magnification.
+In analogy to the results for the photo-$z$ systematics parameters, we thus find that cross power spectra carry important information and it will thus be beneficial to include these cross correlations in current and future photometric clustering analyses.
+
+    \begin{figure}
+      \begin{center}
+        \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
+        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
+      \end{center}
+    \end{figure}
+
+    \begin{figure}
+      \begin{center}
+        \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
+        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
+The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
+        \label{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}
+      \end{center}
+    \end{figure}
+
+  \subsection{Joint cosmology and HOD constraints}\label{ssec:results.cosmo}
+    Finally we also consider jointly fitting cosmological, HOD and photo-$z$ systematics parameters.
+This analysis should be regarded as exploratory and only provide a means to illustrate the potential of photometric galaxy clustering analyses to jointly constrain these parameters.
+An in-depth cosmological analysis would require validation of the analysis and HOD modeling framework on simulations, which is beyond the scope of this work.
+
+    To illustrate the cosmological constraining power of the data considered in our analysis, we allow for variations in the r.m.s.
+of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc, $\sigma_{8}$, and the fractional cold matter density today, $\Omega_{c}$, in addition to our baseline set of parameters (c.f.
+Sec.~\ref{ssec:methods.constr}).
+All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.837\substack{+0.193 \\ -0.211}$ and $\Omega_{c} = 0.228\substack{+0.022 \\ -0.023}$, consistent with our assumed fiducial cosmology.
+The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
+As can be seen from Tab.~\ref{tab:constraints_robustness}, the derived constraints on HOD parameters agree well with our fiducial results, which shows that our HOD constraints are robust to variations in $\Omega_{c}$ and $\sigma_{8}$ as allowed by the data.
+This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
+Therefore, photometric current and future galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
+
+    \begin{figure}
+      \begin{center}
+        \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
+        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \label{fig:constraints-fit=Oc+s8}
+      \end{center}
+    \end{figure}
+
+\section{Discussion and Conclusions}\label{sec:discussion}
+
+This paper has presented a comprehensive analysis of clustering of galaxies from the HSC-SSP DR1 dataset.
+It has demonstrated that despite relatively small area, the quality of the data allow serious scientific analysis leading to new insights both into physics of galaxy formation as well as methodology of clustering analysis.
+
+In terms of physics we show that a simple flux magnitude cut can be used to create useful samples for galaxy clustering analysis.
+This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshift (see e.g.
+\cite{1507.05460,1807.10163}).
+Using magnitude cuts yield more galaxies that decrease the shot noise and thus improve the total statistical sensitivity of the survey despite somewhat lower bias leading to less pronounced clustering.
+In particular, the halo model results in observed galaxies occupying smaller halos toward higher redhifts, but these trends can be well understood by looking at how faint red galaxies drop out from our selection.
+These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts.
+Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and also the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669}.
+\as{should we comment on number density compared to SRD?}
+
+Encouragingly, we find no barriers to estimating clustering using our samples both in auto and cross-correlation.
+The deprojection technique has a small but statistically significant effect, especially on large scales.
+This bodes well for \ldots
 
@@
 
-This is the most common positions for acknowledgments. A macro is
-available to maintain the same layout and spelling of the heading.
+DA acknowledges support from the Beecroft trust and from STFC through
+an Ernest Rutherford Fellowship, grant reference ST/P004474/1.  HA, BA
+and EG have been supported by the Rutgers Discovery Informatics
+Institute Fellowship of Excellence in Computational and Data Science
+(AY 2017-2020) and Rutgers University \& Bevier Dissertation
+Completion Fellowship (AY 2019-2020). HA, AB, and EG were supported by
+the Department of Energy (grants DE-SC0011636 and DE-SC0010008). HA
+also thanks the LSSTC Data Science Fellowship Program, which is funded
+by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation,
+and the Moore Foundation, as participation in the program has
+benefited this work. ZG is supported by a Rhodes Scholarship granted
+by the Rhodes Trust. JAN us supported by grant DOE DE-SC0007914 from
+the U.S. Department of Energy Office of Science (Office of High Energy
+Physics). This manuscript has been authored by Fermi Research
+Alliance, LLC under Contract No. DE-AC02-07CH11359 with the
+U.S. Department of Energy, Office of Science, Office of High Energy
+Physics. The work by JS was supported by the U.S. Department of Energy
+award DE-SC0009920. This project was supported in part by the
+U.S. Department of Energy, Office of Science, Office of Workforce
+Development for Teachers and Scientists (WDTS) under the Science
+Undergraduate Laboratory Internships Program (SULI).
 
-\paragraph{Note added.} This is also a good position for notes added
-after the paper has been written.
+\appendix
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+\caption{Fiducial constraints on HOD and systematics parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+\label{fig:constraints-fid-full}
+\end{center}
+\end{figure}
+
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+%\caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalizing over shifts in the means and setting $z_{w, i} = 0$.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+%\label{fig:constraints-HOD-fit-pz-shifts-pz-methods}
+%\end{center}
+%\end{figure}
+%
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+%\caption{Comparison of the constraints on photo-$z$ systematics parameters obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalizing over shifts in the means and setting $z_{w, i} = 0$.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+%\label{fig:constraints-pz-syst-fit-pz-shifts-pz-methods}
+%\end{center}
+%\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} setting $z_{w, i} = 0, \Delta z_{i} = 0$.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+\label{fig:constraints-HOD-no-pz-shifts-pz-methods}
+\end{center}
+\end{figure}
 

### 2019-10-02 doc/Paper/main.tex
typo

@@
 These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts.
-Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and also the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669}.
+Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
 \as{should we comment on number density compared to SRD?}

### 2019-10-02 doc/Paper/main.tex
Added theoretical predictions including magnification to Fig. 13 and some discussion.

@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}
+\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
 \caption{Measured auto- and cross power spectra considered in our analysis.
-The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra.}
+The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
 \label{fig:cls-best-fit}
@@
 This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 95.8 - 83.8 = 12.0$, consistent with the $\sim 3 \sigma$ detection.
+Fig.~\ref{fig:cls-best-fit} shows the corresponding theoretical predictions derived from the maximum likelihood parameters alongside the observed data.
 The constraints on HOD parameters obtained when including magnification agree very well with our fiducial constraints, as can be seen from Fig.~\ref{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}.

### 2019-10-02 doc/Paper/main.tex
srd comments

--- 2019-10-02 doc/Paper/main.tex
@@
 The red data points with error bars show the coadded power spectra (see Section \ref{sssec:results.spectra.fid}), with the hollow circles showing the absolute value of negative data.
-The noise and deprojection biases subtracted from the raw power spectra are shown as grey and blue lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
+The Poisson noise contribution and deprojection biases subtracted from the raw power spectra are shown as grey and blue lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
 The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.}
@@
 These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts.
-Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and also the LSST forecasting exercises, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669}.
-\as{should we comment on number density compared to SRD?}
+Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
+The same data could also be used to compare the effective number densities.
+In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities.
+We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
 

### 2019-10-03 plot_scripts/plots_cls_consistency.py
regenerated some plots

@@ -7,7 +7,7 @@ prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
 
 def read_cls(field,
              msk_name='sirius',
-             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1'):
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1_newDepth'):
     file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
 
     s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")

### 2019-10-03 plot_scripts/plots_cls_summary.py

@@ -7,7 +7,7 @@ prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
 
 def read_cls(field,
              msk_name='sirius',
-             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj1_DpjBands1'):
+             directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1_newDepth'):
     """Reads all power spectra for a given field"""
     file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
     

### 2019-10-07 doc/Paper/main.tex
Replaced some plots and updated table.

@@
     \begin{table*}
-      \caption{Summary of parameters varied in the MCMC with their respective priors.
+      \caption{\todo{UPDATE} Summary of parameters varied in the MCMC with their respective priors.
 The posterior means and best-fits denote the values derived for our fiducial analysis.
@@
 \includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
-\caption{Measured auto- and cross power spectra considered in our analysis.
+\caption{\todo{UPDATE} Measured auto- and cross power spectra considered in our analysis.
 The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
@@
 \begin{center}
-\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
-\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
 \caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
@@
 \begin{sidewaystable}
-\caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
+\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
 The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
@@
 Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
-fiducial & $\sfrac{95.8}{80}$ $(0.11)$ & $2.93\substack{+1.56 \\ -1.47}$ & $12.29 \pm 0.15$ & $6.00\substack{+2.14 \\ -2.05}$ & $13.69 \pm 0.21$ & - & - & - \\
-auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.32\substack{+2.03 \\ -1.79}$ & $12.32 \pm 0.14$ & $6.49\substack{+2.80 \\ -2.47}$ & $13.72\substack{+0.20 \\ -0.19}$  & - & - & - \\
-G cov & $\sfrac{98.4}{80}$ $(0.080)$ & $3.59\substack{+1.52 \\ -1.44}$ & $12.34 \pm 0.14$ & $6.89\substack{+1.96 \\ -1.89}$ & $13.74\substack{+0.19 \\ -0.20}$ & - & - & - \\
-G+SSC cov & $\sfrac{97.8}{80}$ $(0.086)$ & $3.28\substack{+1.57 \\ -1.51}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.46\substack{+2.15 \\ -2.10}$ & $13.71 \pm 0.20$ & - & - & - \\
-no $z_{w, i}$ & $\sfrac{97.8}{84}$ $(0.14)$ & $2.69\substack{+1.17 \\ -1.08}$ & $12.24 \pm 0.09$ & $5.74\substack{+1.95 \\ -1.66}$ & $13.62\substack{+0.14 \\ -0.13}$ & - & - & - \\
-no $z_{w, i}, \Delta z_{i}$ & $\sfrac{102.2}{88}$ $(0.18)$ & $3.23 \pm 0.76$ & $12.27 \pm 0.06$ & $6.43\substack{+1.17 \\ -1.18}$ & $13.65 \pm 0.10$ & - & - & - \\
-bins = 0, 1, 2 & $\sfrac{56.2}{43}$ $(0.085)$ & $2.83\substack{+2.25 \\ -2.11}$ & $12.26\substack{+0.18 \\ -0.19}$ & $5.44\substack{+3.07 \\ -2.93}$ & $13.64\substack{+0.25 \\ -0.26}$ & - & - & - \\
-bins = 1, 2, 3 & $\sfrac{45.8}{46}$ $(0.48)$ & $2.38\substack{+2.32 \\ -2.26}$ & $12.16\substack{+0.25 \\ -0.13}$ & $5.31\substack{+3.17 \\ -3.09}$ & $13.53\substack{+0.32 \\ -0.19}$ & - & - & - \\
-pz = \texttt{Ephor\_AB} & $\sfrac{99.8}{80}$ $(0.066)$ & $2.96\substack{+1.22 \\ -1.12}$ & $12.45 \pm 0.11$ & $6.07\substack{+1.66 \\ -1.54}$ & $13.90 \pm 0.16$ & - & - & - \\
-pz = \texttt{Ephor} & $\sfrac{107.6}{80}$ $(0.022)$ & $3.18\substack{+1.24 \\ -1.27}$ & $12.43 \pm 0.12$ & $6.34\substack{+1.75 \\ -1.77}$ & $13.87 \pm 0.17$ & - & - & - \\
-pz = \texttt{DEmP} & $\sfrac{106.4}{80}$ $(0.026)$ & $2.90\substack{+1.35 \\ -1.33}$ & $12.37 \pm 0.12$ & $5.95\substack{+1.87 \\ -1.83}$ & $13.78 \pm 0.17$ & - & - & - \\
-pz = \texttt{FRANKEN-Z} & $\sfrac{98.6}{80}$ $(0.078)$ & $2.66\substack{+1.17 \\ -1.08}$ & $12.45 \pm 0.11$ & $5.63\substack{+1.61 \\ -1.51}$ & $13.88 \pm 0.16$ & - & - & - \\
+fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
+auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
+G cov & $\sfrac{84.0}{80}$ $(0.36)$ & $0.361\substack{+3.06 \\ -2.63}$ & $11.89\substack{+0.23 \\ -0.24}$ & $2.01\substack{+3.97 \\ -3.41}$ & $13.09\substack{+0.28 \\ -0.29}$ & - & - & - \\
+G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
+no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
+no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
+bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
+bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
+pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
+pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
+pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
+pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
 fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
 \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
 \caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
 \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}.
@@
 \begin{center}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
 \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
@@
         \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
-        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{\todo{UPDATE} Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
@@
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
-        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
+        \caption{\todo{UPDATE} Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
 The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{\todo{UPDATE} Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} setting $z_{w, i} = 0, \Delta z_{i} = 0$.

### 2019-10-08 doc/Paper/main.tex
More figure updates and changed numbers given in text.

@@
     \begin{table*}
-      \caption{\todo{UPDATE} Summary of parameters varied in the MCMC with their respective priors.
+      \caption{Summary of parameters varied in the MCMC with their respective priors.
 The posterior means and best-fits denote the values derived for our fiducial analysis.
@@
           Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
-          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
-          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
-          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
-          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
-          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
-          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
-          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
-          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
-          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
-          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
-          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
-          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
-          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
-          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
-          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
+          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.89\substack{+0.24 \\ -0.25}$ & $11.76$ \\ 
+          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $-2.95$ \\
+          $M_{0}$ & flat $\in [0., \,15.]$ & $5.85\substack{+4.03 \\ -4.05}$ & $5.58$ \\
+          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.33\substack{+5.12 \\ -4.93}$ & $-0.925$ \\
+          $M_{1}$ & flat $\in [0., \,15.]$ & $13.09\substack{+0.24 \\ -0.25}$ & $12.96$ \\ 
+          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $1.49\substack{+3.21 \\ -3.08}$ & $-2.07$ \\
+          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000147\substack{+0.102 \\ -0.096}$ & $-0.0456$ \\
+          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0128\substack{+0.103 \\ -0.096}$ & $-0.0923$ \\
+          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00170\substack{+0.109 \\ -0.104}$ & $-0.103$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0148\substack{+0.109 \\ -0.106}$ & $-0.0727$ \\
+          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0300\substack{+0.130 \\ -0.119}$ & $-0.177$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.000837\substack{+0.0780 \\ -0.0785}$ & $-0.0991$ \\
+          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0342\substack{+0.0825 \\ -0.0794}$ & $0.0243$ \\
+          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0355\substack{+0.122 \\ -0.138}$ & $0.151$ \\ \\
+          $A_{\mu}$ & flat $\in [-3., \,3.]$ & $ - $ & $ - $ \\
           $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
@@
 Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
-The corresponding minimum $\chi^{2}$ is $\chi^{2} = 95.8$.
-Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.20$ ($p$-value $= 0.11$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
+The corresponding minimum $\chi^{2}$ is $\chi^{2} = 82.0$.
+Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.03$ ($p$-value $= 0.42$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
 \cite{Andrae:2010}).
@@
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
-As can be seen, we find that the data prefer both a decreasing $M_{\mathrm{min}}$ and $M_{1}$.
+As can be seen, we find that, within or uncertainties, the data prefer both a constant $M_{\mathrm{min}}$ and $M_{1}$.
 This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times.
@@
 auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
-G cov & $\sfrac{84.0}{80}$ $(0.36)$ & $0.361\substack{+3.06 \\ -2.63}$ & $11.89\substack{+0.23 \\ -0.24}$ & $2.01\substack{+3.97 \\ -3.41}$ & $13.09\substack{+0.28 \\ -0.29}$ & - & - & - \\
+G cov & $\sfrac{83.4}{80}$ $(0.38)$ & $-0.0602\substack{+2.71 \\ -2.16}$ & $11.91\substack{+0.20 \\ -0.21}$ & $1.46\substack{+3.36 \\ -2.78}$ & $13.10\substack{+0.25 \\ -0.26}$ & - & - & - \\
 G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
@@
 As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
-We find $\chi^{2} = 102.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra (see Tab.~\ref{tab:constraints_robustness}).
+We find $\chi^{2} = 90.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
 This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.
@@
 Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra.
-Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data increase as we account for less contributions to the total covariance, as expected.
+Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we account for less contributions to the total covariance, as expected.
 However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.
@@
 We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
-While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.021$ ($68 \%$ c.l.).
+While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
 This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.
@@
 In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties.
-The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 2.08$ and $\chi^{2}_{\mathrm{red}} = 5.04$.
+The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.88$ and $\chi^{2}_{\mathrm{red}} = 4.88$.
 This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.
@@
 \subsubsection{Interpretation of HOD results}\label{sssec:results.hod-constraints.constraints-interpretation}
-As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to decrease with redshift.
+As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to be redshift independent.
 In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies considered in our analysis and how these change with redshift.
@@
 This is probably due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$, which translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
-As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed decreasing trend in $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
+As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
 This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift})
@@
 \begin{center}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
 \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
@@
     \begin{equation}
-      \delta^i_g(\nv)=\int dz\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
+      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
     \end{equation}
@@
     \begin{equation}
-      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty dz'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
+      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
     \end{equation}
@@
     \begin{equation}\label{eq:cell_gg_wmag}
-      C^{ij}_\ell = \int dz\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
+      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
     \end{equation}

### 2019-10-09 doc/Paper/main.tex
Reverted changes to covariance matrix section.

@@
 
-    Using the halo model, the connected part of the trispectrum $T^{abcd}$ is given by (e.g. \cite{Takada:2013}):
+    Using the halo model, the connected part of the trispectrum $T^{abcd}$ can be written as (e.g. \cite{Takada:2013}):
     \begin{equation}
@@
       &T^{abcd, 2h}_{13}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = P_{\mathrm{lin}}(k_{a})I^{1}_{a}(k_{a})I^{1}_{bcd}(k_{b}, k_{b}, k_{c}) + 3 \; \mathrm{perm.}, \\
-      &T^{abcd, 3h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = B^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{cd})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 5 \; \mathrm{perm.}, \\
+      &T^{abcd, 3h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = B^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{cd})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 5 \; \mathrm{perm.},\\
       &T^{abcd, 4h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = T^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{c}(k_{c})I^{1}_{d}(k_{d}).
@@
 \cite{Krause:2017}):
-    \begin{align}
-      I^{n}_{a_1...a_m}(k_1,...,k_m) &= \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
-    \end{align}
+    \begin{equation}
+      I^{n}_{a_1...a_m}(k_1,...,k_m) = \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
+    \end{equation}
     where $b_{h,1}(M)\equiv b_h(M)$ is the halo bias, $b_{h,0}\equiv1$, and $\tilde{u}_{a_i}$ is the halo profile for the $i$-th field being correlated (e.g.
@@
     \end{equation}
-where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Eq.~\ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling.
-\todo{Also, do you want to say anything about shot noise terms?}
-
-    Finally, we compute the super-sample covariance contribution following the treatment of \todo{cite}:
+where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
+    \begin{equation}
+      b_{a}=\frac{1}{\bar{n}_{g, a}}\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}b_{h}(M) \bar{N}_{c, a}(1+\bar{N}_{s, a}).
+    \end{equation}
+    The 1-halo trispectrum $T^{abcd, 1h}$ for galaxies also receives contributions due to shot noise \cite{Lacasa:2018}.
+However, these are expected to be small \cite{Lacasa:2018} and we thus neglect them in this work.
+
+    Finally, we compute the super-sample covariance contribution following the treatment of \cite{Krause:2017}, i.e.:
     \begin{align}
-       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) = \int & \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
+       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) &= \int \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
     \end{align}
-    The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the matter power spectrum to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as\footnote{We note that we also consider an alternative SSC model, in which we estimate the response of the matter power spectrum as the linearly biased response for the matter field.
-We find our parameter constraints to be unaffected by this change.} (e.g.
+        The quantity $\sigma_b^2(z)$ is the variance of the long wavelength mode $\delta_{\rm LS}$ over the survey footprint, given by
+    \begin{equation}
+      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
+    \end{equation}
+    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
+    \begin{equation}
+      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
+    \end{equation}
+    where $J_1(x)$ is the cylindrical Bessel function of order 1.
+    Finally, the quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
 \cite{Krause:2017}):
@@
     \end{align}
-    The last term in the above equation accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
-In addition, the quantity $b_{a}$ denotes the large-scale HOD bias for the $a$-th sample, computed as
-    \begin{equation}
-      b_{a}=\frac{1}{\bar{n}_{g, a}}\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}b_{h}(M) \bar{N}_{c, a}(1+\bar{N}_{s, a}),
-    \end{equation}
-    and $\sigma_b^2(z)$ is the variance of the long wavelength mode over the survey footprint, given by
-    \begin{equation}
-      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
-    \end{equation}
-    Finally $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
-    \begin{equation}
-      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
-    \end{equation}
-    where $J_1(x)$ is the cylindrical Bessel function of order 1.
+The last term in Eq.~\ref{eq:ps-resp} accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
+
+For consistency with our implementation of the trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
+We find our parameter constraints to be unaffected by this change and therefore resort to the approach described above for consistency.}.
 

### 2019-10-14 doc/Paper/main.tex
Updated some plots and results.

@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
+\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
 \caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
@@
 \begin{center}
-\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
-\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
-\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
-\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
+\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
+\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
+\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
+\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
 \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
@@
 fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
-auto & $\sfrac{18.0}{25}$ $(0.84)$ & $-0.665\substack{2.66 \\ -2.72}$ & $11.78\substack{0.31 \\ -0.28}$ & $0.705\substack{+3.29 \\ -3.30}$ & $12.95\substack{+0.37 \\ -0.33}$  & - & - & - \\
-G cov & $\sfrac{83.4}{80}$ $(0.38)$ & $-0.0602\substack{+2.71 \\ -2.16}$ & $11.91\substack{+0.20 \\ -0.21}$ & $1.46\substack{+3.36 \\ -2.78}$ & $13.10\substack{+0.25 \\ -0.26}$ & - & - & - \\
-G+SSC cov & $\sfrac{83.0}{80}$ $(0.39)$ & $-0.370\substack{+2.38 \\ -2.18}$ & $11.87\substack{+0.24 \\ -0.25}$ & $1.12\substack{+3.05 \\ -2.75}$ & $13.06\substack{+0.29 \\ -0.30}$ & - & - & - \\
-no $z_{w, i}$ & $\sfrac{83.6}{84}$ $(0.49)$ & $0.770\substack{+0.679 \\ -0.891}$ & $11.86\substack{+0.13 \\ -0.14}$ & $0.494\substack{+0.929 \\ -1.21}$ & $13.05\substack{+0.18 \\ -0.20}$ & - & - & - \\
-no $z_{w, i}, \Delta z_{i}$ & $\sfrac{90.2}{88}$ $(0.42)$ & $-1.16\substack{+0.632 \\ -0.845}$ & $11.75 \pm 0.14$ & $-0.130\substack{+0.687 \\ -1.01}$ & $12.89 \pm 0.17$ & - & - & - \\
-bins = 0, 1, 2 & $\sfrac{41.0}{43}$ $(0.56)$ & $-0.408\substack{+2.35 \\ -2.46}$ & $11.84 \pm 0.25$ & $0.585\substack{+2.84 \\ -2.99}$ & $13.03\substack{+0.31 \\ -0.30}$ & - & - & - \\
-bins = 1, 2, 3 & $\sfrac{42.6}{46}$ $(0.62)$ & $1.22\substack{+3.27 \\ -3.22}$ & $11.94\substack{+0.34 \\ -0.39}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
-pz = \texttt{Ephor\_AB} & $\sfrac{89.6}{80}$ $(0.22)$ & $0.396\substack{+2.2 \\ -2.1}$ & $12.12\substack{+0.20 \\ -0.19}$ & $2.02\substack{+3.07 \\ -2.88}$ & $13.37\substack{+0.27 \\ -0.26}$ & - & - & - \\
-pz = \texttt{Ephor} & $\sfrac{102.0}{80}$ $(0.049)$ & $1.16\substack{+2.02 \\ -2.09}$ & $12.14\substack{+0.18 \\ -0.17}$ & $3.01\substack{+2.75 \\ -2.87}$ & $13.39\substack{+0.23 \\ -0.22}$ & - & - & - \\
-pz = \texttt{DEmP} & $\sfrac{100.8}{80}$ $(0.058)$ & $0.493\substack{+1.93 \\ -1.97}$ & $12.03 \pm 0.20$ & $2.15\substack{+2.64 \\ -2.67}$ & $13.25 \pm 0.27$ & - & - & - \\
-pz = \texttt{FRANKEN-Z} & $\sfrac{87.2}{80}$ $(0.27)$ & $0.387\substack{+1.99 \\ -1.96}$ & $12.13 \pm 0.18$ & $2.00\substack{+2.79 \\ -2.74}$ & $13.38 \pm 0.24$ & - & - & - \\
+auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
+G cov & $\sfrac{80.6}{80}$ $(0.46)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
+G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
+no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
+no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
+bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
+bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
+pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
+pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
+pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
+pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
 fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
 fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
-fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
+fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
 fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
@@
 As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
-We find $\chi^{2} = 90.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
+We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
 This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.

### 2019-10-14 doc/Paper/main.tex
Fixed table entry.

@@
 auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
-G cov & $\sfrac{80.6}{80}$ $(0.46)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
+G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
 G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\

### 2019-10-15 doc/Paper/main.tex
Updated figures and text.

@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
-\caption{\todo{UPDATE} Measured auto- and cross power spectra considered in our analysis.
+\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
+\caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Measured auto- and cross power spectra considered in our analysis.
 The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
@@
 In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties.
-The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.88$ and $\chi^{2}_{\mathrm{red}} = 4.88$.
+The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.97$ and $\chi^{2}_{\mathrm{red}} = 5.13$.
 This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.
@@
         \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
-        \caption{\todo{UPDATE} Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
         \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
@@
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
-        \caption{\todo{UPDATE} Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
+        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
 The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{\todo{UPDATE} Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}

### 2019-10-16 doc/Paper/main.tex
Updated plots and table with latest results.

@@
 \abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program.
-Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets such that the Large Synoptic Survey Telescope will acquire, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
+Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets as will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
 We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$.
@@
 We demonstrate the use of map-level deprojection methods to account for non-physical fluctuations in the galaxy number density caused by observational systematics.
-Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses characterizing this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$ including both auto- and cross-correlations.
+Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations.
 Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, reproducing previous results.
@@
 
-The past two decades have seen a revolution in our understanding of Universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular expansion history and growth that are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
+The past two decades have seen a revolution in our understanding of the universe and its constituents.
+While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular to the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
 
@@
 Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments including spectroscopic ones such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric ones such as DES \cite{1708.01531,1708.01530,1708.01536}, Hyper-SupremeCam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} and major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
@@
 But even with perfect measurements of fluxes, our ability to infer redshift distribution of sources is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as the scattered light from bright objects, errors in the galaxy-star separation, reddedning by the milky way dust and others will impriment their own fluctuations into the galaxy density of objects.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as the scattered light from bright objects, errors in the galaxy-star separation, reddening by the milky way dust and others will impriment their own fluctuations into the galaxy density of objects.
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
-Therefore, it is likely that the Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
+Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
 
@@
 On the other hand, we are re-analyzing the existing precursor data to test-drive our methods and codes in realistic environment.
-In this paper we focus on the latter approach using Hyper Supreme-Cam Subaru Strategic Program (HSC-SSP) first data release  \cite{2018PASJ...70S...8A}.
+In this paper we focus on the latter approach using Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) first data release  \cite{2018PASJ...70S...8A}.
 The main advantage of this dataset is that it is in many respects very similar to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
@@
 The paper is structured as follows.
-In Section \ref{sec:data} we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
-In Section \ref{sec:methods} we go through the methodology employed in our analysis of the data and in Section \ref{sec:results} we present results together with numerous tests.
+In Section \ref{sec:data}, we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
+In Section \ref{sec:methods}, we go through the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
 We discuss and conclude in Section \ref{sec:discussion}.
@@
 
-  HSC-SSP is a photometric galaxy survey that has been awared 300 nights on the Subaru Telescope starting in 2014.
-The DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degreesto $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
+  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014.
+DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
 In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields between 5 and 20 square degrees each.
@@
           Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
-          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.89\substack{+0.24 \\ -0.25}$ & $11.76$ \\ 
-          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $-2.95$ \\
-          $M_{0}$ & flat $\in [0., \,15.]$ & $5.85\substack{+4.03 \\ -4.05}$ & $5.58$ \\
-          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.33\substack{+5.12 \\ -4.93}$ & $-0.925$ \\
-          $M_{1}$ & flat $\in [0., \,15.]$ & $13.09\substack{+0.24 \\ -0.25}$ & $12.96$ \\ 
-          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $1.49\substack{+3.21 \\ -3.08}$ & $-2.07$ \\
-          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000147\substack{+0.102 \\ -0.096}$ & $-0.0456$ \\
-          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0128\substack{+0.103 \\ -0.096}$ & $-0.0923$ \\
-          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00170\substack{+0.109 \\ -0.104}$ & $-0.103$ \\
-          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0148\substack{+0.109 \\ -0.106}$ & $-0.0727$ \\
-          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0300\substack{+0.130 \\ -0.119}$ & $-0.177$ \\
-          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.000837\substack{+0.0780 \\ -0.0785}$ & $-0.0991$ \\
-          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0342\substack{+0.0825 \\ -0.0794}$ & $0.0243$ \\
-          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0355\substack{+0.122 \\ -0.138}$ & $0.151$ \\ \\
-          $A_{\mu}$ & flat $\in [-3., \,3.]$ & $ - $ & $ - $ \\
+          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
+          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
+          $M_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
+          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
+          $M_{1}$ & flat $\in [0., \,15.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
+          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
+          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
+          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0159\substack{+0.096 \\ -0.086}$ & $-0.0865$ \\
+          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0727$ \\
+          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
+          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
+          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0543\substack{+0.112 \\ -0.126}$ & $0.182$ \\ \\
+          $A_{\mu}$ & flat $\in [-5., \,5.]$ & $ - $ & $ - $ \\
           $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
-          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
+          $\sigma_{8}$ & flat $\in [0.2, \,1.5]$ & $ - $ & $ - $ \\
           \hline\hline 
@@
 The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.
-As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}.
+As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.} \todo{explain upper bound}.
 Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
-The corresponding minimum $\chi^{2}$ is $\chi^{2} = 82.0$.
-Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.03$ ($p$-value $= 0.42$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
+The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$.
+Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
 \cite{Andrae:2010}).
@@
 \includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
-\caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Measured auto- and cross power spectra considered in our analysis.
+\caption{Measured auto- and cross power spectra considered in our analysis.
 The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
@@
 \begin{sidewaystable}
-\caption{\todo{UPDATE last 4 entries} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
+\caption{\todo{UPDATE LAST ENTRY WITH FULLY CONVERGED RESULTS} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
 The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
@@
 Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
-fiducial & $\sfrac{82.0}{80}$ $(0.42)$ & $-0.0606\substack{+2.50 \\ -2.40}$ & $11.89\substack{+0.24 \\ -0.25}$ & $1.49\substack{+3.21 \\ -3.08}$ & $13.09\substack{+0.29 \\ -0.30}$ & - & - & - \\
+fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
 auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
@@
 pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
-fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
-fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
+fiducial magn. & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
+fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
 fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
-fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
+fit cosmo & $\sfrac{84.4}{78}$ $(0.12)$ & $0.0867\substack{+2.69 \\ -2.50}$ & $11.81\substack{+0.27 \\ -0.23}$ & $1.70\substack{+3.39 \\ -3.16}$ & $12.97\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.806\substack{+0.148 \\ -0.145}$ \\
  \hline \hline
@@
 
-    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 0.99\substack{+0.37 \\ -0.36}$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
-This is consistent with our fiducial model for $s(z)$, which corresponds to $A_{\mu} = 1$ and constitutes a $\sim 2.8 \sigma$ detection of magnification from our HSC sample.
-The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 83.8$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 83.4$.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.06$ ($p$-value $= 0.33$).
-This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 95.8 - 83.8 = 12.0$, consistent with the $\sim 3 \sigma$ detection.
+    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 2.18 \pm 0.74$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+This constitutes a $\sim 2.9 \sigma$ detection of magnification from our HSC sample.
+Furthermore, this constraint is consistent with our fiducial model for $s(z)$, which corresponds to $A_{\mu} = 1$, at the $\sim 1.6 \sigma$ level.
+This marginal inconsistency is probably due to uncertainties in the data-driven estimation of $s(z)$.
+The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 69.0$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 72.8$, as can be seen from Tab.~\ref{tab:constraints_robustness}.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.87$ ($p$-value $= 0.78$).
+This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 86.2 - 69.0 = 17.2$, consistent with the $\sim 3 \sigma$ detection.
 Fig.~\ref{fig:cls-best-fit} shows the corresponding theoretical predictions derived from the maximum likelihood parameters alongside the observed data.
@@
         \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
-        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
+        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
@@
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
-        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
+        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
 The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.837\substack{+0.193 \\ -0.211}$ and $\Omega_{c} = 0.228\substack{+0.022 \\ -0.023}$, consistent with our assumed fiducial cosmology.
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.806\substack{+0.148 \\ -0.145}$ and $\Omega_{c} = 0.237 \pm 0.025$, \todo{UPDATE WITH FULLY CONVERGED RESULTS} consistent with our assumed fiducial cosmology.
 The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.

### 2019-10-16 doc/Paper/main.tex
Started cleaning up notation confusion for HOD parameters.

@@
     We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis.
-Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$ and choose a functional form given by:
-    \begin{equation}
-      M_{i}(z) = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
-    \end{equation}
-    where $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
-This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$.
+Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
+    \begin{equation}
+      \log{M_{i}(z)} = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
+    \end{equation}
+    where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
+This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$.
 We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.
@@
 
-Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
+Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
 The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.

### 2019-10-18 doc/Paper/main.tex
Added cosmology fit results.

@@
 In Section \ref{sec:data}, we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
-In Section \ref{sec:methods}, we go through the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
+In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
 We discuss and conclude in Section \ref{sec:discussion}.
@@
       \bar{n}_g=\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\bar{N}_c(M)\left[1+\bar{N}_s(M)\right].
+      \label{eq:ng_hod}
     \end{equation}
@@
 The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.
-As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.} \todo{explain upper bound}.
+As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}.
 Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
@@
 
-In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}$ and the mass scale for satellites $M_{1}$ obtained in our analysis.
+In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis.
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
@@
 We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.
+Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low.
+This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}).
+Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses, i.e.
+the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.
 
@@
 \begin{sidewaystable}
-\caption{\todo{UPDATE LAST ENTRY WITH FULLY CONVERGED RESULTS} Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
+\caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
 The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
@@
 fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
-fit cosmo & $\sfrac{84.4}{78}$ $(0.12)$ & $0.0867\substack{+2.69 \\ -2.50}$ & $11.81\substack{+0.27 \\ -0.23}$ & $1.70\substack{+3.39 \\ -3.16}$ & $12.97\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.806\substack{+0.148 \\ -0.145}$ \\
+fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0143\substack{+2.72 \\ -2.53}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.63\substack{+3.44 \\ -3.20}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.807\substack{+0.149 \\ -0.143}$ \\
  \hline \hline
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.806\substack{+0.148 \\ -0.145}$ and $\Omega_{c} = 0.237 \pm 0.025$, \todo{UPDATE WITH FULLY CONVERGED RESULTS} consistent with our assumed fiducial cosmology.
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{c} = 0.237 \pm 0.025$, consistent with our assumed fiducial cosmology.
 The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{\todo{UPDATE WITH FULLY CONVERGED RESULTS} Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
+        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}

### 2019-10-18 doc/Paper/main.tex
First go at magnitude cuts section.

@@
   \subsection{Joint cosmology and HOD constraints}\label{ssec:results.cosmo}
-    Finally we also consider jointly fitting cosmological, HOD and photo-$z$ systematics parameters.
+    Additionally we also consider jointly fitting cosmological, HOD and photo-$z$ systematics parameters.
 This analysis should be regarded as exploratory and only provide a means to illustrate the potential of photometric galaxy clustering analyses to jointly constrain these parameters.
@@
 As can be seen from Tab.~\ref{tab:constraints_robustness}, the derived constraints on HOD parameters agree well with our fiducial results, which shows that our HOD constraints are robust to variations in $\Omega_{c}$ and $\sigma_{8}$ as allowed by the data.
-This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
+This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
 Therefore, photometric current and future galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
@@
         \label{fig:constraints-fit=Oc+s8}
+      \end{center}
+    \end{figure}
+
+\subsection{Constraints on linear galaxy bias for different magnitude-limited samples}\label{ssec:results.mag_cuts}
+
+Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$.
+
+To this end we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively.
+We then subdivide each of these samples into four redshift bins of approximately equal galaxy number and use our pipeline to compute constraints on HOD parameters for our fiducial analysis variant.
+This allows us to derive constraints on the large-scale galaxy bias as a function of redshift for each sample.
+We determine the bias from the mean of the posterior distribution as we find it to yield more stable constraints than the best-fit value.
+The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample.
+As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected.
+Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \sim \sfrac{1}{D(z)}$, for all samples.
+In order to obtain a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude, we assume it to be separable in $z$ and $m_{\mathrm{lim}}$ and make the following Ansatz:
+\begin{equation}
+b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha}.
+\label{eq:bias-fit-func}
+\end{equation}  
+We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a two-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
+We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value.
+In a last step, we fit a linear function to $\bar{b}(m_{\mathrm{lim}})$, finally yielding
+\begin{align}
+\alpha &= -1.32, \\
+\bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
+\label{eq:bias-fit-func}
+\end{align}  
+where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
+The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
+As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g.
+modeling the galaxy bias when forecasting the constraining power of magnitude-limited galaxy samples.
+
+\begin{figure}
+\begin{center}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+\caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis.
+For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Eq.~\ref{eq:bias-fit-func}.
+The shaded regions denote the $68 \%$ c.l..}
+\label{fig:magnitude-cuts-bias}
 \end{center}

### 2019-10-19 doc/Paper/main.tex
Small changes.

@@
 Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
 Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}.
-For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources in the field.
+For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources.
 The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
 These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}.
-But even with perfect measurements of fluxes, our ability to infer redshift distribution of sources is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as the scattered light from bright objects, errors in the galaxy-star separation, reddening by the milky way dust and others will impriment their own fluctuations into the galaxy density of objects.
+But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
@@
 
-Community is well aware of these challenges lying ahead.
+The community is well aware of these challenges lying ahead.
 There are two main approaches that are being used in preparation for the arrival of data.
-On one hand, we are building very sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
-On the other hand, we are re-analyzing the existing precursor data to test-drive our methods and codes in realistic environment.
-In this paper we focus on the latter approach using Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) first data release  \cite{2018PASJ...70S...8A}.
-The main advantage of this dataset is that it is in many respects very similar to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
+On one hand, we are building sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
+On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment.
+In this paper, we focus on the latter approach using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}.
+The main advantage of this dataset is its similarity to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
 It covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
@@
 
-The paper is structured as follows.
-In Section \ref{sec:data}, we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
+This paper is structured as follows.
+In Section \ref{sec:data}, we describe the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
 In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
@@
 \end{equation}  
-We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a two-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
+We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
 We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value.
@@
 As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g.
-modeling the galaxy bias when forecasting the constraining power of magnitude-limited galaxy samples.
+modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.
 

### 2019-10-20 doc/Paper/main.tex
Went through intro and conclusions.

@@
 Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
@@
 But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separtation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
@@
 The community is well aware of these challenges lying ahead.
-There are two main approaches that are being used in preparation for the arrival of data.
-On one hand, we are building sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
+There are two main approaches to preparing for the arrival of data.
+On one hand, we are building sophisticated, realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
 On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment.
-In this paper, we focus on the latter approach using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}.
-The main advantage of this dataset is its similarity to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
-It covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
-We will work with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, similar to expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
-The primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
-With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is a perfect example of how the LSST data will look like.
-
-In this paper we focus exclusively on the galaxy clustering part of the data analysis.
+In this paper, we focus on the latter approach and perform an analysis of photometric galaxy clustering using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}.
+This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation.
+Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
+In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, which is similar to the expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
+Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
+With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.
+
+In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data.
+We split the data into four tomographic redshift bins and measure both auto- and cross power spectra, correcting for observational systematics using mode deprojection.
+We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties.
+To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties.
+We additionally perform extended analyses in which we compute constraints on magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters respectively.
+Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.
+In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
+However, we find that it suffices for the statistical precision of data at hand, but we view the use of halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
+
+This paper is structured as follows.
+In Section \ref{sec:data}, we describe the HSC-SSP data and the generation of a set of galaxy over-density maps together with maps of potential systematics.
+In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
+We discuss and conclude in Section \ref{sec:discussion}.
+%In this paper we focus exclusively on the galaxy clustering part of the data analysis.
 While the statistically most powerful data combination includes the full 3$\times$2 point analysis (i.e.
@@
 We will find that the answer is yes, at least over the total area of HSC-SSP DR1 data.
-
-Due to rather small area, we will be employing simple semi-analytical halo model to make theory predictions.
-While this model is most certainly not sophisticated enough for the full sky LSST analysis, it suffices for the statistical precision of data at hand.
-While we will derive some useful constraints on the halo model parameters, the use of halo model here should be viewed as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
-
-This paper is structured as follows.
-In Section \ref{sec:data}, we describe the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
-In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
-We discuss and conclude in Section \ref{sec:discussion}.
 
@@
 
-Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$.
-
-To this end we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively.
+Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$\footnote{We note that we only consider magnitude cuts in the $i$-band and we do not investigate the dependence of our results on the photometric band used to select a magnitude-limited sample.}.
+
+To this end, we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively.
 We then subdivide each of these samples into four redshift bins of approximately equal galaxy number and use our pipeline to compute constraints on HOD parameters for our fiducial analysis variant.
-This allows us to derive constraints on the large-scale galaxy bias as a function of redshift for each sample.
-We determine the bias from the mean of the posterior distribution as we find it to yield more stable constraints than the best-fit value.
+We find all subsamples to be well-fit by our fiducial model described in Sec.~\ref{ssec:methods.theory}.
+In fact, the reduced $\chi^{2}$s for some subsamples are quite low and thus lead to correspondingly high $p$-values, which seem to indicate the presence of overfitting and/or covariance overestimation in our brighter magnitude samples.
+However, for all subsamples, the distribution of the fit residuals is consistent with a Gaussian and we do not find any significant evidence that our covariance is overestimated by comparing the consistency of power spectra across different HSC fields.
+We therefore use the results of these HOD fits to derive constraints on the large-scale galaxy bias as a function of redshift for each sample.
+We determine the bias from the mean of the posterior distribution, as we find it to yield more stable constraints than the best-fit value.
 The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample.
@@
 In a last step, we fit a linear function to $\bar{b}(m_{\mathrm{lim}})$, finally yielding
-\begin{align}
+\begin{equation}
+\begin{aligned}
 \alpha &= -1.32, \\
 \bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
-\label{eq:bias-fit-func}
-\end{align}  
+\label{eq:bias-fit-func-result}
+\end{aligned}  
+\end{equation}
 where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
@@
 \caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis.
-For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Eq.~\ref{eq:bias-fit-func}.
+For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}.
 The shaded regions denote the $68 \%$ c.l..}
@@
 
-This paper has presented a comprehensive analysis of clustering of galaxies from the HSC-SSP DR1 dataset.
-It has demonstrated that despite relatively small area, the quality of the data allow serious scientific analysis leading to new insights both into physics of galaxy formation as well as methodology of clustering analysis.
-
-In terms of physics we show that a simple flux magnitude cut can be used to create useful samples for galaxy clustering analysis.
-This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshift (see e.g.
+In this work, we have presented a comprehensive analysis of photometric galaxy clustering in HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$.
+We have split this sample into four tomographic redshift bins and computed all possible auto- and cross power spectra, accounting for observational systematics in number density fluctuations through map-level deprojection.
+We have then fit the data using a halo model coupled with a halo occupation distribution, marginalizing over a flexible model for photometric redshift uncertainties.
+Our results are well-fit by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$.
+We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
+In order to test the stability of our results, we performed a suite of alternative analyses, finding our results to be robust to photometric redshift uncertainties.
+We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from our data alone.
+In addition, we also allowed for variations in the $\Lambda$CDM cosmological parameters, finding that the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
+Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting magnitude.
+
+Our analysis hence shows that the quality of the HSC data allows scientific analyses leading to new insights into both physics of galaxy formation as well as methodology of clustering analyses.
+In terms of physics, we show that a simple magnitude cut can be used to create useful samples for galaxy clustering analyses.
+This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshifts (see e.g.
 \cite{1507.05460,1807.10163}).
-Using magnitude cuts yield more galaxies that decrease the shot noise and thus improve the total statistical sensitivity of the survey despite somewhat lower bias leading to less pronounced clustering.
-In particular, the halo model results in observed galaxies occupying smaller halos toward higher redhifts, but these trends can be well understood by looking at how faint red galaxies drop out from our selection.
-These results confirm the phenomenological observation that galaxy bias scales approximately inversely with growth function, leading to redshift independent clustering at large redshifts.
-Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
+Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias.
+In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification amplitude.
+
+Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST.
+Our analysis demonstrates the feasibility of photometric galaxy clustering analyses using such high signal-to-noise datasets, which bodes well for future analyses using data from LSST.
+
+%Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
 The same data could also be used to compare the effective number densities.
@@
 We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
-
-Encouragingly, we find no barriers to estimating clustering using our samples both in auto and cross-correlation.
-The deprojection technique has a small but statistically significant effect, especially on large scales.
-This bodes well for \ldots
 
@@
 
+The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of Japan and Taiwan, and Princeton University.
+The HSC instrumentation and software were developed by the National Astronomical Observatory of Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU), the University of Tokyo, the High Energy Accelerator Research Organization (KEK), the Academia Sinica Institute for Astronomy and Astrophysics in Taiwan (ASIAA), and Princeton University.
+Funding was contributed by the FIRST program from Japanese Cabinet Office, the Ministry of Education, Culture, Sports, Science and Technology (MEXT), the Japan Society for the Promotion of Science (JSPS), Japan Science and Technology Agency (JST), the Toray Science Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton University.
+
+This paper makes use of software developed for the Large Synoptic Survey Telescope. We thank the LSST Project for making their code available as free software at  http://dm.lsst.org
+
+This paper is based on data collected at the Subaru Telescope and retrieved from the HSC data archive system, which is operated by Subaru Telescope and Astronomy Data Center at National Astronomical Observatory of Japan.
+Data analysis was in part carried out with the cooperation of Center for Computational Astrophysics, National Astronomical Observatory of Japan.
+
 \appendix

### 2019-10-20 doc/Paper/main.tex
Additional small changes.

@@
 The past two decades have seen a revolution in our understanding of the universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular to the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
+While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they only indirectly probe the physics of the low redshift universe, in particular the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
 
@@
 But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separtation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
@@
 To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties.
-We additionally perform extended analyses in which we compute constraints on magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters respectively.
+We additionally perform extended analyses in which we compute constraints on magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters, respectively.
 Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.
 In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
-However, we find that it suffices for the statistical precision of data at hand, but we view the use of halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
+However, we find that it suffices for the statistical precision of the data at hand, but we view the use of the halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
 
@@
 
-  We use data from the Hyper Suprime-Cam Subaru Strategic Program first data release (HSC DR1 hereon)\footnote{https://hsc-release.mtk.nao.ac.jp}.
+In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp}}.
 The release is extensively documented in \cite{2018PASJ...70S...8A}, and we only provide the details of the galaxy sample and associated data used for our clustering analysis.
@@
   HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014.
-DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
-In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields between 5 and 20 square degrees each.
+DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
+In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields  of areas varying between 5 and 20 square degrees.
 The image quality is impressive at median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arc sec) and also likely better than median seeing that will be achieved by LSST.
-The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and  available to the community as a publicly available database.
+DES with around 0.9 arc sec) and also likely better than the median seeing that will be achieved by LSST.
+The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a publicly available database.
 
@@
 This choice was based on a study of the survey depth-completeness relation in order to select a homogeneous and complete sample of high-confidence ($>10\sigma$) detections (see Section \ref{ssec:methods.syst}).
-We also select only objects with significant detections ($>5\sigma$) in at least two of the 4 remaining bands ($g,\,r,\,z,\,y$), and remove all objects classified as stars by the data reduction pipeline, using the "extendedness`` classifier as described in \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}.
+We also select only objects with significant detections ($>5\sigma$) in at least two of the 4 remaining bands ($g,\,r,\,z,\,y$), and remove all objects classified as stars by the data reduction pipeline, using the ``extendedness'' classifier as described in \cite{2018PASJ...70S..25M,2018PASJ...70S...5B}.
 The resulting sample consists of 9,734,457 objects and covers $\sim88$ square degrees distributed across the 6 HSC DR1 fields, as described in Table \ref{tab:field_summary}.
@@
 Given four tomographic samples, our measurement consists of four auto power spectra and six cross-power spectra.
-In this section we discuss how we construct maps of galaxy density fluctuations and associate maps of potential systematics , how we use these to measure the power spectra and its covariance matrix and finally how these are modeled within the context of halo model.
+In this section we discuss how we construct maps of galaxy density fluctuations and associated maps of potential systematics, how we use these to measure the power spectra and their covariance matrix and finally how these are modeled within the context of the halo model.
 
@@
 
-    To generate maps of all the quantities described in this section we make use of a rectangular pixelization scheme using the Plate Carr\'ee projection (labelled {\tt CAR} in the World Coordinate System standard \cite{2002A&A...395.1077C}).
+    To generate maps of all the quantities described in this section, we make use of a rectangular pixelization scheme using the Plate Carr\'ee projection (labelled {\tt CAR} in the World Coordinate System standard \cite{2002A&A...395.1077C}).
 In this case, pixels are simply defined by equal intervals of colatitude $\theta$ and azimuth $\phi$.
@@
     \begin{align}
-      &\bar{N}_c(M)=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{{\rm ln}M}}\right)\right],\\
+      &\bar{N}_c(M)=\frac{1}{2}\left[1+{\rm erf}\left(\frac{\log(M/M_{\rm min})}{\sigma_{\log M}}\right)\right],\\
       &\bar{N}_s(M)=\Theta(M-M_0)\left(\frac{M-M_0}{M_1'}\right)^\alpha,
@@
 Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$.
-Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by:
+Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by \cite{Navarro:1996}:
     \begin{equation}
@@
 The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}.
-Unless stated otherwise, we fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e.
+The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$.
+Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e.
 $\Omega_{b}=0.0493$, $\Omega_{c}=0.264$, $h=0.6736$, $n_{s}=0.9649$ and $\sigma_{8}=0.8111$ (see the fourth column in Tab.~2 in \cite{Planck:2018}).

### 2019-10-20 doc/Paper/main.tex
changes

--- 2019-10-19 doc/Paper/main.tex
@@
 \abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program.
-Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets as will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
+Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets such that the Large Synoptic Survey Telescope will acquire, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
 We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$.
@@
 We demonstrate the use of map-level deprojection methods to account for non-physical fluctuations in the galaxy number density caused by observational systematics.
-Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations.
+Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses characterizing this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$ including both auto- and cross-correlations.
 Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, reproducing previous results.
@@
 
-The past two decades have seen a revolution in our understanding of the universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular to the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
+The past two decades have seen a revolution in our understanding of Universe and its constituents.
+While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they are only indirectly sensitive to physics of the low redshift universe, in particular expansion history and growth that are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
 
@@
 Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The current Stage III experiments including spectroscopic ones such as eBOSS \cite{1707.09322,1801.03038,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric ones such as DES \cite{1708.01531,1708.01530,1708.01536}, Hyper-SupremeCam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} and major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
 Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}.
-For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources.
+For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources in the field.
 The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
 These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}.
-But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
+But even with perfect measurements of fluxes, our ability to infer redshift distribution of sources is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as the scattered light from bright objects, errors in the galaxy-star separation, reddedning by the milky way dust and others will impriment their own fluctuations into the galaxy density of objects.
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
-Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
-
-The community is well aware of these challenges lying ahead.
+Therefore, it is likely that the Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
+
+Community is well aware of these challenges lying ahead.
 There are two main approaches that are being used in preparation for the arrival of data.
-On one hand, we are building sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
-On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment.
-In this paper, we focus on the latter approach using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}.
-The main advantage of this dataset is its similarity to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
+On one hand, we are building very sophisticated realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
+On the other hand, we are re-analyzing the existing precursor data to test-drive our methods and codes in realistic environment.
+In this paper we focus on the latter approach using Hyper Supreme-Cam Subaru Strategic Program (HSC-SSP) first data release  \cite{2018PASJ...70S...8A}.
+The main advantage of this dataset is that it is in many respects very similar to the LSST data, both in terms of depth and bands as well as primary data reduction and catalog generation.
 It covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
@@
 
-This paper is structured as follows.
-In Section \ref{sec:data}, we describe the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
-In Section \ref{sec:methods}, we detail the methodology employed in our analysis and in Section \ref{sec:results}, we present results alongside numerous tests.
+The paper is structured as follows.
+In Section \ref{sec:data} we discuss the HSC-SSP data and how we process it in order to generate a set of galaxy over-density maps together with maps of potential systematics.
+In Section \ref{sec:methods} we go through the methodology employed in our analysis of the data and in Section \ref{sec:results} we present results together with numerous tests.
 We discuss and conclude in Section \ref{sec:discussion}.
@@
 
-  HSC-SSP is a photometric galaxy survey that has been awarded 300 nights on the Subaru Telescope starting in 2014.
-DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
+  HSC-SSP is a photometric galaxy survey that has been awared 300 nights on the Subaru Telescope starting in 2014.
+The DR1 includes data from 61.5 nights covering and comes with fields of three depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degreesto $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
 In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields between 5 and 20 square degrees each.
@@
       \bar{n}_g=\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\bar{N}_c(M)\left[1+\bar{N}_s(M)\right].
-      \label{eq:ng_hod}
     \end{equation}
@@
     We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis.
-Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
-    \begin{equation}
-      \log{M_{i}(z)} = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
-    \end{equation}
-    where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
-This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$.
+Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$ and choose a functional form given by:
+    \begin{equation}
+      M_{i}(z) = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
+    \end{equation}
+    where $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
+This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}$, $M_{0}$ and $M_{1}$.
 We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.
@@
 
-    Using the halo model, the connected part of the trispectrum $T^{abcd}$ can be written as (e.g. \cite{Takada:2013}):
+    Using the halo model, the connected part of the trispectrum $T^{abcd}$ is given by (e.g. \cite{Takada:2013}):
     \begin{equation}
@@
       &T^{abcd, 2h}_{13}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = P_{\mathrm{lin}}(k_{a})I^{1}_{a}(k_{a})I^{1}_{bcd}(k_{b}, k_{b}, k_{c}) + 3 \; \mathrm{perm.}, \\
-      &T^{abcd, 3h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = B^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{cd})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 5 \; \mathrm{perm.},\\
+      &T^{abcd, 3h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = B^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{cd})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{cd}(k_{c}, k_{d}) + 5 \; \mathrm{perm.}, \\
       &T^{abcd, 4h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = T^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{c}(k_{c})I^{1}_{d}(k_{d}).
@@
 \cite{Krause:2017}):
-    \begin{equation}
-      I^{n}_{a_1...a_m}(k_1,...,k_m) = \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
-    \end{equation}
+    \begin{align}
+      I^{n}_{a_1...a_m}(k_1,...,k_m) &= \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
+    \end{align}
     where $b_{h,1}(M)\equiv b_h(M)$ is the halo bias, $b_{h,0}\equiv1$, and $\tilde{u}_{a_i}$ is the halo profile for the $i$-th field being correlated (e.g.
@@
     \end{equation}
-where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
-    \begin{equation}
-      b_{a}=\frac{1}{\bar{n}_{g, a}}\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}b_{h}(M) \bar{N}_{c, a}(1+\bar{N}_{s, a}).
-    \end{equation}
-    The 1-halo trispectrum $T^{abcd, 1h}$ for galaxies also receives contributions due to shot noise \cite{Lacasa:2018}.
-However, these are expected to be small \cite{Lacasa:2018} and we thus neglect them in this work.
-
-    Finally, we compute the super-sample covariance contribution following the treatment of \cite{Krause:2017}, i.e.:
+where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Eq.~\ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling.
+\todo{Also, do you want to say anything about shot noise terms?}
+
+    Finally, we compute the super-sample covariance contribution following the treatment of \todo{cite}:
     \begin{align}
-       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) &= \int \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
+       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) = \int & \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
     \end{align}
-        The quantity $\sigma_b^2(z)$ is the variance of the long wavelength mode $\delta_{\rm LS}$ over the survey footprint, given by
-    \begin{equation}
-      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
-    \end{equation}
-    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
-    \begin{equation}
-      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
-    \end{equation}
-    where $J_1(x)$ is the cylindrical Bessel function of order 1.
-    Finally, the quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
+    The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the matter power spectrum to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as\footnote{We note that we also consider an alternative SSC model, in which we estimate the response of the matter power spectrum as the linearly biased response for the matter field.
+We find our parameter constraints to be unaffected by this change.} (e.g.
 \cite{Krause:2017}):
@@
     \end{align}
-The last term in Eq.~\ref{eq:ps-resp} accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
-
-For consistency with our implementation of the trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
-We find our parameter constraints to be unaffected by this change and therefore resort to the approach described above for consistency.}.
+    The last term in the above equation accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
+In addition, the quantity $b_{a}$ denotes the large-scale HOD bias for the $a$-th sample, computed as
+    \begin{equation}
+      b_{a}=\frac{1}{\bar{n}_{g, a}}\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}b_{h}(M) \bar{N}_{c, a}(1+\bar{N}_{s, a}),
+    \end{equation}
+    and $\sigma_b^2(z)$ is the variance of the long wavelength mode over the survey footprint, given by
+    \begin{equation}
+      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
+    \end{equation}
+    Finally $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
+    \begin{equation}
+      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
+    \end{equation}
+    where $J_1(x)$ is the cylindrical Bessel function of order 1.
 
@@
           Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
-          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
-          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
-          $M_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
-          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
-          $M_{1}$ & flat $\in [0., \,15.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
-          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
-          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
-          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0159\substack{+0.096 \\ -0.086}$ & $-0.0865$ \\
-          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
-          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0727$ \\
-          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
-          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
-          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
-          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0543\substack{+0.112 \\ -0.126}$ & $0.182$ \\ \\
-          $A_{\mu}$ & flat $\in [-5., \,5.]$ & $ - $ & $ - $ \\
+          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $12.29 \pm 0.15$ & $12.25$ \\ 
+          $M_{\mathrm{min}, p}$ & flat $\in [-5., \,10.]$ & $2.93\substack{+1.56 \\ -1.47}$ & $1.83$ \\
+          $M_{0}$ & flat $\in [0., \,15.]$ & $5.97 \pm 4.00$ & $8.36$ \\
+          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.65 \pm 5.00$ & $7.58$ \\
+          $M_{1}$ & flat $\in [0., \,15.]$ & $13.69 \pm 0.21$ & $13.63$ \\ 
+          $M_{1, p}$ & flat $\in [-5., \,15.]$ & $6.00\substack{+2.14 \\ -2.05}$ & $4.49$ \\
+          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.0170\substack{+0.091 \\ -0.090}$ & $-0.0525$ \\
+          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $0.00470\substack{+0.095 \\ -0.093}$ & $-0.0321$ \\
+          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $0.0198\substack{+0.101 \\ -0.099}$ & $0.0136$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0337\substack{+0.106 \\ -0.105}$ & $0.0174$ \\
+          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0361\substack{+0.1376 \\ -0.1234}$ & $-0.159$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.0252 \pm 0.0799$ & $-0.00141$ \\
+          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0569\substack{+0.0856 \\ -0.0897}$ & $0.0576$ \\
+          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0153\substack{+0.1190 \\ -0.1217}$ & $0.0467$ \\ \\
+          $A_{\mu}$ & flat $\in [-2., \,2.]$ & $ - $ & $ - $ \\
           $\Omega_{c}$ & flat $\in [0.1, \,0.9]$ & $ - $ & $ - $ \\
-          $\sigma_{8}$ & flat $\in [0.2, \,1.5]$ & $ - $ & $ - $ \\
+          $\sigma_{8}$ & flat $\in [0.4, \,1.5]$ & $ - $ & $ - $ \\
           \hline\hline 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
+\includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
 \caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
@@
 \begin{center}
-\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
-\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
-\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
-\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
+\subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
+\subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
+\subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
+\subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=PT-resp_mode=LINBIAS_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
 \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
@@
 
-Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
+Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
 The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.
@@
 Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
-The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$.
-Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.08$ ($p$-value $= 0.30$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
+The corresponding minimum $\chi^{2}$ is $\chi^{2} = 95.8$.
+Computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$, we obtain $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.20$ ($p$-value $= 0.11$), which shows that the data are consistent with the best-fit theoretical model\footnote{We note that this estimate of the degrees of freedom is only valid for linear models and independent basis functions (see e.g.
 \cite{Andrae:2010}).
@@
 
-In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis.
+In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}$ and the mass scale for satellites $M_{1}$ obtained in our analysis.
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
-As can be seen, we find that, within or uncertainties, the data prefer both a constant $M_{\mathrm{min}}$ and $M_{1}$.
+As can be seen, we find that the data prefer both a decreasing $M_{\mathrm{min}}$ and $M_{1}$.
 This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times.
 We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.
-Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low.
-This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}).
-Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses, i.e.
-the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
+\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag_M1p-pr.pdf}
 \caption{Measured auto- and cross power spectra considered in our analysis.
@@
 \begin{center}
-\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
+\subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_best-fit+random-draws.pdf}}
 \caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
@@
 Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
-fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
-auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
-G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
-G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
-no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
-no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
-bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
-bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
-pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
-pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
-pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
-pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
-fiducial magn. & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
-fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
-fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
-fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0143\substack{+2.72 \\ -2.53}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.63\substack{+3.44 \\ -3.20}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.807\substack{+0.149 \\ -0.143}$ \\
+fiducial & $\sfrac{95.8}{80}$ $(0.11)$ & $2.93\substack{+1.56 \\ -1.47}$ & $12.29 \pm 0.15$ & $6.00\substack{+2.14 \\ -2.05}$ & $13.69 \pm 0.21$ & - & - & - \\
+auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.32\substack{+2.03 \\ -1.79}$ & $12.32 \pm 0.14$ & $6.49\substack{+2.80 \\ -2.47}$ & $13.72\substack{+0.20 \\ -0.19}$  & - & - & - \\
+G cov & $\sfrac{98.4}{80}$ $(0.080)$ & $3.59\substack{+1.52 \\ -1.44}$ & $12.34 \pm 0.14$ & $6.89\substack{+1.96 \\ -1.89}$ & $13.74\substack{+0.19 \\ -0.20}$ & - & - & - \\
+G+SSC cov & $\sfrac{97.8}{80}$ $(0.086)$ & $3.28\substack{+1.57 \\ -1.51}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.46\substack{+2.15 \\ -2.10}$ & $13.71 \pm 0.20$ & - & - & - \\
+no $z_{w, i}$ & $\sfrac{97.8}{84}$ $(0.14)$ & $2.69\substack{+1.17 \\ -1.08}$ & $12.24 \pm 0.09$ & $5.74\substack{+1.95 \\ -1.66}$ & $13.62\substack{+0.14 \\ -0.13}$ & - & - & - \\
+no $z_{w, i}, \Delta z_{i}$ & $\sfrac{102.2}{88}$ $(0.18)$ & $3.23 \pm 0.76$ & $12.27 \pm 0.06$ & $6.43\substack{+1.17 \\ -1.18}$ & $13.65 \pm 0.10$ & - & - & - \\
+bins = 0, 1, 2 & $\sfrac{56.2}{43}$ $(0.085)$ & $2.83\substack{+2.25 \\ -2.11}$ & $12.26\substack{+0.18 \\ -0.19}$ & $5.44\substack{+3.07 \\ -2.93}$ & $13.64\substack{+0.25 \\ -0.26}$ & - & - & - \\
+bins = 1, 2, 3 & $\sfrac{45.8}{46}$ $(0.48)$ & $2.38\substack{+2.32 \\ -2.26}$ & $12.16\substack{+0.25 \\ -0.13}$ & $5.31\substack{+3.17 \\ -3.09}$ & $13.53\substack{+0.32 \\ -0.19}$ & - & - & - \\
+pz = \texttt{Ephor\_AB} & $\sfrac{99.8}{80}$ $(0.066)$ & $2.96\substack{+1.22 \\ -1.12}$ & $12.45 \pm 0.11$ & $6.07\substack{+1.66 \\ -1.54}$ & $13.90 \pm 0.16$ & - & - & - \\
+pz = \texttt{Ephor} & $\sfrac{107.6}{80}$ $(0.022)$ & $3.18\substack{+1.24 \\ -1.27}$ & $12.43 \pm 0.12$ & $6.34\substack{+1.75 \\ -1.77}$ & $13.87 \pm 0.17$ & - & - & - \\
+pz = \texttt{DEmP} & $\sfrac{106.4}{80}$ $(0.026)$ & $2.90\substack{+1.35 \\ -1.33}$ & $12.37 \pm 0.12$ & $5.95\substack{+1.87 \\ -1.83}$ & $13.78 \pm 0.17$ & - & - & - \\
+pz = \texttt{FRANKEN-Z} & $\sfrac{98.6}{80}$ $(0.078)$ & $2.66\substack{+1.17 \\ -1.08}$ & $12.45 \pm 0.11$ & $5.63\substack{+1.61 \\ -1.51}$ & $13.88 \pm 0.16$ & - & - & - \\
+fiducial magn. & $\sfrac{83.4}{79}$ $(0.35)$ & $3.53\substack{+1.88 \\ -1.71}$ & $12.33 \pm 0.15$ & $6.63\substack{+2.50 \\ -2.23}$ & $13.72\substack{+0.20 \\ -0.21}$  & - & - & - \\
+fit magn., auto+cross & $\sfrac{83.8}{79}$ $(0.33)$ & $3.34\substack{+1.85 \\ -1.74}$ & $12.32 \pm 0.15$ & $6.45\substack{+2.47 \\ -2.31}$ & $13.72\substack{+0.20 \\ -0.21}$  & $0.99\substack{+0.37 \\ -0.36}$ & - & - \\
+fit magn., auto & $\sfrac{26.8}{25}$ $(0.37)$ & $3.16\substack{+1.80 \\ -1.63}$ & $12.31\substack{+0.14 \\ -0.13}$ & $6.34\substack{+2.52 \\ -2.29}$ & $13.72\substack{+0.20 \\ -0.19}$  & $-0.25\substack{+1.34 \\ -1.27}$ & - & - \\
+fit cosmo & $\sfrac{93.0}{78}$ $(0.12)$ & $3.37\substack{+1.73 \\ -1.66}$ & $12.19\substack{+0.20 \\ -0.17}$ & $6.55\substack{+2.33 \\ -2.30}$ & $13.58\substack{+0.31 \\ -0.30}$  & - & $-0.228\substack{+0.022 \\ -0.023}$ & $0.837\substack{+0.193 \\ -0.211}$ \\
  \hline \hline
@@
 As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
-We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
+We find $\chi^{2} = 102.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra (see Tab.~\ref{tab:constraints_robustness}).
 This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.
@@
 Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra.
-Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we account for less contributions to the total covariance, as expected.
+Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data increase as we account for less contributions to the total covariance, as expected.
 However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
 \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
@@
 We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
-While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
+While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.021$ ($68 \%$ c.l.).
 This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.
@@
 We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin.
-This secondary peak contains 5\% of galaxies and peaks around $z\sim 2.5$ (hence cannot be seen in Figure \ref{fig:nzs}).
-To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.1$.
+This secondary peak contains $\sim$5\% of galaxies and peaks around $z\sim 3$ (hence cannot be seen in Figure \ref{fig:nzs}).
+To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.05$.
 This indicates that the effect of this bump is to small to be statistically significant.
 We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
-\as{Fix numbers once Sarah gets back}
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
 \caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
 \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations.
@@
 In contrast to the results obtained using our fiducial COSMOS30 photo-$z$ distributions, we find that we cannot obtain an acceptable fit to the data for the alternative four methods when not accounting for photometric redshift uncertainties.
-The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.97$ and $\chi^{2}_{\mathrm{red}} = 5.13$.
+The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 2.08$ and $\chi^{2}_{\mathrm{red}} = 5.04$.
 This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of our fiducial HOD constraints to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalized over both shifts in the means and changes in the widths of the distributions.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained using the redshift distributions derived from \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}.
@@
 \subsubsection{Interpretation of HOD results}\label{sssec:results.hod-constraints.constraints-interpretation}
-As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to be redshift independent.
+As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to decrease with redshift.
 In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies considered in our analysis and how these change with redshift.
@@
 This is probably due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$, which translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
-As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
+As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed decreasing trend in $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
 This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift})
@@
 \begin{center}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
+\subfigure{\includegraphics[width=0.3\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_M1p-pr.pdf}}
 \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
@@
     \begin{equation}
-      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
+      \delta^i_g(\nv)=\int dz\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
     \end{equation}
@@
     \begin{equation}
-      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
+      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty dz'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
     \end{equation}
@@
     \begin{equation}\label{eq:cell_gg_wmag}
-      C^{ij}_\ell = \int \mathrm{d}z\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
+      C^{ij}_\ell = \int dz\,\frac{H(z)}{\chi^2(z)}\left[p^ip^j\,P_{gg}+\left(p^iW_\mu^j+p^jW_\mu^i\right)\frac{\ell(\ell+1)}{Hk^2}P_{gm}+W_\mu^iW_\mu^j\left(\frac{\ell(\ell+1)}{Hk^2}\right)^2P_{mm}\right],
     \end{equation}
@@
 
-    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 2.18 \pm 0.74$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
-This constitutes a $\sim 2.9 \sigma$ detection of magnification from our HSC sample.
-Furthermore, this constraint is consistent with our fiducial model for $s(z)$, which corresponds to $A_{\mu} = 1$, at the $\sim 1.6 \sigma$ level.
-This marginal inconsistency is probably due to uncertainties in the data-driven estimation of $s(z)$.
-The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 69.0$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 72.8$, as can be seen from Tab.~\ref{tab:constraints_robustness}.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.87$ ($p$-value $= 0.78$).
-This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 86.2 - 69.0 = 17.2$, consistent with the $\sim 3 \sigma$ detection.
+    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 0.99\substack{+0.37 \\ -0.36}$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+This is consistent with our fiducial model for $s(z)$, which corresponds to $A_{\mu} = 1$ and constitutes a $\sim 2.8 \sigma$ detection of magnification from our HSC sample.
+The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 83.8$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 83.4$.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 1.06$ ($p$-value $= 0.33$).
+This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 95.8 - 83.8 = 12.0$, consistent with the $\sim 3 \sigma$ detection.
 Fig.~\ref{fig:cls-best-fit} shows the corresponding theoretical predictions derived from the maximum likelihood parameters alongside the observed data.
@@
   \subsection{Joint cosmology and HOD constraints}\label{ssec:results.cosmo}
-    Additionally we also consider jointly fitting cosmological, HOD and photo-$z$ systematics parameters.
+    Finally we also consider jointly fitting cosmological, HOD and photo-$z$ systematics parameters.
 This analysis should be regarded as exploratory and only provide a means to illustrate the potential of photometric galaxy clustering analyses to jointly constrain these parameters.
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{c} = 0.237 \pm 0.025$, consistent with our assumed fiducial cosmology.
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.837\substack{+0.193 \\ -0.211}$ and $\Omega_{c} = 0.228\substack{+0.022 \\ -0.023}$, consistent with our assumed fiducial cosmology.
 The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
 As can be seen from Tab.~\ref{tab:constraints_robustness}, the derived constraints on HOD parameters agree well with our fiducial results, which shows that our HOD constraints are robust to variations in $\Omega_{c}$ and $\sigma_{8}$ as allowed by the data.
-This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
+This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
 Therefore, photometric current and future galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
@@
         \label{fig:constraints-fit=Oc+s8}
-      \end{center}
-    \end{figure}
-
-\subsection{Constraints on linear galaxy bias for different magnitude-limited samples}\label{ssec:results.mag_cuts}
-
-Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$.
-
-To this end we split our fiducial galaxy sample into four brighter subsamples with limiting magnitudes $i_{\mathrm{corr}} < 20.5$, $i_{\mathrm{corr}} < 21.5$, $i_{\mathrm{corr}} < 22.5$ and $i_{\mathrm{corr}} < 23.5$, respectively.
-We then subdivide each of these samples into four redshift bins of approximately equal galaxy number and use our pipeline to compute constraints on HOD parameters for our fiducial analysis variant.
-This allows us to derive constraints on the large-scale galaxy bias as a function of redshift for each sample.
-We determine the bias from the mean of the posterior distribution as we find it to yield more stable constraints than the best-fit value.
-The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample.
-As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected.
-Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \sim \sfrac{1}{D(z)}$, for all samples.
-In order to obtain a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude, we assume it to be separable in $z$ and $m_{\mathrm{lim}}$ and make the following Ansatz:
-\begin{equation}
-b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha}.
-\label{eq:bias-fit-func}
-\end{equation}  
-We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
-We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value.
-In a last step, we fit a linear function to $\bar{b}(m_{\mathrm{lim}})$, finally yielding
-\begin{align}
-\alpha &= -1.32, \\
-\bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
-\label{eq:bias-fit-func}
-\end{align}  
-where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
-The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
-As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g.
-modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.
-
-\begin{figure}
-\begin{center}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-\subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-\caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis.
-For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Eq.~\ref{eq:bias-fit-func}.
-The shaded regions denote the $68 \%$ c.l..}
-\label{fig:magnitude-cuts-bias}
       \end{center}
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
 \caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} setting $z_{w, i} = 0, \Delta z_{i} = 0$.

### 2019-10-20 doc/Paper/main.tex
my changes

@@
 The past two decades have seen a revolution in our understanding of the universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role \cite{Planck:2018}, they only indirectly probe the physics of the low redshift universe, in particular the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
-
-In studies of the low redshift universe, surveys of the large scale structure play an increasingly important role.
+While observations of the cosmic microwave background play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift universe.
+In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
+At the moment, this is only possible with the optical large scale structure surveys.
+
 Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
@@
 This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation.
-Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
+Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes.
 In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, which is similar to the expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
@@
 Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.
+
 In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
-However, we find that it suffices for the statistical precision of the data at hand, but we view the use of the halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
+LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}.
+However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use we use it as a ``good enough'' substitute for the final modeling.
 
@@
 The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}.
-\an{We don't use HECTOMAP in the fitting.
-Shall we even show it here?}} \label{tab:field_summary}
+We note that HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
   \end{table}

### 2019-10-20 doc/Paper/main.tex
cosmology

@@
 
-    In the presence of magnification, the equations in Section \ref{ssec:methods.theory} get slightly modified. The projected galaxy overdensity becomes:
+    In the presence of magnification, the equations in Section \ref{ssec:methods.theory} get additional terms. The projected galaxy overdensity becomes:
     \begin{equation}
@@
     where $m$ denotes the observed magnitude.
-    The angular power spectrum is then given by:
+In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.
+Overdensities along the line of sight causes the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increaseing the observed number density).
+The two effects cancel at leading order when $s=\sfrac{5}{2}$.
+
+    The angular power spectrum is then given by
     \begin{equation}\label{eq:cell_gg_wmag}
@@
 As can be seen, the three estimates agree well with each other and we use the $s(z)$ function derived from our fiducial WIDE sample in the following.
+Our uncertainty on estimation of $s(z)$ is subdominant to statistical precision of the detection and so we ignore it.
     \begin{figure}
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{c} = 0.237 \pm 0.025$, consistent with our assumed fiducial cosmology.
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.298 \pm 0.025$,
+%%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
+    consistent with our assumed fiducial cosmology.
+In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ albeit with a different parameterization.
+The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$, showing an excellent internal consistency.
+We note that our modeling makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.
+
     The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).
+\as{Can we replot this as $\Omega_m$ rather than $\Omega_c$.?}}
         \label{fig:constraints-fit=Oc+s8}

### 2019-10-20 doc/Paper/main.tex
more cosmology

@@
 When freeing up cosmological parameters, we find constraints on the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ that agree well with measurements from Planck and low-redshift probes.
-Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple model for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}
+Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple fitting function for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}
 
@@
     consistent with our assumed fiducial cosmology.
-In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ albeit with a different parameterization.
-The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$, showing an excellent internal consistency.
+In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{1807.06209} albeit with a different parameterization.
+The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency.
 We note that our modeling makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.

### 2019-10-20 doc/Paper/main.tex
my changes

--- 2019-10-20 doc/Paper/main.tex
@@
 \author[c]{An\v{z}e Slosar,}
-\author[d]{Humna Awan,}
-\author[d]{Adam Broussard,}
+\author[d,e]{Javier S\'anchez,}
+\author[f]{Humna Awan,}
+\author[f]{Adam Broussard,}
 \author[b]{Zahra Gomes,}
-\author[d]{Eric Gawiser,}
+\author[f]{Eric Gawiser,}
 \author[x]{Rachel Mandelbaum,}
 \author[x]{Hironao Miyatake,}
-\author[e]{Jeffrey A. Newman,}
-\author[f,g]{Javier S\'anchez,}
+\author[g]{Jeffrey A. Newman,}
 \author[x]{Ignacio Sevilla,}
@@
 \affiliation[c]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
-\affiliation[d]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
-\affiliation[e]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
-\affiliation[f]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
-\affiliation[g]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation[d]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
+\affiliation[e]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
+\affiliation[g]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
 \affiliation[h]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
@@
 
-The past two decades have seen a revolution in our understanding of the universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift universe.
-In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
-At the moment, this is only possible with the optical large scale structure surveys.
-
-Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The past two decades have seen a revolution in our understanding of the Universe and its constituents.
+While observations of the cosmic microwave background (CMB) play a pivotal role \cite{Planck:2018}, they only indirectly probe the physics of the low-redshift Universe, in particular the expansion history and growth, which are uniquely sensitive to properties of dark energy and modified gravity \cite{1903.12016}.
+
+In studying the late-time Universe, surveys of the large scale structure play an increasingly important role.
+Over a decade ago, the Dark Energy Task Force divided the evolution of optical experiments into approximate stages \cite{0609591}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion, and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
@@
 The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
-These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function with blending \cite{1708.01533,1905.01324,1907.10572}.
+These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function (PSF) with blending \cite{1708.01533,1905.01324,1907.10572}.
 But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
-Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by milky way dust and others will imprint spurious fluctuations on the observed galaxy density field.
-These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density fields.
+Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by Milky Way dust, and varying observing conditions, will imprint spurious fluctuations on the observed galaxy density field.
+These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density field.
 Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
@@
 This dataset bears significant similarities to the data expected from LSST, both in terms of survey depth and photometric bands as well as primary data reduction and catalog generation.
-Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes.
-In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, which is similar to the expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
-Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
+Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes, which are unlikely to play a major role in cosmological data analysis.
+In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude of $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after 1 year \cite{1809.01669} ($i<25.1$).
+Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
 With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.
+This analysis has the additional attraction that no other photometric galaxy clustering study has been carried out with these data.
 
 In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data.
-We split the data into four tomographic redshift bins and measure both auto- and cross power spectra, correcting for observational systematics using mode deprojection.
+We split the data into four tomographic redshift bins and measure both auto- and cross power spectra between all bins, correcting for observational systematics using mode deprojection.
 We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties.
@@
 Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.
-
 In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
-LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}.
-However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use we use it as a ``good enough'' substitute for the final modeling.
+However, we find that it suffices for the statistical precision of the data at hand, and we view the use of the halo model as a ``good enough'' substitute for the final modeling, which will likely include bias expansion approaches \cite{0902.0991,1402.5916,1611.09787} and power spectrum emulators \cite{1804.05865,1705.03388}.
 
@@
 The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}.
-We note that HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
+\an{We don't use HECTOMAP in the fitting.
+Shall we even show it here?}} \label{tab:field_summary}
   \end{table}
@@
 
-In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp}}.
+  In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\url{https://hsc-release.mtk.nao.ac.jp}}.
 The release is extensively documented in \cite{2018PASJ...70S...8A}, and we only provide the details of the galaxy sample and associated data used for our clustering analysis.
@@
 DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
-In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 7 fields  of areas varying between 5 and 20 square degrees.
+In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees.
 The image quality is impressive at median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
 DES with around 0.9 arc sec) and also likely better than the median seeing that will be achieved by LSST.
-The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a publicly available database.
+The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
 
@@
 Since we do not have direct access to the latter, we used, as coadd weights, the inverse of the sky level of each exposure, which should be close to inverse-variance weighting.
-Following this procedure we produce maps of the following quantities: airmass, CCD temperature, seeing, point-spread function (PSF) ellipticity, exposure time, sky count level, root-mean square deviation of the sky count and number of visits.
+Following this procedure we produce maps of the following quantities: airmass, CCD temperature, seeing, PSF ellipticity, exposure time, sky count level, root-mean square deviation of the sky count and number of visits.
     \end{enumerate}
@@
 We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin.
-This secondary peak contains $\sim$5\% of galaxies and peaks around $z\sim 3$ (hence cannot be seen in Figure \ref{fig:nzs}).
-To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.05$.
+This secondary peak contains 5\% of galaxies and peaks around $z\sim 2.5$ (hence cannot be seen in Figure \ref{fig:nzs}).
+To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.1$.
 This indicates that the effect of this bump is to small to be statistically significant.
 We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
+\as{Fix numbers once Sarah gets back}
 

### 2019-10-20 doc/Paper/main.tex

--- 2019-10-20 doc/Paper/main.tex
@@
 
-The past two decades have seen a revolution in our understanding of the universe and its constituents.
-While observations of the cosmic microwave background play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift universe.
+The past two decades have seen a revolution in our understanding of the Universe and its constituents.
+While observations of the cosmic microwave background (CMB) play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift Universe.
 In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
@@
 
-Over a decade ago, the Dark Energy Task Force has divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669} as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+Over a decade ago, the Dark Energy Task Force divided the evolution of optical experiments into approximate stages \cite{0609591}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
@@
 Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes.
-In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude for 5-$\sigma$ source detection of $i<24.5$, which is similar to the expected magnitude cut to be used for LSST of $i<25.1$ after 1 year \cite{1809.01669}.
+In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after 1 year \cite{1809.01669} ($i<25.1$).
 Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
 With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.
+This analysis has the additional attraction that no other photometric galaxy clustering study has been carried out with these data.
 
 In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data.
-We split the data into four tomographic redshift bins and measure both auto- and cross power spectra, correcting for observational systematics using mode deprojection.
+We split the data into four tomographic redshift bins and measure both the auto- and cross power spectra of all bins, correcting for observational systematics using mode deprojection.
 We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties.

### 2019-10-20 doc/Paper/main.tex
mag limit fits

--- 2019-10-20 doc/Paper/main.tex
@@
 where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
-The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
-As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g.
-modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.
+\as{Do we want to rewrite this as $\bar{b} = b_0 + b_1 (m-24)$?} The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
+
+This analysis yields a few interesting results.
+First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid.
+In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnituce cut, the low redshift galaxies are \emph{different population} of galaxies.
+We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
+
+The most common use of this results is for Fisher matrix forecasts for constraining power of magnitude-limited samples. \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?}
+
+An alternative use is galaxy evolution studies, where this results provides a convenient cross-check formula.
+Our full parameter chains for different magnitudes are available upon request.
+\as{Is this the case?}
 

### 2019-10-20 doc/Paper/main.tex
Switched from Omega_c to Omega_m and fixed bias plot.

@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.298 \pm 0.025$,
+From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$,
 %%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
     consistent with our assumed fiducial cosmology.
-In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{1807.06209} albeit with a different parameterization.
+In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{Planck:2018} albeit with a different parameterization.
 The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency.
-We note that our modeling makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.
+We note that our analysis makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.
 
@@
       \begin{center}
-        \includegraphics[width=0.49\textwidth]{figures/contours-Oc-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).
-\as{Can we replot this as $\Omega_m$ rather than $\Omega_c$.?}}
+        \includegraphics[width=0.49\textwidth]{figures/contours-Om-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
+        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}
@@
 First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid.
-In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnituce cut, the low redshift galaxies are \emph{different population} of galaxies.
+In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnitude cut, the low redshift galaxies are \emph{different population} of galaxies.
 We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
@@
 Our full parameter chains for different magnitudes are available upon request.
-\as{Is this the case?}
+\as{Is this the case?} \an{That would be totally fine with me.}
 

### 2019-10-20 doc/Paper/main.tex
Small changes to magnitude cuts section.

@@
 In Fig.~\ref{fig:HOD-redshift}, we additionally show the large-scale galaxy bias as a function of redshift derived from our best-fit HOD model.
-As can be seen, the large-scale bias scales approximately as $b(z) \sim \sfrac{1}{D(z)}$, where $D(z)$ denotes the linear growth factor.
+As can be seen, the large-scale bias scales approximately as $b(z) \propto \sfrac{1}{D(z)}$, where $D(z)$ denotes the linear growth factor.
 This behavior is consistent with e.g.
-studies of galaxies in the DEEP2 survey, which found constant clustering strengths as a function of redshift (and thus $b(z) \sim \sfrac{1}{D(z)}$) for magnitude-limited samples \cite{Coil:2004}.
+studies of galaxies in the DEEP2 survey, which found constant clustering strengths as a function of redshift (and thus $b(z) \propto \sfrac{1}{D(z)}$) for magnitude-limited samples \cite{Coil:2004}.
 \todo{How about saying that a more thorough analysis of the color-dependence of clustering properties would be needed to fully characterize this effect and that we leave this for future work?}
@@
 \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
-The third panel illustrates the empirical scaling $b(z) \sim \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
+The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
 \label{fig:HOD-redshift}
@@
 As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected.
-Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \sim \sfrac{1}{D(z)}$, for all samples.
-In order to obtain a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude, we assume it to be separable in $z$ and $m_{\mathrm{lim}}$ and make the following Ansatz:
-\begin{equation}
-b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha}.
+Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \propto \sfrac{1}{D(z)}$, for all samples, as can be seen from the middle panel of Fig.~\ref{fig:magnitude-cuts-bias}.
+Motivated by these results, we make the following Ansatz to derive a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude:
+\begin{equation}
+b(z, m_{\mathrm{lim}}) = \bar{b}(m_{\mathrm{lim}}) D(z)^{\alpha},
 \label{eq:bias-fit-func}
 \end{equation}  
+where we have assumed the bias to be separable in $z$ and $m_{\mathrm{lim}}$ and the parameter $\alpha$ accounts for deviations to the simple inverse growth function proportionality.
 We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
@@
 This analysis yields a few interesting results.
-First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid.
+First, we find that the approximation $b(z) \propto D(z)^{-1}$ (i.e $\alpha=-1$) is only approximately valid.
 In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnitude cut, the low redshift galaxies are \emph{different population} of galaxies.
@@
 
-The most common use of this results is for Fisher matrix forecasts for constraining power of magnitude-limited samples. \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?}
-
-An alternative use is galaxy evolution studies, where this results provides a convenient cross-check formula.
-Our full parameter chains for different magnitudes are available upon request.
+We anticipate that these results will mostly be useful for forecasting the  constraining power of magnitude-limited samples in Fisher matrix forecasts.
+\as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?}
+
+An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
+Our full parameter chains for the different limiting magnitudes are available upon request.
 \as{Is this the case?} \an{That would be totally fine with me.}

### 2019-10-21 doc/Paper/main.tex
small things

--- 2019-10-20 doc/Paper/main.tex
@@
 In the context of pseudo-$C_\ell$ estimators this is achieved in practice by obtaining the best-fit value of $A_{\rm syst}$, subtracting the corresponding best-fit contaminant contribution from the maps and analytically accounting for the associated loss of modes when computing the angular power spectrum.
-Further details of this method can be found in \cite{2017MNRAS.465.1847E,2019MNRAS.484.4127A}.
+Further details about this method can be found in \cite{2017MNRAS.465.1847E,2019MNRAS.484.4127A}.
 
@@
     \end{equation}
-    A central assumption in standard HOD parametrizations is that centrals/satellites follow a binomial/Poisson distribution.
+    A central assumption in standard HOD parametrizations is that centrals/satellites follow a Bernoulli/Poisson distribution.
 
@@
 where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
-\as{Do we want to rewrite this as $\bar{b} = b_0 + b_1 (m-24)$?} The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
-
-This analysis yields a few interesting results.
-First we find that the approximation $b(z)\propto D(z)^{-1}$ (i.e $\alpha=-1$ is only approximately valid.
-In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnituce cut, the low redshift galaxies are \emph{different population} of galaxies.
-We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
-
-The most common use of this results is for Fisher matrix forecasts for constraining power of magnitude-limited samples. \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?}
-
-An alternative use is galaxy evolution studies, where this results provides a convenient cross-check formula.
-Our full parameter chains for different magnitudes are available upon request.
-\as{Is this the case?}
+The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
+As can be seen, the fitting function provides a rather good fit and it might thus become a useful tool for e.g.
+modeling galaxy bias when forecasting the constraining power of magnitude-limited samples.
 

### 2019-10-21 doc/Paper/main.tex
Small changes to fitting function results.
more stuff

@@
   \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
-
     Uncertainties in photometric redshifts (photo-$z$) represent one of the major systematics in photometric galaxy clustering analyses.
@@
 
-    We estimate the Gaussian covariance of the pseudo-$C_\ell$ estimator as described in \cite{2004MNRAS.349..603E,2019arXiv190611765G}.
-In the absence of any approximations, the covariance of the observed power spectra is given by
+    We estimate the Gaussian covariance of the pseudo-$C_\ell$ estimator as described in \cite{2004MNRAS.349..603E,2019arXiv190611765G}. The covariance of the observed pseudo-power spectra is given by
     \begin{equation}
@@
     where $W^x_{{\bf l}{\bf l}'}$ are coupling coefficients depending only on the mask of $x$ (see \cite{2019arXiv190611765G} for further details).
-In the absence of further approximations, computing the covariance matrix would therefore imply solving a 4-dimensional integral for each pair $(\ell,\ell')$.
+Without further approximations, computing the covariance matrix would therefore imply solving a 4-dimensional integral for each pair $(\ell,\ell')$.
 This is an $O(\ell_{\rm max}^6)$ operation which easily becomes computationally unfeasible.
@@
     \begin{equation}
-      {\rm Cov}\left(\tilde{C}^{ab}_\ell,\tilde{C}^{cd}_{\ell'}\right)=(2\ell'+1)^{-1}\left[C^{ac}_{(\ell}C^{bd}_{\ell')}M_{\ell\ell'}(w_aw_c,w_bw_d)+C^{ad}_{(\ell}C^{bc}_{\ell')}M_{\ell\ell'}(w_aw_d,w_bw_c)\right].
-    \end{equation}
-
-    Where $M_{\ell\ell'}$ are the mode-coupling matrices described in the previous section, except now they are computed from the products of two masks.
+      {\rm Cov}\left(\tilde{C}^{ab}_\ell,\tilde{C}^{cd}_{\ell'}\right)=(2\ell'+1)^{-1}\left[C^{ac}_{(\ell}C^{bd}_{\ell')}M_{\ell\ell'}(w_aw_c,w_bw_d)+C^{ad}_{(\ell}C^{bc}_{\ell')}M_{\ell\ell'}(w_aw_d,w_bw_c)\right],
+    \end{equation}
+    where $M_{\ell\ell'}$ are the mode-coupling matrices described in the previous section, except now they are computed from the products of two masks.
 It has been shown by \cite{2019arXiv190611765G} that this approach yields a very good approximation for the power spectrum covariance, fully accounting for the effects of mode coupling due to survey geometry.
@@
 In general, this contribution is given by the angular projection of the three-dimensional trispectrum as (see e.g.
-\cite{Krause:2017}) \todo{Also, you need to define the $q$s.}
+\cite{Krause:2017})
     \begin{equation}
@@
     The quantity $A(\ell_{i})$ denotes the area of an annulus of width $\Delta \ell_{i}$ around $\ell_{i}$, i.e.
-$A(\ell_{i}) = \int_{\vert \boldsymbol{\ell} \vert \in \ell_{i}} \mathrm{d}^{2}\boldsymbol{\ell}$, which is approximately given by $A(\ell_{i}) \approx 2 \pi \Delta \ell_{i} \ell_{i}$ for $\ell_{i} \gg \Delta \ell_{i}$.
+$A(\ell_{i}) \equiv \int_{\vert \boldsymbol{\ell} \vert \in \ell_{i}} \mathrm{d}^{2}\boldsymbol{\ell}$, which is approximately given by $A(\ell_{i}) \approx 2 \pi \Delta \ell_{i} \ell_{i}$ for $\ell_{i} \gg \Delta \ell_{i}$.
+$q^a(\chi)\equiv H(z)p^a(z)$ is the window function for the $a$-th redshift bin.
 
@@
     where
-    \begin{align}
+    \begin{align}\label{eq:halo-mod-trisp-start}
       &T^{abcd, 1h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = I^{0}_{abcd}(k_{a}, k_{b}, k_{c}, k_{d}), \\
@@
       &T^{abcd, 4h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = T^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{c}(k_{c})I^{1}_{d}(k_{d}).
-    \label{eq:halo-mod-trisp}
+    \label{eq:halo-mod-trisp-end}
     \end{align}
@@
     \end{equation}
-where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
+    where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp-start}-\ref{eq:halo-mod-trisp-end} \todo{are you setting the $I$s to 1 in the case of the $>1h$ terms?} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
     \begin{equation}
@@
 
-For consistency with our implementation of the trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
+    For consistency with our implementation of the connected trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field \todo{Again, does this mean $I_a^1=1$?}\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
 We find our parameter constraints to be unaffected by this change and therefore resort to the approach described above for consistency.}.
@@
 For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
-For the cross correlations, we set $\ell_{\mathrm{max}}$ to the minimal value derived for the respective two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
+For the cross correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
 
@@
 From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean), and compute the mean redshift of each realization.
-Estimating the standard deviation in the mean redshift of all realizations, we find that sample variance uncertainty in COSMOS leads to 1-sigma  shifts around $\Delta z\sim0.006$ and fractional widths around $z_w\sim 0.04$.
+Estimating the standard deviation in the mean redshift of all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.
 We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties.
@@
 estimated directly from the observed galaxy overdensity maps).
-This test allows us to test the worst-case scenario where any source of contamination is completely ignored.
+This allows us to test the worst-case scenario where any source of contamination is completely ignored.
 The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in red in Figure \ref{fig:cls_systematics}.
 In most cases we observe very small differences (smaller than $1\sigma$) between both spectra.
-However, we see that some of the spectra involving the first redshift bin are slightly more sensitive to deprojection, exhibiting differences of up to 3$\sigma$ in the range of scales used in our analysis.
+\todo{not anymore} However, we see that some of the spectra involving the first redshift bin are slightly more sensitive to deprojection, exhibiting differences of up to 3$\sigma$ in the range of scales used in our analysis.
 This suggests that, although the level of contamination in the raw galaxy overdensity maps is small, it is necessary to address it.
@@
 Figure \ref{fig:shotnoise_avg} shows the comparison between the analytic estimate in Eq.
-\ref{eq:nell} (transparent lines) and the estimate from the difference map power spectra (solid lines) for the four different redshift bins \todo{what order?}.
+\ref{eq:nell} (transparent lines) and the estimate from the difference map power spectra (solid lines) for the four different redshift bins.
 Within the statistical noise of the split-map estimate, both methods agree well, particularly at high $\ell$, validating our procedure to subtract the shot-noise contribution.
@@
   \subsection{Covariance matrix}\label{ssec:results.covariance}
-
     We estimate the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}.
@@
 This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
-
     \begin{figure}
@@
         \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
-\caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}
-\label{fig:covmat}
+        \caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
       \end{center}
@@
         \subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
-\caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} 
-\label{fig:covariance-contributions}
+        \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} \label{fig:covariance-contributions}
       \end{center}
@@
   \subsection{Constraints on HOD parameters}\label{ssec:results.hod-constraints}
-
     \subsubsection{Fiducial constraints}\label{sssec:results.hod-constraints.fiducial}
-
-Both the auto- and cross power spectra shown in Fig.~\ref{fig:cls_summary} carry information on astrophysical, systematics and cosmological parameters.
-We especially expect the cross correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and shifts in the means of the bins.
-In this work, we therefore compute fiducial constraints from a joint fit to both auto- and cross power spectra.
+      Both the auto- and cross-power spectra shown in Fig.~\ref{fig:cls_summary} carry information on astrophysical, systematics and cosmological parameters.
+We especially expect the cross-correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and shifts in the means of the bins.
+In this work, we therefore compute fiducial constraints from a joint fit to both auto- and cross-power spectra.
 

### 2019-10-21 doc/Paper/main.tex
pass through the whole paper

@@
   \subsection{Parameter constraints}\label{ssec:methods.constr}
-    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross power spectra to be Gaussian 
+    In order to derive constraints on HOD, cosmological and systematics parameters, we assume the joint likelihood of all auto- and cross-power spectra to be Gaussian 
     \begin{align}
@@
 For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
-For the cross correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
+For the cross-correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
 
@@
         \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
-        \caption{Correlation matrix for all auto- and cross power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
+        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
       \end{center}
@@
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
-As can be seen, we find that, within or uncertainties, the data prefer both a constant $M_{\mathrm{min}}$ and $M_{1}$.
-This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift since galaxies will only form in the most massive halos at early times.
+As can be seen, we find that, within or uncertainties, the data prefer both a roughly constant $M_{\mathrm{min}}$ and $M_{1}$.
+This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift, since galaxies will only form in the most massive halos at early times.
 We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.
-Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low.
+Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low \todo{This table doesn't really contain information about $M_0$.}.
 This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}).
-Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses, i.e.
+Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses.
+I.e.
 the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.
-
+Physically, this means that the data show preference for a model in which all halos massive enough to host a central galaxy are likely to host satellites too.
       \begin{figure}
@@
           \includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
-\caption{Measured auto- and cross power spectra considered in our analysis.
-The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
+          \caption{Measured auto- and cross-power spectra considered in our analysis.
+The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross-power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
           \label{fig:cls-best-fit}
@@
           \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-\caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
+          \caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
+\todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?}}
           \label{fig:hod-params-z-dep}
@@
     \subsubsection{Robustness to modeling and data choices}
-
-In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants, as described in the following.
+      In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants as follows.
 A summary of all robustness tests performed and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.
@@
         \caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
-The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
+\todo{it would be good to specify what the error bars are.
+I imagine they're watershed errors (i.e.
+values with equal probability enclosing 60\% of $p$.
+Is that correct?} The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
 In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$.
@@
             pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
-fiducial magn. & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
+            fiducial magn.
+& $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
             fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
@@
 
-As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross power spectra.
-However, cross correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
-In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross power spectra.
+      As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross-power spectra.
+However, cross-correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
+In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross-power spectra.
 Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone.
-As can be seen, the constraints from auto power spectra and auto- and cross power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis.
-Furthermore, we see that the constraining power on HOD parameters is unaffected by including the cross power spectra.
-As a final consistency check between auto- and cross power spectra we test how well the auto power spectra predict the cross power spectra.
-To this end we compute the $\chi^{2}$ between the observed auto- and cross power spectra and the theoretical predictions derived from auto power spectra only.
+As can be seen, the constraints from auto-spectra and from both auto- and cross-power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis.
+Furthermore, we see that the constraining power on HOD parameters is mostly unaffected by including the cross-power spectra.
+As a final consistency check between auto- and cross-power spectra we test how well the auto-spectra predict the cross-spectra.
+To this end we compute the $\chi^{2}$ between the observed auto- and cross-power spectra and the theoretical predictions derived from auto power spectra only.
 As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
-We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
-This shows that the auto power spectra are able to predict the cross power spectra and provides further confirmation of their consistency.
+We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross-power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
+This shows that the auto power spectra are able to predict the cross-power spectra and provides further confirmation of their consistency.
 
       An important part of our data model is the analytical covariance matrix described in Sec.~\ref{sssec:methods.theory.covar}.
-In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian contributions.
+In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian connected contributions.
 As can be seen from Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}, these constraints agree very well with each other.
@@
 Accounting for all non-Gaussian contributions to the covariance results in slightly broadened but consistent constraints.
-Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales and therefore do not have a significant impact when computing constraints from all power spectra.
-Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we account for less contributions to the total covariance, as expected.
+Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales, and therefore do not have a significant impact when computing constraints from all power spectra.
+Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we remove the non-Gaussian contributions, as expected.
 However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.
@@
 The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
-\label{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}
+($95 \%$ c.l.).} \label{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}
         \end{center}
@@
     \subsubsection{Robustness to photometric redshift uncertainties}
-
       One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.
@@
 We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those.
-We therefore show the constraints in terms of the reparametrized parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
+We therefore show the constraints in terms of the reparametrized variables $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
 While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
@@
       It is instructive to investigate which part of the data drives the constraints on photometric redshift systematics.
-To this end we compare the constraints obtained using auto power spectra only to those obtained from auto- and cross power spectra (our fiducial case).
-As can be seen from Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we find that the auto power spectra do not constrain the photo-$z$ systematics parameters $\Delta z_{i} - \Delta z_{j}$, as opposed to the combination of auto- and cross power spectra.
-This shows that the cross correlations drive the constraints on photometric redshift systematics and are thus essential for jointly constraining redshift systematics and astrophysical/cosmological parameters from galaxy clustering data.
+To this end we compare the constraints obtained using auto power spectra only to those obtained from auto- and cross-power spectra (our fiducial case).
+As can be seen from Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we find that the auto-spectra do not constrain the photo-$z$ systematics parameters $\Delta z_{i} - \Delta z_{j}$, as opposed to the combination of auto- and cross-power spectra.
+This shows that the cross-correlations drive the constraints on photometric redshift systematics and are thus essential for jointly constraining redshift systematics and astrophysical/cosmological parameters from galaxy clustering data.
 
@@
 However, as noted in \cite{Joudaki:2019}, catastrophic outliers that are erroneously assigned to too low redshifts are more likely to fall into our sample than outliers assigned to too high redshifts.
-Therefore, the lowest redshift bin in particular might also be affected by photometric redshift errors \an{not sure this is the reason for which Jeff asked us to remove the low-z bin...}.
-In order to test the robustness of our results to photometric redshift uncertainties at low and high redshifts, we compute parameter constraints separately neglecting the high and low redshift bin and all its cross-correlations.
+Therefore, the lowest redshift bin in particular might also be affected by photometric redshift errors.
+In order to test the robustness of our results to photometric redshift uncertainties at low and high redshifts, we compute parameter constraints separately neglecting the high- and low-redshift bin and all its cross-correlations.
 The results of these two analyses are shown alongside our fiducial constraints in Fig.~\ref{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}.
@@
 This secondary peak contains $\sim$5\% of galaxies and peaks around $z\sim 3$ (hence cannot be seen in Figure \ref{fig:nzs}).
-To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\Delta \chi^2\sim 0.05$.
-This indicates that the effect of this bump is to small to be statistically significant.
+To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\chi^2$, corresponding to $\Delta \chi^2\sim 0.05$.
+This indicates that the effect of this peak is too small to be statistically significant.
 We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=auto+cross-vs-fit=auto.pdf}
-\caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained from auto power spectra alone. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+          \caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained from auto power spectra alone.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
           \label{fig:constraints-pz-syst-auto+cross-vs-auto}
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=pz-shifts+widths-vs-fit=pz-shifts-vs-no-pz-shifts.pdf}
-\caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+          \caption{Comparison of our fiducial HOD constraints to those obtained setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
           \label{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3.pdf}
-\caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross correlations and those obtained from the three highest bins and their cross correlations.
+          \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from the three lowest redshift bins and their cross-correlations and those obtained from the three highest bins and their cross-correlations.
 The inner (outer) contour shows the $68 \%$ c.l.
@@
 Investigating this further, we find that the observed differences in $\Delta z_{i}$ cannot be explained with the differences in mean redshift between the distributions derived using the five separate methods.
-In addition, we find that for the redshift distributions considered in this analysis, mean shifts mainly affect low redshift auto power spectra but have a significantly smaller impact on high redshift bins.
+In addition, we find that for the redshift distributions considered in this analysis, mean shifts mainly affect low redshift auto-power spectra but have a significantly smaller impact on high redshift bins.
 Variations in the widths of the photo-$z$ distributions on the other hand, have a similar impact at low and high redshifts.
@@
 As borne out by the observed discrepancies in HOD constraints, our analysis is sensitive to these differences and we therefore need to extend the photo-$z$ error model.
-From the discussion above it follows that additionally accounting for variations in the widths of the distributions is sufficient, as this error model yields HOD constraints that are robust to changes in the photo-$z$ estimation method.
+From the discussion above, it follows that additionally accounting for variations in the widths of the distributions is sufficient, as this error model yields HOD constraints that are robust to changes in the photo-$z$ estimation method.
 
@@
 We can quantify this effect by computing the fraction of red galaxies in our sample as a function of redshift: we empirically determine the separation between the blue and red clouds (denoted by the solid lines in the figure) and compute the fraction of galaxies in the red cloud as $f_{R} = \sfrac{N_{R}}{(N_{R}+N_{B})}$, where $N_{R}$ denotes the number of galaxies above the separation line, while $N_{B}$ is the number of galaxies below the line.
-Consistent with the figure, we find decreasing $f_{R}$ as a function of redshift.
+Consistent with the figure, we find a decreasing $f_{R}$ as a function of redshift.
 
       These results suggest that red galaxies are increasingly underrepresented with respect to blue galaxies in our sample at higher redshifts.
-This is probably due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$, which translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
-As red galaxies become very faint at these wavelengths, they drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
-This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift})
+This is due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$: the $i$-band filter translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
+Red galaxies with a strong $4000$ \AA break therefore become very faint at these wavelengths and drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
+This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift}).
 
@@
 studies of galaxies in the DEEP2 survey, which found constant clustering strengths as a function of redshift (and thus $b(z) \propto \sfrac{1}{D(z)}$) for magnitude-limited samples \cite{Coil:2004}.
-\todo{How about saying that a more thorough analysis of the color-dependence of clustering properties would be needed to fully characterize this effect and that we leave this for future work?}
-
       \begin{figure}
@@
   \subsection{Magnification}\label{ssec:results.magnification}
-
     In addition to intrinsic correlations between galaxy positions, there exist several additional effects affecting the observed clustering of galaxies.
-One of these is the magnification of distant sources due to gravitational lensing by the intervening LSS, an effect usually called magnification bias (e.g.
+The most relevant one for projected clustering studies is the magnification of distant sources due to gravitational lensing by the intervening LSS, an effect usually called magnification bias (e.g.
 \cite{Schneider:1989, Narayan:1989}).
@@
 The combined effect, is a position-dependent modulation of the number density that distorts the clustering pattern.
-It has been shown that the clustering signal due to magnification can be comparable to the intrinsic clustering signal for cross-correlations between widely separated redshift bins (see e.g.
+It has been shown that the clustering signal due to magnification can be comparable to the intrinsic clustering signal for cross-correlations between widely-separated redshift bins (see e.g.
 \cite{Challinor:2011}).
@@
 In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.
-Overdensities along the line of sight causes the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increaseing the observed number density).
+Overdensities along the line of sight causes the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density).
 The two effects cancel at leading order when $s=\sfrac{5}{2}$.
@@
     \end{equation}
-    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=(\ell+1/2)/\chi$ for brevity.
+    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=(\ell+1/2)/\chi$.
 
@@
 As can be seen, the three estimates agree well with each other and we use the $s(z)$ function derived from our fiducial WIDE sample in the following.
-Our uncertainty on estimation of $s(z)$ is subdominant to statistical precision of the detection and so we ignore it.
+Our uncertainty on the estimation of $s(z)$ is subdominant given the statistical precision of our measurement, and therefore we ignore it.
     \begin{figure}
@@
 
-    From a joint fit to all auto- and cross power spectra we obtain $A_{\mu} = 2.18 \pm 0.74$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+    From a joint fit to all auto- and cross-power spectra we obtain $A_{\mu} = 2.18 \pm 0.74$ and the constraint is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
 This constitutes a $\sim 2.9 \sigma$ detection of magnification from our HSC sample.
@@
 
-    In order to identify the part of the data vector driving the constraints on $A_{\mu}$, we repeat this analysis only including the auto power spectra.
-The comparison between the constraints on $A_{\mu}$ from auto- and cross power spectra to those obtained from auto power spectra alone in shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
-As can be seen, the auto power spectra alone do not constrain $A_{\mu}$, which implies that the constraints on the magnification amplitude are solely driven by the cross power spectra.
-This sensitivity of the cross power spectra to magnification mainly stems from the fact that the intrinsic cross correlations between widely separated bins are small, which leads to an increased sensitivity to any non-intrinsic source of cross correlation, such as magnification.
-In analogy to the results for the photo-$z$ systematics parameters, we thus find that cross power spectra carry important information and it will thus be beneficial to include these cross correlations in current and future photometric clustering analyses.
+    In order to identify the part of the data vector driving the constraints on $A_{\mu}$, we repeat this analysis only including the auto-spectra.
+The comparison between the constraints on $A_{\mu}$ from auto- and cross-power spectra to those obtained from auto power spectra alone in shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+As can be seen, the auto power spectra alone do not constrain $A_{\mu}$, which implies that the constraints on the magnification amplitude are solely driven by the cross-power spectra.
+This sensitivity of the cross-power spectra to magnification mainly stems from the fact that the cross-correlations between widely separated bins caused by intrinsic clustering are small, which leads to an increased sensitivity to any non-intrinsic source of cross-correlation, such as magnification.
+In analogy to the results for the photo-$z$ systematics parameters, we thus find that cross-power spectra carry important information and it will thus be beneficial to include these cross-correlations in current and future photometric clustering analyses.
 
@@
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
-        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross power spectra.
+        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross-power spectra.
 The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$,
+From a joint fit to all auto- and cross-power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$,
 %%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Om-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross-power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}
@@
   \subsection{Constraints on linear galaxy bias for different magnitude-limited samples}\label{ssec:results.mag_cuts}
-
-Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$\footnote{We note that we only consider magnitude cuts in the $i$-band and we do not investigate the dependence of our results on the photometric band used to select a magnitude-limited sample.}.
+    Finally we use our analysis pipeline described in Sec.~\ref{sec:methods} to investigate the dependence of galaxy clustering on limiting magnitude $m_{\mathrm{lim}}$ of the sample and derive an approximate fitting function for the linear galaxy bias as a function of redshift and $m_{\mathrm{lim}}$.
+We only consider magnitude cuts in the $i$-band and we do not investigate the dependence of our results on the photometric band used to select a magnitude-limited sample.
 
@@
     \end{equation}
-where we have assumed the bias to be separable in $z$ and $m_{\mathrm{lim}}$ and the parameter $\alpha$ accounts for deviations to the simple inverse growth function proportionality.
+    where we have assumed the bias to be separable in $z$ and $m_{\mathrm{lim}}$, and the parameter $\alpha$ accounts for deviations from the simple inverse growth function proportionality.
 We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
@@
       \begin{aligned}
-\alpha &= -1.32, \\
-\bar{b}(m_{\mathrm{lim}}) &= b_{1}m_{\mathrm{lim}} + b_{0},
+        \alpha &= -1.30, \\
+        \bar{b}(m_{\mathrm{lim}}) &= b_{1}(m_{\mathrm{lim}}-24) + b_{0},
         \label{eq:bias-fit-func-result}
@@
     \end{equation}
-where $b_{1} = -0.0627$ and $b_{0} = 2.35$.
-\as{Do we want to rewrite this as $\bar{b} = b_0 + b_1 (m-24)$?} The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
+    where $b_{1} = -0.0631$ and $b_{0} = 0.8356$. The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
 
@@
 We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
-
-We anticipate that these results will mostly be useful for forecasting the  constraining power of magnitude-limited samples in Fisher matrix forecasts.
-\as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?}
-
-An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
+\todo{DA: I don't really understand if there should be a physical reason for the $1/D$ scaling even if the population was the same.}
+
+    We anticipate that these results will be useful for forecasting the  constraining power of magnitude-limited samples.
+\as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?} \todo{DA: I'd suggest adding Andrina's latest plot with the SRD lines to Figure \ref{fig:HOD-redshift} to avoid new figures.} An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
 Our full parameter chains for the different limiting magnitudes are available upon request.
 \as{Is this the case?} \an{That would be totally fine with me.}
-
+    %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
+The same data could also be used to compare the effective number densities.
+In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities.
+We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
     \begin{figure}
@@
 \section{Discussion and Conclusions}\label{sec:discussion}
-
   In this work, we have presented a comprehensive analysis of photometric galaxy clustering in HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$.
-We have split this sample into four tomographic redshift bins and computed all possible auto- and cross power spectra, accounting for observational systematics in number density fluctuations through map-level deprojection.
-We have then fit the data using a halo model coupled with a halo occupation distribution, marginalizing over a flexible model for photometric redshift uncertainties.
-Our results are well-fit by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$.
+We have split this sample into four tomographic redshift bins and computed all possible auto- and cross-power spectra, accounting for observational systematics in number density fluctuations through map-level deprojection.
+We have then fitted the data using a halo model coupled with a halo occupation distribution, marginalizing over a flexible model for photometric redshift uncertainties.
+Our results are well fitted by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$.
 We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
@@
 We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from our data alone.
-In addition, we also allowed for variations in the $\Lambda$CDM cosmological parameters, finding that the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
-Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting magnitude.
-
-Our analysis hence shows that the quality of the HSC data allows scientific analyses leading to new insights into both physics of galaxy formation as well as methodology of clustering analyses.
-In terms of physics, we show that a simple magnitude cut can be used to create useful samples for galaxy clustering analyses.
-This contrasts with other approaches that focus on red central galaxies to create smaller samples with more reliable redshifts (see e.g.
+In addition to this, we also allowed for variations in the $\Lambda$CDM cosmological parameters, finding that the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
+Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting $i$-band magnitude (Eq.
+\ref{eq:bias-fit-func-result}).
+
+  Our analysis hence shows that the quality of the HSC data allows scientific analyses leading to new insights into both physics of galaxy formation as well as analysis strategies for galaxy clustering.
+In terms of physics, we show that a simple magnitude cut leading to a sufficiently homogeneous sample can be used to carry out robust galaxy clustering analyses, provided that photometric redshift systematics can be kept under control.
+This contrasts with other approaches that focus on red galaxies to create significantly smaller samples with more precise redshifts (see e.g.
 \cite{1507.05460,1807.10163}).
-Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias.
-In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification amplitude.
+Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias and larger projection effects.
+In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification.
 
   Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST.
-Our analysis demonstrates the feasibility of photometric galaxy clustering analyses using such high signal-to-noise datasets, which bodes well for future analyses using data from LSST.
-
-%Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
-The same data could also be used to compare the effective number densities.
-In fact \cite{1809.01669} already uses the HSC-SSP data to estimate number densities.
-We do find, however, that compared to LSST DESC SRD, the area lost to masking is considerably higher, around 20\% rather than 12\% assumed in \cite{1809.01669}.
+Our analysis demonstrates the feasibility of photometric galaxy clustering analyses using such high signal-to-noise datasets, which bodes well for future cosmological constraints using data from LSST.
 

### 2019-10-21 doc/Paper/main.tex
Adding fiducial magnification in main text.

@@
 This marginal inconsistency is probably due to uncertainties in the data-driven estimation of $s(z)$.
-The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 69.0$\footnote{This is consistent with the case in which we set $A_{\mu}=1$, where we obtain consistent constraints with best-fit $\chi^{2} = 72.8$, as can be seen from Tab.~\ref{tab:constraints_robustness}.}, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.87$ ($p$-value $= 0.78$).
+The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 69.0$, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.87$ ($p$-value $= 0.78$).
 This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 86.2 - 69.0 = 17.2$, consistent with the $\sim 3 \sigma$ detection.
@@
 In addition, we find the significance of the magnification detection to be largely insensitive to photo-$z$ systematics modeling choices, as it is not significantly affected by relaxing our photo-$z$ systematics model by fixing $z_{w, i} = 0$.
+
+These results are consistent with those obtained when we fix $A_{\mu} = 1$, as can be seen from Tab.~\ref{tab:constraints_robustness}.
+In the latter case, we obtain a best-fit $\chi^{2}$ of $\chi^{2} = 72.8$, which corresponds to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.91$ ($p$-value $= 0.70$) for $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$.
+The improvement in $\chi^{2}$ with respect to the fiducial analysis amounts to $\Delta \chi^{2} = 86.2 - 72.8 = 13.4$, which is lower than the value obtained with free magnification amplitude, but nevertheless constitutes a sizeable $\chi^{2}$ improvement.
 

### 2019-10-21 doc/Paper/main.tex
A couple of small changes.

@@
 Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations.
-Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, reproducing previous results.
+Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
 In terms of photometric redshift systematics, we show that additional care is needed in order to marginalize over uncertainties in the redshift distribution in galaxy clustering, even for samples of this small size, and that these uncertainties can be significantly constrained by including cross-bin correlations.
@@
 In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
-At the moment, this is only possible with the optical large scale structure surveys.
+At the moment, this is only possible with optical large scale structure surveys.
 
@@
 Specifically, HSC covers essentially the same bands as LSST, with the exception of missing the UV $u$-band fluxes.
-In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after 1 year \cite{1809.01669} ($i<25.1$).
-Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
+In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after one year \cite{1809.01669} ($i<25.1$).
+Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
 With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.
@@
 To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties.
-We additionally perform extended analyses in which we compute constraints on magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters, respectively.
+We additionally perform extended analyses in which we compute constraints on lensing magnification in our sample and allow for variations in the $\Lambda$CDM cosmological parameters, respectively.
 Finally, we use our data to derive a simple fitting function for the linear galaxy bias as a function of redshift and limiting magnitude of the sample.
 
-In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to model the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
-LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}.
-However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use we use it as a ``good enough'' substitute for the final modeling.
+In our analysis, we make several simplifying approximations; in particular we employ a simple semi-analytical halo model to derive theoretical predictions for the data, which will most certainly not be sophisticated enough for the full sky LSST analysis.
+The analysis of LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}.
+However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use it as a ``good enough'' substitute for the final modeling.
 
@@
 The area was calculated as the sum of pixel areas allowed by the sky mask described in Section \ref{ssec:methods.mask}.
-We note that HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
+We note that the HECTOMAP field is not included in our analysis due to its smaller area.} \label{tab:field_summary}
   \end{table}
@@
   In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\url{https://hsc-release.mtk.nao.ac.jp}}.
-The release is extensively documented in \cite{2018PASJ...70S...8A}, and we only provide the details of the galaxy sample and associated data used for our clustering analysis.
+The release is extensively documented in \cite{2018PASJ...70S...8A}, and here we only provide the details of the galaxy sample and associated data used for our clustering analysis.
 
@@
 In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees.
-The image quality is impressive at median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arc sec) and also likely better than the median seeing that will be achieved by LSST.
+The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
+DES with around 0.9 arc sec) and also likely better than the median seeing expected to be achieved by LSST.
 The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
@@
   All objects have photometric redshift measurements from 6 different codes as presented in \cite{2018PASJ...70S...9T}.
-We use the {\tt photoz\_best} redshift estimator assigned by the {\tt ephor\_ab} method as a marker to divide the sample into four tomographic samples containing roughly equal numbers of galaxies.
+We use the {\tt photoz\_best} redshift estimator assigned by the {\tt ephor\_ab} method as a marker to divide the sample into four tomographic samples containing roughly equal galaxy numbers.
 The {\tt photoz\_best} estimator is defined to minimize the risk that the true galaxy redshift lies outside the range $z_{\rm true}\pm 0.15(1+z_{\rm true})$, where $z_{\rm true}$ is the galaxy's true redshift.
@@
 As part of our systematics analysis (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
-It is worth noting that the NOMAD star catalog \cite{2004AAS...205.4815Z}, one of the datasets used to construct the brigh-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
+It is worth noting that the NOMAD star catalog \cite{2004AAS...205.4815Z}, one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
 To study the impact of this contamination on our clustering measurements, we have also estimated the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).
@@
     A number of astrophysical and observational systematic effects can affect the observed distribution of galaxies, and therefore may bias our inference of their clustering properties.
-To mitigate this effect we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}.
+To mitigate this effect, we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}.
 We generate maps of the most plausible sources of systematic variations in the galaxy number density:
@@
 Since we do not have direct access to the latter, we used, as coadd weights, the inverse of the sky level of each exposure, which should be close to inverse-variance weighting.
-Following this procedure we produce maps of the following quantities: airmass, CCD temperature, seeing, PSF ellipticity, exposure time, sky count level, root-mean square deviation of the sky count and number of visits.
+Following this procedure, we produce maps of the following quantities: airmass, CCD temperature, seeing, PSF ellipticity, exposure time, sky count level, root-mean square deviation of the sky count and number of visits.
     \end{enumerate}
@@
 
-    To estimate the fiducial redshift distributions used in our main analysis we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
+    To estimate the fiducial redshift distributions used in our main analysis, we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
 The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histogramming these redshifts with appropriate weights.
@@
     \begin{enumerate}
-      \item We first cross-match all objects in the COSMOS 30-band catalog with sources in the HSC COSMOS field that satisfy our sample cuts (see Section \ref{sec:data}).
+      \item We first cross-match all objects in the COSMOS 30-band catalog with sources in the HSC COSMOS field that satisfy our sample selection cuts (see Section \ref{sec:data}).
 Matches are found as pairs of objects with an angular separation smaller than 1 arcsecond.
@@
       \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbours in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
-We record the distance in this space to the furthest neighbour.
+We record the distance to the furthest neighbour in this space.
       \item We then compute the number of HSC sources $N_{\rm neigh}^{\rm HSC}$ found within the same radius in magnitude space.
@@
     There are a number of caveats associated with this method to estimate redshift distributions.
-First, the COSMOS 30-band photometric redshifts are not as good as a purely spectroscopic sample in terms of redshift accuracy and precision.
+First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample.
 Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the colour-redshift relation has an environmental dependence.
@@
 
-    In the absence of a sky mask, the flat-sky auto-power spectrum could be simply estimated Fourier transforming a given map $a_{\bf l}={\rm FT}[a(\nv),{\bf l}]$ (where ${\rm FT}$ denotes a Fourier transform operation, and ${\bf l}$ is a 2D wavenumber), and averaging its modulus squared over bins of $\ell\equiv|{\bf l}|$.
-In any practical situation, however, it will be desirable to apply weights on the map to e.g.
+    In the absence of a sky mask, the flat-sky auto-power spectrum could be simply estimated by Fourier transforming a given map $a_{\bf l}={\rm FT}[a(\nv),{\bf l}]$ (where ${\rm FT}$ denotes a Fourier transform operation, and ${\bf l}$ is a 2D wavenumber), and averaging its modulus squared over bins of $\ell\equiv|{\bf l}|$.
+In any practical situation however, it will be desirable to apply weights on the map to e.g.
 downweight noisy areas or altogether remove pixels that haven't been observed.
@@
     Finally, a noise bias term must be subtracted from all auto-power spectra.
-In the case of galaxy clustering, and assuming this noise is entirely due to Poisson shot noise, this can be done analytically as described in \cite{2019MNRAS.484.4127A}.
+In the case of galaxy clustering, and assuming this noise to be entirely due to Poissonian shot noise, this can be done analytically as described in \cite{2019MNRAS.484.4127A}.
 In short, the noise power spectrum before mode-decoupling (i.e.
@@
     \begin{equation}
-      \delta^i_g(\nv)=\int \mathrm{d}z\,p^i(z)\,\Delta_g\left(t(z),\chi(z)\nv\right).
-    \end{equation}
-    Here $t(z)$ and $\chi(z)$ are the cosmic time and radial comoving distance as a function of redshift, and $p^i(z)$ is the redshift bin window function, given by the true redshift distribution of objects in the bin normalized to unit area.
-
-    Given the small size of the sky patches covered by the HSC DR1, we will adopt the flat sky approximation for simplicity, in which case $\nv$ is a 2D vector.
+      \delta^i_g(\nv)=\int \mathrm{d}z\,p^i(z)\,\Delta_g\left(t(z),\chi(z)\nv\right),
+    \end{equation}
+where we have assumed a flat cosmological model, i.e. $\Omega_{k} = 0$ for simplicity.
+    In the above equation, $t(z)$ and $\chi(z)$ are the cosmic time and radial comoving distance as a function of redshift, and $p^i(z)$ is the redshift bin window function, given by the true redshift distribution of objects in the bin normalized to unit area.
+
+    Given the small size of the sky patches covered by HSC DR1, we will adopt the flat sky approximation for simplicity, in which case $\nv$ is a 2D vector.
 It is common to decompose $\delta^i_g(\nv)$ into its Fourier coefficients
@@
 We define $R_\Delta$ as the radius that encloses $\Delta=200$ times the background matter density.
-The concentration-mass relation $c(M)$ also depends on the choice of $\Delta$, and we follow the parametrization of \cite{Duffy:2008}.
 In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}.
@@
     \begin{equation}
-      R(z,k)=\frac{P^{\rm Halofit}_{mm}(z,k)}{P^{\rm halo\,model}_{mm}(z,k)},
-    \end{equation}
- which we compute for our fiducial cosmological model given in Sec.~\ref{ssec:methods.constr}.
-
-    We expect mean galaxy properties to evolve as a function of redshift for the magnitude-limited sample considered in this analysis.
+      R(z,k)=\frac{P^{\rm Halofit}_{mm}(z,k)}{P^{\rm halo\,model}_{mm}(z,k)}.
+    \end{equation}
+We compute the quantity $R(z,k)$ for our fiducial cosmological model given in Sec.~\ref{ssec:methods.constr}.
+
+    We expect mean galaxy properties to evolve as a function of redshift $z$ for the magnitude-limited sample considered in this analysis.
 Instead of fitting a separate HOD model to each redshift bin, we fit redshift-dependent functions to $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$ and choose a functional form given by:
@@
   \subsubsection{Covariance matrices}\label{sssec:methods.theory.covar}
-    We use an analytical procedure to estimate the uncertainties of our measured power spectra, inspired in the methods used by \cite{Krause:2017}.
+    We use an analytical procedure to estimate the uncertainties of our measured power spectra, inspired by the methods used by \cite{Krause:2017}.
 As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labelled SSC here).
@@
     \end{equation}
-    where $W^x_{{\bf l}{\bf l}'}$ are coupling coefficients depending only on the mask of $x$ (see \cite{2019arXiv190611765G} for further details).
+    where the quantities $W^x_{{\bf l}{\bf l}'}$ are coupling coefficients depending only on the mask of $x$ (see \cite{2019arXiv190611765G} for further details).
 Without further approximations, computing the covariance matrix would therefore imply solving a 4-dimensional integral for each pair $(\ell,\ell')$.
@@
     where
-    \begin{align}\label{eq:halo-mod-trisp-start}
+    \begin{equation}
+    \begin{aligned}
       &T^{abcd, 1h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = I^{0}_{abcd}(k_{a}, k_{b}, k_{c}, k_{d}), \\
@@
       &T^{abcd, 4h}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d}) = T^{\mathrm{PT}}(\mathbf{k}_{a}, \mathbf{k}_{b}, \mathbf{k}_{c}, \mathbf{k}_{d})I^{1}_{a}(k_{a})I^{1}_{b}(k_{b})I^{1}_{c}(k_{c})I^{1}_{d}(k_{d}).
-    \label{eq:halo-mod-trisp-end}
-    \end{align}
+    \label{eq:halo-mod-trisp}
+    \end{aligned}
+    \end{equation}
     Here, ${\bf k}_{ab}\equiv {\bf k}_a+{\bf k}_b$, and the quantities $B^{\mathrm{PT}}$ and $T^{\mathrm{PT}}$ denote the matter bi- and trispectrum respectively, as estimated using tree-level perturbation theory.
@@
     \end{equation}
-    where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp-start}-\ref{eq:halo-mod-trisp-end} \todo{are you setting the $I$s to 1 in the case of the $>1h$ terms?} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
+    where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp} \todo{are you setting the $I$s to 1 in the case of the $>1h$ terms?} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
     \begin{equation}
@@
     Finally, we compute the super-sample covariance contribution following the treatment of \cite{Krause:2017}, i.e.:
-    \begin{align}
+     \begin{equation}
+    \begin{aligned}
        \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) &= \int \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
-    \end{align}
+    \end{aligned}
+    \end{equation}
         The quantity $\sigma_b^2(z)$ is the variance of the long wavelength mode $\delta_{\rm LS}$ over the survey footprint, given by
@@
     \end{align}
-    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and is kept constant during parameter estimation \citep{2019OJAp....2E...3K}.
+    The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and which we keep constant during parameter estimation \citep{2019OJAp....2E...3K}.
     We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}.
@@
 The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}.
-We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s.
+We perform additional analyses in which we separately allow for variations in the amplitude $A_{\mu}$ of the magnification bias kernel $W_{\mu}$ and the cosmological parameters $\Omega_{c}$ and $\sigma_{8}$, where $\Omega_{c}$ is the fractional cold matter density today and $\sigma_{8}$ denotes the r.m.s.
 of linear matter fluctuations in spheres of comoving radius 8 $h^{-1}$ Mpc.
@@
       The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as red circles with error bars.
-In all cases we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a grey solid line in the auto-correlations.
+In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a grey solid line in the auto-correlations.
 As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection.
@@
       \begin{equation}
-       {\rm Var}(\hat{\bar n})=\int \frac{\mathrm{d}{\bf l}^2}{(2\pi)^2}\left|\frac{W_{\bf l}}{\int d\nv^2\,W(\nv)}\right|^2\,C_\ell.
+       {\rm Var}(\hat{\bar n})=\int \frac{\mathrm{d}{\bf l}^2}{(2\pi)^2}\left|\frac{W_{\bf l}}{\int \mathrm{d}\nv^2\,W(\nv)}\right|^2\,C_\ell.
       \end{equation}
@@
 We find that the error on $\hat{\bar n}$ is dominated by cosmic variance (as opposed to shot noise) by more than a factor of $\sim5$ in all cases.}.
-Following this procedure we estimate the number density in each field and redshift bin as well as its uncertainty (where we use the mask described in Section \ref{ssec:methods.mask} and the best-fit theory power spectra to compute the latter).
+Following this procedure, we estimate the number density in each field and redshift bin as well as its uncertainty (where we use the mask described in Section \ref{ssec:methods.mask} and the best-fit theory power spectra to compute the latter).
 The results are shown in Figure \ref{fig:ndens_consistency}.

### 2019-10-21 doc/Paper/main.tex
Further small changes.

@@
 We will discuss these findings in detail in Sec.~\ref{sssec:results.hod-constraints.constraints-interpretation}.
-Finally we see from Tab.~\ref{tab:constraints_robustness} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low \todo{This table doesn't really contain information about $M_0$.}.
+Finally we see from Tab.~\ref{tab:params} that the minimal mass to host a satellite galaxy, $M_{0}(z)$, obtained in our analysis is quite low.
 This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}).

### 2019-10-22 doc/Paper/main.tex
Additional small chnanges.

@@
       \end{figure}
-      As described in Section \ref{ssec:methods.cell}, our main strategy to address possible contamination of the measured power by systematics causing artificial density fluctuations is to project out the systematics templates discussed above from the data at the map level.
+      As described in Section \ref{ssec:methods.cell}, our main strategy to address possible contamination of the measured power spectra by systematics causing artificial density fluctuations is to project out the systematics templates discussed above from the data at the map level.
 This procedure can also be understood as building a linear model for the contamination (see Eq.
@@
 
-      Second, in order to explore the breakdown of the linear model used in deprojection, we have made a direct study of the relation between galaxy overdensity and the different systematics as follows: for each field and redshift bin we produce a map of the relative galaxy density $R(N_g)\equiv N_g(\nv)/\bar{N}_g$, where $N_g(\nv)$ is the number of galaxies in the pixel with coordinates $\nv$, and $\bar{N}_g$ is the mean number of galaxies per pixel across the map.
+      Second, in order to explore the breakdown of the linear model used in deprojection, we have made a direct study of the relation between galaxy overdensity and the different systematics as follows: for each field and redshift bin, we produce a map of the relative galaxy density $R(N_g)\equiv N_g(\nv)/\bar{N}_g$, where $N_g(\nv)$ is the number of galaxies in the pixel with coordinates $\nv$, and $\bar{N}_g$ is the mean number of galaxies per pixel across the map.
 Then, for each of the 48 systematic templates $S$, we create a similar map $R(S)\equiv S(\nv)/\bar{S}$.
 We then use both maps to calculate the mean value of $R(N_g)$ in bins of $R(S)$, estimating the error on this mean via bootstrap.
-Finally, we produce plots of this relation for all fields, bins and systematic maps, finding results such as those displayed in the left panels of Figure \ref{fig:ndens_syst}, which show this relation for bin 3 of the VVDS field for the dust absorption and $r$-band airmass templates (bottom and top panels respectively).
+Finally, we produce plots of this relation for all fields, redshift bins and systematic maps, finding results such as those displayed in the left panels of Figure \ref{fig:ndens_syst}, which show the relation between the galaxy density fluctuation and the fluctuations in dust absorption and $r$-band airmass for the third redshift bin of the VVDS field (bottom and top panels respectively).
 In most cases we find that the relation between galaxy density and systematic fluctuation is either flat or well approximated by a linear relation, as is the case for dust absorption in the figure.
@@
 Since the latter will be correlated at some level with some of the sources used in our clustering analysis, it is important to check for a possible bias associated with masking them.
-To do so, and to test our fiducial power spectra against the exact procedure used to produce the bright object mask, we have repeated our measurements making use of the bright star mask published by \cite{2018PASJ...70S...7C} (the so-called ``Arcturus mask).
+To do so, and to test our fiducial power spectra against the exact procedure used to create the bright object mask, we have repeated our measurements making use of the bright star mask published by \cite{2018PASJ...70S...7C} (the so-called ``Arcturus'' mask).
 The top-right and bottom-right panels of Figure \ref{fig:ndens_syst} show both masks for the VVDS field.
 We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different \todo{we could give some details of what the differences are here}.
-The yellow datapoints in Figure \ref{fig:cls_summary} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
+The yellow datapoints in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
 As before, we do not observe any statistically significant deviation between these spectra.
@@
 We then construct overdensity maps for each of the galaxy subsamples, which we call $\delta_1$ and $\delta_2$.
-Each of these subsamples can be thought of as an independent Poisson processes that samples the same underlying smooth overdensity field $\delta$.
-I.e.
+Each of these subsamples can be thought of as an independent Poisson processes that samples the same underlying smooth overdensity field $\delta$, i.e.
 $\delta_i = \delta + n_i$, where $n_i$ is the shot-noise contribution in $\delta_i$.
@@
       Both the auto- and cross-power spectra shown in Fig.~\ref{fig:cls_summary} carry information on astrophysical, systematics and cosmological parameters.
-We especially expect the cross-correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and shifts in the means of the bins.
+We especially expect the cross-correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and \an{changes in the photometric redshift distributions}.
 In this work, we therefore compute fiducial constraints from a joint fit to both auto- and cross-power spectra.
@@
 As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}.
-Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters together with our the measured power spectra.
+Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters alongside the measured power spectra.
 The corresponding minimum $\chi^{2}$ is $\chi^{2} = 86.2$.
@@
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
-As can be seen, we find that, within or uncertainties, the data prefer both a roughly constant $M_{\mathrm{min}}$ and $M_{1}$.
+As can be seen, we find that, within or uncertainties, the data prefer both $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ to be approximately redshift-independent.
 This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift, since galaxies will only form in the most massive halos at early times.
@@
           \includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-vs-mag.pdf}
-          \caption{Measured auto- and cross-power spectra considered in our analysis.
-The solid lines show the theoretical predictions obtained from the best-fit model parameters obtained in a joint fit to both auto- and cross-power spectra not allowing for magnification while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
+          \caption{Measured auto- and cross-power spectra obtained in our analysis.
+The solid lines show the theoretical predictions derived from the best-fit model parameters not allowing for magnification, while the dashed lines show the theoretical predictions obtained allowing for a free magnification amplitude $A_{\mu}$.}
           \label{fig:cls-best-fit}
@@
           \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-          \caption{Functional forms for $M_{\mathrm{min}}$ and $M_{1}$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
-\todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?}}
+          \caption{Functional forms for $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
+\todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?} \an{change figure labels}}
           \label{fig:hod-params-z-dep}
@@
 In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$.
-The uncertainties denote the $68 \%$ c.l..} \label{tab:constraints_robustness}
+The uncertainties denote the $68 \%$ c.l.
+as estimated from the isocontours.} \label{tab:constraints_robustness}
         \begin{center}
@@
 However, cross-correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
-In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto power spectra to those obtained when jointly fitting auto- and cross-power spectra.
-Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto power spectra alone.
+In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto-power spectra to those obtained when jointly fitting auto- and cross-power spectra.
+Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto-power spectra alone.
 As can be seen, the constraints from auto-spectra and from both auto- and cross-power spectra agree very well with each other, suggesting that uncertainties in photometric redshifts do not significantly affect the cross-correlations measured in our analysis.
@@
       An important part of our data model is the analytical covariance matrix described in Sec.~\ref{sssec:methods.theory.covar}.
-In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian connected contributions.
+In order to test the impact of the non-Gaussianity of the covariance on our results, we compare the HOD constraints obtained accounting for Gaussian (G) and Gaussian and SSC contributions (G+SSC) to our fiducial constraints, which include Gaussian, SSC and non-Gaussian (connected) contributions.
 As can be seen from Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto}, these constraints agree very well with each other.

### 2019-10-22 doc/Paper/main.tex
depth explained

@@
     \begin{enumerate}
-      \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth in different directions using a method similar to that outlined in \cite{2018PASJ...70S..25M}.
-In a given sky pixel, we collect all galaxies with $i$-band {\tt cmodel} fluxes measured with a signal-to-noise ratio between 9 and 11 (i.e.
-$9\le{\tt icmodel\_flux}/{\tt icmodel\_flux\_err}\le11$), and compute the mean of their $i$-band  {\tt cmodel} magnitude.
-We verified that we obtain similar depth estimates using other methods (e.g.
-magnitude corresponding to $10$ times the mean flux error), and that the magnitude limit of our sample ($i<24.5$) is bright enough that little or no area is lost in any of the fields by imposing this cut.
+      \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth in different directions as follows.
+For each pixel, we compute the average $i$-band flux error of all objects in it that are classified as stars.
+The corresponding survey depth is then given by this mean flux error multiplied by 10 and translated into a magnitude.
+Not all pixels contain enough stars to estimate a reliable mean flux error.
+We use a nearest-neighbor interpolation to assign a depth value to those pixels with fewer than 4 stars.
+We verified that we obtain similar depth estimates using other methods, such as that outlined in \cite{2018PASJ...70S..25M}, in which 10$\sigma$ depth is defined as the mean {\tt cmodel} magnitude of all sources with $i$-band signal-to-noise ratio between 9 and 11.
+It is worth emphasizing that our method uses only stars, discarding all sources classified as galaxies.
+The use of galaxies to estimate any systematics map is dangerous in the context of template deprojection, since the stochastic noise in the map associated with the discrete sampling of these sources correlates directly with the galaxy distribution, and can give rise to spurious correlations that bias the estimated power spectrum after deprojection (see Section \ref{ssec:methods.cell}).
+We provide further details in Appendix \ref{app:depth}.
       \item {\bf Dust extinction}: we make maps of dust absorption in each band using the data from \cite{1998ApJ...500..525S} projected onto the 6 HSC DR1 fields.
@@
 
+\appendix
+\section{Reconstructing depth from discrete sources}\label{app:depth}
+  The depth map used in our analysis (see Section \ref{ssec:methods.syst}) is constructed from the signal-to-noise ratios of sources classified as stars.
+The use of all sources, including galaxies, to generate this map, would result on spurious correlations with the true galaxy distribution that wbias the power spectra estimated from them.
+ould cause a bias in the power spectra after deprojecting it.
+We explore this effect further here.
+
+  In a simplified model, let us assume that galaxies can be separated into discrete types labelled by an index $\alpha$.
+If we want to compute the value of a given quantity $Q$ in a pixel $p$ by averaging over all galaxies in that pixel, the result is:
+  \begin{equation}
+    \bar{Q}_p = \frac{\sum_\alpha N_{\alpha,p}Q_{\alpha,p}}{\sum_\alpha N_{\alpha,p}},
+  \end{equation}
+  where $N_{\alpha,p}$ is the number of galaxies of type $\alpha$ in pixel $p$, and $Q_{\alpha,p}$ is the value of $Q$ for those galaxies.
+Expanding $N_{\alpha,p}=\bar{N}_\alpha(1+\delta_{\alpha,p})$, where $\bar{N}_\alpha$ is the average number of galaxies of type $\alpha$ per pixel, and $\delta_{\alpha,p}$ is their overdensity, we obtain:
+  \begin{align}\nonumber
+    \bar{Q}_p&=\frac{\langle Q\rangle_p+\langle Q\delta\rangle_p}{1+\langle \delta\rangle_p}\\
+             &\simeq\langle Q\rangle_p+\langle Q\delta\rangle_p-\langle Q\rangle_p\langle\delta\rangle_p+\mathcal{O}(\delta^2),
+  \end{align}
+  where we have defined $\langle f\rangle_p\equiv \sum_\alpha \bar{N}_\alpha f_{\alpha,p}/\sum_\alpha \bar{N}_\alpha$, and we have expanded to first order in $\delta$ in the second line.
+If $Q$ is constant across all galaxies, the second and third term in the second line cancel out, and the resulting map would receive no noise from the inhomogenous galaxy distribution ($\bar{Q}_p=\langle Q\rangle_p$) up to second order.
+This is however not the case for the flux errors used to estimate the depth map.
+Brighter sources have lower number densities (and therefore stronger shot-noise fluctuations), and also larger flux errors.
+Therefore, althought the depth map that results from using this method on galaxies is dominated by the large-scale depth fluctuations, the small-scale fluctuations trace the spatial distribution of the brightest sample, and would correlate with the true galaxy distribution.
+This violates the core assumption of template deprojection (that the deprojected contaminant templates do not correlate with the true map fluctuations), and cause a bias in the power spectrum.
+
+  Our depth map is computed from star-classified objects and therefore, although it will be subject to the same small-scale noise due to this discrete sampling, these noise fluctuations do not correlate with the galaxy distribution, and therefore do not bias our results.
+A second-order correlation could arise from the small fraction of galaxies mis-classified as stars, but the associated effect is negligible given our uncertainties.
+Due to these complications, in the future it will be desirable to estimate the survey depth using image properties directly (e.g.
+by injecting fake galaxies, or using the background noise integrated over PSF-size apertures).
+
 \end{document}

### 2019-10-22 doc/Paper/main.tex
bias references, hectomap

@@
 In this case, for a given photo-$z$ code, we produce an estimate of the redshift distribution of each tomographic bin by adding the photo-$z$ probability distributions of all objects in that bin.
-Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt demp}, {\tt ephor}, {\tt ephor\_ab} and {\tt frankenz} (see \cite{2018PASJ...70S...9T}) \an{HSC gives the pzs from 6 different codes.
-Should we maybe explain here why we only use 4?.} \da{The only reason is that I had a look at the HSC photo-z paper and it seemed like these ones performed best.
-We could say that we use a ``representative sample'' of the best-performing photo-z codes?}.
+Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt demp}, {\tt ephor}, {\tt ephor\_ab} and {\tt frankenz}.
+These are some of the best-peforming algorithms presented in \cite{2018PASJ...70S...9T}, and constitute a fair representation of the underlying photo-$z$ uncertainties.
 The different redshift distributions for all tomographic bins and photo-$z$ methods are shown in Figure \ref{fig:nzs}.
@@
 We conclude that there is no evidence for systematics from the power spectrum measurements in different fields, and therefore it is safe to coadd them and use the coadded spectra to obtain model constraints.
+We observe that the HECTOMAP field exhibits some of the lowest PTEs in the exercise above.
+Although none of these are cause for concern, we have omitted the measurements from HECTOMAP when obtaining the coadded power spectra for safety.
+Since this is by far the smallest field ($\sim5\,{\rm deg}^2$), the associated loss of sensitivity is negligible.
       \begin{figure}
@@
 The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in red in Figure \ref{fig:cls_systematics}.
-In most cases we observe very small differences (smaller than $1\sigma$) between both spectra.
-\todo{not anymore} However, we see that some of the spectra involving the first redshift bin are slightly more sensitive to deprojection, exhibiting differences of up to 3$\sigma$ in the range of scales used in our analysis.
-This suggests that, although the level of contamination in the raw galaxy overdensity maps is small, it is necessary to address it.
+In all cases we observe very small differences (smaller than $1\sigma$) between both spectra.
+This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely enough to account for it.
       \begin{figure}
@@
 The top-right and bottom-right panels of Figure \ref{fig:ndens_syst} show both masks for the VVDS field.
-We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different \todo{we could give some details of what the differences are here}.
+We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different (see \cite{2018PASJ...70S...7C} for further details).
 The yellow datapoints in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
@@
     This analysis yields a few interesting results.
-First, we find that the approximation $b(z) \propto D(z)^{-1}$ (i.e $\alpha=-1$) is only approximately valid.
-In fact, there is no physical reason for it, because the cut is on the observed magnitude, so at the same observed magnitude cut, the low redshift galaxies are \emph{different population} of galaxies.
-We find that the bias increases somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
-\todo{DA: I don't really understand if there should be a physical reason for the $1/D$ scaling even if the population was the same.}
+First, we observe a deviation from the scaling $b(z) \propto D(z)^{-1}$ (i.e $\alpha=-1$), which can be expected from objects forming in rare peaks at early times with a high bias \cite{1986ApJ...304...15B,1996MNRAS.282..347M,1998ApJ...500L..79T,Coil:2004}.
+This is not unexpected: even in the case where this model is valid for objects of a given type, our cut on observed magnitude implies that the samples observed and high and low redshifts are different populations.
+We find that the bias increases with redshift somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
 

### 2019-10-22 doc/Paper/main.tex
hironao

@@
 \author[x]{Rachel Mandelbaum,}
-\author[x]{Hironao Miyatake,}
-\author[g]{Jeffrey A. Newman,}
+\author[g,h,i,j]{Hironao Miyatake,}
+\author[k]{Jeffrey A. Newman,}
 \author[x]{Ignacio Sevilla,}
-\author[c,h]{Sarah Skinner,}
+\author[c,l]{Sarah Skinner,}
 \author[x]{Erica Wagoner}
@@
 \affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
-\affiliation[g]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
-\affiliation[h]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
+\affiliation[g]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
+\affiliation[h]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
+\affiliation[i]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
+\affiliation[j]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+\affiliation[k]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
+\affiliation[l]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
 

### 2019-10-22 doc/Paper/main.tex
more hironao
First pass through most of the draft. A couple of sections and todo items still left to do. Addressing now.

@@
       \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth in different directions as follows.
-For each pixel, we compute the average $i$-band flux error of all objects in it that are classified as stars.
+For each pixel, we compute the average $i$-band flux error of all objects classified as stars that fall into it.
 The corresponding survey depth is then given by this mean flux error multiplied by 10 and translated into a magnitude.
 Not all pixels contain enough stars to estimate a reliable mean flux error.
-We use a nearest-neighbor interpolation to assign a depth value to those pixels with fewer than 4 stars.
+We use a nearest-neighbor interpolation to assign a depth value to those pixels that contain less than 4 stars.
 We verified that we obtain similar depth estimates using other methods, such as that outlined in \cite{2018PASJ...70S..25M}, in which 10$\sigma$ depth is defined as the mean {\tt cmodel} magnitude of all sources with $i$-band signal-to-noise ratio between 9 and 11.
@@
 
-    For consistency with our implementation of the connected trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field \todo{Again, does this mean $I_a^1=1$?}\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
+    For consistency with our implementation of the connected trispectrum, we compute the response function $\sfrac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} $ for a given probe as the linearly biased response of the matter field\footnote{In order to test the robustness of our results to this approximation, we also compute the SSC contribution to the covariance using the probe-specific halo model quantities in Eq.~\ref{eq:ps-resp}.
 We find our parameter constraints to be unaffected by this change and therefore resort to the approach described above for consistency.}.
@@
       In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants as follows.
-A summary of all robustness tests performed and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.
+A summary of all robustness tests performed, and the respective constraints on HOD parameters and extended models can be found in Tab.~\ref{tab:constraints_robustness}.
 
@@
 Furthermore, we see that the constraining power on HOD parameters is mostly unaffected by including the cross-power spectra.
-As a final consistency check between auto- and cross-power spectra we test how well the auto-spectra predict the cross-spectra.
-To this end we compute the $\chi^{2}$ between the observed auto- and cross-power spectra and the theoretical predictions derived from auto power spectra only.
-As we will discuss below, the auto power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
+As an additional consistency check between auto- and cross-power spectra we test how well the auto-spectra predict the cross-spectra.
+To this end we compute the $\chi^{2}$ between the observed auto- and cross-power spectra and the theoretical predictions derived from auto-power spectra only.
+As we will discuss below, the auto-power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
 We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross-power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
-This shows that the auto power spectra are able to predict the cross-power spectra and provides further confirmation of their consistency.
+This shows that the auto-spectra are able to predict the cross-spectra and provides further confirmation of their consistency.
 
@@
 Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we remove the non-Gaussian contributions, as expected.
-However, we find an acceptable goodness of fit, even when only accounting for the Gaussian covariance.
+However, the differences are not significant and we find almost identical goodness of fits, even when only accounting for the Gaussian covariance.
 
@@
 We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those.
-We therefore show the constraints in terms of the reparametrized variables $\Sigma_{i} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
-While $\Sigma_{i} \Delta z_{i}$ and $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
+We therefore show the constraints in terms of the reparametrized variables $\Sigma_{i=0}^{3} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
+While $\Sigma_{i=0}^{3} \Delta z_{i}$ and the width parameters $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
 This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.
@@
       It is instructive to investigate which part of the data drives the constraints on photometric redshift systematics.
-To this end we compare the constraints obtained using auto power spectra only to those obtained from auto- and cross-power spectra (our fiducial case).
+To this end we compare the constraints obtained using auto-power spectra only to those obtained from auto- and cross-power spectra (our fiducial case).
 As can be seen from Fig.~\ref{fig:constraints-pz-syst-auto+cross-vs-auto}, we find that the auto-spectra do not constrain the photo-$z$ systematics parameters $\Delta z_{i} - \Delta z_{j}$, as opposed to the combination of auto- and cross-power spectra.
@@
 The results are shown in Fig.~\ref{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts}.
-As expected, we find that the constraints on HOD parameters successively weaken as we include more freedom in the photo-$z$ error model.
+As expected, we find that the constraints on HOD parameters weaken as we include more freedom in the photo-$z$ error model.
 However, as can be seen both from Fig.~\ref{fig:constraints-hod-pz-shifts-pz-widths-vs-pz-shifts-vs-no-pz-shifts} and Tab.~\ref{tab:constraints_robustness}, the constraints obtained in the three cases agree very well.
@@
 
-      We have also investigated the impact of a secondary mode in the redshift distribution for the first tomographic bin.
-This secondary peak contains $\sim$5\% of galaxies and peaks around $z\sim 3$ (hence cannot be seen in Figure \ref{fig:nzs}).
-To investigate the impact of this mode, we manually excise it from redshift distribution and calculate the resulting change in $\chi^2$, corresponding to $\Delta \chi^2\sim 0.05$.
+      We also investigate the impact of a secondary mode in the redshift distribution of the first tomographic bin.
+This secondary peak contains $\sim$5\% of all galaxies and peaks at around $z\sim 3$ (and hence cannot be seen in Fig.~\ref{fig:nzs}).
+To investigate the impact of this mode, we manually excise it from the redshift distribution and calculate the resulting change in $\chi^2$, finding it to be $\Delta \chi^2\sim 0.05$.
 This indicates that the effect of this peak is too small to be statistically significant.
-We therefore do not need to worry whether it is real or an artifact of photometric redshift inference.
+We therefore conclude that we do not need to worry whether it is real or an artifact of photometric redshift inference.
 
@@
 
-      As a last test of robustness against photometric redshift errors, we compare our fiducial constraints to those obtained with the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}, as provided by the HSC Collaboration \cite{2018PASJ...70S...9T}.
+      As a last test of robustness against photometric redshift errors, we compare our fiducial constraints to those obtained using the stacked pdfs from the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z}, as provided by the HSC Collaboration \cite{2018PASJ...70S...9T}.
 In analogy to our fiducial analysis, we use the photometric redshift error model given in Eq.~\ref{eq:photo-z-model} for each photo-$z$ code.
@@
       In order to further illustrate the effects of an incomplete photo-$z$ error model, we perform two additional analyses in which we compare the constraints obtained from the five photo-$z$ methods setting $z_{w, i} = 0$ and $z_{w, i} = 0, \Delta z_{i} = 0$ respectively.
-In the former case we find that the values for the photo-$z$ systematics parameters $\Sigma_{i} \Delta z_{i}, \Delta z_{i} - \Delta z_{j}$ required by the different codes differ significantly, which leads to differences in both constraining power and constraints on HOD parameters.
+In the former case we find that the values for the photo-$z$ systematics parameters $\Sigma_{i=0}^{3} \Delta z_{i}, \Delta z_{i} - \Delta z_{j}$ required by the five methods differ significantly, which leads to differences in both constraining power and constraints on HOD parameters.
 We especially find significant shifts in $M_{\mathrm{min}}$ and $M_{1}$ along their degeneracy direction.
@@
 The corresponding reduced $\chi^{2}$s range between $\chi^{2}_{\mathrm{red}} = 1.97$ and $\chi^{2}_{\mathrm{red}} = 5.13$.
-This suggests that the data are able to detect the presence of significant photometric redshift errors in the distributions derived using the photo-$z$ codes \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to those derived using COSMOS 30-band data.
+This suggests that the data are able to detect the presence of significant photometric redshift errors in the stacked photo-$z$ distributions derived using \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} as opposed to the distributions derived using COSMOS 30-band data.
 
@@
       As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to be redshift independent.
-In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies considered in our analysis and how these change with redshift.
+In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies in our sample and how these change with redshift.
 However, computing k-corrections and absolute magnitudes for broad-band photometric data can be challenging and we therefore choose an alternative approach.
 We cross-match galaxies passing our selection criteria within the HSC COSMOS field to galaxies also included in the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
-The COSMOS 30-band catalog contains, among others, absolute magnitudes in Subaru \texttt{B}-band, $M_{B}$, and Subaru \texttt{r+}-band, $M_{R}$.
+The COSMOS 30-band catalog contains, amongst others, absolute magnitudes in Subaru \texttt{B}-band, $M_{B}$, and Subaru \texttt{r+}-band, $M_{R}$.
 Using these quantities, we construct color-magnitude diagrams for all cross-matched galaxies.
-Fig.~\ref{fig:color-mag} shows the $M_{B}-M_{R}$ color as a function of $M_{R}$ magnitude for 10 equally spaced redshift bins in $z \in [0.15, 1.5]$\footnote{The galaxies are split into redshift bins according to COSMOS 30-band photometric redshifts.
+Fig.~\ref{fig:color-mag} shows the $M_{B}-M_{R}$ color as a function of $M_{R}$ magnitude for 10 equally spaced redshift bins in $z \in [0.15, 1.5]$\footnote{The galaxies are split into bins according to COSMOS 30-band photometric redshifts.
 We note that we have repeated the analysis splitting the sample according to HSC \texttt{Ephor\_AB} photometric redshifts, finding consistent results.}.
 In this diagram, red galaxies populate the high $M_{B}-M_{R}$ color, high $M_{R}$ magnitude plane, while blue galaxies tend to have lower $M_{B}-M_{R}$ and $M_{R}$.
-As can be seen from the figure, red galaxies increasingly drop-out of the high redshift samples.
+As can be seen from the figure, red galaxies increasingly drop-out of our sample at high redshift.
 We can quantify this effect by computing the fraction of red galaxies in our sample as a function of redshift: we empirically determine the separation between the blue and red clouds (denoted by the solid lines in the figure) and compute the fraction of galaxies in the red cloud as $f_{R} = \sfrac{N_{R}}{(N_{R}+N_{B})}$, where $N_{R}$ denotes the number of galaxies above the separation line, while $N_{B}$ is the number of galaxies below the line.
@@
       These results suggest that red galaxies are increasingly underrepresented with respect to blue galaxies in our sample at higher redshifts.
-This is due to the applied magnitude limit of $m_{\mathrm{lim}, i} < 24.5$: the $i$-band filter translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
-Red galaxies with a strong $4000$ \AA break therefore become very faint at these wavelengths and drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
+This is due to the applied magnitude limit of $i < 24.5$: the $i$-band filter translates to rest-frame wavelengths smaller than $4000$ \AA \, at redshifts $z \gtrsim 0.9$.
+Red galaxies with a strong $4000$ \AA \, break therefore become very faint at these wavelengths and drop out of our selection, thus explaining the observed constancy of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ with redshift.
 This interpretation is consistent with the results from the HOD fits that predict a decreasing mean halo mass as a function of redshift for our sample (see Fig.~\ref{fig:HOD-redshift}).
@@
   \subsection{Magnification}\label{ssec:results.magnification}
-    In addition to intrinsic correlations between galaxy positions, there exist several additional effects affecting the observed clustering of galaxies.
+    In addition to intrinsic correlations between galaxy positions, there exist several additional effects impacting the observed clustering of galaxies.
 The most relevant one for projected clustering studies is the magnification of distant sources due to gravitational lensing by the intervening LSS, an effect usually called magnification bias (e.g.
@@
 The main effect of magnification on the statistical distribution of galaxies is to increase observed galaxy fluxes, thus allowing dim galaxies to pass survey selection thresholds, and to alter their observed angular positions.
-The combined effect, is a position-dependent modulation of the number density that distorts the clustering pattern.
+The combined effect is a position-dependent modulation of the number density that distorts the clustering pattern.
 It has been shown that the clustering signal due to magnification can be comparable to the intrinsic clustering signal for cross-correlations between widely-separated redshift bins (see e.g.
@@
 
-    In the presence of magnification, the equations in Section \ref{ssec:methods.theory} get additional terms. The projected galaxy overdensity becomes:
+    In the presence of magnification, the equations presented in Section \ref{ssec:methods.theory} acquire additional terms. The projected galaxy overdensity becomes:
     \begin{equation}
@@
     \begin{equation}
-      W_\mu(z)=\frac{3H_0^2\Omega_M(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
-    \end{equation}
-    Here, $H_0\equiv H(z=0)$, $\Omega_M$ is the cosmological matter fraction, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
-    \begin{equation}
-      s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m},
+      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
+    \end{equation}
+    Here, $H_0\equiv H(z=0)$, $\Omega_{m}$ is the fractional matter density today, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
+    \begin{equation}
+      \left. s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
       \label{eq:s-func}
     \end{equation}
-    where $m$ denotes the observed magnitude.
+    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered.
 In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.
-Overdensities along the line of sight causes the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density).
-The two effects cancel at leading order when $s=\sfrac{5}{2}$.
+Overdensities along the line of sight cause the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density).
+The two effects cancel at leading order when $s=\sfrac{2}{5}$.
 
@@
 
-    The magnitude of the magnification signal crucially depends on the derivative of the galaxy number counts with respect to observed magnitude, $s(z)$.
+    The magnitude of the magnification signal crucially depends on the derivative of the cumulative galaxy number counts with respect to observed magnitude, $s(z)$.
 In order to obtain a data-driven model for magnification in our particular sample, we therefore estimate $s(z)$ from the observed number counts.
@@
 $m_{i, \mathrm{lim}} = 24.5$.
-In addition to the WIDE HSC galaxy data used in this work, PDR1 also contains data from two deep patches, called DEEP and UDEEP.
+In addition to the WIDE HSC galaxy data used in this work, HSC DR1 also contains data from two deep patches, called DEEP and UDEEP.
 We repeat the above analysis with these galaxy samples to ensure the stability of our results.
 As an example, Fig.~\ref{fig:s-func-estimation} shows the observed number counts as a function of $i$-band magnitude for the lowest redshift bin in the WIDE sample alongside the derived best-fit function.
-In Fig.~\ref{fig:s-func-estimation}, we show the $s(z)$ functions derived as outlined above for HSC WIDE, DEEP and UDEEP.
+In Fig.~\ref{fig:s-func-estimation}, we also show the $s(z)$ functions derived as outlined above for HSC WIDE, DEEP and UDEEP.
 As can be seen, the three estimates agree well with each other and we use the $s(z)$ function derived from our fiducial WIDE sample in the following.
-Our uncertainty on the estimation of $s(z)$ is subdominant given the statistical precision of our measurement, and therefore we ignore it.
+Our uncertainty on the estimation of $s(z)$ is subdominant given the statistical precision of our measurement, and we therefore ignore it.
     \begin{figure}
@@
     Using the estimated $s(z)$, we can derive theoretical predictions for the angular galaxy power spectra in presence of magnification.
-In order to investigate the sensitivity of the data to magnification we run two different MCMC analyses: in the first case, we fix the magnification amplitude to the predictions from the empirically determined $s(z)$ function.
-In the second case we include an additional magnification parameter $A_{\mu}$ that scales the amplitude of the magnification kernel $W_{\mu}$ and we fit it alongside our fiducial parameter set.
+In order to investigate the sensitivity of the data to magnification, we run two different MCMC analyses: in the first case, we fix the magnification amplitude to the predictions from the empirically determined $s(z)$ function.
+In the second case, we include an additional magnification parameter $A_{\mu}$ that scales the amplitude of the magnification kernel $W_{\mu}$ and we fit it alongside our fiducial parameter set.
 
@@
 The best-fit $\chi^{2}$ including magnification is $\chi^{2} = 69.0$, which, computing the degrees of freedom as $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 15 = 79$, leads to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.87$ ($p$-value $= 0.78$).
-This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 86.2 - 69.0 = 17.2$, consistent with the $\sim 3 \sigma$ detection.
+This corresponds to an improvement in $\chi^{2}$ compared to the fiducial analysis of $\Delta \chi^{2} = 86.2 - 69.0 = 17.2$, roughly consistent with the $\sim 3 \sigma$ detection.
 Fig.~\ref{fig:cls-best-fit} shows the corresponding theoretical predictions derived from the maximum likelihood parameters alongside the observed data.
@@
     In order to identify the part of the data vector driving the constraints on $A_{\mu}$, we repeat this analysis only including the auto-spectra.
-The comparison between the constraints on $A_{\mu}$ from auto- and cross-power spectra to those obtained from auto power spectra alone in shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
-As can be seen, the auto power spectra alone do not constrain $A_{\mu}$, which implies that the constraints on the magnification amplitude are solely driven by the cross-power spectra.
+The comparison between the constraints on $A_{\mu}$ from auto- and cross-power spectra to those obtained from auto-spectra alone is shown in Fig.~\ref{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}.
+As can be seen, the auto-power spectra alone do not constrain $A_{\mu}$, which implies that the constraints on the magnification amplitude are solely driven by the cross-power spectra.
 This sensitivity of the cross-power spectra to magnification mainly stems from the fact that the cross-correlations between widely separated bins caused by intrinsic clustering are small, which leads to an increased sensitivity to any non-intrinsic source of cross-correlation, such as magnification.
@@
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
-        \caption{Comparison of the constraints on magnification amplitude obtained from auto power spectra alone to those obtained from auto and cross-power spectra.
-The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model described in Sec.~\ref{ssec:results.magnification}.}
+        \caption{Comparison of the constraints on magnification amplitude obtained from auto-power spectra alone to those obtained from auto- and cross-power spectra.
+The solid line denotes the expectation value of the magnification amplitude determined from our data-driven fiducial model, described in Sec.~\ref{ssec:results.magnification}.}
         \label{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}
@@
 All other cosmological parameters remain fixed to their fiducial Planck 2018 values.
-From a joint fit to all auto- and cross-power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$,
+From a joint fit to all auto- and cross-power spectra we obtain $\sigma_{8} = 0.807\substack{+0.149 \\ -0.143}$ and $\Omega_{m} = 0.286 \pm 0.025$\footnote{We have recast our constraints on $\Omega_{c}$ in terms of $\Omega_{m}$ for ease of comparison with other analyses.},
 %%%-> 0.247+0.0493+0.06/93.4/0.7**2 = 0.297611
     consistent with our assumed fiducial cosmology.
-In particular, this is consistent with Planck and BAO measurement, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{Planck:2018} albeit with a different parameterization.
-The HSC analysis of the weak lensing data from the the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency.
-We note that our analysis makes considerably stronger modeling assumption and thus gives errorbars that are likely under-estimated.
+In particular, this is consistent with the constraints obtained from combining Planck 2018 and BAO measurements, which give $\Omega_m=0.3110\pm 0.006$ and $\sigma_8=0.8099 \pm 0.0071$ \cite{Planck:2018} albeit with a different parameterization.
+The weak lensing analysis of the full first year HSC data (similar in size, but somewhat larger than the public release) gives $\Omega_m=0.346^{+0.052}_{-0.100}$ \cite{1906.06041}, showing an excellent internal consistency.
+We note that our analysis makes considerably stronger modeling assumptions and thus gives error bars that are likely under-estimated.
 
@@
 As can be seen from Tab.~\ref{tab:constraints_robustness}, the derived constraints on HOD parameters agree well with our fiducial results, which shows that our HOD constraints are robust to variations in $\Omega_{c}$ and $\sigma_{8}$ as allowed by the data.
-This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
-Therefore, photometric current and future galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
+This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ (and hence $\Omega_{m}$) while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
+Therefore, current and future photometric galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
 
@@
         \includegraphics[width=0.49\textwidth]{figures/contours-Om-s8_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=Oc+s8.pdf}
-        \caption{Constraints on cosmological parameters obtained from a joint fit to all auto- and cross-power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \caption{Constraints on $\Omega_{m}$ and $\sigma_{8}$ obtained from a joint fit to all auto- and cross-power spectra. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
         \label{fig:constraints-fit=Oc+s8}
@@
 As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected.
-Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \propto \sfrac{1}{D(z)}$, for all samples, as can be seen from the middle panel of Fig.~\ref{fig:magnitude-cuts-bias}.
+Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \propto \sfrac{1}{D(z)}$, for all samples, as illustrated in the middle panel of Fig.~\ref{fig:magnitude-cuts-bias}.
 Motivated by these results, we make the following Ansatz to derive a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude:
@@
     where we have assumed the bias to be separable in $z$ and $m_{\mathrm{lim}}$, and the parameter $\alpha$ accounts for deviations from the simple inverse growth function proportionality.
-We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a three-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
+We determine the values of $\alpha$ and $\bar{b}(m_{\mathrm{lim}})$ in a multi-step weighted, linear least squares fit: we first fit Eq.~\ref{eq:bias-fit-func} to all five samples separately and determine our fiducial $\alpha$ as the median of these values\footnote{We note that we find slightly better results using the median, which is the reason for preferring it over the mean.}.
 We then fit Eq.~\ref{eq:bias-fit-func} to all samples again, obtaining constraints on $\bar{b}(m_{\mathrm{lim}})$ for $\alpha$ fixed to our fiducial value.
@@
     This analysis yields a few interesting results.
-First, we observe a deviation from the scaling $b(z) \propto D(z)^{-1}$ (i.e $\alpha=-1$), which can be expected from objects forming in rare peaks at early times with a high bias \cite{1986ApJ...304...15B,1996MNRAS.282..347M,1998ApJ...500L..79T,Coil:2004}.
+First, we observe a deviation from the scaling $b(z) \propto \sfrac{1}{D(z)}$ (i.e $\alpha=-1$), which can be expected from objects forming in rare peaks at early times with a high bias \cite{1986ApJ...304...15B,1996MNRAS.282..347M,1998ApJ...500L..79T,Coil:2004}.
 This is not unexpected: even in the case where this model is valid for objects of a given type, our cut on observed magnitude implies that the samples observed and high and low redshifts are different populations.
-We find that the bias increases with redshift somewhat faster than the standard empirical assumption of $D(z)^{-1}$.
+We find that the bias increases with redshift somewhat faster than the standard empirical assumption of $\sfrac{1}{D(z)}$.
 
@@
 Our results are well fitted by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$.
-We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
+We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a magnitude-limited sample, consistent with previous analyses.
 In order to test the stability of our results, we performed a suite of alternative analyses, finding our results to be robust to photometric redshift uncertainties.
@@
 benefited this work. ZG is supported by a Rhodes Scholarship granted
-by the Rhodes Trust. JAN us supported by grant DOE DE-SC0007914 from
+by the Rhodes Trust. HM has been supported by the Jet Propulsion Laboratory,
+California Institute of Technology, under a contract with the National
+Aeronautics and Space Administration and Grant-in-Aid for Scientific
+Research from the JSPS Promotion of Science (No. 18H04350). 
+JAN us supported by grant DOE DE-SC0007914 from
 the U.S. Department of Energy Office of Science (Office of High Energy
@@
   The depth map used in our analysis (see Section \ref{ssec:methods.syst}) is constructed from the signal-to-noise ratios of sources classified as stars.
-The use of all sources, including galaxies, to generate this map, would result on spurious correlations with the true galaxy distribution that wbias the power spectra estimated from them.
-ould cause a bias in the power spectra after deprojecting it.
-We explore this effect further here.
+The use of all sources, including galaxies, to generate this map, would result in spurious correlations with the true galaxy distribution that would cause a bias in the power spectra after deprojecting it.
+We explore this effect further in this section.
 
@@
   where we have defined $\langle f\rangle_p\equiv \sum_\alpha \bar{N}_\alpha f_{\alpha,p}/\sum_\alpha \bar{N}_\alpha$, and we have expanded to first order in $\delta$ in the second line.
-If $Q$ is constant across all galaxies, the second and third term in the second line cancel out, and the resulting map would receive no noise from the inhomogenous galaxy distribution ($\bar{Q}_p=\langle Q\rangle_p$) up to second order.
+If $Q$ is constant across all galaxies, the second and third term in the second line cancel, and the resulting map would receive no noise from the inhomogeneous galaxy distribution ($\bar{Q}_p=\langle Q\rangle_p$) up to second order.
 This is however not the case for the flux errors used to estimate the depth map.
 Brighter sources have lower number densities (and therefore stronger shot-noise fluctuations), and also larger flux errors.
-Therefore, althought the depth map that results from using this method on galaxies is dominated by the large-scale depth fluctuations, the small-scale fluctuations trace the spatial distribution of the brightest sample, and would correlate with the true galaxy distribution.
-This violates the core assumption of template deprojection (that the deprojected contaminant templates do not correlate with the true map fluctuations), and cause a bias in the power spectrum.
+Therefore, although the depth map estimated from mean galaxy flux errors is dominated by the large-scale depth fluctuations, the small-scale fluctuations trace the spatial distribution of the brightest galaxies, and thus correlate with the true galaxy distribution.
+This violates the core assumption of template deprojection (that the deprojected contaminant templates do not correlate with the true map fluctuations), and causes a bias in the estimated power spectrum.
 

### 2019-10-22 doc/Paper/main.tex
Further small changes.

@@
 We conclude that there is no evidence for systematics from the power spectrum measurements in different fields, and therefore it is safe to coadd them and use the coadded spectra to obtain model constraints.
-We observe that the HECTOMAP field exhibits some of the lowest PTEs in the exercise above.
+We observe that the HECTOMAP field exhibits some of the lowest PTEs in the analysis described above.
 Although none of these are cause for concern, we have omitted the measurements from HECTOMAP when obtaining the coadded power spectra for safety.
@@
         \caption{Difference between the power spectra measured in each field and the mean coadded spectra normalized by the 1$\sigma$ errors.
-The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.
+The pair of numbers in the upper left corner of each panel corresponds to the indices of the bins being cross-correlated.
 We find no inconsistency between the different measurements.}
@@
 Finally, the estimated power spectra must be corrected for the loss of modes incurred (blue line in Figure \ref{fig:cls_summary}).
-This method is therefore able to account for any systematic contamination that is well described as a linear contribution.
+This method is therefore able to account for any systematic contamination that is well described by a linear contribution.
 Since the impact of any contaminant can always be Taylor-expanded, this treatment is appropriate as long as the level of contamination is sufficiently small.
@@
 In all cases we observe very small differences (smaller than $1\sigma$) between both spectra.
-This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely enough to account for it.
+This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely accurate enough to account for it.
       \begin{figure}
@@
 
-      Second, in order to explore the breakdown of the linear model used in deprojection, we have made a direct study of the relation between galaxy overdensity and the different systematics as follows: for each field and redshift bin, we produce a map of the relative galaxy density $R(N_g)\equiv N_g(\nv)/\bar{N}_g$, where $N_g(\nv)$ is the number of galaxies in the pixel with coordinates $\nv$, and $\bar{N}_g$ is the mean number of galaxies per pixel across the map.
+      Second, in order to explore the breakdown of the linear model used in deprojection, we have conducted a direct study of the relation between galaxy overdensity and the different systematics as follows: for each field and redshift bin, we produce a map of the relative galaxy density $R(N_g)\equiv N_g(\nv)/\bar{N}_g$, where $N_g(\nv)$ is the number of galaxies in the pixel with coordinates $\nv$, and $\bar{N}_g$ is the mean number of galaxies per pixel across the map.
 Then, for each of the 48 systematic templates $S$, we create a similar map $R(S)\equiv S(\nv)/\bar{S}$.
@@
 Finally, we produce plots of this relation for all fields, redshift bins and systematic maps, finding results such as those displayed in the left panels of Figure \ref{fig:ndens_syst}, which show the relation between the galaxy density fluctuation and the fluctuations in dust absorption and $r$-band airmass for the third redshift bin of the VVDS field (bottom and top panels respectively).
-In most cases we find that the relation between galaxy density and systematic fluctuation is either flat or well approximated by a linear relation, as is the case for dust absorption in the figure.
+In most cases, we find that the relation between galaxy density and systematic fluctuation is either flat or well approximated by a linear relation, as is the case for dust absorption in the figure.
 In a few cases, however, we find that a linear relation is only appropriate in parts of the range of contaminant values, and that the observed galaxy overdensity grows or decreases much faster for large or small values of $R(S)$.
@@
 The masked regions correspond to $\sim20\%$ of the available footprint on average, and are shown in the top right panel of Figure \ref{fig:ndens_syst} in turquoise for the VVDS field.
-The blue datapoints in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the power spectra estimated using these more restrictive masks, normalized by their $1\sigma$ errors.
+The blue datapoints in Figure \ref{fig:cls_systematics} show the difference of the power spectra estimated using these more restrictive masks with respect to our fiducial power spectra, normalized by their $1\sigma$ errors.
 In the vast majority of cases we see only $<1\sigma$ differences between both spectra.
@@
 
-      In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis.
+      In Fig.~\ref{fig:hod-params-z-dep} we show the redshift dependence of the logarithm of the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ obtained in our analysis.
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
@@
           \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-          \caption{Functional forms for $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
+          \caption{Functional forms for the logarithm of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
 \todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?} \an{change figure labels}}

### 2019-10-22 doc/Paper/main.tex
author fix

--- 2019-10-22 doc/Paper/main.tex
@@
 \author[b]{David Alonso,}
-\author[c]{An\v{z}e Slosar,}
-\author[d,e]{Javier S\'anchez,}
+\author[c,d]{Javier S\'anchez,}
+
+\author[e]{An\v{z}e Slosar,}
+
 \author[f]{Humna Awan,}
@@
 \author[x]{Ignacio Sevilla,}
-\author[c,l]{Sarah Skinner,}
+\author[e,l]{Sarah Skinner,}
 \author[x]{Erica Wagoner}
@@
 \affiliation[b]{Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, United Kingdom}
-\affiliation[c]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
-\affiliation[d]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
-\affiliation[e]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation[c]{Fermi National Accelerator Laboratory, Batavia, IL, 60510, USA}
+\affiliation[d]{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}
+\affiliation[e]{Brookhaven National Laboratory, Physics Department, Upton, NY 11973, USA}
 \affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}

### 2019-10-22 doc/Paper/main.tex
some changes

@@
 To do so, we estimated the covariance matrix of the redshift distribution amplitudes in each narrow histogram bin shown in Fig.
-\ref{fig:nzs} using a simplified linear bias model.
-From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean), and compute the mean redshift of each realization.
-Estimating the standard deviation in the mean redshift of all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.
+\ref{fig:nzs} assuming a simple cylindrical survey geometry and that volume-to-volume number density correlations follow a normal distribution given a biased linear power spectrum.
+From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean).
+For each realization, we compute the mean and the width of corresponding $N(z)$ distributions.
+Estimating the standard deviation in the means and widths from all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.
 We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties.
-It is interesting to note that, having access to the covariance matrix of the redshift distribution would allow us to perform a more general characterization of the $N(z)$ uncertainties, beyond shift-width parametrizations (e.g.
+It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance, beyond the simple shift-width parametrizations (e.g.
 through principal component analysis).
@@
 \as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?} \todo{DA: I'd suggest adding Andrina's latest plot with the SRD lines to Figure \ref{fig:HOD-redshift} to avoid new figures.} An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
-Our full parameter chains for the different limiting magnitudes are available upon request.
-\as{Is this the case?} \an{That would be totally fine with me.}
+Our full parameter chains with full halo model parameterization for the different limiting magnitudes are available upon request.
     %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.

### 2019-10-22 doc/Paper/main.tex
some changes

@@
 \cite{1507.05460,1807.10163}).
-Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias and larger projection effects.
+Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias and larger systematic projection effects.
 In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification.

### 2019-10-23 doc/Paper/main.tex
Added SRD plot and addressed todos.

@@
 In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data.
-We split the data into four tomographic redshift bins and measure both the auto- and cross power spectra of all bins, correcting for observational systematics using mode deprojection.
+We split the data into four tomographic redshift bins and measure both the auto- and cross-power spectra of all bins, correcting for observational systematics using mode deprojection.
 We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties.
@@
 We work in the Fourier domain, so our basic quantity is the angular power spectrum $C_\ell$.
-Given four tomographic samples, our measurement consists of four auto power spectra and six cross-power spectra.
+Given four tomographic samples, our measurement consists of four auto-power spectra and six cross-power spectra.
 In this section we discuss how we construct maps of galaxy density fluctuations and associated maps of potential systematics, how we use these to measure the power spectra and their covariance matrix and finally how these are modeled within the context of the halo model.
@@
 From top to bottom and left to right, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density.
-We can visually appreciate the existing correlations between differnt systematics (e.g.
+We can visually appreciate the existing correlations between different systematics (e.g.
 seeing and airmass), which are automatically taken into account by the deprojection method described in Section \ref{ssec:methods.cell} and in \cite{2019MNRAS.484.4127A}.}
@@
 These are the fiducial redshift distributions used in our analysis.
-The solid curves in each panel show the stacked redshift distribution inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt Franken-Z} from left to right and top to bottom).
+The solid curves in each panel show the stacked redshift distributions inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt Franken-Z} from left to right and top to bottom).
 The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in red, blue orange and green respectively.
@@
 Matches are found as pairs of objects with an angular separation smaller than 1 arcsecond.
-All unmached objects in either catalog are discarded.
-      \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbours in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
-We record the distance to the furthest neighbour in this space.
+All unmatched objects in either catalog are discarded.
+      \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbors in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
+We record the distance to the furthest neighbor in this space.
       \item We then compute the number of HSC sources $N_{\rm neigh}^{\rm HSC}$ found within the same radius in magnitude space.
@@
 First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample.
-Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the colour-redshift relation has an environmental dependence.
+Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence.
 Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
@@
 Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt demp}, {\tt ephor}, {\tt ephor\_ab} and {\tt frankenz}.
-These are some of the best-peforming algorithms presented in \cite{2018PASJ...70S...9T}, and constitute a fair representation of the underlying photo-$z$ uncertainties.
+These are some of the best-performing algorithms presented in \cite{2018PASJ...70S...9T}, and constitute a fair representation of the underlying photo-$z$ uncertainties.
 The different redshift distributions for all tomographic bins and photo-$z$ methods are shown in Figure \ref{fig:nzs}.
@@
 
-  \subsection{Modelling the signal}\label{ssec:methods.theory}
+  \subsection{Modeling the signal}\label{ssec:methods.theory}
   \subsubsection{Projected quantities and power spectra}\label{sssec:methods.theory.cellpk}
@@
 In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass.
-Details about HOD parametrizations can be found in \cite{2011ApJ...736...59Z}.
+Details about HOD parameterizations can be found in \cite{2011ApJ...736...59Z}.
 In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
@@
     \end{equation}
-    A central assumption in standard HOD parametrizations is that centrals/satellites follow a Bernoulli/Poisson distribution.
-
-    Following \cite{2011ApJ...736...59Z}, we parametrise the number of centrals and satellites as a function of mass as:
+    A central assumption in standard HOD parameterizations is that centrals/satellites follow a Bernoulli/Poisson distribution.
+
+    Following \cite{2011ApJ...736...59Z}, we parametrize the number of centrals and satellites as a function of mass as:
     \begin{align}
@@
     where $\log$ is the logarithm to base 10, $i \in [\mathrm{min}, 0, 1]$ and $z_{p}$ denotes a pivot redshift, which we set to $z_{p} = 0.65$.
-This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$.
+This functional form is motivated by an initial analysis in which we separately fit an HOD to each auto-power spectrum and determine a function consistent with the observed redshift evolution of the three parameters $M_{\mathrm{min}}(z)$, $M_{0}(z)$ and $M_{1}(z)$.
 We additionally include a pivot redshift $z_{p}$ in our parametrization to remove degeneracies between the fitted parameters.
@@
     \begin{equation}
-      I^{n}_{a_1...a_m}(k_1,...,k_m) = \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, \\
+      I^{n}_{a_1...a_m}(k_1,...,k_m) = \int \mathrm{d}M \frac{\mathrm{d}n}{\mathrm{d}M}b_{h, n}(M)  \left\langle\prod_{i=1}^m \left[\tilde{u}_{a_i}(k_i, M) \right]\right\rangle, 
+      \label{eq:halo-mod-intg}
     \end{equation}
@@
 the HOD profile described in Section \ref{sssec:methods.theory.hod} in the case of galaxy clustering).
-For simplicity, we follow \cite{Krause:2017} and approximate the 2- to 4-halo trispectrum as the linearily biased matter trispectrum and only include a probe-specific 1-halo trispectrum contribution.
+For simplicity, we follow \cite{Krause:2017} and approximate the 2- to 4-halo trispectrum as the linearly biased matter trispectrum and only include a probe-specific 1-halo trispectrum contribution.
 Specifically, we set
@@
     \end{equation}
-    where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp} \todo{are you setting the $I$s to 1 in the case of the $>1h$ terms?} and $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
+    where $T^{abcd, 1h}$ and $T^{m, 2h+3h+4h}$ are computed following Equations \ref{eq:halo-mod-trisp}.
+For $T^{abcd, 1h}$, we evaluate Eq.~\ref{eq:halo-mod-intg} for the galaxy distribution, while for $T^{m, 2h+3h+4h}$, we use the corresponding expressions for the matter distribution.
+Finally, $b_{i}$ denotes the linear bias predicted using halo occupation distribution modeling, given by
     \begin{equation}
@@
     We fit all power spectra up to a maximal angular multipole $\ell_{\mathrm{max}}$ approximately corresponding to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$, as determined through the Limber relation $k_{\mathrm{max}} = \sfrac{\ell_{\mathrm{max}}}{\chi(z)}$.
-For the auto power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
+For the auto-power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
 For the cross-correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
@@
 From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean).
-For each realization, we compute the mean and the width of corresponding $N(z)$ distributions.
-Estimating the standard deviation in the means and widths from all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.
+For each realization, we compute the mean and the width of the corresponding $N(z)$ distributions.
+Estimating the standard deviation of the means and widths from all realizations, we find that sample variance uncertainty in COSMOS leads to 1-$\sigma$ shifts of $\Delta z\sim0.006$ and fractional widths $z_w\sim 0.04$.
 We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties.
-It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance, beyond the simple shift-width parametrizations (e.g.
+It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance, beyond the simple shift-width parameterizations (e.g.
 through principal component analysis).
@@
 The posterior means and best-fits denote the values derived for our fiducial analysis.
-The uncertainties denote the $68 \%$ c.l..} \label{tab:params}
+The uncertainties denote the $68 \%$ c.l.
+corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:params}
       \begin{center}
@@
       The fact that the HSC DR1 sample is distributed across 6 different disconnected fields allows us to carry out consistency tests of the measurements in individual fields.
-For example, it is reasonable to expect that, if a given undetected systematic is biasing our measurements significantly, its impact would vary across different fields, and would therefore lead to inconsitent power spectrum measurements between them.
+For example, it is reasonable to expect that, if a given undetected systematic is biasing our measurements significantly, its impact would vary across different fields, and would therefore lead to inconsistent power spectrum measurements between them.
 We carry out two basic consistency tests, involving the number density of objects in each field (i.e.
@@
 This procedure can also be understood as building a linear model for the contamination (see Eq.
-\ref{eq:deproj1}), finding the best-fit linear coefficients for each contaminant and substracting the corresponding contribution from the observed map.
+\ref{eq:deproj1}), finding the best-fit linear coefficients for each contaminant and subtracting the corresponding contribution from the observed map.
 Finally, the estimated power spectra must be corrected for the loss of modes incurred (blue line in Figure \ref{fig:cls_summary}).
@@
 The masked regions correspond to $\sim20\%$ of the available footprint on average, and are shown in the top right panel of Figure \ref{fig:ndens_syst} in turquoise for the VVDS field.
-The blue datapoints in Figure \ref{fig:cls_systematics} show the difference of the power spectra estimated using these more restrictive masks with respect to our fiducial power spectra, normalized by their $1\sigma$ errors.
+The blue data points in Figure \ref{fig:cls_systematics} show the difference of the power spectra estimated using these more restrictive masks with respect to our fiducial power spectra, normalized by their $1\sigma$ errors.
 In the vast majority of cases we see only $<1\sigma$ differences between both spectra.
@@
 We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different (see \cite{2018PASJ...70S...7C} for further details).
-The yellow datapoints in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
+The yellow data points in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
 As before, we do not observe any statistically significant deviation between these spectra.
@@
       Both the auto- and cross-power spectra shown in Fig.~\ref{fig:cls_summary} carry information on astrophysical, systematics and cosmological parameters.
-We especially expect the cross-correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and \an{changes in the photometric redshift distributions}.
+We especially expect the cross-correlations to help constrain photo-$z$ systematics parameters, as they probe the relative clustering strength in different redshift bins and thus help break degeneracies between the clustering amplitude and changes in the photometric redshift distributions.
 In this work, we therefore compute fiducial constraints from a joint fit to both auto- and cross-power spectra.
@@
           \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-          \caption{Functional forms for the logarithm of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.
-\todo{could we make the samples semi-transparent so we see how they bunch up around the best-fit?} \an{change figure labels}}
+          \caption{Functional forms for the logarithm of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
           \label{fig:hod-params-z-dep}
@@
         \caption{Parameter constraints and best-fit $\chi^{2}$ values obtained for all considered analysis variants.
-\todo{it would be good to specify what the error bars are.
-I imagine they're watershed errors (i.e.
-values with equal probability enclosing 60\% of $p$.
-Is that correct?} The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
+The number of degrees of freedom $\nu$ is estimated according to $\nu = N_{\mathrm{data}}-N_{\mathrm{param}}$.
 In the second column of the table, the values in brackets denote the $p$-values corresponding to the observed best-fit $\chi^{2}$.
 The uncertainties denote the $68 \%$ c.l.
-as estimated from the isocontours.} \label{tab:constraints_robustness}
+corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:constraints_robustness}
         \begin{center}
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
-          \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
+          \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto-power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
 The inner (outer) contour shows the $68 \%$ c.l.
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_fit=auto+cross-vs-fit=auto.pdf}
-          \caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained from auto power spectra alone.
+          \caption{Comparison of our fiducial constraints on photo-$z$ systematics parameters to those obtained from auto-power spectra alone.
 The inner (outer) contour shows the $68 \%$ c.l.
@@
       Even though the photo-$z$ error model given in Eq.~\ref{eq:photo-z-model} leads to consistent constraints on HOD parameters from all photo-$z$ methods considered, there is no guarantee that it is flexible enough to capture all redshift distribution differences important for galaxy clustering statistics.
-We investigate this by comparing the auto power spectra for a fixed HOD model obtained when forcing the five redshift distributions to have approximately the same means and widths.
+We investigate this by comparing the auto-power spectra for a fixed HOD model obtained when forcing the five redshift distributions to have approximately the same means and widths.
 We find that the resulting power spectra exhibit significant differences, which suggests that features in the redshift distribution beyond mean and width can significantly impact observed galaxy clustering power spectra.
@@
       \begin{center}
-        \subfigure[Cumulative galaxy number counts as a function of $i$-band magnitude for lowest tomographic redshift bin.]{\includegraphics[width=0.49\textwidth]{figures/mag-dist-cumulative=True+fit-mmin=23-sample=WIDE-bin=0.pdf}}
-        \subfigure[Comparison of $s(z)$ (see Eq.~\ref{eq:s-func}) derived using WIDE, DEEP and UDEEP HSC galaxy samples.]{\includegraphics[width=0.49\textwidth]{figures/s-z-func-samples=WIDE-DEEP-UDEEP.pdf}}
-        \caption{Illustration of data-driven estimation of $s(z)$ for galaxy sample used in our analysis.} 
+        \subfigure[Cumulative galaxy number counts as a function of $i$-band magnitude for the lowest tomographic redshift bin used in this analysis.]{\includegraphics[width=0.49\textwidth]{figures/mag-dist-cumulative=True+fit-mmin=23-sample=WIDE-bin=0.pdf}}
+        \subfigure[Comparison of $s(z)$ (see Eq.~\ref{eq:s-func}) derived using the WIDE, DEEP and UDEEP HSC galaxy samples.]{\includegraphics[width=0.49\textwidth]{figures/s-z-func-samples=WIDE-DEEP-UDEEP.pdf}}
+        \caption{Illustration of data-driven estimation of $s(z)$ for the galaxy sample used in our analysis.} 
         \label{fig:s-func-estimation}
@@
 We determine the bias from the mean of the posterior distribution, as we find it to yield more stable constraints than the best-fit value.
-The results for the bias evaluated at the effective redshift of each tomographic bin are shown in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample.
+The results for the bias evaluated at the effective redshift of each tomographic bin are shown in the upper left panel of Fig.~\ref{fig:magnitude-cuts-bias}, alongside the results for our fiducial sample.
 As can be seen, we find the linear bias to increase for decreasing limiting magnitude, as expected.
-Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \propto \sfrac{1}{D(z)}$, for all samples, as illustrated in the middle panel of Fig.~\ref{fig:magnitude-cuts-bias}.
+Furthermore, the redshift-dependence of the bias can be roughly approximated as inversely proportional to the growth factor, $b(z) \propto \sfrac{1}{D(z)}$, for all samples, as illustrated in the upper right panel of Fig.~\ref{fig:magnitude-cuts-bias}.
 Motivated by these results, we make the following Ansatz to derive a fitting function for the large-scale galaxy bias as a function of redshift and limiting magnitude:
@@
 
-    We anticipate that these results will be useful for forecasting the  constraining power of magnitude-limited samples.
-\as{Do we want to show our result for LSST vs SRD assumption of $0.95/D(z)$?} \todo{DA: I'd suggest adding Andrina's latest plot with the SRD lines to Figure \ref{fig:HOD-redshift} to avoid new figures.} An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
-Our full parameter chains with full halo model parameterization for the different limiting magnitudes are available upon request.
+    We anticipate that these results will be useful for forecasting the constraining power of magnitude-limited samples, e.g.
+from LSST.
+In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) analysis.
+As can be seen, we find significant differences between these two.
+An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
+Our parameter chains for halo model and systematics parameters for the different limiting magnitudes are available upon request.
     %Our measured evolution of bias is thus consistent with previous measurements, such as those from DEEP2 survey \cite{Coil:2004} and are also in agreement the LSST DESC SRD forecasting exercise, which assumed $b(z) = 0.95/D(z)$ \cite{1809.01669} to better than 5\%.
@@
       \begin{center}
-        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-        \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-        \caption{Constraints on the large-scale galaxy bias $b(z, m_{\mathrm{lim}})$ as a function of redshift and limiting magnitude for the different galaxy samples considered in this analysis.
+        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
+          \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_i24p5-vs-DESC-SRD.pdf}}
+        \caption{\textit{Upper panels:} Constraints on the large-scale galaxy bias $b(z)$ and $b(z)D(z)$ as a function of redshift for the different magnitude-limited galaxy samples considered in this analysis.
 For all plots, the points denote the values derived from the mean of the posterior distribution of the parameters and the solid lines show the predictions from the fitting function given in Equations \ref{eq:bias-fit-func} and \ref{eq:bias-fit-func-result}.
-The shaded regions denote the $68 \%$ c.l..}
+The shaded regions denote the $68 \%$ c.l..
+\textit{Lower left panel:} Constraints on $\bar{b}(m_{\mathrm{lim}})$, as defined in Eq.~\ref{eq:bias-fit-func}.
+The solid line illustrates the best-fit relation given in Eq.~\ref{eq:bias-fit-func-result}.
+\textit{Lower right panel:} Comparison of the results obtained in this analysis to the bias values assumed for LSST forecasts in the DESC SRD.}
         \label{fig:magnitude-cuts-bias}

### 2019-10-23 doc/Paper/main.tex
affiliations and acknowledgements

@@
 \author[f]{Eric Gawiser,}
-\author[x]{Rachel Mandelbaum,}
-\author[g,h,i,j]{Hironao Miyatake,}
-\author[k]{Jeffrey A. Newman,}
-\author[x]{Ignacio Sevilla,}
-\author[e,l]{Sarah Skinner,}
-\author[x]{Erica Wagoner}
+\author[g]{Rachel Mandelbaum,}
+\author[h,i,j,k]{Hironao Miyatake,}
+\author[l]{Jeffrey A. Newman,}
+\author[m]{Ignacio Sevilla,}
+\author[e,n]{Sarah Skinner,}
+\author[o]{Erica Wagoner}
 
@@
 \affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
-\affiliation[g]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
-\affiliation[h]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
-\affiliation[i]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
-\affiliation[j]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
-\affiliation[k]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
-\affiliation[l]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
+\affiliation[g]{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\affiliation[h]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
+\affiliation[i]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
+\affiliation[j]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
+\affiliation[k]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+\affiliation[l]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
+\affiliation[m]{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
+\affiliation[n]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
+\affiliation[o]{Department of Physics, University of Arizona, Tucson, AZ, 85721, USA}
 
@@
 \section{Introduction}\label{sec:intro}
-
   The past two decades have seen a revolution in our understanding of the Universe and its constituents.
@@
 There are two main approaches to preparing for the arrival of data.
-On one hand, we are building sophisticated, realistic mock data sets, such as LSST DESC Data Challenge 2 \cite{1909.07340,1907.06530}.
+On one hand, we are building sophisticated, realistic mock data sets, such as LSST Dark Energy Science Collaboration (DESC) Data Challenge 2 \cite{1909.07340,1907.06530}.
 On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment.
@@
   Despite the small fraction of sky covered by the data used in this work, HSC DR1 constitutes an ideal proxy for the data expected for LSST.
-Our analysis demonstrates the feasibility of photometric galaxy clustering analyses using such high signal-to-noise datasets, which bodes well for future cosmological constraints using data from LSST.
+Our analysis demonstrates the feasibility of photometric galaxy clustering studies using such high signal-to-noise datasets.
+In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics.
+These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.
 
 \acknowledgments
-
-DA acknowledges support from the Beecroft trust and from STFC through
-an Ernest Rutherford Fellowship, grant reference ST/P004474/1.  HA, BA
-and EG have been supported by the Rutgers Discovery Informatics
-Institute Fellowship of Excellence in Computational and Data Science
-(AY 2017-2020) and Rutgers University \& Bevier Dissertation
-Completion Fellowship (AY 2019-2020). HA, AB, and EG were supported by
-the Department of Energy (grants DE-SC0011636 and DE-SC0010008). HA
-also thanks the LSSTC Data Science Fellowship Program, which is funded
-by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation,
-and the Moore Foundation, as participation in the program has
-benefited this work. ZG is supported by a Rhodes Scholarship granted
-by the Rhodes Trust. HM has been supported by the Jet Propulsion Laboratory,
-California Institute of Technology, under a contract with the National
-Aeronautics and Space Administration and Grant-in-Aid for Scientific
-Research from the JSPS Promotion of Science (No. 18H04350). 
-JAN us supported by grant DOE DE-SC0007914 from
-the U.S. Department of Energy Office of Science (Office of High Energy
-Physics). This manuscript has been authored by Fermi Research
-Alliance, LLC under Contract No. DE-AC02-07CH11359 with the
-U.S. Department of Energy, Office of Science, Office of High Energy
-Physics. The work by JS was supported by the U.S. Department of Energy
-award DE-SC0009920. This project was supported in part by the
-U.S. Department of Energy, Office of Science, Office of Workforce
-Development for Teachers and Scientists (WDTS) under the Science
-Undergraduate Laboratory Internships Program (SULI).
+  DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
+  HA, BA and EG have been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020).
+  HA, AB, and EG were supported by the Department of Energy (grants DE-SC0011636 and DE-SC0010008).
+  HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation, and the Moore Foundation, as participation in the program has benefited this work.
+  ZG is supported by a Rhodes Scholarship granted by the Rhodes Trust.
+  RM is supported by the Department of Energy Cosmic Frontier program, grant DE-SC0010118.
+  HM has been supported by the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration and Grant-in-Aid for Scientific Research from the JSPS Promotion of Science (No.
+18H04350).
+  JAN us supported by grant DOE DE-SC0007914 from the U.S. Department of Energy Office of Science (Office of High Energy Physics).
+  This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
+  The work by JS was supported by the U.S. Department of Energy award DE-SC0009920.
+  This work was supported by the grant MDM-2015-0509 from the Spanish Ministry of Science and Innovation.
+  This project was supported in part by the U.S.
+Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
 
@@
 
-This paper makes use of software developed for the Large Synoptic Survey Telescope. We thank the LSST Project for making their code available as free software at  http://dm.lsst.org
+  This paper makes use of software developed for the Large Synoptic Survey Telescope. We thank the LSST Project for making their code available as free software at \url{http://dm.lsst.org}.
 

### 2019-10-23 doc/Paper/main.tex
Acknowledgments.

@@
 In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) analysis.
-As can be seen, we find significant differences between these two.
+As can be seen, we find these two to differ at approximately $2 \sigma$, using the uncertainties on our bias measurement.
 An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
@@
   DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
+  AN would like to thank Jo Dunkley and David Spergel for numerous helpful discussions and suggestions. AN further acknowledges support from National Science Foundation Grant No. 1814971.
   HA, BA and EG have been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020).

### 2019-10-23 doc/Paper/main.tex
Fixed typos in table.

@@
 To do so, we estimated the covariance matrix of the redshift distribution amplitudes in each narrow histogram bin shown in Fig.
-\ref{fig:nzs} assuming a simple cylindrical survey geometry and that volume-to-volume number density correlations follow a normal distribution given a biased linear power spectrum.
+\ref{fig:nzs}, assuming a simple cylindrical survey geometry and that volume-to-volume number density correlations follow a normal distribution given a biased linear power spectrum.
 From this covariance matrix, we then draw Gaussian realizations of the redshift distributions (with our fiducial estimate as the mean).
@@
 We therefore conclude that the priors used here are conservative, and encompass the range of shift and width values allowed by our uncertainties.
-It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance, beyond the simple shift-width parameterizations (e.g.
+It is interesting to note that, having access to the covariance matrix of the redshift distribution uncertainties  allows us to perform a more general characterization of the $N(z)$ uncertainties associated with sample variance beyond the simple shift-width parameterizations (e.g.
 through principal component analysis).
@@
           Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
-          $M_{\mathrm{min}}$ & flat $\in [0., \,17.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
+          $M_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
           $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
@@
           $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
-          $M_{1}$ & flat $\in [0., \,15.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
-          $M_{1, p}$ & flat $\in [-10., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
+          $M_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
+          $M_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
           $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
@@
           $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
-          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0727$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0303$ \\
           $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
-          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $-0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
           $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
@@
             fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
-            auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $13.00 \pm 0.33$  & - & - & - \\
+            auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $12.99 \pm 0.33$  & - & - & - \\
             G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
             G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
-            no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.645 \\ -0.652}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
+            no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.648 \\ -0.653}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
             no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
             bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
-            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.97}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.49\substack{+4.16 \\ -4.08}$ & $13.19\substack{+0.42 \\ -0.39}$ & - & - & - \\
+            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.94}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.46\substack{+3.66 \\ -3.63}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
             pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
@@
 & $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
-            fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.14 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
+            fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.13 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
             fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\

### 2019-10-23 doc/Paper/main.tex
More typos.

@@
     To estimate the fiducial redshift distributions used in our main analysis, we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
-The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histogramming these redshifts with appropriate weights.
+The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histograming these redshifts with appropriate weights.
 These weights are calculated following the procedure described in \cite{2017MNRAS.465.1454H,2019PASJ...71...43H}, which we summarize here for completeness:
@@
 We find that the data cannot separately constrain the mean shift parameters $\Delta z_{i}$, as opposed to pairwise differences between those.
-We therefore show the constraints in terms of the reparametrized variables $\Sigma_{i=0}^{3} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
+We therefore show the constraints in terms of the reparameterized variables $\Sigma_{i=0}^{3} \Delta z_{i}, \Delta z_{1} - \Delta z_{0}, \Delta z_{2} - \Delta z_{1}, \Delta z_{3} - \Delta z_{2}$, which denote the sum of the $\Delta z_{i}$ and their pairwise differences respectively.
 While $\Sigma_{i=0}^{3} \Delta z_{i}$ and the width parameters $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).

### 2019-11-16 doc/Paper/main.tex
Started implementing IR comments.

@@
 
+%\usepackage{lineno}
+%\linenumbers
+
 \definecolor{internationalkleinblue}{rgb}{0.0, 0.18, 0.65}
@@
   Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}.
-For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where effects of blending affect a significant fraction of all sources.
+For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources.
 The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
@@
    \hline
-   Total    & 9734457 & 87.7 & $2.1\times10^{-3}$ \\
+   Total    & 9,734,457 & 87.7 & $2.1\times10^{-3}$ \\
    \hline
@@
 The {\tt photoz\_best} estimator is defined to minimize the risk that the true galaxy redshift lies outside the range $z_{\rm true}\pm 0.15(1+z_{\rm true})$, where $z_{\rm true}$ is the galaxy's true redshift.
-A preliminary Fisher matrix study showed that the information content saturates quickly when slicing the data into more than four samples.
+A preliminary Fisher matrix \cite{Fisher:1935} study showed that the information content saturates quickly when slicing the data into more than four samples.
 The redshift bins are described in Table \ref{tab:bins_summary}, and the associated redshift distributions are discussed in Section \ref{ssec:methods.nz}.
@@
 Not all pixels contain enough stars to estimate a reliable mean flux error.
-We use a nearest-neighbor interpolation to assign a depth value to those pixels that contain less than 4 stars.
+We use a nearest-neighbor interpolation to assign a depth value to those pixels that contain fewer than 4 stars.
 We verified that we obtain similar depth estimates using other methods, such as that outlined in \cite{2018PASJ...70S..25M}, in which 10$\sigma$ depth is defined as the mean {\tt cmodel} magnitude of all sources with $i$-band signal-to-noise ratio between 9 and 11.
-It is worth emphasizing that our method uses only stars, discarding all sources classified as galaxies.
+We emphasize that our method uses only stars, discarding all sources classified as galaxies.
 The use of galaxies to estimate any systematics map is dangerous in the context of template deprojection, since the stochastic noise in the map associated with the discrete sampling of these sources correlates directly with the galaxy distribution, and can give rise to spurious correlations that bias the estimated power spectrum after deprojection (see Section \ref{ssec:methods.cell}).
@@
 \cite{Krause:2017}):
-    \begin{align}
-      \frac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} &= \left( \frac{68}{21} - \frac{1}{3}\frac{\mathrm{d}\log{k^{3} P_{\mathrm{lin}}}(k, z)}{\mathrm{d}\log k} \right) I_{a}^{1}(k)I_{b}^{1}(k)P_{\mathrm{lin}}(k, z) + I_{ab}^{1}(k, k) \\ &- (b_{a} + b_{b})P_{ab}(k, z).
+     \begin{equation}
+    \begin{aligned}
+      \frac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} =& \left( \frac{68}{21} - \frac{1}{3}\frac{\mathrm{d}\log{k^{3} P_{\mathrm{lin}}}(k, z)}{\mathrm{d}\log k} \right) I_{a}^{1}(k)I_{b}^{1}(k)P_{\mathrm{lin}}(k, z) + I_{ab}^{1}(k, k) \\ &- (b_{a} + b_{b})P_{ab}(k, z).
     \label{eq:ps-resp}  
-    \end{align}
+    \end{aligned}
+     \end{equation}
     The last term in Eq.~\ref{eq:ps-resp} accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.
@@
       \caption{Summary of parameters varied in the MCMC with their respective priors.
-The posterior means and best-fits denote the values derived for our fiducial analysis.
-The uncertainties denote the $68 \%$ c.l.
+The posterior means and best-fits are given for our fiducial analysis.
+The best-fit is defined as the maximum likelihood value of each parameter and the uncertainties denote the $68 \%$ c.l.
 corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:params}
@@
 To illustrate the uncertainty on this relation, we also show a sample of curves derived from 1000 random realizations from the MCMCs.
-As can be seen, we find that, within or uncertainties, the data prefer both $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ to be approximately redshift-independent.
+As can be seen, we find that, within our uncertainties, the data prefer both $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ to be approximately redshift-independent.
 This is somewhat counterintuitive, as we would naively expect at least the minimal mass to host a central galaxy to increase with redshift, since galaxies will only form in the most massive halos at early times.

### 2019-11-16 doc/Paper/main.tex
Couple of more changes.

@@
     \begin{equation}
-      \log{M_{i}(z)} = M_{i} + M_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
+      \log{M_{i}(z)} = \mu_{i} + \mu_{i, p} \left(\frac{1}{1+z} - \frac{1}{1+z_{p}}\right),
     \end{equation}
@@
     We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}.
-In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{0}, \allowbreak \, M_{0, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}.
+In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{\mu_{\mathrm{min}}, \allowbreak \, \mu_{\mathrm{min}, p}, \allowbreak \, \mu_{0}, \allowbreak \, \mu_{0, p}, \allowbreak \, \mu_{1}, \allowbreak \, \mu_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}.
 The remaining parameters account for photometric redshift uncertainties as described in Sec.~\ref{sssec:methods.theory.photoz_syst}.
@@
           Parameter & Prior & Posterior mean & Best-fit \\ \hline \Tstrut                             
-          $M_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
-          $M_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
-          $M_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
-          $M_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
-          $M_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
-          $M_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
+          $\mu_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
+          $\mu_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
+          $\mu_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
+          $\mu_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
+          $\mu_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
+          $\mu_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
           $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
@@
 
-      Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $M_{\mathrm{min}}, \allowbreak \, M_{\mathrm{min}, p}, \allowbreak \, M_{1}, \allowbreak \, M_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
+      Fig.~\ref{fig:constraints-fid-hod} shows the constraints on the HOD parameters $\mu_{\mathrm{min}}, \allowbreak \, \mu_{\mathrm{min}, p}, \allowbreak \, \mu_{1}, \allowbreak \, \mu_{1, p}$ for our fiducial model described in Sec.~\ref{ssec:methods.constr}.
 The constraints on all fitted parameters are shown in Fig.~\ref{fig:constraints-fid-full} and the corresponding best-fit values and means are shown alongside their $68 \%$ confidence limits in Tab.~\ref{tab:params}.
-As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $M_{\mathrm{min}}, \, M_{\mathrm{min}, p}, \, M_{1}, \, M_{1, p}$.}.
+As can be seen from Figures \ref{fig:constraints-fid-hod} and \ref{fig:constraints-fid-full}, the data allow us to constrain $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ whereas $M_{0}(z)$ is unconstrained\footnote{In the following, we therefore only show constraints on the HOD parameters $\mu_{\mathrm{min}}, \, \mu_{\mathrm{min}, p}, \, \mu_{1}, \, \mu_{1, p}$.}.
 Fig.~\ref{fig:cls-best-fit} shows the theoretical predictions derived from maximum likelihood parameters alongside the measured power spectra.
@@
             \hline\hline 
-            Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $M_{\mathrm{min}, p}$ & $M_{\mathrm{min}}$ & $M_{1, p}$ & $M_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
+            Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $\mu_{\mathrm{min}, p}$ & $\mu_{\mathrm{min}}$ & $\mu_{1, p}$ & $\mu_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
             fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
@@
     \end{equation}
-    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=(\ell+1/2)/\chi$.
+    where $P_{mm}$ is the 3D power spectrum of matter fluctuations, $P_{gm}$ is the galaxy-matter cross-spectrum and we have omitted the dependence of all quantities on $z$ or $k=\sfrac{(\ell+\sfrac{1}{2})}{\chi}$.
 

### 2019-11-16 doc/Paper/main.tex
Added errors for bias fitting function parameters.

@@
 We discuss and conclude in Section \ref{sec:discussion}.
+More detailed descriptions of the generation of systematics maps are deferred to the Appendix.
   %In this paper we focus exclusively on the galaxy clustering part of the data analysis.
@@
 In the former case we find that the values for the photo-$z$ systematics parameters $\Sigma_{i=0}^{3} \Delta z_{i}, \Delta z_{i} - \Delta z_{j}$ required by the five methods differ significantly, which leads to differences in both constraining power and constraints on HOD parameters.
-We especially find significant shifts in $M_{\mathrm{min}}$ and $M_{1}$ along their degeneracy direction.
+We especially find significant shifts in $\mu_{\mathrm{min}}$ and $\mu_{1}$ along their degeneracy direction.
 Investigating this further, we find that the observed differences in $\Delta z_{i}$ cannot be explained with the differences in mean redshift between the distributions derived using the five separate methods.
@@
       \begin{aligned}
-        \alpha &= -1.30, \\
+        \alpha &= -1.30 \pm 0.19\footnotemark,\\
         \bar{b}(m_{\mathrm{lim}}) &= b_{1}(m_{\mathrm{lim}}-24) + b_{0},
@@
     \end{equation}
-    where $b_{1} = -0.0631$ and $b_{0} = 0.8356$. The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
+    \footnotetext{We note that we used $\sigma(\tilde{x}) = 1.253 \; \sigma(\bar{x})$, where $\tilde{x}$ denotes the median and $\bar{x}$ is the mean of a given sample.}
+    where $b_{1} = -0.0624 \pm 0.0070$ and $b_{0} = 0.8346 \pm 0.161$.
+The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
 

### 2019-11-17 doc/Paper/main.tex
Changed notation of log masses to mu.

@@
 \usepackage{mathrsfs}
-\usepackage{subfigure}
+\usepackage{subcaption}
 \usepackage{rotating}
@@
       \begin{center}
-        \subfigure[$C_{\ell}^{00}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}}
-        \subfigure[$C_{\ell}^{11}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}} \\
-        \subfigure[$C_{\ell}^{22}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}}
-        \subfigure[$C_{\ell}^{33}$]{\includegraphics[width=0.49\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}}
+        \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}
+        \caption{$C_{\ell}^{00}$}
+        \end{subfigure}
+        \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf} \\
+        \caption{$C_{\ell}^{11}$}
+        \end{subfigure}
+        \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}
+        \caption{$C_{\ell}^{22}$}
+        \end{subfigure}
+        \begin{subfigure}{0.49\textwidth}
+        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}
+        \caption{$C_{\ell}^{33}$}
+        \end{subfigure}
         \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} \label{fig:covariance-contributions}
@@
         \begin{center}
-          \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
-          \subfigure{\includegraphics[width=0.49\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}}
+          \begin{subfigure}[t]{0.49\textwidth}
+          \includegraphics[width=\textwidth]{figures/logM_min_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}
+          \end{subfigure}
+          \begin{subfigure}[t]{0.49\textwidth}
+          \includegraphics[width=\textwidth]{figures/logM_1_z_dependence_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_best-fit+random-draws.pdf}
+          \end{subfigure}
           \caption{Functional forms for the logarithm of $M_{\mathrm{min}}(z)$ and $M_{1}(z)$ derived from our best-fit theoretical model alongside the functions derived from 1000 random realizations of the MCMCs to illustrate the uncertainty.}
@@
         \begin{center}
-          \subfigure{\includegraphics[width=0.32\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-          \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
-          \subfigure{\includegraphics[width=0.32\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}}
+          \begin{subfigure}{0.32\textwidth}
+          \includegraphics[width=\textwidth]{figures/M_halo_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+          \end{subfigure}
+          \begin{subfigure}{0.32\textwidth}
+          \includegraphics[width=\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+          \end{subfigure}
+          \begin{subfigure}{0.32\textwidth}
+          \includegraphics[width=\textwidth]{figures/bias-growth_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+          \end{subfigure}
           \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
@@
       \begin{center}
-        \subfigure[Cumulative galaxy number counts as a function of $i$-band magnitude for the lowest tomographic redshift bin used in this analysis.]{\includegraphics[width=0.49\textwidth]{figures/mag-dist-cumulative=True+fit-mmin=23-sample=WIDE-bin=0.pdf}}
-        \subfigure[Comparison of $s(z)$ (see Eq.~\ref{eq:s-func}) derived using the WIDE, DEEP and UDEEP HSC galaxy samples.]{\includegraphics[width=0.49\textwidth]{figures/s-z-func-samples=WIDE-DEEP-UDEEP.pdf}}
+        \begin{subfigure}[t]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/mag-dist-cumulative=True+fit-mmin=23-sample=WIDE-bin=0.pdf}
+        \caption{Cumulative galaxy number counts as a function of $i$-band magnitude for the lowest tomographic redshift bin used in this analysis.}
+        \end{subfigure}\hfill
+        \begin{subfigure}[t]{0.47\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figures/s-z-func-samples=WIDE-DEEP-UDEEP.pdf}
+        \caption{Comparison of $s(z)$ (see Eq.~\ref{eq:s-func}) derived using the WIDE, DEEP and UDEEP HSC galaxy samples.}
+        \end{subfigure}
         \caption{Illustration of data-driven estimation of $s(z)$ for the galaxy sample used in our analysis.} 
@@
       \begin{center}
-        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-        \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}}
-          \subfigure{\includegraphics[width=0.48\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_i24p5-vs-DESC-SRD.pdf}}
+        \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=0.9\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}
+        \end{subfigure}
+        \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=0.9\textwidth]{figures/bias-growth-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}
+        \end{subfigure}
+       \begin{subfigure}{0.48\textwidth}
+       \includegraphics[width=0.9\textwidth]{figures/bias-mlim_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_magnitude_cuts_fitting-func.pdf}
+       \end{subfigure}
+          \begin{subfigure}{0.48\textwidth}
+          \includegraphics[width=0.9\textwidth]{figures/bias-redshift_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_i24p5-vs-DESC-SRD.pdf}
+           \end{subfigure}
         \caption{\textit{Upper panels:} Constraints on the large-scale galaxy bias $b(z)$ and $b(z)D(z)$ as a function of redshift for the different magnitude-limited galaxy samples considered in this analysis.

### 2019-11-17 doc/Paper/main.tex
Added footnote about blinding in introduction.
Done with first pass through IR comments from Jon and Tom.

@@
 \usepackage{rotating}
+\usepackage{chngcntr}
 \newcommand{\nv}{\vec{\theta}}
@@
 
-  In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data.
+  In this work, we present an analysis of photometric galaxy clustering using HSC DR1 data\footnote{We note that we do not blind our results in any stage of the analysis.}.
 We split the data into four tomographic redshift bins and measure both the auto- and cross-power spectra of all bins, correcting for observational systematics using mode deprojection.
@@
 
-  In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\url{https://hsc-release.mtk.nao.ac.jp}}.
+  In this work, we use data from the first data release of the Hyper Suprime-Cam Subaru Strategic Program (HSC DR1 hereon)\footnote{\url{https://hsc-release.mtk.nao.ac.jp}.}.
 The release is extensively documented in \cite{2018PASJ...70S...8A}, and here we only provide the details of the galaxy sample and associated data used for our clustering analysis.
@@
       \begin{center}
-        \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
-        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
-        \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
-      \end{center}
-    \end{figure}
-
-    \begin{figure}
-      \begin{center}
         \includegraphics[width=0.3\textwidth]{figures/contours-A_mu_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_mag-bias-free-fit=auto+cross-vs-mag-bias-free-fit=auto.pdf}
@@
         \label{fig:constraints-fit=mag-bias-ampl_fit=auto+cross-vs-fit=mag-bias-ampl_fit=auto}
+      \end{center}
+    \end{figure}
+
+    \begin{figure}
+      \begin{center}
+        \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_no-mag-bias-vs-mag-bias-free.pdf}
+        \caption{Comparison of our fiducial HOD constraints to those obtained when varying the magnification amplitude. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+        \label{fig:constraints-no-mag-bias-vs-fit=mag-bias-ampl}
       \end{center}
@@
 \appendix
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.95\textwidth]{figures/contours_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
-    \caption{Fiducial constraints on HOD and systematics parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
-    \label{fig:constraints-fid-full}
-  \end{center}
-\end{figure}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
-%\caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalizing over shifts in the means and setting $z_{w, i} = 0$.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
-%\label{fig:constraints-HOD-fit-pz-shifts-pz-methods}
-%\end{center}
-%\end{figure}
-%
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.95\textwidth]{figures/contours-pz-syst_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2_fit=auto+cross_cosmo=const-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
-%\caption{Comparison of the constraints on photo-$z$ systematics parameters obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} marginalizing over shifts in the means and setting $z_{w, i} = 0$.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
-%\label{fig:constraints-pz-syst-fit-pz-shifts-pz-methods}
-%\end{center}
-%\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
-    \caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} setting $z_{w, i} = 0, \Delta z_{i} = 0$.
-The inner (outer) contour shows the $68 \%$ c.l.
-($95 \%$ c.l.).}
-    \label{fig:constraints-HOD-no-pz-shifts-pz-methods}
-  \end{center}
-\end{figure}
-
-\bibliography{bibliography}
-
-\appendix
+\counterwithin{figure}{section}
+
 \section{Reconstructing depth from discrete sources}\label{app:depth}
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.95\textwidth]{figures/contours_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}
+    \caption{Fiducial constraints on HOD and systematics parameters obtained in this work. The inner (outer) contour shows the $68 \%$ c.l. ($95 \%$ c.l.).}
+    \label{fig:constraints-fid-full}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_no-pz-shifts_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_pz-methods.pdf}
+    \caption{Comparison of the HOD constraints obtained using the redshift distributions derived from COSMOS30, \texttt{Ephor\_AB}, \texttt{Ephor}, \texttt{DEmP} and \texttt{FRANKEN-Z} setting $z_{w, i} = 0, \Delta z_{i} = 0$.
+The inner (outer) contour shows the $68 \%$ c.l.
+($95 \%$ c.l.).}
+    \label{fig:constraints-HOD-no-pz-shifts-pz-methods}
+  \end{center}
+\end{figure}
+
+\bibliography{bibliography}
+
 \end{document}

### 2019-11-18 doc/Paper/main.tex
Started addressing comments from Elisabeth.

@@
     The second contribution to the total covariance matrix for galaxy clustering is caused by the connected part of the trispectrum, which accounts for mode-coupling due to the non-Gaussian nature of the density field.
-In our work we estimate this contribution using the halo model coupled with a halo occupation distribution.
+In our work we compute this contribution using the halo model coupled with a halo occupation distribution.
 In general, this contribution is given by the angular projection of the three-dimensional trispectrum as (see e.g.
@@
 $A(\ell_{i}) \equiv \int_{\vert \boldsymbol{\ell} \vert \in \ell_{i}} \mathrm{d}^{2}\boldsymbol{\ell}$, which is approximately given by $A(\ell_{i}) \approx 2 \pi \Delta \ell_{i} \ell_{i}$ for $\ell_{i} \gg \Delta \ell_{i}$.
-$q^a(\chi)\equiv H(z)p^a(z)$ is the window function for the $a$-th redshift bin.
+Finally, $q^a(\chi(z))\equiv \sfrac{H(z)}{c} \;p^a(z)$ is the window function for the $a$-th redshift bin.
 
@@
   \subsection{Covariance matrix}\label{ssec:results.covariance}
-    We estimate the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}.
+    We compute the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}.
 In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions.
@@
         \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
-        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, estimated as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
+        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, computed analytically as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
       \end{center}
@@
 studies of galaxies in the DEEP2 survey, which found constant clustering strengths as a function of redshift (and thus $b(z) \propto \sfrac{1}{D(z)}$) for magnitude-limited samples \cite{Coil:2004}.
+
+Finally we note that in our analysis, we assume the observed fraction of central galaxies $f_{c}$ to be unity and constant with redshift.
+In light of the observed drop-out of red galaxies from our sample at high redshift, this may not be true, as $f_{c}$ could potentially decrease with redshift.
+In order to test our assumption, we perform separate HOD fits to the four redshift bins, allowing for variations in $f_{c}$ on top of $M_{\mathrm{min}}, M_{1}$ and $M_{0}$.
+We find the data to not have the statistical power to constrain $f_{c}$ and the derived values to be consistent with redshift-independent.
+Furthermore, our constraints on $M_{\mathrm{min}}, M_{1}$ and $M_{0}$ are robust to variations in $f_{c}$.
+We therefore conclude that our results are not significantly affected by the choice of $f_{c}=1$.
+
       \begin{figure}
@@
       \end{figure}
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[scale=0.55]{figures/color-magnitude_cut=pz_best_eab_nbin=4_weights=True.pdf}
-%\caption{Synopsis of the framework for integrated probe combination employed in this work.}
-%\label{fig:color-mag}
-%\end{center}
-%\end{figure}
 

### 2019-11-18 plot_scripts/plots_masks.py
changed masks

@@ -1,7 +1,15 @@
 import flatmaps as fm
 import numpy as np
 import matplotlib.pyplot as plt
+from astropy import units as u
 
+yticks={'GAMA09H':[0.,1.,2.],
+        'GAMA15H':[-1., 0., 1.],
+        'HECTOMAP':[43., 44.],
+        'VVDS':[0., 1., 2.],
+        'WIDE12H':[-1., 0., 1.],
+        'XMMLSS':[-6., -5., -4.]
+        }
 for field in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
     fsk,msk=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"+field+"_sirius_i24p5_out/masked_fraction.fits")
     fig=plt.figure()
@@ -11,5 +19,7 @@ for field in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
                  origin='lower', interpolation='nearest')
     ax.set_xlabel('R.A.', fontsize=14)
     ax.set_ylabel('Dec.', fontsize=14)
+    ax.coords[1].set_ticks(np.array(yticks[field]) * u.deg)
+    ax.coords[1].set_major_formatter('dd')
     plt.savefig("../doc/Paper/figures/mask_"+field+".pdf",bbox_inches='tight')
 plt.show()

### 2019-11-18 plot_scripts/plots_sysmaps.py
good coords in all maps

@@ -1,6 +1,7 @@
 import flatmaps as fm
 import numpy as np
 import matplotlib.pyplot as plt
+from astropy import units as u
 
 prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/"
 fsk,msk=fm.read_flat_map(prefix+"masked_fraction.fits")
@@ -30,6 +31,9 @@ def plot_syst(name,fname,band,units=None,savename=None):
     im.cmap.set_under('#FFFFFF')
     cbar=plt.colorbar(im,orientation='horizontal')
     cbar.ax.set_xlabel(label,fontsize=14)
+    yticks = np.array([-6., -5., -4.])
+    ax.coords[1].set_ticks(yticks * u.deg)
+    ax.coords[1].set_major_formatter('dd')
     ax.set_xlabel('R.A.', fontsize=14)
     ax.set_ylabel('Dec.', fontsize=14)
     if savename is not None:

### 2019-11-18 plot_scripts/plots_systmask.py

@@ -1,6 +1,7 @@
 import flatmaps as fm
 import numpy as np
 import matplotlib.pyplot as plt
+from astropy import units as u
 
 prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_"
 field="VVDS"
@@ -19,12 +20,18 @@ ax=fig.add_subplot(211,projection=fsk.wcs)
 ax.set_title("Sirius mask",fontsize=14)
 im=ax.imshow((msk1+msk2).reshape([fsk.ny,fsk.nx]),vmin=0,vmax=2,
              origin='lower', interpolation='nearest')
+yticks = np.array([0., 1., 2.])
+ax.coords[1].set_ticks(yticks * u.deg)
+ax.coords[1].set_major_formatter('dd')
 ax.set_xlabel('R.A.', fontsize=14)
 ax.set_ylabel('Dec.', fontsize=14)
 ax=fig.add_subplot(212,projection=fsk.wcs)
 ax.set_title("Arcturus mask",fontsize=14)
 im=ax.imshow(msk3.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
              origin='lower', interpolation='nearest')
+yticks = np.array([0., 1., 2.])
+ax.coords[1].set_ticks(yticks * u.deg)
+ax.coords[1].set_major_formatter('dd')
 ax.set_xlabel('R.A.', fontsize=14)
 ax.set_ylabel('Dec.', fontsize=14)
 plt.savefig("../doc/Paper/figures/systmask.pdf",

### 2019-11-18 doc/Paper/main.tex
Added footnote explaining s(z) notation.

@@
     \end{equation}
-    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered.
+    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered\footnote{In the following, we omit the dependence of $s(z)$ on $m_{\mathrm{lim}}$ for brevity.}.
 In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.

### 2019-11-18 doc/Paper/main.tex
responses

--- 2019-11-18 doc/Paper/main.tex
@@
     \end{enumerate}
-    It is worth noting that the resolution of the resulting mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis.
+    We verified that the resulting mask is robust by comparing the power spectra estimated with it with those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask.
+It is worth noting that the resolution of this mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis.
 After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.
@@
     A central assumption in standard HOD parameterizations is that centrals/satellites follow a Bernoulli/Poisson distribution.
+The model used here also assumes that halos can only contain satellites if they contain a central.
 
@@
     \begin{equation}
-      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
+      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z',m_{\rm lim})-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
     \end{equation}
@@
     \begin{equation}
-      \left. s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
+      \left. s(z,m_{\rm lim}) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
       \label{eq:s-func}
@@
     where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered.
+In what follows we will omit the dependence of $s$ on $m_{\rm lim}$ for brevity.
 In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.

### 2019-11-18 doc/Paper/main.tex

@@
     \end{equation}
-    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered.
-In what follows we will omit the dependence of $s$ on $m_{\rm lim}$ for brevity.
+    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered\footnote{In the following, we omit the dependence of $s(z)$ on $m_{\mathrm{lim}}$ for brevity.}.
 In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies.

### 2019-11-19 hsc_lss/__init__.py
Added shot noise calculations in LSS_nmaps.py.  Other files modified to make it run without some standard dependencies.

@@ -1,6 +1,6 @@
 from ceci import PipelineStage
 from .reduce_cat import ReduceCat
-from .syst_mapper import SystMapper
+# from .syst_mapper import SystMapper
 from .pdf_match import PDFMatch
 from .cosmos_weight import COSMOSWeight
 from .cat_mapper import CatMapper

### 2019-11-19 hsc_lss/power_specter.py

@@ -6,7 +6,7 @@ from astropy.io import fits
 import pymaster as nmt
 from .tracer import Tracer
 import os
-import sacc
+#import sacc
 from scipy.interpolate import interp1d
 
 class PowerSpecter(PipelineStage) :

### 2019-11-19 notebooks/LSS_nmaps.py

@@ -14,12 +14,15 @@ from astropy.wcs import WCS
 from numpy.random import poisson
 from hsc_lss.flatmaps import read_flat_map, FlatMapInfo
 from hsc_lss.map_utils import createCountsMap
-from hsc_lss.tracer import Tracer
 import pymaster as nmt
 from tqdm import tqdm
 
 import matplotlib as mpl
 from matplotlib import pyplot as plt
+from matplotlib import rc
+# rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+# rc('text', usetex=True)
+
 
 
 catalogs = glob('/global/cscratch1/sd/damonge/HSC_ceci/WIDE_*_sirius_out/')
@@ -242,7 +245,7 @@ class field:
 
 
 
-def plot_shotnoise_avg_test():
+def plot_shotnoise_avg_test(savepath = False):
 
     """
     Plots the average shot noise estimates across all of the HSC fields
@@ -279,20 +282,35 @@ def plot_shotnoise_avg_test():
     fig = plt.figure(figsize = (8,8))
     sp = fig.add_subplot(111)
 
-    for znum, (this_atn, this_ase) in enumerate(zip(avg_theoretical_noise, avg_shot_estimate)):
+    labeltext = ['$%.2f<z<%.2f$'%(zbin1, zbin2) for zbin1, zbin2 in zip(pz_bins[:-1], pz_bins[1:])]
+
+    for znum, (this_atn, this_ase, thislabel) in enumerate(zip(avg_theoretical_noise, avg_shot_estimate, labeltext)):
 
         sp.plot(ells, avg_theoretical_noise[znum], linewidth = 1.5, color = 'C' + str(znum), zorder = 0, alpha = 0.4)
-        sp.plot(ells, avg_shot_estimate[znum], linewidth = 2, color = 'C' + str(znum), zorder = 1)
+        sp.plot(ells, avg_shot_estimate[znum], linewidth = 2, color = 'C' + str(znum), zorder = 1, label = thislabel)
+
+    if savepath:
+        header = 'Estimated Shot Noise from Adam\'s LSS_nmaps.py\n'
+        header+= 'en_zb: Estimated noise in redshift bins; calculated from 0.25*(<s1s1> + <s2s2> - 2*<s1s2>)\n'
+        header+= 'tn_zp: Theoretical noise in redshift bins; calculted by Namaster\n'
[…]

### 2019-11-19 doc/Paper/main.tex
homogeneous plot format

@@
 The solid curves in each panel show the stacked redshift distributions inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt Franken-Z} from left to right and top to bottom).
-The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in red, blue orange and green respectively.
+The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in different colors.
 Note that all four redshift estimation codes use the same COSMOS 30-band catalog so the level of visual agreement should not be taken as realistic measure of uncertainty on the redshift distributions.}
@@
 The red data points with error bars show the coadded power spectra (see Section \ref{sssec:results.spectra.fid}), with the hollow circles showing the absolute value of negative data.
-The Poisson noise contribution and deprojection biases subtracted from the raw power spectra are shown as grey and blue lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
+The Poisson noise contribution and deprojection biases subtracted from the raw power spectra are shown as grey and pink lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
 The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.}
@@
 As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection.
-This bias is also shown as a blue solid line in Figure \ref{fig:cls_summary}, where the dashed parts show the absolute value of the bias when it is negative.
+This bias is also shown as a pink solid line in Figure \ref{fig:cls_summary}, where the dashed parts show the absolute value of the bias when it is negative.
 This bias is always at least a factor $\sim5$ smaller than the measured power spectra, and is most relevant on large scales.
@@
         \caption{Difference with respect to our fiducial power spectra of alternative estimates of the power spectra normalized by their $1\sigma$ errors.
-The red points show the spectra estimated without contaminant deprojection.
-The blue points show spectra estimated using a conservative sky mask that removes highly contaminated regions (see Section \ref{sssec:results.spectra.syst} for details).
-The yellow points show the spectra calculated using the Arcturus bright star mask.}
+The pink points show the spectra estimated without contaminant deprojection.
+The light blue points show spectra estimated using a conservative sky mask that removes highly contaminated regions (see Section \ref{sssec:results.spectra.syst} for details).
+The dark blue points show the spectra calculated using the Arcturus bright star mask.}
         \label{fig:cls_systematics}
@@
 \ref{eq:deproj1}), finding the best-fit linear coefficients for each contaminant and subtracting the corresponding contribution from the observed map.
-Finally, the estimated power spectra must be corrected for the loss of modes incurred (blue line in Figure \ref{fig:cls_summary}).
+Finally, the estimated power spectra must be corrected for the loss of modes incurred (pink line in Figure \ref{fig:cls_summary}).
 This method is therefore able to account for any systematic contamination that is well described by a linear contribution.
@@
 This allows us to test the worst-case scenario where any source of contamination is completely ignored.
-The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in red in Figure \ref{fig:cls_systematics}.
+The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in pink in Figure \ref{fig:cls_systematics}.
 In all cases we observe very small differences (smaller than $1\sigma$) between both spectra.
@@
 Results are shown for $r$-band airmass (top) and dust absorption (bottom) for the third redshift bin in the VVDS field.
-The data are shown in red, while the solid black line shows the best-fit linear relation between both quantities.
+The data are shown in burgundy, while the solid black line shows the best-fit linear relation between both quantities.
 In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here).
@@
 The masked regions correspond to $\sim20\%$ of the available footprint on average, and are shown in the top right panel of Figure \ref{fig:ndens_syst} in turquoise for the VVDS field.
-The blue data points in Figure \ref{fig:cls_systematics} show the difference of the power spectra estimated using these more restrictive masks with respect to our fiducial power spectra, normalized by their $1\sigma$ errors.
+The light blue data points in Figure \ref{fig:cls_systematics} show the difference of the power spectra estimated using these more restrictive masks with respect to our fiducial power spectra, normalized by their $1\sigma$ errors.
 In the vast majority of cases we see only $<1\sigma$ differences between both spectra.
@@
 We can see that, while the masked regions are mostly centered around the same sources, the prescriptions used to define the masking radii are different (see \cite{2018PASJ...70S...7C} for further details).
-The yellow data points in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
+The dark blue data points in Figure \ref{fig:cls_systematics} show the difference with respect to our fiducial power spectra of the spectra computed using the Arcturus mask, normalized by their 1$\sigma$ errors.
 As before, we do not observe any statistically significant deviation between these spectra.

### 2019-11-19 plot_scripts/flatmaps.py

@@ -2,9 +2,10 @@ from __future__ import print_function
 import numpy as np
 import matplotlib.pyplot as plt
 from matplotlib import cm
-import pymaster as nmt
+#import pymaster as nmt
 from astropy.io import fits
 from astropy.wcs import WCS
+import formatting
 
 class FlatMapInfo(object) :
     def __init__(self,wcs,nx=None,ny=None,lx=None,ly=None) :

### 2019-11-19 plot_scripts/formatting.py

@@ -1,0 +1,42 @@
+import matplotlib
+
+matplotlib.rcParams['lines.linewidth'] = 1.
+matplotlib.rcParams['lines.linestyle'] = '-'
+matplotlib.rcParams['lines.color'] = 'black'
+#fonts & text
+matplotlib.rcParams['font.family'] = 'serif'
+matplotlib.rcParams['font.weight'] = 'normal'
+matplotlib.rcParams['font.size'] = 12.0
+matplotlib.rcParams['text.color'] = 'black'
+matplotlib.rcParams['text.usetex'] = True
+#axes & ticks
+matplotlib.rcParams['axes.edgecolor'] = 'black'
+matplotlib.rcParams['axes.linewidth'] = 1.6
+matplotlib.rcParams['axes.grid'] = False
+matplotlib.rcParams['axes.titlesize'] = 'x-large'
+matplotlib.rcParams['axes.labelsize'] = 32
+matplotlib.rcParams['axes.labelweight'] = 'normal'
+matplotlib.rcParams['axes.labelcolor'] = 'black'
+matplotlib.rcParams['axes.formatter.limits'] = [-4, 4]
+matplotlib.rcParams['xtick.major.size'] = 7
+matplotlib.rcParams['xtick.minor.size'] = 4
+matplotlib.rcParams['xtick.major.pad'] = 6
+matplotlib.rcParams['xtick.minor.pad'] = 6
+matplotlib.rcParams['xtick.labelsize'] = 32
+matplotlib.rcParams['xtick.minor.width'] = 1.6
+matplotlib.rcParams['xtick.major.width'] = 1.6
+matplotlib.rcParams['ytick.major.size'] = 7
+matplotlib.rcParams['ytick.minor.size'] = 4
+matplotlib.rcParams['ytick.major.pad'] = 6
+matplotlib.rcParams['ytick.minor.pad'] = 6
+matplotlib.rcParams['ytick.labelsize'] = 32
+matplotlib.rcParams['ytick.minor.width'] = 1.6
+matplotlib.rcParams['ytick.major.width'] = 1.6
+#legends
+matplotlib.rcParams['legend.numpoints'] = 1
+matplotlib.rcParams['legend.fontsize'] = 32
+matplotlib.rcParams['legend.shadow'] = False
+matplotlib.rcParams['legend.frameon'] = False
+matplotlib.rcParams['figure.autolayout'] = True
+
[…]

### 2019-11-19 plot_scripts/plots_cls_systematics.py

@@ -2,6 +2,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import sacc
 from scipy.stats import chi2 as chi2f
+import formatting
 
 prefix="/global/cscratch1/sd/damonge/HSC_ceci/"
 
@@ -10,6 +11,10 @@ def read_cls(field,
              msk_name='sirius',
              directory='CovAna_NoiAna_MskSirius_ClFit_Dpj0_DpjBands1'):
     file_prefix=prefix+"WIDE_"+field+"_"+msk_name+'_i24p5_out/'+directory+'/'
+    if msk_name=='arcturus':
+        file_prefix='../data_replotting/arcturus/'+field+'/'+directory+'/'
+    else:
+        file_prefix='../data_replotting/'+field+'/'+directory+'/'
 
     if wdpj:
         s=sacc.SACC.loadFromHDF(file_prefix+"power_spectra_wdpj.sacc")
@@ -47,14 +52,14 @@ nbins=4
 for b1 in range(nbins) :
     for b2 in range(nbins) :
         if b2<b1 :
-            axes[b1,b2].axis('off')
+            axes[b2,b1].axis('off')
 
 for t1,t2,typ,ells,ndx in s_fid['data'].sortTracers():
     lmax=min(lmaxs[t1],lmaxs[t2])
     mask=ells<lmax
     ls=ells[mask]
     ndxs=ndx[mask]
-    ax=axes[t1,t2]
+    ax=axes[t2,t1]
     c_fid=s_fid['data'].mean.vector[ndxs]
     c_ndp=s_ndp['data'].mean.vector[ndxs]
     c_sys=s_sys['data'].mean.vector[ndxs]
@@ -75,28 +80,32 @@ for t1,t2,typ,ells,ndx in s_fid['data'].sortTracers():
         label_msk=None
     ax.errorbar(ls*(0.95+0.1*(0+0.5)/3.),(c_ndp-c_fid)/e_ndp,
                 yerr=e_ndp/e_ndp,
-                fmt='.',c='r',label=label_ndp)
+                fmt='.',c=formatting.cmap1[0],label=label_ndp,
+                markersize=5, elinewidth=1.5, capthick=1.5, capsize=3.5)
+                
     ax.errorbar(ls*(0.95+0.1*(1+0.5)/3.),(c_sys-c_fid)/e_sys,
                 yerr=e_sys/e_sys,
-                fmt='.',c='b',label=label_sys)
[…]

### 2019-11-19 doc/Paper/main.tex
Started implementing comments from Jo.

--- 2019-11-18 doc/Paper/main.tex
@@
     \begin{enumerate}
-      \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth in different directions as follows.
+      \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth as a function of angular position on the sky as follows.
 For each pixel, we compute the average $i$-band flux error of all objects classified as stars that fall into it.
@@
 In general we could also consider other cumulants of the per-exposure distribution of observing condition values.
-As shown below, we do not observe an important contamination from these systematics in our results, and we therefore leave this more thorough study for future work.
+As shown in Sec.~\ref{sssec:results.spectra.syst}, we do not observe an important contamination from these systematics in our results, and we therefore leave this more thorough study for future work.
 
@@
   \subsection{Angular power spectra}\label{ssec:methods.cell}
-    We compute angular power spectra using a flat-sky pseudo-$C_\ell$ (PCL) algorithm \citep{2002ApJ...567....2H} as implemented in {\tt NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}.
+    We compute angular power spectra using a flat-sky pseudo-$C_\ell$ (PCL) algorithm \citep{2002ApJ...567....2H} as implemented in {\tt NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}.}.
 The reader is referred to the code's paper \cite{2019MNRAS.484.4127A} for a detailed description of the estimator, but we provide a brief summary here for completeness.
@@
     As noted above, the power spectra are computed in rings of $\ell=|{\bf l}|$, which we will call bandpowers here.
-We use 17 contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 158800).
+We use 17 contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 15800).
 Due to this bandpower averaging, the estimated power spectra cannot, strictly speaking, be compared with theoretical predictions estimated at token multipoles (e.g.
@@
     We use an analytical procedure to estimate the uncertainties of our measured power spectra, inspired by the methods used by \cite{Krause:2017}.
-As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labelled SSC here).
+As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labelled SSC here)\footnote{A comparison of the relative contributions of these three terms to the total covariance can be found in Fig.~\ref{fig:covariance-contributions}.}.
 The SSC contribution accounts for the coherent shift in the amplitude of density fluctuations within the surveyed volume caused by long wavelength modes larger than the survey.
@@
 For all sampled parameters, we assume flat, uniform priors.
-The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}.
-The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$.
+The sampled parameters are shown alongside their priors in Tab.~\ref{tab:params}\footnote{The values of these parameters derived from our analysis will be discussed in Sec.~\ref{ssec:results.hod-constraints}.}.
+The remaining HOD parameters are set to $\alpha = 1.0$ and $\sigma_{\log M} = 0.4$, consistent with the simulation results of Ref.~\cite{2005ApJ...633..791Z}.
 Unless stated otherwise, we further fix all cosmological parameters to the best-fit values derived by the Planck Collaboration in 2018 using temperature, polarization and CMB lensing data, i.e.
@@
       As described in Sec.~\ref{sssec:results.hod-constraints.fiducial}, our best-fit HOD constraints predict both the minimal mass to host a central galaxy $M_{\mathrm{min}}(z)$ and the mass scale for satellites $M_{1}(z)$ to be redshift independent.
+As noted above, this is somewhat counter-intuitive, as we would expect at least $M_{\mathrm{min}}(z)$ to increase with redshift.
 In order to understand this trend, it would be ideal to look at the rest-frame properties of the galaxies in our sample and how these change with redshift.
-However, computing k-corrections and absolute magnitudes for broad-band photometric data can be challenging and we therefore choose an alternative approach.
+However, computing k-corrections (see e.g.
+\cite{Hogg:2002, Blanton:2007}) and absolute magnitudes for broad-band photometric data can be challenging and we therefore choose an alternative approach.
 We cross-match galaxies passing our selection criteria within the HSC COSMOS field to galaxies also included in the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
@@
 Our results are well fitted by our theoretical model including scales up to $k_{\mathrm{max}} = 1$ Mpc$^{-1}$.
-We find monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a magnitude-limited sample, consistent with previous analyses.
+We find monotonically decreasing average halo masses as a function of redshift, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a magnitude-limited sample, consistent with previous analyses.
 In order to test the stability of our results, we performed a suite of alternative analyses, finding our results to be robust to photometric redshift uncertainties.

### 2019-11-19 doc/Paper/main.tex
comments

@@
 The resulting sample consists of 9,734,457 objects and covers $\sim88$ square degrees distributed across the 6 HSC DR1 fields, as described in Table \ref{tab:field_summary}.
+The $i$-band magnitude cut is by far the most stringent one, discarding approximately half of the total sample.
 
@@
 As described in Section \ref{ssec:methods.cell}, the method used to remove the impact of this systematic is slightly different from the rest.
+Note that, if a small number of galaxies have been mis-classified as stars, deprojecting this map could lead to an artificial underestimation of the clustering amplitude.
+We have however verified that the effect on the power spectra of deprojecting the star map is negligible (see Section \ref{sssec:results.spectra.syst}).
       \item {\bf Observing conditions}: the HSC DR1 provides metadata for each filter exposure, containing information about a number of observing conditions.
@@
     \end{align}
-    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ and $\bar{N}_s(M)$ are the mean number of central and satellite galaxies respectively, $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
+    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ is the mean number of central galaxies, $\bar{N}_s(M)$ is the mean number of satellites for halos containing a central galaxy\footnote{Note that, since $\bar{N}_s$ is the average number of satellites for halos with $N_c=1$, the mean number of satellites for all halos is just $\bar{N}_s\bar{N}_c$, since we assume that halos can only contain satellites if they have a central, and that there can be at most one central.}, and $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
     \begin{equation}
@@
 We define $R_\Delta$ as the radius that encloses $\Delta=200$ times the background matter density.
-In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}.
-Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
+In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}.
+We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough studies of these choices for future work.} Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
 
@@
 
+      The scaling of the galaxy correlation function with magnitude limit is also a sensitive test to detect the presence of systematic contaminants in imaging data \citep{BookPeeblesLSS}, which has been used since the early times of galaxy surveys \citep{1996MNRAS.283.1227M}.
+Its use on deep samples is complicated by the unknown evolution of the galaxy luminosity function, and therefore we have not carried out this test here.
+
     \subsubsection{Shot noise subtraction} \label{sssec:results.spectra.shotnoise}

### 2019-11-20 doc/Paper/main.tex
More updated plots and addressed more of Jos comments.

@@
     \end{align}
-    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ is the mean number of central galaxies, $\bar{N}_s(M)$ is the mean number of satellites for halos containing a central galaxy\footnote{Note that, since $\bar{N}_s$ is the average number of satellites for halos with $N_c=1$, the mean number of satellites for all halos is just $\bar{N}_s\bar{N}_c$, since we assume that halos can only contain satellites if they have a central, and that there can be at most one central.}, and $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
+    The quantity $M$ denotes halo mass, which we give in units of Solar mass $M_{\odot}$ throughout this work.
+In addition, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ denotes the mean number of central galaxies, $\bar{N}_s(M)$ is the mean number of satellites for halos containing a central galaxy\footnote{Note that, since $\bar{N}_s$ is the average number of satellites for halos with $N_c=1$, the mean number of satellites for all halos is just $\bar{N}_s\bar{N}_c$, since we assume that halos can only contain satellites if they have a central, and that there can be at most one central.}, and $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies.
+Finally, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ denotes the total mean galaxy density, given by
     \begin{equation}
@@
 In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}.
-We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough studies of these choices for future work.} Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
+We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough study of these choices for future work.} Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
 
@@
 We compute the quantity $R(z,k)$ for our fiducial cosmological model given in Sec.~\ref{ssec:methods.constr}.
+The amplitude of this correction is close to unity at large scales but can reach values of $\sim 1.3$ for large $k$, c.f.
+Ref.~\cite{2015MNRAS.454.1958M}.
 
@@
         \includegraphics[width=0.6\textwidth]{figures/shotnoise_avg.pdf}
-        \caption{Comparison between the shot noise power spectra estimated analytically using Eq.
-\ref{eq:nell} (transparent lines) and estimated from the difference-map power spectra (solid lines).
+        \caption{Comparison between the shot noise power spectra estimated analytically using Eq.~\ref{eq:nell} and estimated from the difference-map power spectra.
 Results are shown for the four different redshift bins.
-Our analytic estimate agrees well with this alternative method.}
+Our analytic estimate agrees well with this alternative method.
+The shot noise power spectra for the different bins have been offset fort clarity.}
         \label{fig:shotnoise_avg}

### 2019-11-20 doc/Paper/main.tex
Addressed some more comments.

@@
 The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details).
-It is worth noting that the information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags.
+The information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags.
 We transform this information into a pixelized sky map through a multi-step process:
@@
 The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
-      \item We upgrade the low-resolution binary mask to a higher resolution (0.2 arcmin), and remove all pixels containing objects flagged by the bright object mask.
+      \item We upgrade the low-resolution binary mask to a higher resolution ($0.2$ arcmin), and remove all pixels containing objects flagged by the bright object mask.
 We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
@@
     \end{enumerate}
-    We verified that the resulting mask is robust by comparing the power spectra estimated with it with those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask.
-It is worth noting that the resolution of this mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis.
+    We verified that the resulting mask is robust by comparing the obtained power spectra to those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask.
+The resolution of our fiducial mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis.
 After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.
@@
 As part of our systematics analysis (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
-It is worth noting that the NOMAD star catalog \cite{2004AAS...205.4815Z}, one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
-To study the impact of this contamination on our clustering measurements, we have also estimated the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).
+In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
+To study the impact of this contamination on our clustering measurements, we therefore also estimate the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).
 
@@
 For each pixel in our map we gather all exposures that fully or partially overlap with it.
-For each quantity $Q$ in filter $f$, this allows us to build a list of values of $Q$ for each exposure\footnote{It is worth noting that we omit any exposure from CCD 9, since it was found to yield unreliable measurements and was never used in the HSC coadd images.}.
+For each quantity $Q$ in filter $f$, this allows us to build a list of values of $Q$ for each exposure\footnote{We note that we omit any exposure from CCD 9, since it was found to yield unreliable measurements and was never used in the HSC coadd images.}.
 We then compute the weighted mean of these values and assign the result to the pixel.
@@
 We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}.
+In this work, we compute theoretical predictions for angular power spectra using \texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.} \cite{Chisari:2019}.
 
@@
     The quantity $\mathsf{C}$ denotes the joint covariance matrix, which we estimate analytically as described in Sec.~\ref{sssec:methods.theory.covar} and which we keep constant during parameter estimation \citep{2019OJAp....2E...3K}.
-    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (https://github.com/slosar/april), finding consistent results for our test case.}.
+    We sample the likelihood in a Monte Carlo Markov Chain (MCMC) using the publicly available code \texttt{CosmoHammer} \cite{Akeret:2013}, which is based on \texttt{emcee} \cite{Foreman-Mackey2013}\footnote{We note that we have compared the MCMC results obtained using \texttt{CosmoHammer} to those obtained using a Metropolis-Hastings algorithm as implemented in \texttt{april} (\url{https://github.com/slosar/april}), finding consistent results for our test case.}.
 In our fiducial analysis we sample the parameter set $\boldsymbol{\theta} = \{\mu_{\mathrm{min}}, \allowbreak \, \mu_{\mathrm{min}, p}, \allowbreak \, \mu_{0}, \allowbreak \, \mu_{0, p}, \allowbreak \, \mu_{1}, \allowbreak \, \mu_{1, p}, \allowbreak \, \Delta z_{i}, \allowbreak \, z_{w, i}\}$, $i = 0, \dots ,3$, where the first six parameters describe the HOD of galaxies as outlined in Sec.~\ref{sssec:methods.theory.hod}.
@@
 
-    It is worth noting that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$.
+We note that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$.
 This prior was estimated as the scatter between the best-fit shift parameters that recover the same shear power spectrum for different estimates of the redshift distribution and different photo-$z$ codes.
@@
 Furthermore, we see that the constraining power on HOD parameters is mostly unaffected by including the cross-power spectra.
-As an additional consistency check between auto- and cross-power spectra we test how well the auto-spectra predict the cross-spectra.
+As an additional consistency check between auto- and cross-power spectra, we test how well the auto-spectra predict the cross-spectra.
 To this end we compute the $\chi^{2}$ between the observed auto- and cross-power spectra and the theoretical predictions derived from auto-power spectra only.
 As we will discuss below, the auto-power spectra cannot constrain the photo-$z$ systematics parameters and we therefore fix $z_{w, i} = 0, \Delta z_{i} = 0$ for this test.
-We find $\chi^{2} = 95.3$, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross-power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
+We find $\chi^{2} = 95.3$\footnote{We note that the number of degrees of freedom $\nu$ in this case is not well-defined as we compare the theoretical predictions obtained from auto-spectra only to the observed auto- and cross-power spectra.
+As a rough estimate, we can compute $\nu$ as the difference between the number of elements of the full data vector and the number of model parameters, leading to $\nu = 88$, which is equal to the number quoted in Tab.~\ref{tab:constraints_robustness}.}, which is practically equivalent to the best-fit $\chi^{2}$ obtained when fitting both auto- and cross-power spectra without accounting for photo-$z$ systematics (see Tab.~\ref{tab:constraints_robustness}).
 This shows that the auto-spectra are able to predict the cross-spectra and provides further confirmation of their consistency.
@@
 We note that our analysis makes considerably stronger modeling assumptions and thus gives error bars that are likely under-estimated.
-
-    The corresponding constraints are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
+In order to illustrate this, we perform an additional analysis additionally allowing for variations $n_{s}$, which, as $\Omega_{m}$, affects the shape of the matter power spectrum.
+The uncertainty on $\Omega_{m}$ in this case increases significantly to $\sigma(\Omega_{m}) \sim 0.15$, thus showing the impact of our strong modeling assumptions.
+
+    The constraints obtained when fixing $n_{s}$ are shown in Fig.~\ref{fig:constraints-fit=Oc+s8}.
 As can be seen from Tab.~\ref{tab:constraints_robustness}, the derived constraints on HOD parameters agree well with our fiducial results, which shows that our HOD constraints are robust to variations in $\Omega_{c}$ and $\sigma_{8}$ as allowed by the data.
-This exploratory cosmological analysis further shows that the data are able to constrain $\Omega_{c}$ (and hence $\Omega_{m}$) while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
-Therefore, current and future photometric galaxy clustering analyses constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
+This exploratory cosmological analysis with strong modeling assumptions further shows that the data are able to constrain $\Omega_{c}$ (and hence $\Omega_{m}$) while $\sigma_{8}$ is largely unconstrained, showing that the halo model is sufficiently flexible to allow effective marginalization over linear galaxy bias.
+Therefore, current and future photometric galaxy clustering analyses combined with external data constitute a promising way to jointly constrain HOD and cosmological parameters, which we leave to future work.
 
@@
 We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from our data alone.
-In addition to this, we also allowed for variations in the $\Lambda$CDM cosmological parameters, finding that the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
+In addition to this, we also allowed for variations in $\Omega_{c}$ and $\sigma_{8}$, finding that, within our strong model priors, the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
 Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting $i$-band magnitude (Eq.

### 2019-11-20 doc/Paper/main.tex
Addressed two open comments.

@@
 %\usepackage[utf8]{inputenc}
-\usepackage{lipsum}
 \usepackage{xfrac}
@@
 We are able to make a $\sim3\sigma$ detection of the effects of lensing magnification in the HSC data.
-When freeing up cosmological parameters, we find constraints on the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ that agree well with measurements from Planck and low-redshift probes.
+Our results are stable to variations in the amplitude of density fluctuations $\sigma_8$ and the cold dark matter abundance $\Omega_c$ and we find constraints that agree well with measurements from Planck and low-redshift probes.
 Finally, we use our analysis pipeline to study the clustering of galaxies as a function of limiting flux, and provide a simple fitting function for the linear galaxy bias for magnitude limited samples as a function of limiting magnitude and redshift.}
@@
 These are the fiducial redshift distributions used in our analysis.
-The solid curves in each panel show the stacked redshift distributions inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt Franken-Z} from left to right and top to bottom).
+The solid curves in each panel show the stacked redshift distributions inferred by stacking the per-object photo-$z$ probability distributions obtained with the four alternative photo-$z$ codes explored here ({\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt FRANKEN-Z} from left to right and top to bottom).
 The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in different colors.
@@
 In this case, for a given photo-$z$ code, we produce an estimate of the redshift distribution of each tomographic bin by adding the photo-$z$ probability distributions of all objects in that bin.
-Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt demp}, {\tt ephor}, {\tt ephor\_ab} and {\tt frankenz}.
+Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt FRANKEN-Z}.
 These are some of the best-performing algorithms presented in \cite{2018PASJ...70S...9T}, and constitute a fair representation of the underlying photo-$z$ uncertainties.
@@
 In the latter case, we obtain a best-fit $\chi^{2}$ of $\chi^{2} = 72.8$, which corresponds to $\chi^{2}_{\mathrm{red}} = \sfrac{\chi^{2}}{\nu} = 0.91$ ($p$-value $= 0.70$) for $\nu = N_{\mathrm{data}} - N_{\mathrm{param}} = 94 - 14 = 80$.
-The improvement in $\chi^{2}$ with respect to the fiducial analysis amounts to $\Delta \chi^{2} = 86.2 - 72.8 = 13.4$, which is lower than the value obtained with free magnification amplitude, but nevertheless constitutes a sizeable $\chi^{2}$ improvement.
+The improvement in $\chi^{2}$ with respect to the fiducial analysis amounts to $\Delta \chi^{2} = 86.2 - 72.8 = 13.4$, which is lower than the value obtained with free magnification amplitude, but nevertheless constitutes a sizable $\chi^{2}$ improvement.
 
@@
 In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics.
+We anticipate that future development of this pipeline will include improvements to photo-z marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.
 These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.

### 2019-11-20 doc/Paper/main.tex
Implemented comment from Tom.
Couple more fixes.

@@
 The first two columns show the photo-$z$ bin edges.
-We used the {\tt photoz\_best} redshift estimator for the photo-$z$ code {\tt ephor\_ab} to assign galaxies to different bins.
+We used the {\tt photoz\_best} redshift estimator for the photo-$z$ code {\tt Ephor\_AB} to assign galaxies to different bins.
 The second column shows the mean redshift of each bin calculated from the fiducial redshift distributions described in Section \ref{ssec:methods.nz}.
@@
   All objects have photometric redshift measurements from 6 different codes as presented in \cite{2018PASJ...70S...9T}.
-We use the {\tt photoz\_best} redshift estimator assigned by the {\tt ephor\_ab} method as a marker to divide the sample into four tomographic samples containing roughly equal galaxy numbers.
+We use the {\tt photoz\_best} redshift estimator assigned by the {\tt Ephor\_AB} method as a marker to divide the sample into four tomographic samples containing roughly equal galaxy numbers.
 The {\tt photoz\_best} estimator is defined to minimize the risk that the true galaxy redshift lies outside the range $z_{\rm true}\pm 0.15(1+z_{\rm true})$, where $z_{\rm true}$ is the galaxy's true redshift.
@@
 In light of the observed drop-out of red galaxies from our sample at high redshift, this may not be true, as $f_{c}$ could potentially decrease with redshift.
-In order to test our assumption, we perform separate HOD fits to the four redshift bins, allowing for variations in $f_{c}$ on top of $M_{\mathrm{min}}, M_{1}$ and $M_{0}$.
+In order to test our assumption, we perform separate HOD fits to the four redshift bins, allowing for variations in $f_{c}$ on top of $\mu_{\mathrm{min}}, \mu_{1}$ and $\mu_{0}$\footnote{As we fit each redshift bin separately, we do not account for any redshift-dependence in the HOD parameters.}.
 We find the data to not have the statistical power to constrain $f_{c}$ and the derived values to be consistent with redshift-independent.
-Furthermore, our constraints on $M_{\mathrm{min}}, M_{1}$ and $M_{0}$ are robust to variations in $f_{c}$.
+Furthermore, our constraints on $\mu_{\mathrm{min}}, \mu_{1}$ and $\mu_{0}$ are robust to variations in $f_{c}$.
 We therefore conclude that our results are not significantly affected by the choice of $f_{c}=1$.
@@
 As can be seen, we find these two to differ at approximately $2 \sigma$, using the uncertainties on our bias measurement.
-An alternative use might be galaxy evolution studies, where these results provide a convenient cross-check formula.
+An alternative use might be galaxy evolution or simulation studies, where these results provide a convenient cross-check formula.
 Our parameter chains for halo model and systematics parameters for the different limiting magnitudes are available upon request.

### 2019-11-20 doc/Paper/main.tex
addressed last few comments

@@
 We use square pixels of size $\alpha_{\rm pix}=0.6$ arcmin on a side, corresponding to a Nyquist frequency $\ell_{\rm Nyquist}=18,000$.
+The pixel size was chosen as a compromise between the need to have several galaxies in each pixel on average and the need to study small-scale clustering (the corresponding comoving wavenumber is $k\sim5\,{\rm Mpc}^{-1}$ at redshift $z=1$), as well as to describe the variation in survey coverage accurately.
 The maps are defined on a rectangular patch large enough to cover all objects in each field, leaving a buffer of 10 masked pixels on all edges to avoid boundary effects when computing the FFTs.
@@
 
-    In order to study the dependence of our results on the method used to estimate the redshift distributions, we have also produced alternative estimates through a stacking approach.
+    Other methods to estimate source redshift distributions have been used in the literature.
+For instance, the first-year cosmology analysis of the Dark Energy Survey \citep{1708.01530,2018MNRAS.478..592H} used an initial guess redshift distribution estimated by drawing from the photo-$z$ posterior of all sources in each bin.
+These were then calibrated by shifting them in redshift, with the best-fit value and uncertainty in the shift parameter $\Delta z$ determined directly from a matched sample of COSMOS galaxies \citep{2018MNRAS.478..592H} and through cross-correlations with redMaGiC galaxies \citep{2018MNRAS.481.2427C}.
+As described in Sections \ref{sssec:methods.theory.photoz_syst} and \ref{sssec:methods.theory.photoz_syst}, we follow a similar approach to propagate photo-$z$ uncertainties, but we additionally explore uncertainties in the distribution widths.
+
+    In order to study the dependence of our results on the method used to estimate the fiducial redshift distributions, we have also produced alternative estimates through a stacking approach.
 In this case, for a given photo-$z$ code, we produce an estimate of the redshift distribution of each tomographic bin by adding the photo-$z$ probability distributions of all objects in that bin.
@@
     We estimate the Gaussian covariance of the pseudo-$C_\ell$ estimator as described in \cite{2004MNRAS.349..603E,2019arXiv190611765G}. The covariance of the observed pseudo-power spectra is given by
-    \begin{equation}
+    \begin{equation}\label{eq:pcl_cov_0}
       {\rm Cov}\left(\tilde{C}^{ab}_\ell,\tilde{C}^{cd}_{\ell'}\right)=\sum_{{\bf l}_1,{\bf l}_2} C^{ac}_{\ell_1}C^{bd}_{\ell_2}W^a_{{\bf l}{\bf l}_1}W^b_{{\bf l}{\bf l}_2}W^c_{{\bf l}'{\bf l}_1}W^d_{{\bf l}'{\bf l}_2} + C^{ad}_{\ell_1}C^{bc}_{\ell_2}W^a_{{\bf l}{\bf l}_1}W^b_{{\bf l}{\bf l}_2}W^c_{{\bf l}'{\bf l}_2}W^d_{{\bf l}'{\bf l}_1},
@@
 Since the coupling coefficients $W^x_{{\bf l}{\bf l}'}$ are usually highly peaked around ${\bf l}={\bf l}'$, we can proceed further by approximating the power spectra to be constant within the support of $W^x_{{\bf l},{\bf l}'}$.
-Effectively this implies approximating
+Effectively this implies approximating $C^{ac}_{\ell_1}C^{bd}_{\ell_2}$ in Eq \ref{eq:pcl_cov_0} as
     \begin{equation}

### 2019-11-21 doc/Paper/main.tex
Fixed typo.

@@
 In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics.
-We anticipate that future development of this pipeline will include improvements to photo-z marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.
+We anticipate that future development of this pipeline will include improvements to photo-$z$ marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.
 These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.

### 2019-11-21 plot_scripts/flatmaps.py
fixed nstar plot

@@ -5,7 +5,6 @@ from matplotlib import cm
 #import pymaster as nmt
 from astropy.io import fits
 from astropy.wcs import WCS
-import formatting
 
 class FlatMapInfo(object) :
     def __init__(self,wcs,nx=None,ny=None,lx=None,ly=None) :

### 2019-11-21 plot_scripts/plots_sysmaps.py

@@ -22,6 +22,8 @@ def plot_syst(name,fname,band,units=None,savename=None):
     mp_plot=msk_bin*(mp-mp_mean)+mp_mean
     mp_min=np.amin(mp_plot)
     mp_max=np.amax(mp_plot)
+    if name == "Star count":
+        mp_max=4
     mp_plot[msk_bin<1]=mp_min-1
     fig=plt.figure()
     ax=fig.add_subplot(111,projection=fsk.wcs)

### 2019-11-22 doc/Paper/main.tex
Added 1h/2h plot.

@@
 Our analytic estimate agrees well with this alternative method.
-The shot noise power spectra for the different bins have been offset fort clarity.}
+The shot noise power spectra for the different bins have been offset for clarity.}
         \label{fig:shotnoise_avg}
@@
 However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.
+In Fig.~\ref{fig:cls-best-fit-1h-2h}, we additionally show our fiducial theoretical power spectra split into their 1- and 2-halo contributions.
+As can be seen, the contribution of the 1-halo term to the total power spectrum is most pronounced at low redshift.
+At higher redshift, the importance of the 1-halo term decreases and the transition from the 1- to 2-halo-dominated regime moves to smaller angular scales.
 
@@
 \begin{center}
+\includegraphics[width=0.95\textwidth]{figures/Cls-data-vs-best-fit_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol_1h-2h_lin.pdf}
+\caption{Measured auto- and cross-power spectra obtained in our analysis.
+The lines show the theoretical predictions derived from our fiducial best-fit model parameters, additionally split into the 1- and 2-halo contributions to the total power spectrum.}
+\label{fig:cls-best-fit-1h-2h}
+\end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
     \includegraphics[width=0.95\textwidth]{figures/contours_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts+prior=0p2-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_cov=G+NG+SSC-LINBIAS_HOD-param=zfid_clfit=HOD-zevol.pdf}

### 2019-11-22 doc/Paper/main.tex
discussed self-calibration and KiDS

@@
 
+      The positive side of the enhanced sensitivity of galaxy clustering to photometric redshift uncertainties compared to cosmic shear is the possibility of using clustering measurements to self-calibrate some of these uncertainties.
+As an example, our analysis hints towards a consistently positive value of the relative shift parameters $\Delta z_i-\Delta z_j,\,i>j$ (see e.g.
+Figs.
+\ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e.: the different bins are more widely separated than their fiducial distributions assumes.
+Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions).
+Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
       \begin{figure}

### 2019-11-22 doc/Paper/main.tex
Addressed comments from Masahiro.

@@
 DR1 includes data from 61.5 nights observed to three different depths: Wide (108 square degrees to $i\sim 26.4$), Deep (26 square degrees to $i\sim26.5$) and UltraDeep (4 square degrees to $i\sim 27$).
-In this work we focus on the Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees.
+In this work we focus on the HSC Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees.
 The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arc sec) and also likely better than the median seeing expected to be achieved by LSST.
+DES with around 0.9 arcsec) and also likely better than the median seeing expected to be achieved by LSST.
 The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
 
-  We use a magnitude-limited sample constructed from the WIDE DR1 sample by imposing data cuts that are similar to those used to create the HSC shear catalog \cite{2018PASJ...70S..25M}.
+  We use a magnitude-limited sample constructed from the HSC Wide DR1 sample by imposing data cuts that are similar to those used to create the HSC shear catalog \cite{2018PASJ...70S..25M}.
 The exact cuts are shown in Table~\ref{tab:cuts_summary}, and can be summarized as follows: besides a minimal set of quality cuts (selecting only primary detections with well-measured fluxes in all bands, removing objects near bad pixels, deblender artifacts, etc.), we impose an overall apparent magnitude cut in the extinction-corrected band $i_{\rm corr}<24.5$.
@@
     As noted above, the power spectra are computed in rings of $\ell=|{\bf l}|$, which we will call bandpowers here.
-We use 17 contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 15800).
+We use 17 piecewise-linear, contiguous bandpowers with edges $\ell=$(100, 200, 300, 400, 600, 800, 1000, 1400, 1800, 2200, 3000, 3800, 4600, 6200, 7800, 9400, 12600, 15800)\footnote{This choice is motivated by mimicking logarithmic binning as closely as possible, while avoiding very small bin widths at low angular multipoles, which typically arise for logarithmic binning schemes.}.
 Due to this bandpower averaging, the estimated power spectra cannot, strictly speaking, be compared with theoretical predictions estimated at token multipoles (e.g.
@@
     \begin{equation}
-      p_{i}(z) = \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
+      p_{i}(z) \propto \hat{p}_{i}(z_{c} + (1 + z_{w, i})(z-z_{c}) + \Delta z_{i}),
       \label{eq:photo-z-model}
@@
     where the index $i$ runs over the number of redshift bins considered in our analysis.
-In the above equation, $\hat{p}(z)$ denotes the estimated redshift distribution while $p(z)$ is the underlying true distribution.
+In the above equation, $\hat{p}_{i}(z)$ denotes the estimated redshift distribution while $p_{i}(z)$ is the underlying true distribution.
 The parameters $\Delta z_{i}$ account for shifts in the means of the distributions and changes to their widths are parameterized through $z_{w, i}$.
-The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}(z)$ attains its maximal value.
+The quantity $z_{c}$ is kept constant in our analysis and is set to the redshift at which $\hat{p}_{i}(z)$ attains its maximal value.
+The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.
 
@@
 We leave this type of study for future work.
+
+Finally we note that using the galaxy number density $\bar{n}$ as an additional data point in Eq.~\ref{eq:likelihood} has the potential to improve the constraining power of the data on HOD parameters, as it effectively fixes one of the parameters (see e.g.
+\cite{Zhai:2017}).
+However, we have chosen to not include this additional constraint in our analysis, as including it would require the modeling of the effects of photometric redshift errors and observational systematics on the estimated number density $\hat{\bar{n}}$, which is beyond the scope of this paper.
 
@@
 Figs.
-\ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e.: the different bins are more widely separated than their fiducial distributions assumes.
+\ref{fig:constraints-pz-syst-auto+cross-vs-auto} and \ref{fig:constraints-pz-syst-fit-pz-shifts+pz-widths-pz-methods}), i.e.
+the different bins are more widely separated than their fiducial distributions assume.
 Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions).

### 2019-11-26 doc/Paper/main.tex
Addressed comments from Eric.

@@
 Through a halo occupation distribution analysis, we place constraints on the characteristic halo masses of this sample as a function of redshift, finding a good fit up to scales $k_{\rm max}=1\,{\rm Mpc}^{-1}$, including both auto- and cross-correlations.
-Our results show monotonically decreasing average halo masses, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
+Our results show monotonically decreasing average halo masses with increasing redshift, which can be interpreted in terms of the drop-out of red galaxies at high redshifts for a flux-limited sample, consistent with previous analyses.
 In terms of photometric redshift systematics, we show that additional care is needed in order to marginalize over uncertainties in the redshift distribution in galaxy clustering, even for samples of this small size, and that these uncertainties can be significantly constrained by including cross-bin correlations.
@@
       In Fig.~\ref{fig:HOD-redshift}, we additionally show the large-scale galaxy bias as a function of redshift derived from our best-fit HOD model.
-As can be seen, the large-scale bias scales approximately as $b(z) \propto \sfrac{1}{D(z)}$, where $D(z)$ denotes the linear growth factor.
+As can be seen, the large-scale bias scales approximately as $b(z) \propto \sfrac{1}{D(z)}$ (to within approximately $5 \%$), where $D(z)$ denotes the linear growth factor.
 This behavior is consistent with e.g.
@@
           \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
-The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$ derived from the galaxy sample used in this analysis.}
+The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$, which is consistent with the bias-redshift relation derived from the galaxy sample used in this analysis to within approximately $5 \%$.}
           \label{fig:HOD-redshift}
@@
     \end{equation}
-    \footnotetext{We note that we used $\sigma(\tilde{x}) = 1.253 \; \sigma(\bar{x})$, where $\tilde{x}$ denotes the median and $\bar{x}$ is the mean of a given sample.}
+    \footnotetext{We note that we use $\sigma(\tilde{x}) = 1.253 \; \sigma(\bar{x})$, where $\tilde{x}$ denotes the median and $\bar{x}$ is the mean of a given sample.}
     where $b_{1} = -0.0624 \pm 0.0070$ and $b_{0} = 0.8346 \pm 0.161$.

### 2019-12-06 doc/Paper/main.tex
Started addressing comments from Rachel.

@@
 \abstract{We analyze the clustering of galaxies in the first public data release of the Hyper Suprime-Cam Subaru Strategic Program.
-Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets as will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the Dark Energy Science Collaboration.
+Despite the relatively small footprints of the observed fields, the data are an excellent proxy for the very deep photometric datasets that will be acquired by the Large Synoptic Survey Telescope, and are therefore an ideal test bed for the analysis methods being implemented by the LSST Dark Energy Science Collaboration.
 We select a magnitude limited sample with $i<24.5$ and analyze it in four tomographic redshift bins covering the range $0.15\lesssim z\lesssim1.5$.
@@
   The past two decades have seen a revolution in our understanding of the Universe and its constituents.
-While observations of the cosmic microwave background (CMB) play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low redshift Universe.
+While observations of the cosmic microwave background (CMB) play a pivotal role in anchoring the standard  cosmological model \cite{Planck:2018}, they are not a direct probe of the physics of the low-redshift Universe.
 In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
@@
   Over a decade ago, the Dark Energy Task Force divided the evolution of optical experiments into approximate stages \cite{0609591}.
-The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
+The current Stage III experiments, including spectroscopic surveys such as eBOSS \cite{1707.09322,Zhu:2018,1712.08064,1801.02689,1801.02891} and VIPERS \cite{1611.07048,1612.05645,1708.00026} and photometric surveys such as DES \cite{1708.01531,1708.01530,1708.01536}, the Hyper Suprime-Cam survey \cite{1704.05858,2019PASJ...71...43H,1906.06041} and the Kilo-Degree Survey / VIKING-450 \cite{1902.11265,1812.06077,Joudaki:2019} are approaching completion and the field is preparing for the Stage IV surveys, such as the ground-based DESI \cite{1611.00036,1907.10688} and LSST \cite{0912.0201,1809.01669, Ivezic:2019}, as well as major satellite missions like Euclid \cite{1606.00180} and WFIRST \cite{1904.01174}.
 
@@
 For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources.
-The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their shear estimates.
+The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their weak gravitational lensing shear estimates.
 These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function (PSF) with blending \cite{1708.01533,1905.01324,1907.10572}.
-But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to calibrate redshifts \cite{1903.09325}.
+But even with perfect measurements of fluxes, our ability to infer source redshift distributions is hampered by incompleteness in spectroscopic samples used to train and calibrate redshifts \cite{1903.09325}.
 Finally, at the depths of Stage IV photometric surveys, instrumental and observational effects, such as scattered light from bright objects, errors in star-galaxy separation, reddening by Milky Way dust, and varying observing conditions, will imprint spurious fluctuations on the observed galaxy density field.
@@
 On one hand, we are building sophisticated, realistic mock data sets, such as LSST Dark Energy Science Collaboration (DESC) Data Challenge 2 \cite{1909.07340,1907.06530}.
-On the other hand, we are (re-)analyzing existing precursor data to test-drive our methods and codes in a realistic environment.
+On the other hand, we are (re-)analyzing existing precursor data to validate our methods and codes in a realistic environment.
 In this paper, we focus on the latter approach and perform an analysis of photometric galaxy clustering using the first data release (DR1) of the Hyper Suprime-Cam Subaru Strategic Program (HSC-SSP) \cite{2018PASJ...70S...8A}.
@@
 In this work, we focus on a magnitude-limited galaxy sample with limiting magnitude $i<24.5$, which is similar to the expected 5-$\sigma$ detection limit for LSST after one year \cite{1809.01669} ($i<25.1$).
-Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing much of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
+Finally, the primary data reduction codes used in HSC-SSP and planned for LSST are of the same lineage, employing many of the same methods \cite{2018PASJ...70S...5B,1812.03248}.
 With the exception of a rather small sky area of around 90 square degrees used in this paper, the HSC-SSP data is therefore a perfect proxy for future LSST data.
@@
 We split the data into four tomographic redshift bins and measure both the auto- and cross-power spectra of all bins, correcting for observational systematics using mode deprojection.
-We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift uncertainties.
+We then use the halo model coupled with a halo occupation distribution to fit the data and derive constraints on astrophysical parameters, marginalizing over photometric redshift (photo-$z$) uncertainties.
 To ensure the stability of our results, we perform a suite of complementary analyses and find our constraints to be robust to photometric redshift uncertainties.
@@
 The analysis of LSST data will likely require  a combination of  bias expansion approaches \cite{0902.0991,1402.5916,1611.09787,1910.07097} and power spectrum emulators \cite{1804.05865,1705.03388}.
-However, given the level of statistical precision of the data at hand, we find that a simple halo model suffices, and thus use it as a ``good enough'' substitute for the final modeling.
+However, we find that a simple halo model suffices to describe the data at the current level of precision.
 
@@
    WIDE12H  & 1,220,816 & 11.6 & $2.8\times10^{-4}$ \\
-   XMMLSS   & 2,139,629 & 20.8 & $5.0\times10^{-4}$ \\
+   XMM-LSS   & 2,139,629 & 20.8 & $5.0\times10^{-4}$ \\
    \hline
@@
 In this work we focus on the HSC Wide field, which has been observed in five broadband filters ($grizy$) and is distributed among 6 fields  of areas varying between 5 and 20 square degrees.
-The image quality is impressive with a median seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arcsec) and also likely better than the median seeing expected to be achieved by LSST.
+The image quality is impressive with a median $i$-band seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
+DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST.
 The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
@@
 This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis.
-The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details).
+The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S..25M}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (the so-called ``Sirius'' mask, see \cite{2018PASJ...70S..25M} for details).
 The information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags.
@@
       \caption{Maps of different observational systematics that could cause an artificial modulation in the inferred galaxy overdensity.
-The maps correspond to the XMMLSS field, and were obtained as described in Section \ref{ssec:methods.syst}.
-From top to bottom and left to right, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density.
+The maps correspond to the XMM-LSS field, and were obtained as described in Section \ref{ssec:methods.syst}.
+From left to right and top to bottom, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density.
 We can visually appreciate the existing correlations between different systematics (e.g.
@@
     \end{figure}
-    A number of astrophysical and observational systematic effects can affect the observed distribution of galaxies, and therefore may bias our inference of their clustering properties.
+    A number of astrophysical and observational systematic effects can modify the observed distribution of galaxies, and therefore may bias our inference of their clustering properties.
 To mitigate this effect, we deproject maps of these systematics from our data, as described in Section \ref{ssec:methods.cell}.
@@
     To estimate the fiducial redshift distributions used in our main analysis, we make use of the COSMOS 30-band photometric catalog of \cite{2016ApJS..224...24L}.
-The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply histograming these redshifts with appropriate weights.
+The idea is to use the high-fidelity photo-$z$ estimates in the COSMOS 30-band data as the truth, in which case one can estimate the redshift distribution by simply making a histogram these redshifts with appropriate weights.
 These weights are calculated following the procedure described in \cite{2017MNRAS.465.1454H,2019PASJ...71...43H}, which we summarize here for completeness:
@@
 We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}.
-In this work, we compute theoretical predictions for angular power spectra using \texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.} \cite{Chisari:2019}.
+In this work, we compute theoretical predictions for angular power spectra using the DESC Core Cosmology Library (\texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.}) \cite{Chisari:2019}.
 
@@
 In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}.
-We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough study of these choices for future work.} Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
+We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough study of these choices for future work.}.
+Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.
 
@@
   \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
-    Uncertainties in photometric redshifts (photo-$z$) represent one of the major systematics in photometric galaxy clustering analyses.
+    Uncertainties in photometric redshifts represent one of the major systematics in photometric galaxy clustering analyses.
 To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
@@
     We use an analytical procedure to estimate the uncertainties of our measured power spectra, inspired by the methods used by \cite{Krause:2017}.
-As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labelled SSC here)\footnote{A comparison of the relative contributions of these three terms to the total covariance can be found in Fig.~\ref{fig:covariance-contributions}.}.
+As shown in \cite{2009MNRAS.395.2065T,Takada:2013}, the covariance matrix for large-scale structure data can be decomposed into a disconnected trispectrum part, essentially equivalent to the covariance of a Gaussian random field with the same power spectrum as the data, a connected part, caused by the non-Gaussian nature of the density field, and a super-sample covariance term (labeled SSC here)\footnote{A comparison of the relative contributions of these three terms to the total covariance can be found in Fig.~\ref{fig:covariance-contributions}.}.
 The SSC contribution accounts for the coherent shift in the amplitude of density fluctuations within the surveyed volume caused by long wavelength modes larger than the survey.

### 2019-12-07 doc/Paper/main.tex
a few more of Rachel's comments

@@
 For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources.
-The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their weak gravitational lensing shear estimates.
+The increased blending leads to new uncertainties in isolating sources, measuring their fluxes (required for photometric redshifts) and inferring their weak gravitational lensing shear estimates \citep{2016ApJ...816...11D,2018MNRAS.475.4524S,2019MNRAS.483.2487J}.
 These effects in turn lead to subtle sample selection effects, which are amplified by the interaction of the point spread function (PSF) with blending \cite{1708.01533,1905.01324,1907.10572}.
@@
       \item {\bf Survey depth}: we estimate the $10\sigma$ survey depth as a function of angular position on the sky as follows.
-For each pixel, we compute the average $i$-band flux error of all objects classified as stars that fall into it.
+For each pixel, we compute the average $i$-band {\tt cmodel} flux error of all objects classified as stars that fall into it\footnote{It is worth noting that {\tt cmodel} flux errors are underestimated for galaxies.
+Nevertheless we use them to define our depth map due to the fact that our sample selection is based on {\tt cmodel} fluxes and magnitudes.
+Additionally, the corresponding depth map should still provide an appropriate estimate of the relative spatial variations in depth, which is its main role as a contaminant map for clustering measurements.}.
 The corresponding survey depth is then given by this mean flux error multiplied by 10 and translated into a magnitude.

### 2019-12-07 doc/Paper/main.tex
Addressed Limber approximation comment.

@@
     where $H(z)$ is the expansion rate at redshift $z$, and we have used the so-called Limber approximation\footnote{We note that we have compared the power spectra for the redshift distributions employed in this work obtained with the Limber approximation and those obtained making no approximations.
-We find the results to be virtually the same and in the following we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}.
+We find the differences between the power spectra to be around $\sfrac{\Delta C_{\ell}}{C_{\ell}} \sim 10^{-4}-10^{-3}$, and thus negligible compared to the uncertainties.
+In the following, we therefore use the Limber approximation to compute projected power spectra for computational speed.} \citep{Limber:1953, Kaiser:1992, Kaiser:1998}.
 In this work, we compute theoretical predictions for angular power spectra using the DESC Core Cosmology Library (\texttt{CCL}\footnote{\url{https://github.com/LSSTDESC/CCL}.}) \cite{Chisari:2019}.

### 2019-12-07 doc/Paper/main.tex
flat-sky comment

--- 2019-12-07 doc/Paper/main.tex
@@
 Instead, we perform separate power spectrum measurements on each individual field, with maps defined on rectangular sky patches covering them.
-Furthermore, the small size of each field allows us to make use of the flat-sky approximation safely.
+Furthermore, the small size of each field allows us to make use of the flat-sky approximation safely \citep{2014JCAP...10..007N}.
 This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs).
+Since we use a cilindrical projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes, which are small ($\lesssim 1.5^\circ$) in all cases.
 

### 2019-12-07 plot_scripts/plots_masks.py
fixed plots

@@ -1,6 +1,7 @@
 import flatmaps as fm
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib import cm
 from astropy import units as u
 
 yticks={'GAMA09H':[0.,1.,2.],
@@ -16,7 +17,8 @@ for field in ['GAMA09H','GAMA15H','HECTOMAP','VVDS','WIDE12H','XMMLSS']:
     ax=fig.add_subplot(111,projection=fsk.wcs)
     ax.set_title(field,fontsize=14)
     im=ax.imshow(msk.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
-                 origin='lower', interpolation='nearest')
+                 origin='lower', interpolation='nearest',
+                 cmap=cm.gray)
     ax.set_xlabel('R.A.', fontsize=14)
     ax.set_ylabel('Dec.', fontsize=14)
     ax.coords[1].set_ticks(np.array(yticks[field]) * u.deg)

### 2019-12-07 plot_scripts/plots_sysmaps.py

@@ -7,7 +7,7 @@ prefix="/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/"
 fsk,msk=fm.read_flat_map(prefix+"masked_fraction.fits")
 msk_bin=np.zeros_like(msk); msk_bin[msk>0.]=1
 
-def plot_syst(name,fname,band,units=None,savename=None):
+def plot_syst(name,fname,band,units=None,savename=None,scale=1):
     label=name
     if band is None:
         imap=0
@@ -19,7 +19,7 @@ def plot_syst(name,fname,band,units=None,savename=None):
 
     _,mp=fm.read_flat_map(prefix+fname,i_map=imap)
     mp_mean=np.sum(msk_bin*msk*mp)/np.sum(msk_bin*msk)
-    mp_plot=msk_bin*(mp-mp_mean)+mp_mean
+    mp_plot=(msk_bin*(mp-mp_mean)+mp_mean)*scale
     mp_min=np.amin(mp_plot)
     mp_max=np.amax(mp_plot)
     if name == "Star count":
@@ -43,14 +43,14 @@ def plot_syst(name,fname,band,units=None,savename=None):
 plot_syst('Airmass','airmass_maps.fits','g',savename='../doc/Paper/figures/syst_airmass_g.pdf')
 plot_syst('Airmass','airmass_maps.fits','i',savename='../doc/Paper/figures/syst_airmass_i.pdf')
 plot_syst('Airmass','airmass_maps.fits','y',savename='../doc/Paper/figures/syst_airmass_y.pdf')
-plot_syst('Seeing','seeing_maps.fits','g',units='pix.',savename='../doc/Paper/figures/syst_seeing_g.pdf')
-plot_syst('Seeing','seeing_maps.fits','i',units='pix.',savename='../doc/Paper/figures/syst_seeing_i.pdf')
-plot_syst('Seeing','seeing_maps.fits','y',units='pix.',savename='../doc/Paper/figures/syst_seeing_y.pdf')
-plot_syst('Sky level','skylevel_maps.fits','g',savename='../doc/Paper/figures/syst_skylevel_g.pdf')
-plot_syst('Sky level','skylevel_maps.fits','i',savename='../doc/Paper/figures/syst_skylevel_i.pdf')
-plot_syst('Sky level','skylevel_maps.fits','y',savename='../doc/Paper/figures/syst_skylevel_y.pdf')
[…]

### 2019-12-07 doc/Paper/main.tex
caption stars

@@
 The maps correspond to the XMM-LSS field, and were obtained as described in Section \ref{ssec:methods.syst}.
-From left to right and top to bottom, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star density.
+From left to right and top to bottom, the different panels show maps of the seeing in the $g$, $i$ and $y$ bands, airmass in the $y$ band, sky level in the $i$ band, $10\sigma$ $i$-band depth, dust absorption and star counts per pixel.
 We can visually appreciate the existing correlations between different systematics (e.g.

### 2019-12-07 doc/Paper/main.tex
more comments

@@
 We have however verified that the effect on the power spectra of deprojecting the star map is negligible (see Section \ref{sssec:results.spectra.syst}).
+The purity and completeness of the star and galaxy samples associated with this classifier were quantified in \cite{2018PASJ...70S...5B} (see Fig.
+19 there).
       \item {\bf Observing conditions}: the HSC DR1 provides metadata for each filter exposure, containing information about a number of observing conditions.
@@
 All unmatched objects in either catalog are discarded.
+We note that the unmatched objects represent $\sim15-20\%$ of the HSC sample lying on the COSMOS 30-band area.
+This is partially due to the details of the different sky masks applied to both catalogs.
+We do not observe the unmatched sample to come from a particular region in color space.
       \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbors in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
@@
 The weight applied to the COSMOS 30-band object is then given by the ratio $N^{\rm HSC}_{\rm neigh}/N^{\rm COSMOS}_{\rm neigh}$ normalized by the total number of objects in each sample.
+We verified that, applying these weights, we can reproduce the magnitude and color distributions of the HSC sample with the matched COSMOS 30-band sources.
     \end{enumerate}

### 2019-12-07 doc/Paper/main.tex
photo-z comments2

@@
 First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample.
+At our magnitude limit, the normalized median absolute deviation of the COSMOS 30-band photometric redshifts is $\sigma\simeq0.03$.
 Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence.
@@
 In this case, for a given photo-$z$ code, we produce an estimate of the redshift distribution of each tomographic bin by adding the photo-$z$ probability distributions of all objects in that bin.
+This is not a mathematically consistent method to recover the ensemble redshift distributions in the absence of perfect priors.
+However, the resulting distributions allow us to explore the level of uncertainty in the underlying $p(z)$s.
 Following this procedure we generate 4 alternative estimates of $p^i(z)$ for the photo-$z$ codes {\tt DEmP}, {\tt Ephor}, {\tt Ephor\_AB} and {\tt FRANKEN-Z}.

### 2019-12-07 doc/Paper/main.tex
systematics

@@
 
-  Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic errors are becoming considerably more difficult \cite{1808.07335}.
+  Together with transformational sensitivity increases in the Stage IV surveys, the challenges of understanding and controlling systematic biases and uncertainties are becoming considerably more difficult \cite{1808.07335}.
 For photometric surveys, the deep surveys sensitive to many more sources inevitably come with crowded fields where blending affects a significant fraction of all sources.
@@
 These fluctuations will, if not correctly accounted for, masquerade as intrinsic large-scale fluctuations in the cosmic density field.
-Therefore, Stage IV photometric experiments are likely to be limited by our ability to control systematics rather than the intrinsic statistical power of the survey.
+Therefore, Stage IV photometric experiments are likely to be limited by our ability to remove systematic biases and minimize systematic uncertainties rather than the intrinsic statistical power of the survey.
 
@@
     This defines our fiducial masks, which are shown in Figure \ref{fig:masks} for each field.
-As part of our systematics analysis (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
+As part of our analysis of systematic biases (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
 In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
@@
   \subsubsection{Photometric redshift systematics modeling}\label{sssec:methods.theory.photoz_syst}
-    Uncertainties in photometric redshifts represent one of the major systematics in photometric galaxy clustering analyses.
+    Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses.
 To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
@@
 All PTEs are larger than 8\%, with the vast majority of them lying above 30\%.
-We conclude that there is no evidence for systematics from the power spectrum measurements in different fields, and therefore it is safe to coadd them and use the coadded spectra to obtain model constraints.
+We conclude that there is no evidence for systematic biases from the power spectrum measurements in different fields, and therefore it is safe to coadd them and use the coadded spectra to obtain model constraints.
 We observe that the HECTOMAP field exhibits some of the lowest PTEs in the analysis described above.
@@
 However, cross-correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
-In order to test for systematics affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto-power spectra to those obtained when jointly fitting auto- and cross-power spectra.
+In order to test for systematic biases affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto-power spectra to those obtained when jointly fitting auto- and cross-power spectra.
 Fig.~\ref{fig:constraints-cov=G+NG+SSC-vs-cov=G-vs-cov=G+SSC-vs-fit=auto} shows the comparison between our fiducial HOD constraints and those obtained from auto-power spectra alone.
@@
   In this work, we have presented a comprehensive analysis of photometric galaxy clustering in HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$.
-We have split this sample into four tomographic redshift bins and computed all possible auto- and cross-power spectra, accounting for observational systematics in number density fluctuations through map-level deprojection.
+We have split this sample into four tomographic redshift bins and computed all possible auto- and cross-power spectra, accounting for observational systematics in the number density fluctuations through map-level deprojection.
 We have then fitted the data using a halo model coupled with a halo occupation distribution, marginalizing over a flexible model for photometric redshift uncertainties.
@@
   Our analysis hence shows that the quality of the HSC data allows scientific analyses leading to new insights into both physics of galaxy formation as well as analysis strategies for galaxy clustering.
-In terms of physics, we show that a simple magnitude cut leading to a sufficiently homogeneous sample can be used to carry out robust galaxy clustering analyses, provided that photometric redshift systematics can be kept under control.
+In terms of physics, we show that a simple magnitude cut leading to a sufficiently homogeneous sample can be used to carry out robust galaxy clustering analyses, provided that photo-$z$ systematic uncertainties can be kept under control.
 This contrasts with other approaches that focus on red galaxies to create significantly smaller samples with more precise redshifts (see e.g.

### 2019-12-09 doc/Paper/main.tex
Started addressing latest comments from Rachel.

@@
 This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis.
-The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S..25M}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (the so-called ``Sirius'' mask, see \cite{2018PASJ...70S..25M} for details).
+The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...8A}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (the so-called ``Sirius'' mask, see \cite{2018PASJ...70S...8A} for details).
 The information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags.
@@
 We have however verified that the effect on the power spectra of deprojecting the star map is negligible (see Section \ref{sssec:results.spectra.syst}).
-The purity and completeness of the star and galaxy samples associated with this classifier were quantified in \cite{2018PASJ...70S...5B} (see Fig.
-19 there).
+Furthermore, the purity and completeness of the star and galaxy samples associated with this classifier are high for the magnitude range considered in our analysis ($\gtrsim 95 \%$ for galaxies), as can be seen from Fig.
+17 in Ref.~\cite{2018PASJ...70S...5B}.
       \item {\bf Observing conditions}: the HSC DR1 provides metadata for each filter exposure, containing information about a number of observing conditions.
@@
 This is partially due to the details of the different sky masks applied to both catalogs.
-We do not observe the unmatched sample to come from a particular region in color space.
+We do not observe the unmatched sample to populate any particular region in color space.
       \item For each object in the COSMOS 30-band data with a match in HSC, we find its $N_{\rm neigh}^{\rm COSMOS}=20$ nearest neighbors in the COSMOS 30-band sample within the 5-dimensional space of HSC apparent magnitudes $(g,r,i,z,y)$ using a Euclidean metric.
@@
 First, the COSMOS 30-band photometric redshifts have a lower redshift accuracy and precision than a purely spectroscopic sample.
-At our magnitude limit, the normalized median absolute deviation of the COSMOS 30-band photometric redshifts is $\sigma\simeq0.03$.
+At our magnitude limit, the normalized median absolute deviation of the COSMOS 30-band photometric redshifts is $\sigma\simeq0.03$ \cite{2016ApJS..224...24L}.
 Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence.
@@
 For the auto-power spectra, we determine $\ell_{\mathrm{max}}$ at the effective redshift $z_{\mathrm{eff}}$ of the bin using our fiducial Planck 2018 cosmological model\footnote{We define the effective redshift for each tomographic bin as the mean redshift of the galaxy distribution.}.
-For the cross-correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.}.
+For the cross-correlations, we set $\ell_{\mathrm{max}}$ to the minimum value derived for the two redshift bins\footnote{This leads to $\{\ell_{\mathrm{max}, 00}, \allowbreak \, \ell_{\mathrm{max}, 01}, \allowbreak \, \ell_{\mathrm{max}, 02}, \allowbreak \, \ell_{\mathrm{max}, 03}, \allowbreak \, \ell_{\mathrm{max}, 11}, \allowbreak \, \ell_{\mathrm{max}, 12}, \allowbreak \, \ell_{\mathrm{max}, 13}, \allowbreak \, \ell_{\mathrm{max}, 22}, \allowbreak \, \ell_{\mathrm{max}, 23}, \allowbreak \, \ell_{\mathrm{max}, 33}\} = \{2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2000, \allowbreak \, 2600, \allowbreak \, 2600, \allowbreak \, 3400\}$.
+The maximal angular multipoles are the same for the first and second redshift bin due to our choice of bandpowers.}.
 
@@
         \caption{Summary plot showing all measured auto- and cross-power spectra.
-The red data points with error bars show the coadded power spectra (see Section \ref{sssec:results.spectra.fid}), with the hollow circles showing the absolute value of negative data.
-The Poisson noise contribution and deprojection biases subtracted from the raw power spectra are shown as grey and pink lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
-The pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.}
+The dark green data points with error bars show the coadded power spectra (see Section \ref{sssec:results.spectra.fid}), with the hollow blue circles showing the absolute value of negative data.
+The Poisson noise contribution and deprojection biases subtracted from the raw power spectra are shown as gray and pink lines respectively, with the negative parts of the deprojection bias shown as dashed lines.
+The semi-transparent gray bands cover the range of scales excluded from our analysis.
+Finally, the pair of numbers in the upper right corner of each panel corresponds to the indices of the bins being cross-correlated.}
         \label{fig:cls_summary}
@@
 
-      The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as red circles with error bars.
-In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a grey solid line in the auto-correlations.
+      The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data).
+In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a gray solid line in the auto-correlations.
 As described in Section \ref{ssec:methods.cell}, after deprojecting a set of contaminant templates, the power spectra estimated from the projected maps must be corrected for a bias caused by the loss of modes due to deprojection.
@@
 This bias is always at least a factor $\sim5$ smaller than the measured power spectra, and is most relevant on large scales.
-The semi-transparent grey bands in the figure cover the range of scales excluded from our analysis (described in Section \ref{ssec:methods.constr}).
+The semi-transparent gray bands in the figure cover the range of scales excluded from our analysis (described in Section \ref{ssec:methods.constr}).
 Unless otherwise stated, in what follows all our results will not include any of these data.
@@
         \caption{Source number densities estimated in the 6 different fields ($x$-axis) and in the 4 different redshift bins (in each panel, from top to bottom).
-We find no evidence of inconsistency between the number of sources found in each field.}
+We find no evidence of inconsistency between the number density of sources found in each field.}
         \label{fig:ndens_consistency}
@@
 This is a feature of our HOD model enforcing that no halo can host satellites if it does not contain a central galaxy, regardless of $M_{0}(z)$ (see Eq.~\ref{eq:ng_hod}).
-Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses.
-I.e.
-the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.
+Therefore we find that the constraints on $M_{0}(z)$ are unbounded at low masses, which means that the data constrain the maximal $M_{0}(z)$ to be of the order of $M_{\mathrm{min}}(z)$, but our HOD model does not allow us to distinguish between masses smaller than $M_{\mathrm{min}}(z)$.
 Physically, this means that the data show preference for a model in which all halos massive enough to host a central galaxy are likely to host satellites too.
@@
 The uncertainties denote the $68 \%$ c.l.
-corresponding to the equal-probability values encompassing a total probability of 0.68.} \label{tab:constraints_robustness}
+corresponding to the equal-probability values encompassing a total probability of 0.68.
+In the cases in which they are not varied, the parameters $A_{\mu}, \Omega_{c}$ and $\sigma_{8}$ are fixed to $A_{\mu}=0$, $\Omega_{c}=0.264$ and $\sigma_{8} = 0.8111$.} \label{tab:constraints_robustness}
         \begin{center}
@@
       As discussed above, our fiducial constraints are derived from a joint fit to both auto- and cross-power spectra.
-However, cross-correlations between redshift bins are susceptible to photometric redshift errors, such as outliers.
+However, cross-correlations between redshift bins are especially sensitive to photometric redshift errors, such as outliers.
 In order to test for systematic biases affecting the cross-correlations, we therefore test the consistency of the auto- and cross-power spectra by comparing the constraints obtained using only auto-power spectra to those obtained when jointly fitting auto- and cross-power spectra.
@@
 Comparing to Fig.~\ref{fig:covariance-contributions}, this is probably due to the fact that these corrections only affect the lowest redshift bins at small angular scales, and therefore do not have a significant impact when computing constraints from all power spectra.
-Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$s of the data slightly increase as we remove the non-Gaussian contributions, as expected.
+Finally, from Tab.~\ref{tab:constraints_robustness} we see that the reduced $\chi^{2}$ values of the data slightly increase as we remove the non-Gaussian contributions, as expected.
 However, the differences are not significant and we find almost identical goodness of fits, even when only accounting for the Gaussian covariance.
@@
 While $\Sigma_{i=0}^{3} \Delta z_{i}$ and the width parameters $z_{w, i}$ are largely unconstrained, we find that we can constrain the three pairwise differences $\Delta z_{i} - \Delta z_{j}$ to within $\sigma_{\Delta z_{i} - \Delta z_{j}} \approx 0.023$ ($68 \%$ c.l.).
-This means that the data do not allow constraining the absolute position of each redshift bin, but are quite sensitive to their relative positions.
+This means that the data do not constrain the absolute position of each redshift bin, but are quite sensitive to their relative positions.
 
@@
 Therefore, the lowest redshift bin in particular might also be affected by photometric redshift errors.
-In order to test the robustness of our results to photometric redshift uncertainties at low and high redshifts, we compute parameter constraints separately neglecting the high- and low-redshift bin and all its cross-correlations.
+In order to test the robustness of our results to photometric redshift uncertainties at low and high redshifts, we compute parameter constraints separately neglecting the high- and low-redshift bin and all their cross-correlations.
 The results of these two analyses are shown alongside our fiducial constraints in Fig.~\ref{fig:constraints-fit-bins=0+1+2+3-vs-fit-bins=0+1+2-vs-fit-bins=1+2+3}.
@@
 the different bins are more widely separated than their fiducial distributions assume.
-Since the signal-to-noise ratio of cosmic shear measurements tends to increase towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions).
+Since the amplitude of the cosmic shear signal increases towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions).
 Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
@@
           \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
-The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$, which is consistent with the bias-redshift relation derived from the galaxy sample used in this analysis to within approximately $5 \%$.}
+The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$ and shows that $b(z)$ is consistent with $D(z)$ to within approximately $3-7 \%$.}
           \label{fig:HOD-redshift}
@@
 This sensitivity of the cross-power spectra to magnification mainly stems from the fact that the cross-correlations between widely separated bins caused by intrinsic clustering are small, which leads to an increased sensitivity to any non-intrinsic source of cross-correlation, such as magnification.
-In analogy to the results for the photo-$z$ systematics parameters, we thus find that cross-power spectra carry important information and it will thus be beneficial to include these cross-correlations in current and future photometric clustering analyses.
+In analogy to the results for the photo-$z$ systematics parameters, we thus find that cross-power spectra carry important information and it will thus be beneficial to include these cross-correlations in current and future photometric clustering analyses\footnote{We note that we do not find the constraints on $A_{\mu}$ to be strongly degenerate with photo-$z$ systematics parameters.
+In fact, the detection significance of magnification is almost unchanged if we include shift and width parameters in our analysis as opposed to only accounting for shifts.}.
 
@@
 We note that our analysis makes considerably stronger modeling assumptions and thus gives error bars that are likely under-estimated.
-In order to illustrate this, we perform an additional analysis additionally allowing for variations $n_{s}$, which, as $\Omega_{m}$, affects the shape of the matter power spectrum.
+In order to illustrate this, we perform an additional analysis additionally allowing for variations in $n_{s}$, which, like $\Omega_{m}$, affects the shape of the matter power spectrum.
 The uncertainty on $\Omega_{m}$ in this case increases significantly to $\sigma(\Omega_{m}) \sim 0.15$, thus showing the impact of our strong modeling assumptions.
@@
       \begin{aligned}
-        \alpha &= -1.30 \pm 0.19\footnotemark,\\
+        \alpha &= -1.30 \pm 0.19,\\
         \bar{b}(m_{\mathrm{lim}}) &= b_{1}(m_{\mathrm{lim}}-24) + b_{0},
@@
     \end{equation}
-    \footnotetext{We note that we use $\sigma(\tilde{x}) = 1.253 \; \sigma(\bar{x})$, where $\tilde{x}$ denotes the median and $\bar{x}$ is the mean of a given sample.}
-    where $b_{1} = -0.0624 \pm 0.0070$ and $b_{0} = 0.8346 \pm 0.161$.
+    where $b_{1} = -0.0624 \pm 0.0070$ and $b_{0} = 0.8346 \pm 0.161$\footnote{We note that to compute the uncertainty on $\alpha$, we use $\sigma(\tilde{x}) = 1.253 \; \sigma(\bar{x})$, where $\tilde{x}$ denotes the median and $\bar{x}$ is the mean of a given sample.}.
 The results from this fitting function are shown as solid lines in Fig.~\ref{fig:magnitude-cuts-bias}, alongside the values obtained from the HOD fit.
@@
 from LSST.
-In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) analysis.
+In the lower right panel of Fig.~\ref{fig:magnitude-cuts-bias}, we show a comparison between the biases derived using our fitting function to those assumed in the DESC Science Requirements Document (SRD) \cite{LSST:SRD:2018} analysis.
 As can be seen, we find these two to differ at approximately $2 \sigma$, using the uncertainties on our bias measurement.

### 2019-12-09 doc/Paper/main.tex
Added updated plots.

@@
           \includegraphics[width=0.95\textwidth]{figures/color-magnitude_cut=COSMOS30_nbin=10_weights=True.pdf}
-          \caption{Color-magnitude diagrams of COSMOS 30-band galaxies cross-matched to HSC galaxies passing our selection cuts for 10 tomographic redshift bins with $z \in [0.15, 1.5]$.}
+          \caption{Normalized color-magnitude diagrams of COSMOS 30-band galaxies cross-matched to HSC galaxies passing our selection cuts for 10 tomographic redshift bins with $z \in [0.15, 1.5]$.}
           \label{fig:color-mag}

### 2019-12-09 doc/Paper/main.tex
Changed number of sigfigs to 2 for uncertainties and results accordingly.

@@
           $\mu_{\mathrm{min}}$ & flat $\in [0., \,15.]$ & $11.88\substack{+0.22 \\ -0.23}$ & $12.02$ \\ 
-          $\mu_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.491\substack{+2.09 \\ -2.02}$ & $-1.34$ \\
-          $\mu_{0}$ & flat $\in [0., \,15.]$ & $5.72\substack{+3.95 \\ -3.97}$ & $6.60$ \\
-          $\mu_{0, p}$ & flat $\in [-5., \,10.]$ & $2.45\substack{+5.09 \\ -5.02}$ & $-1.43$ \\
+          $\mu_{\mathrm{min}, p}$ & flat $\in [-10., \,10.]$ & $-0.5\substack{+2.1 \\ -2.0}$ & $-1.3$ \\
+          $\mu_{0}$ & flat $\in [0., \,15.]$ & $5.7 \pm 4.0$ & $6.6$ \\
+          $\mu_{0, p}$ & flat $\in [-5., \,10.]$ & $2.5\substack{+5.1 \\ -5.0}$ & $-1.4$ \\
           $\mu_{1}$ & flat $\in [0., \,17.]$ & $13.08\substack{+0.27 \\ -0.28}$ & $13.27$ \\ 
-          $\mu_{1, p}$ & flat $\in [-12., \,15.]$ & $0.933\substack{+2.67 \\ -2.56}$ & $-0.323$ \\
-          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000339\substack{+0.096 \\ -0.091}$ & $-0.0642$ \\
-          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.0159\substack{+0.096 \\ -0.086}$ & $-0.0865$ \\
-          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.00588\substack{+0.105 \\ -0.094}$ & $-0.0681$ \\
-          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.0130\substack{+0.107 \\ -0.097}$ & $-0.0303$ \\
-          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.0451\substack{+0.123 \\ -0.113}$ & $-0.101$ \\
-          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $-0.00962\substack{+0.0780 \\ -0.0789}$ & $-0.0103$ \\
-          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.0346\substack{+0.0789 \\ -0.0778}$ & $0.0824$ \\
-          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.0543\substack{+0.112 \\ -0.126}$ & $0.182$ \\ \\
+          $\mu_{1, p}$ & flat $\in [-12., \,15.]$ & $0.9\substack{+2.7 \\ -2.6}$ & $-0.3$ \\
+          $\Delta z_{0}$ & flat $\in [-0.2, \,0.2]$ & $0.000\substack{+0.096 \\ -0.091}$ & $-0.064$ \\
+          $\Delta z_{1}$ & flat $\in [-0.2, \,0.2]$ & $-0.016\substack{+0.096 \\ -0.086}$ & $-0.087$ \\
+          $\Delta z_{2}$ & flat $\in [-0.2, \,0.2]$ & $-0.01\substack{+0.11 \\ -0.09}$ & $-0.07$ \\
+          $\Delta z_{3}$ & flat $\in [-0.2, \,0.2]$ & $0.01\substack{+0.11 \\ -0.10}$ & $-0.03$ \\
+          $z_{w, 0}$ & flat $\in [-0.2, \,0.2]$ & $-0.05\substack{+0.12 \\ -0.11}$ & $-0.10$ \\
+          $z_{w, 1}$ & flat $\in [-0.2, \,0.2]$ & $-0.010\substack{+0.078 \\ -0.079}$ & $-0.010$ \\
+          $z_{w, 2}$ & flat $\in [-0.2, \,0.2]$ & $0.035\substack{+0.079 \\ -0.078}$ & $0.082$ \\
+          $z_{w, 3}$ & flat $\in [-0.2, \,0.2]$ & $0.05\substack{+0.11 \\ -0.13}$ & $0.18$ \\ \\
           $A_{\mu}$ & flat $\in [-5., \,5.]$ & $ - $ & $ - $ \\
@@
             Analysis variant & $\sfrac{\chi^{2}}{\nu}$ & $\mu_{\mathrm{min}, p}$ & $\mu_{\mathrm{min}}$ & $\mu_{1, p}$ & $\mu_{1}$ & $A_{\mu}$ & $\Omega_{c}$ & $\sigma_{8}$ \\ \hline \Tstrut       
-            fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.491\substack{+2.09 \\ -2.02}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.933\substack{+2.67 \\ -2.56}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
-            auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.886\substack{2.19 \\ -2.17}$ & $11.82 \pm 0.28$ & $0.368\substack{+2.67 \\ -2.64}$ & $12.99 \pm 0.33$  & - & - & - \\
-            G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.675\substack{+2.11 \\ -2.08}$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.70\substack{+2.67 \\ -2.61}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
-            G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.433\substack{+1.96 \\ -1.90}$ & $11.89 \pm 0.20$ & $0.982\substack{+2.55 \\ -2.44}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
-            no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.855\substack{+0.648 \\ -0.653}$ & $11.87 \pm 0.11$ & $0.327\substack{+0.889 \\ -0.900}$ & $13.07 \pm 0.15$ & - & - & - \\
-            no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.624 \\ -0.771}$ & $11.78 \pm 0.13$ & $-0.108\substack{+0.727 \\ -0.940}$ & $12.93 \pm 0.16$ & - & - & - \\
-            bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.354\substack{+2.34 \\ -2.25}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.624\substack{+2.87 \\ -2.75}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
-            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.20\substack{+2.88 \\ -2.94}$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.46\substack{+3.66 \\ -3.63}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
-            pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.270\substack{+2.05 \\ -1.88}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.82\substack{+2.87 \\ -2.59}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
-            pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.895\substack{+1.97 \\ -2.03}$ & $12.15 \pm 0.17$ & $2.64\substack{+2.71 \\ -2.80}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
-            pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.616\substack{+1.90 \\ -1.88}$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.29\substack{+2.59 \\ -2.55}$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
-            pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0421\substack{+1.97 \\ -1.76}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.41\substack{+2.75 \\ -2.44}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
+            fiducial & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.5\substack{+2.1 \\ -2.0}$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.9\substack{+2.7 \\ -2.6}$ & $13.08\substack{+0.27 \\ -0.28}$ & - & - & - \\
+            auto & $\sfrac{19.2}{25}$ $(0.79)$ & $-0.9\pm 2.2$ & $11.82 \pm 0.28$ & $0.4\substack{+2.7 \\ -2.6}$ & $12.99 \pm 0.33$  & - & - & - \\
+            G cov & $\sfrac{87.2}{80}$ $(0.27)$ & $-0.7\pm 2.1$ & $11.88\substack{+0.23 \\ -0.24}$ & $0.7\substack{+2.7 \\ -2.6}$ & $13.08\substack{+0.28 \\ -0.29}$ & - & - & - \\
+            G+SSC cov & $\sfrac{86.2}{80}$ $(0.30)$ & $-0.4\substack{+2.0 \\ -1.9}$ & $11.89 \pm 0.20$ & $1.0\substack{+2.6 \\ -2.4}$ & $13.09\substack{+0.24 \\ -0.25}$ & - & - & - \\
+            no $z_{w, i}$ & $\sfrac{88.0}{84}$ $(0.36)$ & $-0.86 \pm 0.65$ & $11.87 \pm 0.11$ & $0.33\substack{+0.89 \\ -0.90}$ & $13.07 \pm 0.15$ & - & - & - \\
+            no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.62 \\ -0.77}$ & $11.78 \pm 0.13$ & $-0.11\substack{+0.73 \\ -0.94}$ & $12.93 \pm 0.16$ & - & - & - \\
+            bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.4\pm 2.3$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.6\substack{+2.9 \\ -2.8}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
+            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.2\pm 2.9$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.5\substack{+3.7 \\ -3.6}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
+            pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.3\substack{+2.1 \\ -1.9}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.8\substack{+2.9 \\ -2.6}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\
+            pz = \texttt{Ephor} & $\sfrac{107.2}{80}$ $(0.023)$ & $0.9\pm 2.0$ & $12.15 \pm 0.17$ & $2.6\substack{+2.7 \\ -2.8}$ & $13.40\substack{+0.23 \\ -0.22}$ & - & - & - \\
+            pz = \texttt{DEmP} & $\sfrac{105.4}{80}$ $(0.031)$ & $0.6\pm 1.9$ & $12.07\substack{+0.17 \\ -0.16}$ & $2.3\pm 2.6$ & $13.30\substack{+0.22 \\ -0.21}$ & - & - & - \\
+            pz = \texttt{FRANKEN-Z} & $\sfrac{90.8}{80}$ $(0.19)$ & $0.0\substack{+2.0 \\ -1.8}$ & $12.12\substack{+0.18 \\ -0.16}$ & $1.4\substack{+2.8 \\ -2.4}$ & $13.38\substack{+0.23 \\ -0.22}$ & - & - & - \\
             fiducial magn.
-& $\sfrac{72.8}{80}$ $(0.70)$ & $-0.358\substack{+2.56 \\ -2.32}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.04\substack{+3.32 \\ -2.97}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
-            fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.78\substack{+2.13 \\ -2.35}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.724\substack{+2.60 \\ -2.74}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
-            fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.844\substack{+2.29 \\ -2.17}$ & $11.81 \pm 0.26$ & $0.409\substack{+2.80 \\ -2.65}$ & $12.98 \pm 0.31$  & $0.627\substack{+2.71 \\ -2.61}$ & - & - \\
-            fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0143\substack{+2.72 \\ -2.53}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.63\substack{+3.44 \\ -3.20}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.807\substack{+0.149 \\ -0.143}$ \\
+& $\sfrac{72.8}{80}$ $(0.70)$ & $-0.4\substack{+2.6 \\ -2.3}$ & $11.94\substack{+0.21 \\ -0.22}$ & $1.0\substack{+3.3 \\ -3.0}$ & $13.16\substack{+0.26 \\ -0.27}$  & - & - & - \\
+            fit magn., auto+cross & $\sfrac{69.0}{79}$ $(0.78)$ & $-1.8\substack{+2.1 \\ -2.4}$ & $11.79\substack{+0.26 \\ -0.27}$ & $-0.7\substack{+2.6 \\ -2.7}$ & $12.98\substack{+0.30 \\ -0.31}$  & $2.18 \pm 0.74$ & - & - \\
+            fit magn., auto & $\sfrac{19.4}{24}$ $(0.73)$ & $-0.8\substack{+2.3 \\ -2.2}$ & $11.81 \pm 0.26$ & $0.4\substack{+2.8 \\ -2.7}$ & $12.98 \pm 0.31$  & $0.6\substack{+2.7 \\ -2.6}$ & - & - \\
+            fit cosmo & $\sfrac{84.4}{78}$ $(0.29)$ & $0.0\substack{+2.7 \\ -2.5}$ & $11.79\substack{+0.27 \\ -0.24}$ & $1.6\substack{+3.4 \\ -3.2}$ & $12.96\substack{+0.36 \\ -0.35}$  & - & $0.237 \pm 0.025$ & $0.81\substack{+0.15 \\ -0.14}$ \\
             \hline \hline

### 2019-12-10 doc/Paper/main.tex
comments onf fig 7

@@
 This allows us to test the worst-case scenario where any source of contamination is completely ignored.
-The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in pink in Figure \ref{fig:cls_systematics}.
-In all cases we observe very small differences (smaller than $1\sigma$) between both spectra.
+The result, shown as the differences between both power spectra normalized by their 1$\sigma$ uncertainty, is shown in pink in Figure \ref{fig:cls_systematics} (note that the different curves shown there are strongly correlated with each other).
+In all cases we observe very small differences (smaller than $\sim0.3\sigma$) between both spectra.
 This suggests that the level of contamination in the raw galaxy overdensity maps is small, and the linear model implemented through template deprojection is likely accurate enough to account for it.

### 2019-12-10 hsc_lss/map_utils.py
Added spin-2 functionality to map_utils and shear calibration script for HSC.

@@ -1,4 +1,8 @@
 import numpy as np
+import copy
+import logging
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
 
 def createCountsMap(ra, dec, flatSkyGrid):
     """
@@ -10,6 +14,57 @@ def createCountsMap(ra, dec, flatSkyGrid):
     flatmap= flatSkyGrid.pos2pix(ra, dec)
     mp= np.bincount(flatmap, weights= None, minlength= flatSkyGrid.get_size())
     
+    return mp
+
+def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
+    """
+    Creates two maps containing the averages (optionally weighted) of the Q, U components of a
+    spin-2 field.
+    :param ra:
+    :param dec:
+    :param q:
+    :param u:
+    :param flatSkyGrid:
+    :param weights:
+    :param shearrot:
+    :return:
+    """
+
+    flatmap = flatSkyGrid.pos2pix(ra, dec)
+
+    if weights is not None:
+        q = weights*copy.deepcopy(q)
+        u = weights*copy.deepcopy(u)
+
+    qmap = np.bincount(flatmap, weights=q, minlength=flatSkyGrid.get_size())
+    umap = np.bincount(flatmap, weights=u, minlength=flatSkyGrid.get_size())
+    weightsmap = np.bincount(flatmap, weights=weights, minlength=flatSkyGrid.get_size())
+
+    qmap[weightsmap != 0] /= weightsmap[weightsmap != 0]
+    umap[weightsmap != 0] /= weightsmap[weightsmap != 0]
+
+    if shearrot is None:
+        logger.info('shearrot is None. Not applying shear transformation.')
+
+    else:
+
+        if shearrot == 'flipqu':
+            logger.info('shearrot is {}. Applying shear transformation.'.format(shearrot))
+            qmap *= (-1.)
+            umap *= (-1.)
+        elif shearrot == 'flipq':
+            logger.info('shearrot is {}. Applying shear transformation.'.format(shearrot))
+            qmap *= (-1.)
+        elif shearrot == 'flipu':
+            logger.info('shearrot is {}. Applying shear transformation.'.format(shearrot))
+            umap *= (-1.)
+        elif shearrot == 'noflip':
+            logger.info('shearrot is {}. Applying shear transformation.'.format(shearrot))
+        else:
[…]

### 2019-12-10 hsc_lss/shear_calib.py

@@ -1,0 +1,129 @@
+import numpy as np
+
+import copy
+from astropy.table import Table, vstack
+from astropy.io import fits
+from ceci import PipelineStage
+from .types import FitsFile, ASCIIFile
+
+import logging
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+class ShearCalib(PipelineStage):
+
+    name="ReduceCat"
+    inputs=[('raw_data', None)]
+    outputs=[('calib_catalog', FitsFile),('R', ASCIIFile),('mhat',ASCIIFile)]
+    # config_options={'min_snr':10.,'depth_cut':24.5,'res':0.0285,
+    #                 'res_bo':0.003,'pad':0.1,'band':'i','depth_method':'fluxerr',
+    #                 'flat_project':'CAR','mask_type':'sirius'}
+
+    def _responsivity(self, cat):
+        """
+        Compute shear responsivity.
+        For HSC (see Mandelbaum et al., 2018, arXiv:1705.06745):
+        R = 1 - < e_rms^2 >w (Eq. (A1) in Mandelbaum et al., 2018)
+        :param cat:
+        :return:
+        """
+
+        R = 1. - np.average(cat['ishape_hsm_regauss_derived_rms_e']**2, weights=cat['ishape_hsm_regauss_derived_shape_weight'])
+
+        return R
+
+    def _mhat(self, cat):
+        """
+        Compute multiplicative bias.
+        For HSC (see Mandelbaum et al., 2018, arXiv:1705.06745):
+        mhat = < m >w (Eq. (A2) in Mandelbaum et al., 2018)
+        :param cat:
+        :return:
+        """
+
+        mhat = np.average(cat['ishape_hsm_regauss_derived_shear_bias_m'], weights=cat['ishape_hsm_regauss_derived_shape_weight'])
+
+        return mhat
+
+    def calibrated_catalog(self, cat, R=None, mhat=None):
+        """
+        Calibrate shear catalog and add calibrated shear columns to existing catalog.
+        For HSC (see Mandelbaum et al., 2018, arXiv:1705.06745):
+        gi = 1/(1 + mhat)[ei/(2R) - ci] (Eq. (A6) in Mandelbaum et al., 2018)
+        R = 1 - < e_rms^2 >w (Eq. (A1) in Mandelbaum et al., 2018)
+        mhat = < m >w (Eq. (A2) in Mandelbaum et al., 2018)
+        :param cat:
+        :param R:
+        :param mhat:
+        :return:
[…]

### 2019-12-11 hsc_lss/reduce_shear_cat.py
Shear catalog reduction.

@@ -12,12 +12,10 @@ logger = logging.getLogger(__name__)
 
 class ShearCalib(PipelineStage):
 
-    name="ReduceCat"
-    inputs=[('raw_data', None)]
-    outputs=[('calib_catalog', FitsFile),('R', ASCIIFile),('mhat',ASCIIFile)]
-    # config_options={'min_snr':10.,'depth_cut':24.5,'res':0.0285,
-    #                 'res_bo':0.003,'pad':0.1,'band':'i','depth_method':'fluxerr',
-    #                 'flat_project':'CAR','mask_type':'sirius'}
+    name = "ReduceCat"
+    inputs = [('raw_data', None)]
+    outputs = [('calib_catalog', FitsFile),('R', ASCIIFile),('mhat',ASCIIFile)]
+    config_options = {'photoz_method': 'ephor_ab_photoz_best', 'photoz_min':0.3, 'photoz_max': 1.5}
 
     def _responsivity(self, cat):
         """
@@ -85,10 +83,29 @@ class ShearCalib(PipelineStage):
 
         return cat_calib, e1_corr, e2_corr
 
+    def pz_cut(self, cat):
+        """
+        Apply pz cut to catalog.
+        :param cat:
+        :return:
+        """
+
+        logger.info('Applying pz cut to catalog. Using {} with zmin = {}, zmax = {}.'.\
+                    format(self.config['photoz_method'], self.config['photoz_min'], self.config['photoz_max']))
+
+        photozmask = (cat[self.config['photoz_method']]>=self.config['photoz_min'])\
+                     &(cat[self.config['photoz_method']]<self.config['photoz_max'])
+
+        cat = copy.deepcopy(cat)
+        cat = cat[photozmask]
+
+        return cat
+
     def run(self) :
         """
         Main function.
         This stage:
+        - Reduces shear catalog.
         - Computes responsivity and multiplicative bias.
         - Computes calibrated shear components g1, g2 and writes calibrated catalog.
         """
@@ -106,6 +123,8 @@ class ShearCalib(PipelineStage):
                 cat = vstack([cat, c], join_type='exact')
 
         logger.info('Initial catalog size: {}.'.format(len(cat)))
+        cat = self.pz_cut(cat)
+        logger.info('Catalog size after pz cut: {}.'.format(len(cat)))
 
         cat_calib, R, mhat = self.calibrated_catalog(cat)
 

### 2019-12-11 hsc_lss/map_utils.py
Further mapping.

@@ -16,7 +16,7 @@ def createCountsMap(ra, dec, flatSkyGrid):
     
     return mp
 
-def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
+def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None, weightmask=True):
     """
     Creates two maps containing the averages (optionally weighted) of the Q, U components of a
     spin-2 field.
@@ -43,11 +43,18 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
     qmap[weightsmap != 0] /= weightsmap[weightsmap != 0]
     umap[weightsmap != 0] /= weightsmap[weightsmap != 0]
 
+    if weightmask:
+        logger.info('Computing weightmask.')
+        mask = weightsmap
+    else:
+        logger.info('Computing binary mask.')
+        mask = weightsmap != 0.
+        mask = mask.astype('int')
+
     if shearrot is None:
         logger.info('shearrot is None. Not applying shear transformation.')
 
     else:
-
         if shearrot == 'flipqu':
             logger.info('shearrot is {}. Applying shear transformation.'.format(shearrot))
             qmap *= (-1.)
@@ -65,7 +72,7 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
 
     mp = [qmap, umap]
 
-    return mp
+    return mp, mask
 
 def createMeanStdMaps(ra, dec, quantity, flatSkyGrid) :
     """

### 2019-12-11 hsc_lss/reduce_shear_cat.py

@@ -10,9 +10,9 @@ import logging
 logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
-class ShearCalib(PipelineStage):
+class ReduceShearCat(PipelineStage):
 
-    name = "ReduceCat"
+    name = "ReduceShearCat"
     inputs = [('raw_data', None)]
     outputs = [('calib_catalog', FitsFile),('R', ASCIIFile),('mhat',ASCIIFile)]
     config_options = {'photoz_method': 'ephor_ab_photoz_best', 'photoz_min':0.3, 'photoz_max': 1.5}

### 2019-12-11 hsc_lss/shear_cat_mapper.py

@@ -1,0 +1,115 @@
+from ceci import PipelineStage
+from .types import FitsFile,ASCIIFile
+import numpy as np
+from .flatmaps import read_flat_map
+from .map_utils import createSpin2Map
+from astropy.io import fits
+
+import logging
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+class ShearCatMapper(PipelineStage) :
+    name="ShearCatMapper"
+    inputs=[('clean_catalog', FitsFile), ('masked_fraction', FitsFile)]
+    outputs=[('gamma_maps', FitsFile)]
+    config_options={'pz_code':'ephor_ab', 'pz_mark':'best',
+                    'pz_bins':[0.15,0.50,0.75,1.00,1.50], 'nz_bin_num':200,
+                    'nz_bin_max':3.0, 'shearrot': 'flipuq'}
+    
+    def get_gamma_maps(self, cat):
+        """
+        Get gamma1, gamma2 maps and corresponding mask from catalog.
+        :param cat:
+        :return:
+        """
+
+        if not 'ishape_hsm_regauss_e1_calib' in cat.dtype.names:
+            raise RuntimeError('get_gamma_maps must be called with calibrated shear catalog. Aborting.')
+        maps = []
+
+        for zi, zf in zip(self.zi_arr, self.zf_arr) :
+            msk_bin = (cat[self.column_mark]<=zf) & (cat[self.column_mark]>zi)
+            subcat = cat[msk_bin]
+            gammamaps, gammamask = createSpin2Map(subcat['ra'], subcat['dec'], subcat['ishape_hsm_regauss_e1_calib'], \
+                                     subcat['ishape_hsm_regauss_e2_calib'], self.fsk, \
+                                     weights=subcat['ishape_hsm_regauss_derived_shape_weight'], \
+                                     shearrot=self.config['shearrot'])
+            maps_combined = [gammamaps, gammamask]
+            maps.append(maps_combined)
+
+        return maps
+
+    def parse_input(self):
+        """
+        Check config parameters for consistency
+        """
+        #Parse input params
+        if self.config['pz_code']=='ephor_ab' :
+            self.pz_code='eab'
+        elif self.config['pz_code']=='frankenz' :
+            self.pz_code='frz'
+        elif self.config['pz_code']=='nnpz' :
+            self.pz_code='nnz'
+        else :
+            raise KeyError("Photo-z method "+self.config['pz_code']+
[…]

### 2019-12-15 doc/Paper/main.tex
Added and updated acknowledgments.

@@
 \author[f]{Adam Broussard,}
+\author[a,g]{Jo Dunkley,}
 \author[b]{Zahra Gomes,}
 \author[f]{Eric Gawiser,}
-\author[g]{Rachel Mandelbaum,}
-\author[h,i,j,k]{Hironao Miyatake,}
-\author[l]{Jeffrey A. Newman,}
-\author[m]{Ignacio Sevilla,}
-\author[e,n]{Sarah Skinner,}
-\author[o]{Erica Wagoner}
+\author[h]{Rachel Mandelbaum,}
+\author[i,j,k,l]{Hironao Miyatake,}
+\author[m]{Jeffrey A. Newman,}
+\author[n]{Ignacio Sevilla,}
+\author[e,o]{Sarah Skinner,}
+\author[p]{Erica Wagoner}
+
+\author{\\(The LSST Dark Energy Science Collaboration)}
 
@@
 \affiliation[f]{Rutgers University, Physics \& Astronomy Department, Piscataway, NJ 08854, USA}
-\affiliation[g]{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
-\affiliation[h]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
-\affiliation[i]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
-\affiliation[j]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
-\affiliation[k]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
-\affiliation[l]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
-\affiliation[m]{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
-\affiliation[n]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
-\affiliation[o]{Department of Physics, University of Arizona, Tucson, AZ, 85721, USA}
+\affiliation[g]{Department of Physics, Princeton University, Princeton, New Jersey 08544, USA}
+\affiliation[h]{McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\affiliation[i]{Institute for Advanced Research, Nagoya University, Nagoya 464-8601, Japan}
+\affiliation[j]{Division of Physics and Astrophysical Science, Graduate School of Science, Nagoya University, Nagoya 464-8602, Japan}
+\affiliation[k]{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), UTIAS, The University of Tokyo, Chiba 277- 8583, Japan}
+\affiliation[l]{Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}
+\affiliation[m]{Department of Physics and Astronomy and PITT PACC, University of Pittsburgh, Pittsburgh, PA, 15260, USA}
+\affiliation[n]{Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain}
+\affiliation[o]{Department of Physics, Missouri University of Science and Technology, Rolla, MO 65401, USA}
+\affiliation[p]{Department of Physics, University of Arizona, Tucson, AZ, 85721, USA}
 
@@
 \acknowledgments
+This paper has undergone internal review in the LSST Dark Energy Science Collaboration. 
+We would like to thank the internal reviewers Elisabeth Krause, Jonathan Loveday, Thomas McClintock and Masahiro Takada for their comments, which helped improve this paper.
+We would also like to thank David Spergel for numerous helpful discussions and suggestions.
+
   DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
-  AN would like to thank Jo Dunkley and David Spergel for numerous helpful discussions and suggestions. AN further acknowledges support from National Science Foundation Grant No. 1814971.
-  HA, BA and EG have been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020).
+AN acknowledges support from National Science Foundation Grant No. 1814971.
+HA has been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020); HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant No.
+1829740, the Brinson Foundation, and the Moore Foundation, as participation in the program has benefited this work.
 HA, AB, and EG were supported by the Department of Energy (grants DE-SC0011636 and DE-SC0010008).
-  HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant \#1829740, the Brinson Foundation, and the Moore Foundation, as participation in the program has benefited this work.
   ZG is supported by a Rhodes Scholarship granted by the Rhodes Trust.
@@
 Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
+
+The DESC acknowledges ongoing support from the Institut National de Physique Nucl\'eaire et de Physique des Particules in France; the Science \& Technology Facilities Council in the United Kingdom; and the Department of Energy, the National Science Foundation, and the LSST Corporation in the United States.
+DESC uses resources of the IN2P3 Computing Center (CC-IN2P3--Lyon/Villeurbanne - France) funded by the Centre National de la Recherche Scientifique; the National Energy Research Scientific Computing Center, a DOE Office of Science User Facility supported by the Office of Science of the U.S.\ Department of Energy under Contract No.\ DE-AC02-05CH11231; STFC DiRAC HPC Facilities, funded by UK BIS National E-infrastructure capital grants; and the UK particle physics grid, supported by the GridPP Collaboration.
+This work was performed in part under DOE Contract DE-AC02-76SF00515.
 

### 2019-12-16 doc/Paper/main.tex
contributions

@@
   DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
-AN acknowledges support from National Science Foundation Grant No. 1814971.
   HA has been supported by the Rutgers Discovery Informatics Institute Fellowship of Excellence in Computational and Data Science (AY 2017-2020) and Rutgers University \& Bevier Dissertation Completion Fellowship (AY 2019-2020); HA also thanks the LSSTC Data Science Fellowship Program, which is funded by LSSTC, NSF Cybertraining Grant No.
@@
   JAN us supported by grant DOE DE-SC0007914 from the U.S. Department of Energy Office of Science (Office of High Energy Physics).
+  AN acknowledges support from National Science Foundation Grant No. 1814971.
   This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
@@
 Department of Energy, Office of Science, Office of Workforce Development for Teachers and Scientists (WDTS) under the Science Undergraduate Laboratory Internships Program (SULI).
+
+  The contributions from the authors are listed below:
+  AN: co-led project, led signal modeling, photo-$z$ systematics characterization, likelihood analysis and interpretation of results.
+  DA: co-led project, led development of the data analysis pipeline, contributed to likelihood and modelling efforts.
+  JS: development of data analysis pipeline, comparisons with simulated data, checked impact of observing conditions (systematics).
+  AS: co-led project, advised student, cross checked MCMC chains, calculated $N(z)$ sample variance uncertainty, contributed to modelling efforts, wrote initial likelihood code.
+  HA: carried out initial data exploration, analyzed HSC photo-$z$ pdfs, and determined tomographic bin selection.
+  AB: shot noise estimation, small updates to HSC pipeline.
+  JD: provided advice and guidance.
+  ZG: calibrated redshift distributions from COSMOS 30-band data.
+  EG: galaxy sample selection and shot noise estimation.
+  RM: provided guidance on how to use the HSC data.
+  HM: provided guidance on how to use the HSC data.
+  JN: assistance in interpretation of galaxy clustering results.
+  SS: model parametrization, testing MCMC chains, studied uncertainties in the first bin's $N(z)$.
+  EW: produced observing condition maps.
 

### 2019-12-16 doc/Paper/main.tex
Added acknowledgments for Jo.
Started to incorporate comments from Eric.

@@
 We used the {\tt photoz\_best} redshift estimator for the photo-$z$ code {\tt Ephor\_AB} to assign galaxies to different bins.
-The second column shows the mean redshift of each bin calculated from the fiducial redshift distributions described in Section \ref{ssec:methods.nz}.
+The third column shows the mean redshift of each bin calculated from the fiducial redshift distributions described in Section \ref{ssec:methods.nz}.
 The last column shows the number of galaxies in each bin.
@@
 The redshift distributions for the four different redshift bins listed in Table \ref{tab:bins_summary} are shown in different colors.
-Note that all four redshift estimation codes use the same COSMOS 30-band catalog so the level of visual agreement should not be taken as realistic measure of uncertainty on the redshift distributions.}
+Note that all four redshift estimation codes use the same COSMOS 30-band catalog so the level of visual agreement might not provide a realistic measure of uncertainty on the redshift distributions.}
       \label{fig:nzs}
@@
         \caption{Source number densities estimated in the 6 different fields ($x$-axis) and in the 4 different redshift bins (in each panel, from top to bottom).
-We find no evidence of inconsistency between the number density of sources found in each field.}
+We find no significant evidence of inconsistency between the number density of sources found in each field.}
         \label{fig:ndens_consistency}
@@
 The pair of numbers in the upper left corner of each panel corresponds to the indices of the bins being cross-correlated.
-We find no inconsistency between the different measurements.}
+We find consistency between the different measurements.}
         \label{fig:cls_consistency}
@@
   \subsection{Covariance matrix}\label{ssec:results.covariance}
-    We compute the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}.
+    We compute the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix\footnote{The correlation matrix $\mathsf{Corr}$ is obtained from the covariance matrix $\mathsf{C}$ as $\mathsf{Corr}_{ij} = \sfrac{\mathsf{C}_{ij}}{\sqrt{\mathsf{C}_{ii} \mathsf{C}_{jj}}}$.} is shown in Fig.~\ref{fig:covmat}.
 In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions.
@@
           \includegraphics[width=0.95\textwidth]{figures/contours-Mmin-M1_mPk=HOD_fix=alpha-fc-sigmaM_HOD=zevol_fit=pz-shifts-pz-widths+prior=0p2_fit=auto+cross_cosmo=const_HOD-param=zfid_clfit=HOD-zevol_cov=G+NG+SSC-vs-fit=auto-vs-cov=G-vs-cov=G+SSC.pdf}
-          \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto-power spectra alone, accounting only for Gaussian and Gaussian and SSC contributions to the covariance matrix.
+          \caption{Comparison of our fiducial constraints on HOD parameters to those obtained from auto-power spectra alone, accounting only for Gaussian or Gaussian and SSC contributions to the covariance matrix.
 The inner (outer) contour shows the $68 \%$ c.l.
@@
   JAN us supported by grant DOE DE-SC0007914 from the U.S. Department of Energy Office of Science (Office of High Energy Physics).
-  AN acknowledges support from National Science Foundation Grant No. 1814971.
+  JD and AN acknowledge support from National Science Foundation Grant No. 1814971.
   This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.

### 2019-12-17 hsc_lss/__init__.py
added shear reduce and map to init

@@ -1,8 +1,10 @@
 from ceci import PipelineStage
 from .reduce_cat import ReduceCat
+from .reduce_shear_cat import ReduceShearCat
 from .syst_mapper import SystMapper
 from .pdf_match import PDFMatch
 from .cosmos_weight import COSMOSWeight
 from .cat_mapper import CatMapper
+from .shear_cat_mapper import ShearCatMapper
 from .map_diagnoser import MapDiagnoser
 from .power_specter import PowerSpecter

### 2019-12-17 plot_scripts/plots_galmap_nice.py
lsst_uk plot

@@ -1,0 +1,55 @@
+import numpy as np
+import flatmaps as fm
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from astropy.io import fits
+
+
+_,mp1=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=0)
+_,mp2=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=2)
+_,mp3=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=4)
+_,mp4=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=6)
+fsk,msk=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/masked_fraction.fits")
+msk[msk<0.001]=0
+msk[msk>=0.001]=1
+#fig=plt.figure(figsize=(20,fsk.ny*20./fsk.nx))
+#ax=fig.add_subplot(111,projection=fsk.wcs)
+#im=ax.imshow(msk.reshape([fsk.ny,fsk.nx]),vmin=0,vmax=1,
+#             cmap=cm.binary, origin='lower', interpolation='nearest')
+cmap=cm.jet
+cmap.set_bad(color='#AAAAAA')
+
+from scipy.ndimage import gaussian_filter
+fig=plt.figure(figsize=(20,4*fsk.ny*20./fsk.nx))
+plt.subplots_adjust(hspace=0)
+for i,mp in enumerate([mp1,mp2,mp3,mp4]):
+    ax=fig.add_subplot(4,1,i+1,projection=fsk.wcs)
+    mean=np.sum(mp*msk)/np.sum(msk)
+    delta=msk*(mp-mean)/mean
+    delta=gaussian_filter(delta.reshape([fsk.ny,fsk.nx]),sigma=1).flatten()
+    delta[msk<1]=np.nan
+    im=ax.imshow(delta.reshape([fsk.ny,fsk.nx]),vmin=-1,vmax=4.5,
+                 cmap=cmap, origin='lower', interpolation='nearest')
[…]

### 2019-12-18 plot_scripts/plots_galmap_nice.py
lsst_uk plot

@@ -1,27 +1,48 @@
+import pyccl as ccl
 import numpy as np
 import flatmaps as fm
 import matplotlib.pyplot as plt
 from matplotlib import cm
 from astropy.io import fits
+import matplotlib
 
+matplotlib.rcParams['font.family'] = 'serif'
+matplotlib.rcParams['xtick.major.size'] = 7
+matplotlib.rcParams['xtick.minor.size'] = 4
+matplotlib.rcParams['xtick.major.pad'] = 6
+matplotlib.rcParams['xtick.minor.pad'] = 6
+matplotlib.rcParams['xtick.labelsize'] = 32
+matplotlib.rcParams['xtick.minor.width'] = 1.6
+matplotlib.rcParams['xtick.major.width'] = 1.6
+matplotlib.rcParams['ytick.major.size'] = 7
+matplotlib.rcParams['ytick.minor.size'] = 4
+matplotlib.rcParams['ytick.major.pad'] = 6
+matplotlib.rcParams['ytick.minor.pad'] = 6
+matplotlib.rcParams['ytick.labelsize'] = 32
+matplotlib.rcParams['ytick.minor.width'] = 1.6
+matplotlib.rcParams['ytick.major.width'] = 1.6
 
-_,mp1=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=0)
-_,mp2=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=2)
-_,mp3=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=4)
-_,mp4=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/ngal_maps.fits",i_map=6)
-fsk,msk=fm.read_flat_map("/global/cscratch1/sd/damonge/HSC_ceci/WIDE_XMMLSS_sirius_i24p5_out/masked_fraction.fits")
+times=np.array([5.705970149253732,
+                6.402985074626866,
+                7.629850746268656,
+                8.938805970149254])
[…]

### 2020-01-14 hsc_lss/flatmaps.py
Updates to shear mapping and added shear tracers.

@@ -420,14 +420,20 @@ def read_flat_map(filename,i_map=0,hdu=None) :
             ny,nx=maps.shape
             maps=maps.flatten()
     else :
-        w=WCS(hdu.header)
-        maps=hdu.data
-        ny,nx=maps.shape
-        maps=maps.flatten()
+        if isinstance(hdu, list):
+            w = WCS(hdu[0].header)
+            maps = np.array([h.data for h in hdu])
+            nm, ny, nx = maps.shape
+            maps = maps.reshape([nm, ny*nx])
+        else:
+            w = WCS(hdu.header)
+            maps = hdu.data
+            ny, nx = maps.shape
+            maps = maps.flatten()
 
-    fmi=FlatMapInfo(w,nx=nx,ny=ny)
+    fmi = FlatMapInfo(w, nx=nx, ny=ny)
 
-    return fmi,maps
+    return fmi, maps
 
 def compare_infos(fsk1,fsk2) :
     """Checks whether two FlatMapInfo objects are compatible"""

### 2020-01-14 hsc_lss/map_utils.py

@@ -16,7 +16,7 @@ def createCountsMap(ra, dec, flatSkyGrid):
     
     return mp
 
-def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None, weightmask=True):
+def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
     """
     Creates two maps containing the averages (optionally weighted) of the Q, U components of a
     spin-2 field.
@@ -43,13 +43,19 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None, weig
     qmap[weightsmap != 0] /= weightsmap[weightsmap != 0]
     umap[weightsmap != 0] /= weightsmap[weightsmap != 0]
 
-    if weightmask:
+    if weights is not None:
+        logger.info('Weights provided.')
         logger.info('Computing weightmask.')
-        mask = weightsmap
-    else:
+        weightmask = weightsmap
         logger.info('Computing binary mask.')
         mask = weightsmap != 0.
         mask = mask.astype('int')
+    else:
+        logger.info('No weights provided.')
+        logger.info('Computing binary mask.')
+        mask = weightsmap != 0.
+        mask = mask.astype('int')
+        weightmask = copy.deepcopy(mask)
 
     if shearrot is None:
         logger.info('shearrot is None. Not applying shear transformation.')
@@ -71,8 +77,9 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None, weig
             logger.error('Accepted values of shearrot = [noflip, flipq, flipu, flipqu].')
 
     mp = [qmap, umap]
+    ms = [weightmask, mask]
 
-    return mp, mask
+    return mp, ms
 
 def createMeanStdMaps(ra, dec, quantity, flatSkyGrid) :
     """

### 2020-01-14 hsc_lss/shear_cat_mapper.py

@@ -31,11 +31,11 @@ class ShearCatMapper(PipelineStage) :
         for zi, zf in zip(self.zi_arr, self.zf_arr) :
             msk_bin = (cat[self.column_mark]<=zf) & (cat[self.column_mark]>zi)
             subcat = cat[msk_bin]
-            gammamaps, gammamask = createSpin2Map(subcat['ra'], subcat['dec'], subcat['ishape_hsm_regauss_e1_calib'], \
+            gammamaps, gammamasks = createSpin2Map(subcat['ra'], subcat['dec'], subcat['ishape_hsm_regauss_e1_calib'], \
                                      subcat['ishape_hsm_regauss_e2_calib'], self.fsk, \
                                      weights=subcat['ishape_hsm_regauss_derived_shape_weight'], \
                                      shearrot=self.config['shearrot'])
-            maps_combined = [gammamaps, gammamask]
+            maps_combined = [gammamaps, gammamasks]
             maps.append(maps_combined)
 
         return maps
@@ -91,8 +91,11 @@ class ShearCatMapper(PipelineStage) :
                 hdu = fits.ImageHDU(data=m_list[0][1].reshape([self.fsk.ny,self.fsk.nx]), header=head)
                 hdus.append(hdu)
                 head = header.copy()
-                head['DESCR'] = ('gamma mask, bin %d'%(im+1), 'Description')
-                hdu = fits.ImageHDU(data=m_list[1].reshape([self.fsk.ny,self.fsk.nx]), header=head)
+                head['DESCR'] = ('gamma weight mask, bin %d'%(im+1), 'Description')
+                hdu = fits.ImageHDU(data=m_list[1][0].reshape([self.fsk.ny,self.fsk.nx]), header=head)
+                hdus.append(hdu)
+                head['DESCR'] = ('gamma binary mask, bin %d'%(im+1), 'Description')
+                hdu = fits.ImageHDU(data=m_list[1][1].reshape([self.fsk.ny,self.fsk.nx]), header=head)
                 hdus.append(hdu)
             else:
                 head = header.copy()
@@ -104,8 +107,11 @@ class ShearCatMapper(PipelineStage) :
                 hdu = fits.ImageHDU(data=m_list[0][1].reshape([self.fsk.ny,self.fsk.nx]), header=head)
                 hdus.append(hdu)
                 head = header.copy()
[…]

### 2020-01-14 hsc_lss/tracer.py

@@ -2,8 +2,12 @@ import pymaster as nmt
 import numpy as np
 from .flatmaps import compare_infos, read_flat_map
 
+import logging
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
 class Tracer(object) :
-    def __init__(self,hdu_list,i_bin,fsk,mask_binary,masked_fraction,contaminants=None) :
+    def __init__(self, hdu_list, i_bin, fsk, mask_binary, masked_fraction, contaminants=None, is_shear=False, weightmask=True) :
         """
         Class used to define the information stored in each of the number density maps generated by CatMapper, which are then transformed into overdensity maps.
         :param hdu_list: list of FITS HDUs containing the number density maps.
@@ -15,42 +19,81 @@ class Tracer(object) :
         
         This class then stores a number of data objects, the most important one being a pymaster `NmtFieldFlat` ready to use in power spectrum estimation.
         """
-        #Read numbers map
-        self.fsk,nmap=read_flat_map(None,hdu=hdu_list[2*i_bin])
-        compare_infos(fsk,self.fsk)
 
-        #Read N(z)
-        self.nz_data=hdu_list[2*i_bin+1].data.copy()
+        if not is_shear:
+            logger.info('Creating tracer object for number density.')
+            #Read numbers map
+            self.fsk,nmap=read_flat_map(None,hdu=hdu_list[2*i_bin])
+            compare_infos(fsk,self.fsk)
 
-        #Make sure other maps are compatible
-        if not self.fsk.is_map_compatible(mask_binary) :
-            raise ValueError("Mask size is incompatible")
-        if not self.fsk.is_map_compatible(masked_fraction) :
-            raise ValueError("Mask size is incompatible")
-        if contaminants is not None :
-            for ic,c in enumerate(contaminants) :
-                if not self.fsk.is_map_compatible(c) :
-                    raise ValueError("%d-th contaminant template is incompatible"%ic)
-          
-        #Translate into delta map
-        self.masked_fraction=masked_fraction
-        self.weight=masked_fraction*mask_binary
-        goodpix=np.where(mask_binary>0.1)[0]
-        self.goodpix=goodpix
-        self.mask_binary=mask_binary
-        self.Ngal = np.sum(nmap*mask_binary)
-        ndens=np.sum(nmap*mask_binary)/np.sum(self.weight)
-        self.ndens_perad=ndens/(np.radians(self.fsk.dx)*np.radians(self.fsk.dy))
[…]

### 2020-01-16 doc/Paper/main.tex

@@
           \caption{Redshift dependence of the mean halo mass $\bar{M}_{\mathrm{halo}}$ and the large-scale galaxy bias $b_{\mathrm{HOD}}$ as derived from our best-fit HOD model.
-The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$ and shows that $b(z)$ is consistent with $D(z)$ to within approximately $3-7 \%$.}
+The third panel illustrates the empirical scaling $b(z) \propto \sfrac{1}{D(z)}$ and shows that $b(z)$ is consistent with $\sfrac{1}{D(z)}$ to within approximately $3-7 \%$.}
           \label{fig:HOD-redshift}
@@
 \section{Discussion and Conclusions}\label{sec:discussion}
-  In this work, we have presented a comprehensive analysis of photometric galaxy clustering in HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$.
+  In this work, we have presented a comprehensive analysis of photometric galaxy clustering in the public HSC-SSP DR1 data using a magnitude-limited sample with $i<24.5$.
 We have split this sample into four tomographic redshift bins and computed all possible auto- and cross-power spectra, accounting for observational systematics in the number density fluctuations through map-level deprojection.
@@
 In order to test the stability of our results, we performed a suite of alternative analyses, finding our results to be robust to photometric redshift uncertainties.
-We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from our data alone.
+We extended our analysis to include the effects of lensing magnification, which results in a $\sim 3 \sigma$ detection of magnification from these data alone.
 In addition to this, we also allowed for variations in $\Omega_{c}$ and $\sigma_{8}$, finding that, within our strong model priors, the data are able to constrain $\Omega_{c}$, while $\sigma_{8}$ remains unconstrained.
-Finally, we used our data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting $i$-band magnitude (Eq.
+Finally, we used these data to derive a simple fitting function for the linear, large-scale galaxy bias of magnitude-limited samples as a function of redshift and limiting $i$-band magnitude (Eq.
 \ref{eq:bias-fit-func-result}).
@@
 \cite{1507.05460,1807.10163}).
-Using magnitude-limited samples on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias and larger systematic projection effects.
+Using magnitude-limited samples, on the other hand, results in larger galaxy samples with smaller shot noise and therefore improved total statistical sensitivity of the survey, despite their less pronounced clustering amplitude due to lower galaxy bias and larger systematics deprojection effects.
 In addition we find that the cross-correlations between redshift bins carry important information, as they drive the constraints on both parameters accounting for photometric redshift uncertainties as well as lensing magnification.
@@
 Our analysis demonstrates the feasibility of photometric galaxy clustering studies using such high signal-to-noise datasets.
-In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering, and the use of template deprojection techniques to handle contamination from sky systematics.
+In particular, this work shows the level of readiness of the LSST DESC analysis pipelines, and showcases the application of power spectrum methods for galaxy clustering and the use of template deprojection techniques to handle contamination from sky systematics.
 We anticipate that future development of this pipeline will include improvements to photo-$z$ marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.

### 2020-01-17 hsc_lss/map_utils.py
Cosmic shear power spectrum and changed to new sacc.

@@ -39,6 +39,7 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
     qmap = np.bincount(flatmap, weights=q, minlength=flatSkyGrid.get_size())
     umap = np.bincount(flatmap, weights=u, minlength=flatSkyGrid.get_size())
     weightsmap = np.bincount(flatmap, weights=weights, minlength=flatSkyGrid.get_size())
+    nmap = np.bincount(flatmap, weights=None, minlength=flatSkyGrid.get_size())
 
     qmap[weightsmap != 0] /= weightsmap[weightsmap != 0]
     umap[weightsmap != 0] /= weightsmap[weightsmap != 0]
@@ -77,7 +78,7 @@ def createSpin2Map(ra, dec, q, u, flatSkyGrid, weights=None, shearrot=None):
             logger.error('Accepted values of shearrot = [noflip, flipq, flipu, flipqu].')
 
     mp = [qmap, umap]
-    ms = [weightmask, mask]
+    ms = [weightmask, mask, nmap]
 
     return mp, ms
 

### 2020-01-17 hsc_lss/power_specter.py

@@ -9,9 +9,17 @@ import os
 import sacc
 from scipy.interpolate import interp1d
 
+import logging
+logging.basicConfig(level=logging.INFO)
+logger = logging.getLogger(__name__)
+
+#TODO: Covariance MCM precompute all cwsps with counts
+#TODO: Put counts in same framework
+#TODO: COSMOS nz for shear weights
+
 class PowerSpecter(PipelineStage) :
     name="PowerSpecter"
-    inputs=[('masked_fraction',FitsFile),('ngal_maps',FitsFile),
+    inputs=[('masked_fraction',FitsFile),('ngal_maps',FitsFile),('shear_maps',FitsFile)
             ('dust_map',FitsFile),('star_map',FitsFile),('depth_map',FitsFile),
             ('ccdtemp_maps',FitsFile),('airmass_maps',FitsFile),('exptime_maps',FitsFile),
             ('skylevel_maps',FitsFile),('sigma_sky_maps',FitsFile),('seeing_maps',FitsFile),
@@ -56,28 +64,97 @@ class PowerSpecter(PipelineStage) :
         """
         Get window functions for each bandpower so they can be stored into the final SACC files.
         """
-        #Compute window functions
-        nbands=wsp.wsp.bin.n_bands
-        l_arr=np.arange(self.lmax+1)
-        if not os.path.isfile(self.get_output_fname('windows_l',ext='npz')) :
-            print("Computing window functions")
-            windows=np.zeros([nbands,self.lmax+1])
-            t_hat=np.zeros(self.lmax+1);
-            for il,l in enumerate(l_arr) :
-                t_hat[il]=1.;
-                windows[:,il]=wsp.decouple_cell(wsp.couple_cell(l_arr,[t_hat]))
-                t_hat[il]=0.;
-            np.savez(self.get_output_fname('windows_l'),windows=windows)
-        else :
-            print("Reading window functions")
-            windows=np.load(self.get_output_fname('windows_l',ext='npz'))['windows']
 
-        windows_sacc=[]
-        #i_x=0
-        for i in range(self.nbins) :
-            for j in range(i,self.nbins) :
-                for b in range(nbands) :
-                    windows_sacc.append(sacc.Window(l_arr,windows[b]))
+        # Compute window functions
+        if self.nshear_maps == 0:
+            print("Computing window functions for counts and shear.")
+            nbands=wsp.wsp.bin.n_bands
+            l_arr=np.arange(self.lmax+1)
[…]

### 2020-01-17 hsc_lss/shear_cat_mapper.py

@@ -40,6 +40,30 @@ class ShearCatMapper(PipelineStage) :
 
         return maps
 
+    def get_e2rms(self, cat):
+        """
+        Get e1_2rms, e2_2rms from catalog.
+        :param cat:
+        :return:
+        """
+
+        if not 'ishape_hsm_regauss_e1_calib' in cat.dtype.names:
+            raise RuntimeError('get_e2rms must be called with calibrated shear catalog. Aborting.')
+        e2rms_arr = []
+
+        for zi, zf in zip(self.zi_arr, self.zf_arr) :
+            msk_bin = (cat[self.column_mark]<=zf) & (cat[self.column_mark]>zi)
+            subcat = cat[msk_bin]
+            e1_2rms = np.average(subcat['ishape_hsm_regauss_e1_calib']**2,
+                                 weights=subcat['ishape_hsm_regauss_derived_shape_weight'])
+            e2_2rms = np.average(subcat['ishape_hsm_regauss_e2_calib'] ** 2,
+                                 weights=subcat['ishape_hsm_regauss_derived_shape_weight'])
+
+            e2rms_combined = np.array([e1_2rms, e2_2rms])
+            e2rms_arr.append(e2rms_combined)
+
+        return e2rms_arr
+
     def parse_input(self):
         """
         Check config parameters for consistency
@@ -76,6 +100,9 @@ class ShearCatMapper(PipelineStage) :
         logger.info("Creating shear maps and corresponding masks.")
         gammamaps = self.get_gamma_maps(cat)
 
+        logger.info("Computing e2rms.")
+        e2rms = self.get_e2rms(cat)
+
         print("Writing output to {}.".format(self.get_output('gamma_maps')))
         header = self.fsk.wcs.to_header()
         hdus = []
@@ -84,35 +111,45 @@ class ShearCatMapper(PipelineStage) :
             if im == 0 :
                 head = header.copy()
                 head['DESCR'] = ('gamma1, bin %d'%(im+1), 'Description')
-                hdu = fits.PrimaryHDU(data=m_list[0][0].reshape([self.fsk.ny,self.fsk.nx]), header=head)
+                hdu = fits.PrimaryHDU(data=m_list[im][0][0].reshape([self.fsk.ny,self.fsk.nx]), header=head)
                 hdus.append(hdu)
                 head = header.copy()
[…]

### 2020-01-17 hsc_lss/tracer.py

@@ -65,10 +65,13 @@ class Tracer(object) :
         else:
             logger.info('Creating tracer object for shear.')
             # Read shear map
-            self.fsk, gammamaps = read_flat_map(None, hdu=[hdu_list[4*i_bin], hdu_list[4*i_bin+1]])
+            self.fsk, gammamaps = read_flat_map(None, hdu=[hdu_list[6*i_bin], hdu_list[6*i_bin+1]])
             compare_infos(fsk, self.fsk)
 
-            _, masks = read_flat_map(None, hdu=[hdu_list[4*i_bin+2], hdu_list[4*i_bin+3]])
+            _, masks = read_flat_map(None, hdu=[hdu_list[6*i_bin+2], hdu_list[6*i_bin+3], hdu_list[6*i_bin+4]])
+
+            #Read N(z)
+            self.nz_data=hdu_list[2*i_bin+1].data.copy()
 
             # Make sure other maps are compatible
             if not self.fsk.is_map_compatible(masks[0]) :
@@ -80,20 +83,31 @@ class Tracer(object) :
                     if not self.fsk.is_map_compatible(c) :
                         raise ValueError("%d-th contaminant template is incompatible."%ic)
 
-            if weightmask:
-                logger.info('Using weight mask.')
-                self.weight = masks[0]
-            else:
-                logger.info('Using binary mask.')
-                self.weight = masks[1]
+            self.weight = masks[0]
+            mask_binary = masks[1]
+            nmap = masks[2]
 
             # Reshape contaminants
             conts = None
             if contaminants is not None:
                 conts = [[c.reshape([self.fsk.ny, self.fsk.nx])] for c in contaminants]
 
+            ndens = np.sum(nmap * mask_binary) / np.sum(weights)
+            self.ndens_perad = ndens / (np.radians(self.fsk.dx) * np.radians(self.fsk.dy))
+            self.e1_2rms_pix = np.average(gammamaps[0]**2, weights=weights)
+            self.e2_2rms_pix = np.average(gammamaps[1] ** 2, weights=weights)
+            self.e1_2rms_cat, self.e2_2rms_cat = hdu_list[6*i_bin+5].data.copy()
+
             # Form NaMaster field
-            self.field = nmt.NmtFieldFlat(np.radians(self.fsk.lx), np.radians(self.fsk.ly),
-                        self.weight.reshape([self.fsk.ny,self.fsk.nx]),
[…]

### 2020-01-19 hsc_lss/power_specter.py
Further clean-up in power specter module.

@@ -13,8 +13,7 @@ import logging
 logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
-#TODO: Covariance MCM precompute all cwsps with counts
-#TODO: Put counts in same framework
+#TODO: Names of files to read
 #TODO: COSMOS nz for shear weights
 
 class PowerSpecter(PipelineStage) :
@@ -60,103 +59,71 @@ class PowerSpecter(PipelineStage) :
 
         return temp
 
-    def get_sacc_windows(self,wsp) :
+    def get_windows(self,wsp) :
         """
         Get window functions for each bandpower so they can be stored into the final SACC files.
         """
 
         # Compute window functions
-        if self.nshear_maps == 0:
-            print("Computing window functions for counts and shear.")
-            nbands=wsp.wsp.bin.n_bands
-            l_arr=np.arange(self.lmax+1)
-            if not os.path.isfile(self.get_output_fname('windows_l',ext='npz')) :
-                print("Computing window functions")
-                windows=np.zeros([nbands,self.lmax+1])
-                t_hat=np.zeros(self.lmax+1);
-                for il,l in enumerate(l_arr) :
-                    t_hat[il]=1.;
-                    windows[:,il]=wsp.decouple_cell(wsp.couple_cell(l_arr,[t_hat]))
-                    t_hat[il]=0.;
-                np.savez(self.get_output_fname('windows_l'),windows=windows)
-            else :
-                print("Reading window functions")
-                windows=np.load(self.get_output_fname('windows_l',ext='npz'))['windows']
+        print("Computing window functions.")
+        nbands = wsp[0, 0].wsp.bin.n_bands
+        l_arr = np.arange(self.lmax + 1)
 
-            windows_sacc=[]
-            #i_x=0
-            for i in range(self.nbins) :
-                for j in range(i,self.nbins) :
-                    for b in range(nbands) :
-                        windows_sacc.append(sacc.Window(l_arr,windows[b]))
+        windows_list = [[0 for i in range(self.ntracers)] for ii in range(self.ntracers)]
+
+        if not os.path.isfile(self.get_output_fname('windows_l', ext='npz')[0]):
+            print("Computing window functions for counts.")
+            windows_counts = np.zeros([nbands, self.lmax + 1])
+            t_hat = np.zeros(self.lmax + 1)
+            for il, l in enumerate(l_arr):
[…]

### 2020-01-19 hsc_lss/shear_cat_mapper.py
Added pz estimation to shear cat mapper.

@@ -3,13 +3,14 @@ from .types import FitsFile,ASCIIFile
 import numpy as np
 from .flatmaps import read_flat_map
 from .map_utils import createSpin2Map
+from .cat_mapper import CatMapper
 from astropy.io import fits
 
 import logging
 logging.basicConfig(level=logging.INFO)
 logger = logging.getLogger(__name__)
 
-class ShearCatMapper(PipelineStage) :
+class ShearCatMapper(PipelineStage, CatMapper) :
     name="ShearCatMapper"
     inputs=[('clean_catalog', FitsFile), ('masked_fraction', FitsFile)]
     outputs=[('gamma_maps', FitsFile)]
@@ -64,25 +65,36 @@ class ShearCatMapper(PipelineStage) :
 
         return e2rms_arr
 
-    def parse_input(self):
+    def get_nz_stack(self, cat, codename):
         """
-        Check config parameters for consistency
+        Get N(z) from pdf stacks.
+        :param cat: object catalog
+        :param codename: photoz code name (demp, ephor, ephor_ab, frankenz or nnpz).
         """
-        #Parse input params
-        if self.config['pz_code']=='ephor_ab' :
-            self.pz_code='eab'
-        elif self.config['pz_code']=='frankenz' :
-            self.pz_code='frz'
-        elif self.config['pz_code']=='nnpz' :
-            self.pz_code='nnz'
-        else :
-            raise KeyError("Photo-z method "+self.config['pz_code']+
-                           " unavailable. Choose ephor_ab, frankenz or nnpz")
+        logger.info("Creating pdf stacks for cosmic shear.")
 
-        if self.config['pz_mark']  not in ['best','mean','mode','mc'] :
-            raise KeyError("Photo-z mark "+self.config['pz_mark']+
-                           " unavailable. Choose between best, mean, mode and mc")
-        self.column_mark='pz_'+self.config['pz_mark']+'_'+self.pz_code
+        from scipy.interpolate import interp1d
+
+        f = fits.open(self.pdf_files[codename])
+        p = f[1].data['pdf']
+        z = f[2].data['bins']
+
+        z_all = np.linspace(0., self.config['nz_bin_max'], self.config['nz_bin_num'] + 1)
+        z0 = z_all[:-1]
+        z1 = z_all[1:]
+        zm = 0.5 * (z0 + z1)
+        pzs = []
[…]

### 2020-01-29 doc/Paper/main.tex
Fixed names, alphabetical order and added Fermilab pub.
Started addressing referee report. All changes in bold.

--- 2019-12-16 doc/Paper/main.tex
@@
 \newcommand{\da}[1]{{\textcolor{red}{[DA: #1]}}}
+\newcommand{\rev}[1]{{\textbf{#1}}}
 
@@
 \bibliographystyle{JHEP}
+
+\usepackage{eso-pic}% http://ctan.org/pkg/eso-pic
+\AddToShipoutPictureBG*{%
+  \AtPageUpperLeft{%
+    \hspace{0.75\paperwidth}%
+    \raisebox{-3.5\baselineskip}{%
+      \makebox[0pt][l]{\textnormal{FERMILAB-PUB-19-626-AE}}
+}}}%
+
 \title{Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release}
@@
 \author[a,g]{Jo Dunkley,}
+\author[f]{Eric Gawiser,}
 \author[b]{Zahra Gomes,}
-\author[f]{Eric Gawiser,}
 \author[h]{Rachel Mandelbaum,}
@@
 \author[e,o]{Sarah Skinner,}
-\author[p]{Erica Wagoner}
+\author[p]{Erika L. Wagoner}
 
@@
 This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs).
-Since we use a cilindrical projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes, which are small ($\lesssim 1.5^\circ$) in all cases.
+Since we use a \rev{cylindrical} projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes.
+\rev{As all fields considered in this analysis span a rather narrow latitude range, the maximal latitudes probed after re-centering are small ($\lesssim 1.5^\circ$), and we can therefore neglect curved-sky effects.}
 
@@
 As part of our analysis of systematic biases (see Section \ref{sssec:results.spectra.syst}), we also study the effect of masking regions with significant contamination from the different observing conditions (described in Section \ref{ssec:methods.syst}) on our measurements.
-In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies ($\sim10\%$).
+In addition it has been observed that the NOMAD star catalog \cite{2004AAS...205.4815Z}, which is one of the datasets used to construct the bright-object mask described above, is contaminated by a small fraction of bright nearby galaxies (\rev{as described in Ref.~\cite{2018PASJ...70S..25M}, approximately $10\%$ of the objects in the NOMAD star catalog are galaxies}).
 To study the impact of this contamination on our clustering measurements, we therefore also estimate the angular power spectra using a more recent version of the star mask (the so-called ``Arcturus'' mask described in \cite{2018PASJ...70S...7C}).
@@
     \end{equation}
-    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$, and $C^{ab}_\ell$ is the true power spectrum.
+    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed (masked), \rev{physical} fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$\footnote{\rev{Examples include the galaxy overdensity field or the CMB temperature anisotropies.}}, and $C^{ab}_\ell$ is the true power spectrum.
 As explicitly written above, the mode-coupling matrix depends exclusively on the properties of the survey masks \citep{2002ApJ...567....2H}, and not on the underlying signal maps.
@@
 In this work, we model the halo mass function $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ following \cite{Tinker:2010}\footnote{More accurate estimates of the mass function can be obtained through the use of emulators \citep{2019ApJ...872...53M}.
-We verified that our analysis was not too sensitive to the choice of parameterization, and therefore we leave a more thorough study of these choices for future work.}.
+\rev{In order to test the sensitivity of our analysis to details of mass function parametrization, we have compared the constraints obtained using the mass functions from Refs.~\cite{Tinker:2010} and \cite{Tinker:2008}.
+We found our results to not change significantly and we therefore leave a more thorough study of these choices for future work.}}.
 Furthermore, we employ the concentration-mass relation $c(M)$ (which depends on the choice of $\Delta$) derived by \cite{Duffy:2008}.

### 2020-01-30 doc/Paper/main.tex
Addressed a few additional comments.

@@
 In order to directly characterize properties of dark energy and modified gravity, we need to measure the expansion history and growth  \cite{1903.12016}.
-At the moment, this is only possible with optical large scale structure surveys.
+\rev{Optical large scale structure surveys constitute a powerful probe of both these effects.}
 
@@
 Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$.
-Finally, we model the distribution of satellites to follow that of the dark matter, and therefore $u_s$ is a Navarro-Frenk-White profile, given by \cite{Navarro:1996}:
+Finally, we model the distribution of satellites to follow that of the dark matter, \rev{which we assume to be given by a Navarro-Frenk-White profile \cite{Navarro:1996}:}
     \begin{equation}
@@
 
-We note that the priors assumed on the photo-$z$ parameters (shifts and widths), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$.
+We note that the priors assumed on the photo-$z$ parameters (\rev{flat, top-hat priors of $[-0.2, 0.2]$ on both shifts and widths, see Tab.~\ref{tab:params}}), are significantly broader than those used in the HSC cosmic shear analysis \cite{2019PASJ...71...43H}, where the prior on the shift parameters is of the order of $0.01-0.04$.
 This prior was estimated as the scatter between the best-fit shift parameters that recover the same shear power spectrum for different estimates of the redshift distribution and different photo-$z$ codes.
@@
         \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
-        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, computed analytically as described in Sec.~\ref{sssec:methods.theory.covar}.}\label{fig:covmat}
+        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, computed analytically as described in Sec.~\ref{sssec:methods.theory.covar}.
+\rev{The indices denote redshift bins, e.g.
+the sub-covariance matrix with indices 00-00 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{00}_{\ell'})$, 00-01 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{01}_{\ell'})$ etc.}}\label{fig:covmat}
       \end{center}
@@
 However, we will use it throughout this work, as it allows us to obtain a rough estimate of the goodness of fit of the different models considered in our analysis.}.
-In Fig.~\ref{fig:cls-best-fit-1h-2h}, we additionally show our fiducial theoretical power spectra split into their 1- and 2-halo contributions.
-As can be seen, the contribution of the 1-halo term to the total power spectrum is most pronounced at low redshift.
+\rev{In order to illustrate the different contributions to our fiducial theoretical power spectra, we additionally show them split into the 1- and 2-halo terms in Fig.~\ref{fig:cls-best-fit-1h-2h}.} As can be seen, the contribution of the 1-halo term to the total power spectrum is most pronounced at low redshift.
 At higher redshift, the importance of the 1-halo term decreases and the transition from the 1- to 2-halo-dominated regime moves to smaller angular scales.
+\rev{This further illustrates that our constraints are significantly driven by the lowest tomographic redshift bin, as it allows us to probe the 1-halo regime most effectively.}
 
@@
       We also investigate the impact of a secondary mode in the redshift distribution of the first tomographic bin.
-This secondary peak contains $\sim$5\% of all galaxies and peaks at around $z\sim 3$ (and hence cannot be seen in Fig.~\ref{fig:nzs}).
+This secondary peak contains $\sim$5\% of the galaxies \rev{belonging to the first redshift bin} and peaks at around $z\sim 3$ (and hence cannot be seen in Fig.~\ref{fig:nzs}).
 To investigate the impact of this mode, we manually excise it from the redshift distribution and calculate the resulting change in $\chi^2$, finding it to be $\Delta \chi^2\sim 0.05$.
@@
 We note that our analysis makes considerably stronger modeling assumptions and thus gives error bars that are likely under-estimated.
-In order to illustrate this, we perform an additional analysis additionally allowing for variations in $n_{s}$, which, like $\Omega_{m}$, affects the shape of the matter power spectrum.
-The uncertainty on $\Omega_{m}$ in this case increases significantly to $\sigma(\Omega_{m}) \sim 0.15$, thus showing the impact of our strong modeling assumptions.
+In order to illustrate this, we perform an additional analysis, \rev{in which we allow for variations in $n_{s}$ within a flat prior $n_{s} \in [0.1, 1.9]$.
+Similarly to $\Omega_{m}$, the scalar spectral index $n_{s}$ affects the shape of the matter power spectrum.} The uncertainty on $\Omega_{m}$ in this case increases significantly to $\sigma(\Omega_{m}) \sim 0.15$, thus showing the impact of our strong modeling assumptions.
 

### 2020-01-30 doc/Paper/main.tex
Fixed Nachos surname.
Fixed Eq. 3.9.

@@
 \author[m]{Jeffrey A. Newman,}
-\author[n]{Ignacio Sevilla,}
+\author[n]{Ignacio Sevilla-Noarbe,}
 \author[e,o]{Sarah Skinner,}
@@
     \begin{align}
-      & P_{gg,{\rm 1h}}(k)=\frac{1}{\bar{n}_g^2} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} \bar{N}_c\,\left[\bar{N}_s^2u_s^2(k)+2\bar{N}_su_s^2(k)\right],\\
+      & P_{gg,{\rm 1h}}(k)=\frac{1}{\bar{n}_g^2} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} \bar{N}_c\,\left[\bar{N}_s^2u_s^2(k)+2\bar{N}_su_s(k)\right],\\
       & P_{gg,{\rm 2h}}(k)=\left(\frac{1}{\bar{n}_g} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\,b_h(M)\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right]\right)^2\,P_{\rm lin}(k).

### 2020-01-30 doc/Paper/main.tex
Addressed photoz comment.

@@
     Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses.
-To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
-In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
+\rev{In this work, we choose to model photo-$z$ errors as causing shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies\footnote{We note our photo-$z$ error model does not take into account the effect of catastrophic outliers but we do test for the presence of this systematic in Sec.~\ref{sec:photoz}.}.
+This allows us to parametrize the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by}
     \begin{equation}
@@
 
-    \subsubsection{Robustness to photometric redshift uncertainties}
+    \subsubsection{Robustness to photometric redshift uncertainties}\label{sec:photoz}
       One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.

### 2020-01-30 doc/Paper/main.tex
more comments

--- 2020-01-30 doc/Paper/main.tex
@@
 The image quality is impressive with a median $i$-band seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST.
-The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
+DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST \rev{($\sim0.8$ arcsec).
+The larger PSF implies that problems such as blending will be more relevant for LSST.} The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
 
@@
 This mask has a pixel size of 0.6 arcmin.
-The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
+\rev{The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) implies that empty pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather represent completely unobserved pixels.}
       \item We upgrade the low-resolution binary mask to a higher resolution ($0.2$ arcmin), and remove all pixels containing objects flagged by the bright object mask.
@@
 Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence.
-Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
+\rev{The model we use to marginalize over residual photo-$z$ uncertainties is described in Section \ref{sssec:methods.theory.photoz_syst}.} Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
 
@@
 In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass.
-Details about HOD parameterizations can be found in \cite{2011ApJ...736...59Z}.
-In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
+\rev{This parametrization allows us to not only model the galaxy distribution on the small, non-linear scales explored here, but also to extract valuable information about the galaxy-dark matter connection.}
+
+    Details about HOD parameterizations can be found in \cite{2011ApJ...736...59Z}. In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
     \begin{equation}
@@
 Furthermore, we assume that $N_c$ follows a Bernoulli distribution with probability $p=\bar{N}_c$, and that the number of satellites is Poisson-distributed with mean $\bar{N}_s$.
-Finally, we model the distribution of satellites to follow that of the dark matter, \rev{which we assume to be given by a Navarro-Frenk-White profile \cite{Navarro:1996}:}
+Finally, we model the distribution of satellites to follow that of the dark matter, \rev{which we assume to be given by a truncated Navarro-Frenk-White profile \cite{Navarro:1996}:}
     \begin{equation}
@@
     Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses.
-To lowest order, errors in photo-$z$'s cause shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
+\rev{In a simplified scenario,} errors in photo-$z$'s \rev{can} cause shifts in the mean and width of the derived redshift distribution for a population of galaxies.
 In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
@@
 The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.
+\rev{It is worth noting that we do not expect for this parametrization to fully capture the complications of realistic catastrophic outliers, and we quantify its ability to account for the underlying photo-$z$ uncertainty given our statistical errors in Section \ref{sssec:results.pz}.}
 
@@
     where $J_1(x)$ is the cylindrical Bessel function of order 1.
-    Finally, the quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
+\rev{It is worth noting that the impact of the SSC on the covariance matrix for galaxy clustering is reduced due to the integral constraint, and therefore this approximation does not affect our results significantly (see also Sections \ref{ssec:results.covariance} and \ref{sssec:results.choices}).}
+    The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
 \cite{Krause:2017}):
@@
 The data are shown in burgundy, while the solid black line shows the best-fit linear relation between both quantities.
-In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here).
+In cases where a linear relation is not appropriate (as shown here for $r$-band airmass), we mask all regions where the associated contaminant is above/below a given threshold (shown as a vertical dashed line here)\rev{, and use the same deprojection method used in the fiducial case on this smaller area}.
 {\sl Right panels:} the top panel shows our fiducial ``Sirius'' mask, with the additionally masked regions associated with high levels of contamination shown in turquoise.
@@
 
-    \subsubsection{Robustness to modeling and data choices}
+    \subsubsection{Robustness to modeling and data choices}\label{sssec:results.choices}
       In order to test the robustness of our fiducial HOD constraints to implementation and data choices, we compare the constraints from several analysis variants as follows.
@@
 
-    \subsubsection{Robustness to photometric redshift uncertainties}
+    \subsubsection{Robustness to photometric redshift uncertainties}\label{sssec:results.pz}
       One of the most important potential systematics in photometric galaxy clustering analyses are photometric redshift uncertainties and we therefore test the stability of our results to photo-$z$s in several different ways, as described in detail below.
@@
 We anticipate that future development of this pipeline will include improvements to photo-$z$ marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.
-These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.
+\rev{In particular, the increased statistical power of LSST will require not only a more rigorous marginalization over photo-$z$ uncertainties, but also a calibration sample significantly larger than the COSMOS 30-band catalog use here in order to reduce the associated sample variance.} These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.
 

### 2020-01-31 doc/Paper/main.tex
Fixed redshift bin numbering.

--- 2020-01-30 doc/Paper/main.tex
@@
     \end{equation}
-    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
+    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set\footnote{\rev{We expect this approximation to be acceptable for the present analysis as HSC covers a small sky fraction and we mainly consider large angular multipoles (see e.g.
+Refs.~\cite{Krause:2017a, Barreira:2018}).}}:
     \begin{equation}
@@
 \rev{The indices denote redshift bins, e.g.
-the sub-covariance matrix with indices 00-00 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{00}_{\ell'})$, 00-01 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{01}_{\ell'})$ etc.}}\label{fig:covmat}
+the sub-covariance matrix with indices 11-11 denotes $\mathrm{Cov}(C^{11}_{\ell}, C^{11}_{\ell'})$, 11-12 denotes $\mathrm{Cov}(C^{11}_{\ell}, C^{12}_{\ell'})$ etc.}}\label{fig:covmat}
       \end{center}
@@
         \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}
-        \caption{$C_{\ell}^{00}$}
+        \caption{$C_{\ell}^{11}$}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf} \\
-        \caption{$C_{\ell}^{11}$}
+        \caption{$C_{\ell}^{22}$}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}
-        \caption{$C_{\ell}^{22}$}
+        \caption{$C_{\ell}^{33}$}
         \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}
-        \caption{$C_{\ell}^{33}$}
+        \caption{$C_{\ell}^{44}$}
         \end{subfigure}
@@
             no $z_{w, i}, \Delta z_{i}$ & $\sfrac{95.2}{88}$ $(0.28)$ & $-1.09\substack{+0.62 \\ -0.77}$ & $11.78 \pm 0.13$ & $-0.11\substack{+0.73 \\ -0.94}$ & $12.93 \pm 0.16$ & - & - & - \\
-            bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.4\pm 2.3$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.6\substack{+2.9 \\ -2.8}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
-            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.2\pm 2.9$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.5\substack{+3.7 \\ -3.6}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
+            bins = 1, 2, 3 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.4\pm 2.3$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.6\substack{+2.9 \\ -2.8}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
+            bins = 2, 3, 4 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.2\pm 2.9$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.5\substack{+3.7 \\ -3.6}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
             pz = \texttt{Ephor\_AB} & $\sfrac{93.6}{80}$ $(0.14)$ & $0.3\substack{+2.1 \\ -1.9}$ & $12.14\substack{+0.19 \\ -0.17}$ & $1.8\substack{+2.9 \\ -2.6}$ & $13.39\substack{+0.24 \\ -0.23}$ & - & - & - \\

### 2020-01-31 doc/Paper/main.tex

--- 2020-01-30 doc/Paper/main.tex
@@
     Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses.
-\rev{In a simplified scenario,} errors in photo-$z$'s \rev{can} cause shifts in the mean and width of the derived redshift distribution for a population of galaxies.
-In this work, we therefore choose to parametrize the impact of photo-$z$ errors on the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by
+\rev{In this work, we choose to model photo-$z$ errors as causing shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies\footnote{We note our photo-$z$ error model does not take into account the full effect of catastrophic outliers but we do test for the presence of this systematic in Sec.~\ref{sssec:results.pz}.}.
+This allows us to parametrize the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by}
     \begin{equation}

### 2020-01-31 doc/Paper/main.tex
Small changes.

@@
     Uncertainties in photometric redshifts represent one of the major systematic uncertainties in photometric galaxy clustering analyses.
-\rev{In this work, we choose to model photo-$z$ errors as causing shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies\footnote{We note our photo-$z$ error model does not take into account the full effect of catastrophic outliers but we do test for the presence of this systematic in Sec.~\ref{sssec:results.pz}.}.
+\rev{In this work, we choose to model photo-$z$ errors as causing shifts in the means and changes in the width of the derived redshift distribution for a population of galaxies.
 This allows us to parametrize the derived galaxy redshift distributions $p_{i}(z)$ using a two-parameter model given by}
@@
     where $J_1(x)$ is the cylindrical Bessel function of order 1.
-\rev{It is worth noting that the impact of the SSC on the covariance matrix for galaxy clustering is reduced due to the integral constraint, and therefore this approximation does not affect our results significantly (see also Sections \ref{ssec:results.covariance} and \ref{sssec:results.choices}).}
+\rev{It is worth noting that the impact of the SSC on the covariance matrix for galaxy clustering is reduced due to the integral constraint (c.f.
+Eq.~\ref{eq:ps-resp}), and therefore this approximation does not affect our results significantly (see also Sections \ref{ssec:results.covariance} and \ref{sssec:results.choices}).}
     The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
@@
         \begin{subfigure}{0.49\textwidth}
-        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf} \\
+        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf}
         \caption{$C_{\ell}^{22}$}
-        \end{subfigure}
+        \end{subfigure}\\
         \begin{subfigure}{0.49\textwidth}
@@
 We anticipate that future development of this pipeline will include improvements to photo-$z$ marginalization and non-linear bias modeling, thus permitting its application to magnitude-limited galaxy samples with even higher signal-to-noise.
-\rev{In particular, the increased statistical power of LSST will require not only a more rigorous marginalization over photo-$z$ uncertainties, but also a calibration sample significantly larger than the COSMOS 30-band catalog use here in order to reduce the associated sample variance.} These results therefore bode well for future cosmological constraints using galaxy clustering data from LSST.
+\rev{In particular, the increased statistical power of LSST will require not only a more rigorous marginalization over photo-$z$ uncertainties, but also a calibration sample significantly larger than the COSMOS 30-band catalog used here in order to reduce the associated sample variance.
+The results presented in this analysis} bode well for future cosmological constraints using galaxy clustering data from LSST.
 
@@
   AN: co-led project, led signal modeling, photo-$z$ systematics characterization, likelihood analysis and interpretation of results.
-  DA: co-led project, led development of the data analysis pipeline, contributed to likelihood and modelling efforts.
+  DA: co-led project, led development of the data analysis pipeline, contributed to likelihood and modeling efforts.
   JS: development of data analysis pipeline, comparisons with simulated data, checked impact of observing conditions (systematics).
-  AS: co-led project, advised student, cross checked MCMC chains, calculated $N(z)$ sample variance uncertainty, contributed to modelling efforts, wrote initial likelihood code.
+  AS: co-led project, advised student, cross checked MCMC chains, calculated $N(z)$ sample variance uncertainty, contributed to modeling efforts, wrote initial likelihood code.
   HA: carried out initial data exploration, analyzed HSC photo-$z$ pdfs, and determined tomographic bin selection.

### 2020-02-01 doc/Paper/main.tex
Spell check.

@@
 
-      The resulting power spectrum measurements are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data).
+      The resulting power spectrum measurements \rev{for the four overlapping redshift bins illustrated in Fig.~\ref{fig:nzs}}, are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data).
 In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a gray solid line in the auto-correlations.
@@
 Since the amplitude of the cosmic shear signal increases towards higher redshifts, a weak lensing analysis based on the fiducial redshift distributions inferred from the COSMOS 30-band catalog that does not account for these shifts would overestimate the amplitude of density perturbations $\sigma_8$ in order to match the comparatively high weak lensing signal (see \cite{2019arXiv190609262J} for a similar discussion with regards to COSMOS-based redshift distributions).
-Although the data analysed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
+Although the data analyzed here are not yet sensitive enough to provide conclusive evidence of these types of systematics, larger samples will be able to provide useful insight on the presence of photometric redshift systematics.
       \begin{figure}
@@
 
-  In a simplified model, let us assume that galaxies can be separated into discrete types labelled by an index $\alpha$.
+  In a simplified model, let us assume that galaxies can be separated into discrete types labeled by an index $\alpha$.
 If we want to compute the value of a given quantity $Q$ in a pixel $p$ by averaging over all galaxies in that pixel, the result is:

### 2020-02-01 doc/Paper/main.tex
Final changes.

@@
 The image quality is impressive with a median $i$-band seeing of around 0.6 arcsec, which is considerably better than other comparable surveys (e.g.
-DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST \rev{($\sim0.8$ arcsec).
-The larger PSF implies that problems such as blending will be more relevant for LSST.} The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
+DES with around 0.9 arcsec in the $riz$-bands) and also likely better than the median seeing expected to be achieved by LSST \rev{($\sim0.8$ arcsec).} The data are processed with \texttt{hscPipe} \cite{2018PASJ...70S...5B} and are available to the community through a public database.
 
@@
 At our magnitude limit, the normalized median absolute deviation of the COSMOS 30-band photometric redshifts is $\sigma\simeq0.03$ \cite{2016ApJS..224...24L}.
-Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence.
-\rev{The model we use to marginalize over residual photo-$z$ uncertainties is described in Section \ref{sssec:methods.theory.photoz_syst}.} Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
+Second, the small area covered by COSMOS may lead to sample variance uncertainties in the inferred redshift distributions that are difficult to quantify, particularly if the color-redshift relation has an environmental dependence\footnote{\rev{We investigate the effects of sample variance in the COSMOS catalog on our results in Sec.~\ref{ssec:methods.constr}.}}.
+Finally, the photo-$z$ codes used in HSC DR1 were trained on the COSMOS 30-band data, which could lead to circularity in the estimation of the redshift distributions.
 
@@
     \end{equation}
-    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed (masked), \rev{physical} fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$\footnote{\rev{Examples include the galaxy overdensity field or the CMB temperature anisotropies.}}, and $C^{ab}_\ell$ is the true power spectrum.
+    Here, $\tilde{C}^{ab}_\ell$ is the power spectrum of two observed \rev{(masked), physical} fields $\tilde{a}=w_a\,a$ and $\tilde{b}=w_b\,b$\footnote{\rev{Examples include the galaxy overdensity field or the CMB temperature anisotropies.}}, and $C^{ab}_\ell$ is the true power spectrum.
 As explicitly written above, the mode-coupling matrix depends exclusively on the properties of the survey masks \citep{2002ApJ...567....2H}, and not on the underlying signal maps.
@@
 In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass.
-\rev{This parametrization allows us to not only model the galaxy distribution on the small, non-linear scales explored here, but also to extract valuable information about the galaxy-dark matter connection.}
+\rev{This parametrization allows us to not only model the galaxy distribution on the small, non-linear scales explored in this work, but also to extract valuable information about the galaxy-dark matter connection.}
 
@@
 The normalization of the redshift distribution $p_{i}(z)$ depends on both $\Delta z_{i}$ and $z_{w, i}$ and we do not account for it in Eq.~\ref{eq:photo-z-model} for clarity.
-\rev{It is worth noting that we do not expect for this parametrization to fully capture the complications of realistic catastrophic outliers, and we quantify its ability to account for the underlying photo-$z$ uncertainty given our statistical errors in Section \ref{sssec:results.pz}.}
+\rev{We note that we do not expect for this parametrization to fully capture the complications of realistic catastrophic outliers, and we investigate its ability to account for the underlying photo-$z$ uncertainty given our statistical errors in Section \ref{sssec:results.pz}.}
 
@@
     Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set\footnote{\rev{We expect this approximation to be acceptable for the present analysis as HSC covers a small sky fraction and we mainly consider large angular multipoles (see e.g.
-Refs.~\cite{Krause:2017a, Barreira:2018}).}}:
+Refs.~\cite{Krause:2017a, Barreira:2018}).
+Furthermore, the SSC does not significantly contribute to the total covariance in our analysis, as discussed in Sections \ref{ssec:results.covariance} and \ref{sssec:results.choices}, and this approximation therefore does not affect our results significantly.}}:
     \begin{equation}
@@
     where $J_1(x)$ is the cylindrical Bessel function of order 1. 
-\rev{It is worth noting that the impact of the SSC on the covariance matrix for galaxy clustering is reduced due to the integral constraint (c.f.
-Eq.~\ref{eq:ps-resp}), and therefore this approximation does not affect our results significantly (see also Sections \ref{ssec:results.covariance} and \ref{sssec:results.choices}).}
     The quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g.
@@
 
-      The resulting power spectrum measurements \rev{for the four overlapping redshift bins illustrated in Fig.~\ref{fig:nzs}}, are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data).
+      The resulting power spectrum measurements \rev{for the four overlapping redshift bins, illustrated in Fig.~\ref{fig:nzs}}, are shown in Figure \ref{fig:cls_summary} as dark green circles with error bars (hollow blue circles show the the absolute value of negative data).
 In all cases, we have subtracted the shot noise bias as described in Section \ref{ssec:methods.cell}, which is also shown as a gray solid line in the auto-correlations.
@@
 \rev{In particular, the increased statistical power of LSST will require not only a more rigorous marginalization over photo-$z$ uncertainties, but also a calibration sample significantly larger than the COSMOS 30-band catalog used here in order to reduce the associated sample variance.
-The results presented in this analysis} bode well for future cosmological constraints using galaxy clustering data from LSST.
+Additionally, the larger seeing expected for LSST as compared to HSC implies that systematics such as blending will be more relevant for LSST.
+The promising results presented in this analysis} bode well for future cosmological constraints using galaxy clustering data from LSST.
 

### 2020-03-29 doc/Paper/main.tex

@@
 This leads to additional gains in speed, since spherical harmonic transforms can be replaced by the far more efficient fast Fourier transforms (FFTs).
-Since we use a \rev{cylindrical} projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), the main source of curved-sky distortions occur at large latitudes.
+Since we use a \rev{cylindrical} projection with the equator at the center of each of our fields to define our flat-sky coordinates (rather than the more common gnomonic projection \citep{2002A&A...395.1077C}), curved-sky distortions are large only at high latitudes.
 \rev{As all fields considered in this analysis span a rather narrow latitude range, the maximal latitudes probed after re-centering are small ($\lesssim 1.5^\circ$), and we can therefore neglect curved-sky effects.}

### 2020-03-29 hsc_lss/cat_mapper.py
Removed pdf information for the moment.

@@ -117,23 +117,23 @@ class CatMapper(PipelineStage) :
                            " not supported. Choose arcturus or sirius")
         cat=cat[self.msk]
 
-        print("Reading pdf filenames")
-        data_syst=np.genfromtxt(self.get_input('pdf_matched'),
-                                dtype=[('pzname','|U8'),('fname','|U256')])
-        self.pdf_files={n:fn for n,fn in zip(data_syst['pzname'],data_syst['fname'])}
-        
-        print("Parsing photo-z bins")
-        self.zi_arr=self.config['pz_bins'][:-1]
-        self.zf_arr=self.config['pz_bins'][ 1:]
-        self.nbins=len(self.zi_arr)
-
-        print("Getting COSMOS N(z)s")
-        pzs_cosmos=self.get_nz_cosmos()
-
-        print("Getting pdf stacks")
-        pzs_stack={}
-        for n in self.pdf_files.keys() :
-            pzs_stack[n]=self.get_nz_stack(cat,n)
+        # print("Reading pdf filenames")
+        # data_syst=np.genfromtxt(self.get_input('pdf_matched'),
+        #                         dtype=[('pzname','|U8'),('fname','|U256')])
+        # self.pdf_files={n:fn for n,fn in zip(data_syst['pzname'],data_syst['fname'])}
+        #
+        # print("Parsing photo-z bins")
+        # self.zi_arr=self.config['pz_bins'][:-1]
+        # self.zf_arr=self.config['pz_bins'][ 1:]
+        # self.nbins=len(self.zi_arr)
+        #
+        # print("Getting COSMOS N(z)s")
+        # pzs_cosmos=self.get_nz_cosmos()
+        #
+        # print("Getting pdf stacks")
+        # pzs_stack={}
+        # for n in self.pdf_files.keys() :
+        #     pzs_stack[n]=self.get_nz_stack(cat,n)
 
         print("Getting number count maps")
         n_maps=self.get_nmaps(cat)
@@ -152,12 +152,12 @@ class CatMapper(PipelineStage) :
             hdus.append(hdu)
             
             #Nz
-            cols=[fits.Column(name='z_i',array=pzs_cosmos[im,0,:],format='E'),
-                  fits.Column(name='z_f',array=pzs_cosmos[im,1,:],format='E'),
-                  fits.Column(name='nz_cosmos',array=pzs_cosmos[im,2,:],format='E'),
[…]
